### 2019-02-15 README.Rmd
Moving to standard organization

---
title: "Assessing the Severity of Service Failures Through Social Chatter"
output: github_document
---

## Abstract

Firms employ a variety of passive listening platforms (e.g., customer comment cards, help lines, social media) that elicit a variety of complaints. Since these complaints are self-selected, it isn't obvious if complaints are widespread or genuinely indicative of systemic service failures. In other words, how can can a firm know when complaints can be ignored and when they need to addressed? This issue is related to a larger class of problems where the goal is to make inference about the size of a population from a non-random sample (e.g., the German tank problem). In this paper, we develop a model that uses a variety of observed customer complaints on Twitter to make inference about the severity of service failures.

### 2019-02-19 Code/README.Rmd
Beginning move to standard project directory organization

---
title: "Code"
output: github_document
---

## Description

Each script should do something specific (like tidyverse functions), have a descriptive name, and include number prefixes if they are meant to be run in a certain order (e.g., `01_import_data.R`, `02_clean_data.R`).

## Project Workflow

* Use RStudio projects.
* Use `here::here()` to specify files paths.
* Use tidyverse functions as much as possible.
* Try and follow the [tidyverse style guide](https://style.tidyverse.org).

### 2019-02-19 Paper/README.Rmd
Beginning move to standard project directory organization

---
title: "Paper"
output: github_document
---

## Description

The manuscript of the paper, without any PDF knits.

### 2019-02-22 Paper/README.Rmd
Moved manuscript over to the Paper/README.rmd

@@
 ---
-title: "Paper"
+title: "Counting the Cockroaches in the Walls or I Know Why the Caged Bird Tweets: Assessing the Severity of Service Failures Through Social Chatter"
 output: github_document
@@
 
-## Description
+## Abstract
 
-The manuscript of the paper, without any PDF knits.
+Firms employ a variety of passive listening platforms (e.g., customer comment cards, help lines, social media) that elicit a variety of complaints.
+Since these complaints are self-selected, it isn't obvious if complaints are widespread or genuinely indicative of systemic service failures.
+In other words, how can can a firm know when complaints can be ignored and when they need to addressed?
+This issue is related to a larger class of problems where the goal is to make inference about the size of a population from a non-random sample (e.g., the German tank problem).
+In this paper, we develop a model that uses a variety of observed customer complaints on Twitter to make inference about the severity of service failures.
+
+## Introduction
+
+It has been said that if you observe a cockroach on your floor, there are likely thousands inside the walls of your home.
+In a similar fashion, a variety of marketing studies have been conducted (by both academics and practitioners) that attempt to provide similar estimates with respect to the severity of service failures.
+For example, a standard rule of thumb is only 10\% of service failures are reported.
+Firms need information on the severity (i.e., type and reach) of service failures in order to know how and when to correct such failures.
+Our interest in this paper is to develop a model that uses readily available data from social media channels to estimate the severity of service failures.
+
+Using complaints (i.e, reports of service failures) on social media to estimate the type and reach of service failures is an opportunity and a challenge.
+The opportunity is access to a much larger, current, and inexpensive dataset compared to the traditional ways of assessing service failure severity (e.g., complaint cards and customer surveys).
+The challenge is considerable, including the non-representativeness of the complaints (i.e., not everyone uses social media and not everyone who experiences a complaint reports it) and that those using social media may be incentivized, given the public nature of the network, to exaggerate complaints.
+
+To illustrate, suppose a firm uses feedback reported on Twitter to assess service failure severity in order to simply determine their competitive position in the marketplace (e.g., the firm with the fewest complaints is the market leader).
+To do this, they simply count the number of negative tweets (i.e., complaints) for each firm for a given type of service failure.
+After accounting for differences in firm size, how accurately do these counts measure the true size of the population affected by the service failure (i.e., the reach of the service failure)?
+The counts could \emph{underestimate} the population size because not everyone that experiences a failure tweets about it.
+However, users could tweet more than once, experience multiple failures, tweet a complaint without experiencing the failure, or be influenced by network effects -- which would all lead to observed counts that \emph{overestimate} the true population size.
+We propose a model that explicitly disentangles the propensity to complain from the propensity to exaggerate complaints.
+
+## Model Specification
+
+### Classifying Complaints and Complaint Types
+
+### Estimating Population Size
+
+Service failure severity of a given type is synonymous with the \emph{size} or \emph{reach} of the service failure (i.e., the proportion of consumers experiencing the service failure).
+However, since service failure complaints are self-reported, we also need to model the probability of observing a complaint (i.e., the propensity to complain).
+This first component is analogous to models of animal abundance and occurrence in ecology (see Royle and Dorazio, 2006; Wu et al., 2015).
+Additionally, since there are incentives to complain on social media, we also need to model the probability of exaggerating complaints (i.e., the propensity to exaggerate).
+This second component represents a departure from the ecology model and will be highlighted in \textcolor{red}{red}.
+
+Let's focus on Twitter data associated with the airline industry.
+First, let's specify the baseline model without the propensity to exaggerate (i.e., the ecology model).
+Second, let's specify the alternative model that accounts for the propensity to exaggerate.
+
+% Baseline Model
+\subsection{Baseline Model}
+\begin{align}
+y_{tj} &\sim \text{Binomial}(N_j,\theta_j)\\
+N_j &\sim \text{Poisson}(\lambda_j)\\
+\lambda_j &= \text{exp}(X\psi)\\
+\theta_j &= \text{logit}(W\gamma)
+\end{align}
+\begin{itemize}\singlespacing
+\item[] $t=1,\dotsc,T$ time periods
+\item[] $j=1,\dotsc,J$ airlines
+\item[] $y_{tj}$: number of observed complaints at time $t$ for airline $j$
+\item[] $N_j$: number of service failures for airline $j$
+\item[] $\lambda_j$: $P$-vector of rate of service failures for airline $j$
+\item[] $\theta_j$: $K$-vector of complaining probabilities for airline $j$
+\item[] $X$: $J \times P$ matrix of covariates driving airline service failures
+\item[] $W$: $J \times K$ matrix of covariates driving complaining
+\end{itemize}
+
+% Alternative Model
+\subsection{Alternative Model}
+\begin{align}
+y_{tij} &\sim \text{Binomial}(N_{ij},\theta_{ij} \cdot \textcolor{red}{\gamma_{ij}})\\
+N_{ij} &\sim \text{Poisson}(\lambda_{ij})\\
+\lambda_{ij} &= \text{exp}(WA)\\
+\theta_{ij} &= \text{logit}(XB)\\
+\textcolor{red}{\gamma_{ij}} & \textcolor{red}{= \text{logit}(ZD)}
+\end{align}
+
+\noindent where
+
+\singlespacing{
+\begin{itemize}
+\item[] $t=1,\dotsc,T$ time periods
+\item[] $i=1,\dotsc,I$ service failure types
+\item[] $j=1,\dotsc,J$ airlines
+\item[] $y_{tij}$: number of observed complaints at time $t$ of type $i$ for airline $j$
+\item[] $N_{ij}$: number of service failures of type $i$ for airline $j$
+\item[] $\theta_{ij}$: probability of complaining about type $i$ for airline $j$
+\item[] \textcolor{red}{$\gamma_{ij}$: probability of exaggerating about type $i$ for airline $j$}
+\item[] $\lambda_{ij}$: rate of service failures of type $i$ for airline $j$
+\item[] $W$: $T \times I \times J \times M$ array of covariates driving airline service failures
+\item[] $X$: $T \times I \times J \times P$ array of covariates driving complaining
+\item[] \textcolor{red}{$Z$: $T \times I \times J \times Q$ array of covariates driving exaggerating}
+\end{itemize}
+}
+
+% Ecological Model Examples
+\subsection{Ecological Model Examples}
+\begin{enumerate}
+\item Royle and Dorazio (2006), Hierarchical Models of Animal Abundance and Occurrence, \textit{Journal of Agricultural, Biological, and Environmental Statistics}.
+\begin{center}
+Blackbird Population Size in Switzerland
+\end{center}
+\begin{align*}
+y_{it}|N_i,\theta_i &\sim \text{Binomial}(N_i,\theta)\\
+N_i|\lambda_i&\sim \text{Poisson}(\lambda_i)\\
+\log(\lambda_i)&=\alpha_0+\alpha_1\texttt{Forest}_i+\alpha_2\texttt{Elev}_i+\alpha_3\texttt{Elev}_i^2\\
+\theta&\sim\text{Unif}(0,1)
+\end{align*}
+
+\item Wu, Holan, Nilon, and Winkle (2015), Bayesian Binomial Mixture Models for Estimating Abundance in Ecological Monitoring Studies, \textit{Annals of Applied Statistics}.
+\begin{center}
+Bird Ecosystem in Baltimore
+\end{center}
+\begin{align*}
+y_{itk}|N_{it},\theta_{it} &\sim \text{Binomial}(N_{it},\theta_{it})\\
+N_{it}|\lambda_{it}&\sim \text{Poisson}(\lambda_{it})\\
+\log(\lambda_{it})&=\alpha_{0t}+\alpha_1\texttt{treecover}_i+\alpha_2\texttt{bachelors}_i+\alpha_3\texttt{income}_i\\
+\text{logit}(\theta_{it})&=\beta_0+\beta_1\texttt{time}_{it}+\beta_2\texttt{airtemp}_{it}+\beta_3\texttt{cloudcover}_{it}
+\end{align*}
+
+\end{enumerate}
+
+% Covariates and Data Sources
+\subsection{Possible Covariates and Data Sources}
+\begin{itemize}
+\item $W$: Why does airline $j$ result in failures of type $i$ at time $t$?
+	\begin{itemize}
+    \item[--] Airline market share ($N$ is proportional to volume counts)
+    \item[--] Late arrivals
+    \item[--] Canceled flights
+    \item[--] Boarding policy
+    \item[--] Baggage policy
+    \item[--] Wifi
+    \item[--] Holiday
+    \item[--] Weather
+    \item[--] Labor/strikes
+    \item[--] Employee satisfaction (Glassdoor)
+    \item[--] Text analysis output
+    \end{itemize}
+\item $X$: Why do individuals in time $t$ complain about failures of type $i$ for airline $j$?
+	\begin{itemize}
+    \item[--] Positive/negative press (Twitter)
+    \item[--] Customer satisfaction (survey)
+    \item[--] Brand equity (survey)
+    \item[--] Profile of social media use (Twitter)
+    \item[--] Business vs. leisure travel
+    \item[--] Proportion of customer base on Twitter (Twitter, need for scaling $N_{tij}$)
+    \end{itemize}
+\end{itemize}
+
+## Empirical Application
+
+## Results
+
+## Discussion
+
+## References
+
+\section{Possible References}
+\subsection{Word of Mouth}
+Moderators of why people share word-of-mouth (Berger, 2014)
+\begin{enumerate}
+\item Impression management (self-enhancement, identity signaling, filling conversation space)
+\item Emotion regulation (social support, venting, sense making, reducing dissonance, taking vengeance, reliving enjoyable experience)
+\item Information acquisition (seeking advice, resolving problems)
+\item Social bonding (reinforce shared views, reducing loneliness/exclusion)
+\item Persuasion
+\end{enumerate}

### 2019-02-22 README.Rmd
Added reference to ra-training
Moved manuscript over to the Paper/README.rmd

@@
 ---
-title: "Assessing the Severity of Service Failures Through Social Chatter"
+title: "Assessing the Severity of Service Failures"
 output: github_document
@@
 In this paper, we develop a model that uses a variety of observed customer complaints on Twitter to make inference about the severity of service failures.
+
+For general details on GitHub usage, project organization, and project workflow, see [Research Assistant Training](https://github.com/marcdotson/ra-training).

### 2019-02-22 Code/01_build_classification_model.Rmd
I created the 01_build_classification_model Rmd (based on the fasttext_supervised_classifier.R) and edited the TestRDSConnection.R

---
title: "Classifier"
output: github_document
---

# Overview
In this R Markdown, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

# Load Packages
```{r}
library(fastrtext)
library(tidyverse)
```

# Define Functions
No functions have been defined in this file.

# About fastText
fastText was designed by Facebook and it allows us to build models for both classification and word embeddings. Classification refers to analyzing a set of text, and labeling it according to the topics it closely relates to. Word embeddings help us predict which words are most closely related to a single word of interest.

fastText boasts that it can perform classification and the creation of word embeddings faster than other tools used for comparable activities (like Word2vec and GloVe) without sacrificing accuracy. This is what drew our team's attention to this method from the beginning.

If you are unfamiliar with Fasttext, we'd reccomend getting to know it better by following along with the tutorials found at https://fasttext.cc/docs/en/supervised-tutorial.html. The tutorial run entirely from the terminal (a.k.a. the command line, shell, bash, command prompt), so if you're uncomfortable navigating your computer from the terminal, it would be worthwhile to find some tutorials on navigating directories within your terminal before beginning to learn fastText. If you'd like to learn more about how fastText works, this post found on Medium is also helpful https://towardsdatascience.com/fasttext-under-the-hood-11efc57b2b3.

Finally, if you don't conceptually understand word embeddings and classification, we reccomend doing a bit of research to get a better grip on those ideas before proceding.

# Execute Code
To build our fasttext classification model, we begin by defining where we want to store our fastText model once we've trained it. In our case, we want to store the model in Output/models and name the model class_mod_1.dat. Within R, we'll refer to this file path as file_model.

As a data input for training our model, we already have two text files: train_data_1.txt and test_data_1.txt. The file paths to these text files (already built) will be referred to as train_data and test_data.
```{r}
file_model <- "Output/models/class_mod_1.dat"
train_data <- "Output/clean_data/train_data_1.txt"
test_data <- "Output/clean_data/test_data_1.txt"
```

## Clean Data

## Build Model

# Analysis

### 2019-02-22 Code/TestRDSConnection.R

@@ -1,5 +1,6 @@
 library(RPostgreSQL)
 library(dbplyr)
+library(tidyverse)
 
 
 # Connect to RDS ----------------------------------------------------------
@@ -31,5 +32,7 @@ sample_tweets <-
 # Once tweets are pulled in, write the lines to a file.
 sample_tweets %>%
   .$tweet_text %>% 
-  write_lines("data/tweet_sample_1hM_noRT.txt")
+  write_lines("Output/clean_data/tweet_sample_1hM_noRT.txt")
+
+DBI::dbDisconnect(con)
 

### 2019-03-01 Code/01_build_classification_model.Rmd
Added more info to the 01 file.

@@
 # Execute Code
+
+## List File Paths of Model and Data
 To build our fasttext classification model, we begin by defining where we want to store our fastText model once we've trained it.
@@
 The file paths to these text files (already built) will be referred to as train_data and test_data.
+
 ```{r}
 file_model <- "Output/models/class_mod_1.dat"
-train_data <- "Output/clean_data/train_data_1.txt"
-test_data <- "Output/clean_data/test_data_1.txt"
+train_data_path <- "Output/clean_data/train_data_1.txt"
+test_data_path <- "Output/clean_data/test_data_1.txt"
 ```
 
-## Clean Data
+## Read in the Data
+We have our training and test data kept in one csv file. We'll read it in after we've filtered all short tweets (with greater than five characters). We'll name this object tweet_data.
+```{r}
+# This code (and all code below) is broken because we don't have access to a tweet_sample_5k_full.csv file.
 
-## Build Model
+# tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>%  
+#  filter(nchar(tweet_text) > 5)
+```
+
+## Format the Training Data
+For any supervised learning model (such as complaint classification), our training and test datasets need to have data labeled with the "correct" answers.
+This will allow our model to "learn" the correct answers, and it will hopefully help our model accurately predict correct answers.
+
+For our fastText model, we need to make sure each tweet is preceded by a label (in our case, the labels will be "complaint" and "non-complaint".
+fastText labels have two underscores before and after the label.
+For example, our complaint labels need to look like this: __label__complaint.
+Furthermore, the data we feed into the fastText model needs to be a character vector (like a .txt file), not a dataframe.
+We'll have to do some formatting before we get to that point.
+
+Now that we have access to the data, we'll edit a variable named "label." Currently the labels are 0 for non-complaints and 1 for complaints.
+When we're done, we'll replace the 0's and 1's with their respective terms.
+Additionally, the label and text need to be in the same cell, so we'll make a new variable that concotenates the text and the label toghether.
+
+Finally, we need to randomly and evenly tag our data: half of it will become training, and half of it will become test data.
+
+```{r}
+# test_train_data <- 
+#   tweet_data %>% 
+#   mutate(label = case_when(label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
+#                               label == 1 ~ "complaint"),
+#             input_lines = paste(label, tweet_text)) %>% 
+#   group_by(label) %>% # get a representative sample of both complaints and non complaints
+#   mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
+#   ungroup()
+```
+
+### Create the .txt Files
+As mentioned earlier, we need to create a text file of our training and test datasets because the fastText model only takes character vectors as inputs.
+With our data labeled both for training/test and complaint/non-complaint, we're ready to do this.
+We will use the write_lines() function to do this.
+The train_data_path is the file location we specified earlier in this script.
+
+!!!!!!!!!! I'm still not sure how we are using the test_labels_without_prefix. If its not the test data, what is it?
+
+```{r}
+# write train data
+# train_data_lines <- 
+#   test_train_data %>% 
+#   filter(test_train == "train") %>% 
+#   pull(input_lines) %>% 
+#   paste0("__label__", .)
+# 
+# write_lines(train_data_lines, train_data_path)
+# 
+# # write test data
+# test_data_lines <- 
+#   test_train_data %>% 
+#   filter(test_train == "test") %>% 
+#   pull(input_lines) %>% 
+#   paste0("__label__", .)
+# 
+# write_lines(test_data_lines, test_data_path)
+
+# create a character vector containing the tweets to test without their labels
+test_labels_without_prefix <- 
+  test_train_data %>% 
+  filter(test_train == "test") %>% 
+  pull(label)
+```
+
+## Train the Model
+The package we are using (fastrtext) uses the execute() function to train the model.
+This function makes more sense if you've followed the fastText tutorials, but put simply, it concotenates the arguments into a single command which is then run in the terminal.
+
+After we train the model, we'll load the model into our environment.
+
+"supervised" specifies that this is a supervised model (classification, as opposed to creating word vectors). 
+"-input" specifies the file location of the training text files.
+"-output" specifies the file location where we want to place our model, once it has finished training.
+
+You can find more information about the parameters of the model (such as -dim, -lr, and -epoch) here: https://fasttext.cc/docs/en/options.html.
+
+!!!!!! Considering that this is such a large dataset, it might be worthwhile to use -loss hs (hierarchical softmax) to speed up the training. It should not significantly affect accuracy.
+
+```{r}
+# train model
+execute(commands = c("supervised", "-input", train_data_path, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
+
+# load model
+model <- load_model(file_model)
+```
+
+## Review Model:
+We'll want to see how a few of the predictions turned out. 
+```{r}
+# prediction are returned as a list with words and probabilities
+predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
+head(predictions, 5)
+```
+
+This will help us confirm that our model worked as expected.
+```{r}
+length(predictions)
+length(test_labels_without_prefix)
+length(test_data_lines)
+```
+
+## Accuracy
+Let's look at how accurately the model predicted names
+```{r}
+# Compute accuracy
+mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
+```
+
+Here, we'll look at the hamming loss, and a few of the predictions.
+
+The hamming loss is the number of wrong labels over the total number of labels.
+Hamming loss is most useful when applied to multi-classifiers because when it is done with binary classifiers (such as ours), it is simply equal to 1 - accuracy.
+```{r}
+# because there is only one category by observation, hamming loss will be the same
+get_hamming_loss(as.list(test_labels_without_prefix), predictions)
+
+# test predictions
+predictions <- predict(model, sentences = test_to_write)
+print(head(predictions, 5))
+
+# you can get flat list of results when you are retrieving only one label per observation
+print(head(predict(model, sentences = test_to_write, simplify = TRUE)))
+```
 

### 2019-03-01 Code/TestRDSConnection.R

@@ -20,7 +20,7 @@ Cockroaches <- tbl(con, "Cockroaches")
 
 # Pull Data Sample --------------------------------------------------------
 
-# Get Tweet text for the first 1500000 tweets in the DB. Remove retweets (there's a lot)
+# Get Tweet text for the first 1,500,000 tweets in the DB. Remove retweets (there's a lot)
 sample_tweets <- 
   Cockroaches %>% 
   filter(substr(tweet_text, 1, 4) != "RT @") %>% 

### 2019-03-01 Paper/01_build_classification_model.Rmd
Knitted the current version of the 01 file

--- 2019-03-01 Code/01_build_classification_model.Rmd
@@
 ```{r}
-library(fastrtext)
-library(tidyverse)
+# library(fastrtext)
+# library(tidyverse)
 ```
@@
 ```{r}
-file_model <- "Output/models/class_mod_1.dat"
-train_data_path <- "Output/clean_data/train_data_1.txt"
-test_data_path <- "Output/clean_data/test_data_1.txt"
+# file_model <- "Output/models/class_mod_1.dat"
+# train_data_path <- "Output/clean_data/train_data_1.txt"
+# test_data_path <- "Output/clean_data/test_data_1.txt"
 ```
@@
 # create a character vector containing the tweets to test without their labels
-test_labels_without_prefix <- 
-  test_train_data %>% 
-  filter(test_train == "test") %>% 
-  pull(label)
+# test_labels_without_prefix <- 
+#   test_train_data %>% 
+#   filter(test_train == "test") %>% 
+#   pull(label)
 ```
@@
 # train model
-execute(commands = c("supervised", "-input", train_data_path, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
-
-# load model
-model <- load_model(file_model)
+# execute(commands = c("supervised", "-input", train_data_path, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
+# 
+# # load model
+# model <- load_model(file_model)
 ```
@@
 # prediction are returned as a list with words and probabilities
-predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
-head(predictions, 5)
+# predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
+# head(predictions, 5)
 ```
@@
 ```{r}
-length(predictions)
-length(test_labels_without_prefix)
-length(test_data_lines)
+# length(predictions)
+# length(test_labels_without_prefix)
+# length(test_data_lines)
 ```
@@
 ```{r}
-# Compute accuracy
-mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
+# # Compute accuracy
+# mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
 ```
@@
 ```{r}
-# because there is only one category by observation, hamming loss will be the same
-get_hamming_loss(as.list(test_labels_without_prefix), predictions)
-
-# test predictions
-predictions <- predict(model, sentences = test_to_write)
-print(head(predictions, 5))
-
-# you can get flat list of results when you are retrieving only one label per observation
-print(head(predict(model, sentences = test_to_write, simplify = TRUE)))
+# # because there is only one category by observation, hamming loss will be the same
+# get_hamming_loss(as.list(test_labels_without_prefix), predictions)
+# 
+# # test predictions
+# predictions <- predict(model, sentences = test_to_write)
+# print(head(predictions, 5))
+# 
+# # you can get flat list of results when you are retrieving only one label per observation
+# print(head(predict(model, sentences = test_to_write, simplify = TRUE)))
 ```

### 2019-03-01 Paper/paper.Rmd
Knitted the current version of the 01 file

--- 2019-03-01 Paper/01_build_classification_model.Rmd
@@
 ---
+# The Classification Model
+A key component to successfuly using twitter data to assess service failures is the ability to classify tweets as complaints and non-complaints.
+If our team can accurately classify a tweet, we will be capable of tackling the greater issue of judging how serious the complaint is, and whether or not a company needs to take action.
 
-# Overview
+While there are an infinite number of methods to perform this task, our team has identified three tools to aid us in our classification: Principal Component Analysis (PCA), FastText, and XGBoost.
+Using these three tools, we've created a "frankenstein model" that incorporates all three tools listed above.
+The model has been trained on 2,500 tweets labeled 0 for "non-complaint" and 1 for "complaint." We have then tested the model on a similarly-sized dataset.
+
+To use our model, we feed a set of tweets into a PCA model and a FastText classification model.
+The output of these two models is then fed into our XGBoost model, which makes a binary prediction for the tweet as a complaint or non-complaint.
+
+Because our model uses three distinct modeling techniques, I will refer to each of these modeling techniques as "sub-models"
+
+# The FastText Sub-Model
+## Overview
 In this R Markdown, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
 
-# Load Packages
+## Load Packages
 ```{r}
@@
 
-# Define Functions
+## Define Functions
 No functions have been defined in this file.
 
-# About fastText
+## About fastText
 fastText was designed by Facebook and it allows us to build models for both classification and word embeddings.
@@
 
-# Execute Code
+## Execute Code
 
-## List File Paths of Model and Data
+### List File Paths of Model and Data
 To build our fasttext classification model, we begin by defining where we want to store our fastText model once we've trained it.
@@
 
-## Read in the Data
+### Read in the Data
 We have our training and test data kept in one csv file. We'll read it in after we've filtered all short tweets (with greater than five characters). We'll name this object tweet_data.
@@
 
-## Format the Training Data
+### Format the Training Data
 For any supervised learning model (such as complaint classification), our training and test datasets need to have data labeled with the "correct" answers.
@@
 
-### Create the .txt Files
+#### Create the .txt Files
 As mentioned earlier, we need to create a text file of our training and test datasets because the fastText model only takes character vectors as inputs.
@@
 
-## Train the Model
+### Train the Model
 The package we are using (fastrtext) uses the execute() function to train the model.
@@
 
-## Review Model:
+### Review Model:
 We'll want to see how a few of the predictions turned out. 
@@
 
-## Accuracy
+### Accuracy
 Let's look at how accurately the model predicted names
@@
 
-# Analysis
+## Analysis
+
+# The PCA Sub-Model
+
+# The XGBoost Sub-Model
+
+## Intro to XGBoost
+XGBoost is a tool that uses gradient-boosted trees for classification.
+A basic understanding of decision trees and random forests is crucial to understanding gradient-boosting as well as the XGBoost package.
+
+Decision Trees:
+Decision trees are models that use a series of binary (yes/no) questions, and classify something based on the answers to those binary questions.
+
+Simple Decision Tree Example:
+Is it snowing? If so, it is a good day to ski. If not, it is not a good day to ski.
+
+Random Forests:
+
+Gradient Boosting:
+
+Links:

### 2019-03-01 Code/rds-data-processing/classifier-testing.R
Add script to pull tweets with predictions from best current model

@@ -1,12 +1,13 @@
 library(fastrtext)
 library(Matrix)
 library(xgboost)
-source("R/predict_func.R")
-source("R/TweetComplaintPredictor.r")
+source("Code/complaint-prediction/R/predict_func.R")
+source("Code/complaint-prediction/R/TweetComplaintPredictor.r")
 
-load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
-fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
-load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat")
+load("Code/complaint-prediction/models/fullClassifierOne/prcomp4.dat")
+fasttextModel <- load_model("Code/complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
+load("Code/complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat")
 TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)
 
-predict(TweetComplaintPredictor, "")
+
+predict(TweetComplaintPredictor, "@delta I hate you sooooo freaking much you made me late to my meeting in Denver")

### 2019-03-19 Code/01_analyze_complaint_categories.Rmd
Wrote more on the basics of the three sub-models we are using. Included a little documentation on the cluster_function script.

---
title: "Labeled Tweets"
output: github_document
---

# Overview
Our team created a subset of roguhly 5,000 tweets for testing and training. We created binary labels for complaints and non-complaints, as well as more descriptive labels for each tweet--labels for delays, poor interactions between employees and customers, etc. We did not systematically generate these categories (i.e. we did not run a topic model on our complaints or anything similar). Rather, we simply read the tweets one-by-one and created categories as topics appeared.

In this document, I will analyze the complaint categories we have created, and specifically investigate 1) if we should further granulize our catch-all event_specific category, and 2) what new categories we should consider creating based on the complaints we see in the event_specific category.

### Tweet Labels
As background information, here is information regarding the intuition behind our tweet labels:

##### Human_service_rude:
  * An employee was cited for rude conduct. (i.e. “@airline Your flight attendants were so rude to me today!”
  * Customer service cited as terrible
  * Repeated calls to amend a problem do not help find a solution/recieves no response.

##### Human_service_hold: 
  * Customer on hold for a long time

##### Check_failure:
  * A customer was dissatisfied with their check-in process. (i.e. “Terrible check-in experience today, never flying with @airline again.”)

##### Baggage
  * A customer did not receive their checked baggage when they landed in their destination.
  * Sometimes, a baggage complaint overlapped with a delay complaint. In these scenarios, we labeled it as a baggage complaint.

##### Delay_delay: 
  * A customer’s flight was delayed

##### Delay_cancel: 
  * A flight was cancelled

##### Delay_tarmac: 
  * A customer’s flight landed, but was waiting on the tarmac (possibly worried they won’t make their connecting flight).

##### Event_vague:
  * Vague complaint, referencing an event that happened, but not specifying details of the situation (i.e. “@airline You suck!”)

##### Event_specific: 
  * Very specific/unique failure (i.e. “The bathroom was broken” or “you won’t let me sit next to my son”)
  * Catch-all complaint for hard-to-classify situations

##### Wishlist
  * Person complains about a feature/service not provided by the airline
  * Person wishes a service were better/higher quality
  * Person wishes a procedure were performed differently

##### App_failure
  * An airline app did not function properly
  * An airline website/booking program did not function properly

# Libraries
```{r}
library(tidyverse)
library(tidytext)
library(topicmodels)
```

# Read in the Labeled Tweets
```{r}
# Note that the labeled tweet data is kept in my Temporary folder
data <- read_csv("../Temporary/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")
```

# Analyze the Data
```{r}
data %>% 
  ggplot(aes(as.factor(complaint_label), fill = complaint_category)) +
  geom_bar() +
  labs(
    title = "Complaints to Non-Complaints"
  ) +
  theme(legend.position = "bottom")
```

```{r}
data %>% 
  filter(complaint_label == 1) %>% 
  count(complaint_category, sort = TRUE) %>% 
  mutate(complaint_category = reorder(complaint_category, n)) %>% 
  ggplot(aes(complaint_category, n)) +
  geom_col() +
  coord_flip() +
  labs(title = "Most Common Complaint Types")

```

It is concerning to me that the second-largest complaint category is our catch-all "event_specific" category. This means that of the roughly 1500 complaints we labeled in the 5000 tweets, about 300 (or 20%) of these tweets recieved the ambiguous, catch-all label.

# Quick TF-IDF Analysis of the Data
```{r}
# Create data compatible for tf_idf analysis
tf_idf_data <- data %>% 
  unnest_tokens(word, tweet_text) %>% 
  group_by(complaint_category) %>% 
  count(word, sort = TRUE) %>% 
  bind_tf_idf(word, complaint_category, n)

# Visualize the data
tf_idf_data %>% 
  group_by(complaint_category) %>% 
  top_n(5) %>%
  ungroup() %>% 
  ggplot(aes(x = reorder(word, tf_idf), y = tf_idf, fill = complaint_category)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ complaint_category, ncol = 3, scales = "free") + 
  coord_flip()

```

Although I will admit that this is not a great-looking graphic, it does help us quickly see that our complaint categories do target the right tweets. event_vague contains vague complaints, containing mostly expletives. delay_cancel contains "cancel" in the tweet. baggage contains "luggage" "lost" and "suitcase." check_failure and wishlist seem to be such small categories, that the analysis couldn't seem to identify any themes.

# TF-IDF Analysis of event_specific Label
This label was our catch-all label for complaints we had difficulty classifying. I'd like to take a better look at it to see if any themes appear. I'm hoping we could find a few themes large enough to merit the creation of a new complaint category. This would reduce the size of our catch-all category, and improve our classifier.
```{r}
tf_idf_data %>% 
  filter(complaint_category == "event_specific") %>% 
  mutate(word = reorder(word, tf_idf)) %>% 
  top_n(20) %>%
  ggplot(aes(word, tf_idf, fill = complaint_category)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ complaint_category, scales = "free") + 
  coord_flip()
```

The word "own" appeared eleven times in all of our tweets and was only associated with event_specific five times. Additionally, this word appeared in very distinct contexts, such as these phrases: "my own seat", "I own an American Express credit card", "your own flight attendant." It seems that this word would not merit a new complaint category.

The word "booked" appeared 66 times in our dataset, and was associated with event_specific eleven times. This seems like too small of a category to create a new category.

"Bathroom" appeared six times in our dataset, and therefore seems like too small of a grouping to create a new category.

The word "seat" appeared 130 times in our dataset, and was associate 29 times with our event_specific label. It could be large enough to merit a new category, if there seems to be a consistent theme. Among these 29 event_specific label, I think we could categorize about 20 of them into a "seating" category--complaints related to people who did not recieve the seat they wanted, had a broken seat, were unhappy about extra charges for normal seating, wanted to move to a different open seat, or felt the seating was ucomfortable. Another issue that resurfaced several times was related to items lost in seat pockets, but it only appeared three times.

The word "charge" appeared in our dataset 33 times, and was associated with event_specific thirteen times. Reading through the tweets, it seems that this word appeared when customers were upset with charges that were unexpected, or seemed uneccesarily large. While this word alone may not merit the creation of a new complaint category, other words such as "pay" "paid" and "paying" might appear frequently enough to merit a new theme.

# Word Count of event_specific Category
Here, I will simply look at wordcounts of the event_specific category, with stop words filtered out.
```{r}
tf_idf_data %>% 
  anti_join(stop_words) %>% 
  filter(complaint_category == "event_specific") %>% 
  mutate(word = reorder(word, n)) %>% 
  top_n(20) %>% 
  ggplot(aes(x = word, y = n, fill = complaint_category)) +
  geom_col(show.legend = FALSE) +
  coord_flip()
```

This graph seems to confirm that "seat" and "charge" appeared frequently in this particular category.

How often do words associated with extra fees and charges appear in the event_specific category?
```{r}
tf_idf_data %>% 
  filter(complaint_category == "event_specific",
         word %in% c("pay", "paid", "paying", "charge", "charged", "fee", "fees")) %>% 
  mutate(word = reorder(word, n)) %>% 
  ggplot(aes(x = word, y = n, fill = complaint_category)) +
  geom_col(show.legend = FALSE) +
  coord_flip()
```

I'll produce the same data, but in a table format.
```{r}
tf_idf_data %>% 
  filter(complaint_category == "event_specific",
         word %in% c("pay", "paid", "paying", "charge", "charged", "fee", "fees")) %>% 
  mutate(word = reorder(word, n)) %>% 
  select(word, n)
```

With this table and bar chart, it seems reasonable to create a new complaint category for "charges" that reflects complaints related to extra/unexpected/large fees the customers complained about, given that about 36 event_specific complaints were related to charges.

# Topic Modeling
Would a topic run model on the complaints reveal topics we overlooked? My only concern with this analysis is that our tweets are very small documents for the model to work with--they might be too small for the LDA model to be effective at detecting topics.
```{r}
data_dtm <- data %>% 
  filter(complaint_label == 1) %>% 
  mutate(row = row_number()) %>% 
  select(row, tweet_text) %>% 
  unnest_tokens(word, tweet_text) %>% 
  count(row, word) %>% 
  cast_dtm(row, word, n)

complaint_lda <- LDA(data_dtm, k = 8, control = list(seed = 1234))

complaint_topics <- tidy(complaint_lda, matrix = "beta")

tweet_top_terms <- complaint_topics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

tweet_top_terms %>%
  ggplot(aes(reorder(term, beta), beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()

```

As expected, I did not find this topic model to be very useful. I imagine that the source of the problem was due to our incredibly short document lenghts (the tweets).

### 2019-03-19 Paper/paper.Rmd

@@
 
-While there are an infinite number of methods to perform this task, our team has identified three tools to aid us in our classification: Principal Component Analysis (PCA), FastText, and XGBoost.
+While there are a massive number of methods to perform this task, our team has identified three tools to aid us in our classification: Principal Component Analysis (PCA), FastText, and XGBoost.
 Using these three tools, we've created a "frankenstein model" that incorporates all three tools listed above.
@@
 
-Because our model uses three distinct modeling techniques, I will refer to each of these modeling techniques as "sub-models"
+Because our model uses three distinct modeling techniques, I will refer to each of these modeling techniques as "sub-models."
 
@@
 ## Overview
-In this R Markdown, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
+In this section, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
 
@@
 # The PCA Sub-Model
+## Intro to PCA
+The idea behind PCA is that a complex multi-dimensional problem can be boiled down to a single-dimensional problem.
+For example, what if you had a model that tried to predict a student's grade on a test by looking at how many hours the student studied, how many lectures the student attended, how many hours of sleep they got, what cereal they eat for breakfast, and how many siblings they have.
+While all of these factors could arguably have an affect on the student's test grade, I would expect the "hours studied" and "lectures attended" variables to have the strongest correlation to test.
+A PCA model would notice the most important variables of a model, and simplify the model to focus on just two "principle components" (note that it still incorporates the other variables in the model, but these variables have been "simplified" or "compressed")
+
+With a PCA model, similar results will cluster together, and clusterings can help with classification.
+With our student example, we would see "A" students cluster together, "B" students to cluster together, etc.
+While this example might seem like a simple explanation, PCA analysis can be very useful when large amounts of data are available, but you don't know which variables are most important in your classification.
+
+For our purposes, we should be able to use PCA analysis by taking large ammounts of data we collect on tweets (their features, their average word vector, etc.) and see a clustering of complaints and non-complaints, without worrying about which features or variables of a tweet are best for classification.
+
+## Useful Resources:
+Quick Explanation of PCA: https://www.youtube.com/watch?v=HMOI_lkzW08
+https://www.youtube.com/watch?v=_UVHneBUBW0
 
@@
 A basic understanding of decision trees and random forests is crucial to understanding gradient-boosting as well as the XGBoost package.
+If any of these terms seem unfamiliar, I'd recommend that you look at the links I've posted below.
 
-Decision Trees:
-Decision trees are models that use a series of binary (yes/no) questions, and classify something based on the answers to those binary questions.
+##### Decision Trees:
+Decision trees are models that use a series of binary (yes/no) questions to classify something based on the answers to those binary questions.
+A decision tree can be randomly generated to model the data.
+This means that you could have an infinite number of trees that model the same data.
 
@@
 
-Random Forests:
+##### Random Forests:
+A single decision tree is not very effective for modeling--singe decision tree models have been known to overfit the data, and therefore innaccurately classify data.
+However, it should be noted that decision trees are more accurate at classification than a random guess, and this can make them very useful.
 
-Gradient Boosting:
+Random forests are models that take advantaged of the fact that a decision tree can still provide a better estimate than a random guess, despite a single tree's inaccuracy.
+Random forests use hundreds of decision trees (each tree randomly generated to model the same data of interest), and classify data based on the consensus of the outputs these trees.
 
-Links:
+##### Gradient Boosting:
+Gradient Boosting builds on the foundation of random forests by optimizing the model.
+A gradient boosted random forest systematically analyzes the individual trees of a forest that perform poorly, and focuses on cleaning and improving those trees.
+With many iterations, a boosted model should improve significantly as it gets trained.
+XGBoost, the package we use for gradient boosting, is simply one popular tool of many for boosted trees.
+
+## Useful Resources:
+When I was first learning about XGBoost, I found these youtube videos to be helpful in explaining the very basic concepts behind boosted trees.
+Hopefully, they can help you too if you're struggling to follow along.
+
+Decision Trees: https://www.youtube.com/watch?v=7VeUPuFGJHk
+Random Forests: https://www.youtube.com/watch?v=J4Wdy0Wc_xQ
+More Random Forests: https://www.youtube.com/watch?v=nyxTdL_4Q-Q
+Cross Validation: https://www.youtube.com/watch?v=TIgfjmp-4BA
+Boostrap Aggregating (Bagging): https://www.youtube.com/watch?v=2Mg8QD0F1dQ
+MIT lecture on Boosting: https://www.youtube.com/watch?v=UHBmv7qCey4

### 2019-03-27 Code/dallin_code_annotations/02_create_clustering_function.Rmd
Made a folder for annotating Adriel's Code named dallin_code_annotations. I am hoping that doing so will help me better understand the code/model created by Adriel.

---
title: "Create a Clustering Function"
output: github_document
---

# Libraries
```{r}
library(fastrtext)
library(tidyverse)
library(cluster)    # clustering algorithms
library(factoextra) # clustering visualization
library(dendextend) # for comparing two dendrograms
library(parallel)
library(pbapply)
library(stringr)
```

# Overview
In this document, we will be creating several functions that will aid in building our classification model. These functions will be referenced in future scripts to help build our model.

### Average Word Vector Function
This function will take the word vectors for each word in a tweet, and will average the vectors to create a single vector representing the tweet as a whole. The word vectors will be generated by a fasttext unsupervised model. This will effectively become a mathmatical summary of each tweet, and will be a valuable input to our model.
```{r}
# This creates the average word vector to represent each tweet as an embedding vector
avg_word_vec <- function(text, model) {
  # tokenize the text, return a list of tokens
  vec_of_tokens <- strsplit(text, " ")[[1]]
  # apply get_word_vectors to each token in the vector, return matrix of word vecs
  matrix_of_vecs <- get_word_vectors(model, vec_of_tokens)
  # convert matrix to a tibble for easy reduction
  tbl_of_vecs <- tbl_df(matrix_of_vecs) 
  # summarise the word vector tibble into one average tibble
  summarise_all(tbl_of_vecs, funs(mean), na.rm = TRUE)
}
```

### Code I don't understand
```{r}
# I imagine that this somehow takes a look at the nearest neigbors of a single word, or a tweet vector?
 nn_filter <- function(model, token, filter_str, n = 1000) {
  out <- get_nn(model, token, n)
  if(!is.na(filter_str)) {
    tibble(word = names(out), value = out) %>% 
      filter(!grepl(paste0(".*", filter_str, ".*"), word, ignore.case = T))
  } else {
    tibble(word = names(out), value = out)
  }
}

model_eval <- function(token, ..., filter_str = NA) {
  models <- list(...)
  names(models) <- GetDotObjectNames(...)
  cl <- detectCores()
  pblapply(models, nn_filter, token, filter_str, cl = cl)
}

GetDotObjectNames <- function(...) {
  strsplit(
    gsub("[\\(\\)]", 
         "", 
         regmatches(
           deparse(
             substitute(
               list(...))), 
           gregexpr("\\(.*?\\)", 
                    deparse(
                      substitute(
                        list(...)))))[[1]]), 
    split = ", ")[[1]]
}

model_eval_plot <- function(eval_list, n = 20, token, filter_str) {
  out <- lapply(names(eval_list), function(model) {
    eval_list[[model]] %>% 
      mutate(model = model)
  }) %>% 
    bind_rows() %>% 
    group_by(model) %>% 
    top_n(n, value) %>% 
    ungroup() %>% 
    arrange(model, value) %>% 
    mutate(order = row_number())

  out %>% 
    ggplot(aes(order, value, fill = model)) +
    geom_bar(stat = "identity", show.legend = FALSE) +
    facet_wrap(~model, scales = "free") +
    labs(y = "Euclidean Dist",
         x = NULL) +
    ggtitle(paste("Top", n, "Closest Words"), subtitle = paste0("In Euclidean Distance from '", token, "'", ifelse(missing(filter_str) || is.na(filter_str), "", paste0(" with '",filter_str,"' filtered out")))) +
    scale_x_continuous(
      breaks = out$order,
      labels = out$word,
      expand = c(0,0)
    ) +
    coord_flip()
}

model_eval_plot_wrap <- function(token, ..., filter_str = NA, n = 20) {
  model_eval(token, ..., filter_str = filter_str) %>% 
    model_eval_plot(n, token, filter_str)
}

# function factory to compute total within-cluster sum of square, given a list column number
wss_func <- function(data, col_num) {
  function(k) {
    kmeans(unnest(data[,col_num]), k, nstart = 10 )$tot.withinss
  }
}

kmeans_assign <- function(data, kseq, colseq, nstart = 15, iter.max = 30) {
  df_length <- nrow(data)
  data <- filter(data, tweet_text != "")
  len_diff <- df_length - nrow(data)
  if(len_diff > 0) {
    message(paste0("Filtered ", len_diff, " num rows of blank strings"))
  }
  data_colnames <- colnames(data)
  for(i in kseq) {
    for(j in colseq) {
      varname <- paste0("k", i, "_", data_colnames[j])
      data <- mutate(data, !!varname := kmeans(unnest(data[,j]), i, nstart = nstart, iter.max = iter.max)$cluster)
    }
  }
  return(data)
}

sample_num_levels <- function(df, sample_col_num, n = 20) {
  for(i in sample_col_num) {
    col_levels <- max(df[,i])
    for(j in 1:col_levels) {
      out <- 
        df %>% 
        .[which(.[,i] == j),] %>% 
        dplyr::select(tweet_text) %>% 
        sample_n(n, replace = T)
      cat(paste("\n\nSampling", n, "observations from cluster", j, "in column ", colnames(df)[i],"\n\n"))
      print(out)
    }
  }
}
```

### 2019-03-27 Code/dallin_code_annotations/04_test_rds_connection.Rmd
Made a folder for annotating Adriel's Code named dallin_code_annotations. I am hoping that doing so will help me better understand the code/model created by Adriel.

---
title: "Test RDS Connection"
output: github_document
---
# Overview
In this document, I will be annotating the code written by Adriel in the script "TestRDSConnection.R."

```{r}
library(RPostgreSQL)
library(dbplyr)
library(tidyverse)

# Connect to RDS ----------------------------------------------------------

# Load drivers to communicate with RDS
drv <- dbDriver("PostgreSQL")
con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
                 user = "adrielc", password = "byuanalytics58") # This will prompt user

# List all tables available within the database
dbListTables(con)

# Create tbl object to reference the table serverside when pulling data
Cockroaches <- tbl(con, "Cockroaches")

# Pull Data Sample --------------------------------------------------------

# Get Tweet text for the first 1,500,000 tweets in the DB. Remove retweets (there's a lot)
sample_tweets <- 
  Cockroaches %>% 
  filter(substr(tweet_text, 1, 4) != "RT @") %>% 
  select(tweet_text) %>% 
  head(1500000) %>% 
  mutate(tweet_text = tolower(tweet_text)) %>%
  collect() # all the processing is done server side before being pulled in by collect()

# Once tweets are pulled in, write the lines to a file.
sample_tweets %>%
  .$tweet_text %>% 
  write_lines("Output/clean_data/tweet_sample_1hM_noRT.txt")

DBI::dbDisconnect(con)

```

### 2019-03-27 Code/dallin_code_annotations/05_counting_cockroaches.Rmd
Made a folder for annotating Adriel's Code named dallin_code_annotations. I am hoping that doing so will help me better understand the code/model created by Adriel.

---
title: "Counting Cockroaches"
output: github_document
---
# Overview
These are my annotations on the "CountingCockroaches.R" file written by Adriel

```{r}
#################################################
####      1) Data Loading and Preparation     ###
#################################################

# Can we build this without using tm?

library(tidyverse); library(tidytext); library(tm); library(topicmodels)
load("/Users/maddatascientist/DATA SCIENCE/Marketing RA/Twitter Subset2.Rdata") # file location dependent on user
tweets <- twitter_subset

# Format tweets
tweets <- tweets %>% 
  mutate(Tweet_Number = row_number()) %>% 
  select(Tweet_Number, Text = text, Sentiment = sentiment)

# Combine tweets into "mega-tweets" by airline:
airlines <- list(c("americanair", "american", "american air"), "united", "delta", 
                 c("southwestair", "southwest") , "klm", "emirates", "indonesiagaruda", "british_airways", 
                 "usairways", "jetblue", "aircanada", "ryanair", "virginamerica", 
                 c("alaskaairlines", "alaskaair"), "aerlingus", "easyjet","flyfrontier","porterairlines",
                 "asercaairlines","singaporeair", "saudiairlines", "saudiairline", "tamairlines",
                 "cebupacificair","airasia","airfrancefr","koreanairke","deltaassist","aviorairline", 
                 "lufthansa", "airbus")

library(stringr)

docs <- list()
for (i in 1:length(airlines)) {     
  docs[[i]] <- tweets$Text %>%
    str_subset( str_c( "(?i)", str_c( airlines[[i]] ), collapse = "|" ) ) %>% # The "(?i)" is ignoring case
    str_c(collapse = " ")
}

# # #     TAKE OUT ALL AIRLINES     # # #
for (k in 1:length(docs)) {
  for (i in 1:length(airlines)) {
    docs[[k]] <- docs[[k]] %>% 
      str_replace_all( str_c( "@?(?i)", str_c(airlines[[i]]), collapse = "|" ) , "" ) 
  }
}

              # Take Out All "Words" w/ Numbers and All Twitter Handles (optional)

              # docs <- docs %>% 
                # str_replace_all("[\\s]@[^\\s]*", "") %>% # for Twitter handles
                # str_replace_all("[^\\s]*\\d.*?\\s", "") # for all words with numbers

# Get custom stop words

mega_tweets <- docs %>% unlist()

freqs <- list()
for (i in 1:length(mega_tweets)) {    # this loop takes around 4 min
  freq <- mega_tweets[i] %>% 
    VectorSource() %>% 
    Corpus() %>%                
    tm_map(content_transformer(tolower))  %>% 
    tm_map(removePunctuation) %>% 
    tm_map(stripWhitespace) %>% 
    tm_map(removeWords,c(stopwords("english"))) %>% 
    DocumentTermMatrix() %>% 
    as.matrix() %>% 
    colSums() %>% 
    sort(decreasing = TRUE) %>% 
    head(100)
  freqs[[i]] <- freq
}

all_names <- list()
for (l in 1:length(freqs)){
  all_names[[l]] <- names(freqs[[l]])
}

combos <- combn(all_names, 6)

all_intersects <- list()

#----------------------------------------------------------------------
# Parallelizing this task brings processing time from 23 min down to less than 2 min

library(parallel)

intersect_all <- function(a){
  Reduce(intersect, a)
}

no_cores <- detectCores() - 1 # Calculate the number of cores
cl <- makeCluster(no_cores, type="FORK") # Initiate cluster, automatically including environment
all_intersects <- parApply(cl, combos, MARGIN = 2, FUN = intersect_all)
stopCluster(cl)

custom <- Reduce(union, all_intersects)
#----------------------------------------------------------------------

#############################################
####      2) Pre-Model Visualization      ###
#############################################

#----------  Wordcloud by "Mega-tweet" (Airline) ---------- #

library(wordcloud)
library(RColorBrewer)
pal <- brewer.pal(9, "BuGn")[-(1:4)] # colors

freqs <- list()
for (i in 1:length(mega_tweets)) {    # takes about 6-7 min
  freq <- mega_tweets[i] %>% 
    VectorSource() %>% 
    Corpus() %>%                
    tm_map(content_transformer(tolower))  %>% 
    tm_map(removePunctuation) %>% 
    tm_map(stripWhitespace) %>% 
    tm_map(removeWords,c(stopwords("english"), custom)) %>%     # custom stops included here
    DocumentTermMatrix() %>% 
    as.matrix() %>% 
    colSums() %>% 
    sort(decreasing = TRUE) %>% 
    head(100)
  freqs[[i]] <- freq
  wordcloud(words = names(freq), freq = freq, min.freq = min(freq), 
            random.order = FALSE, colors = pal)
}

#############################################
####            3) Model Fitting          ###
#############################################

#Run LDA on DTM

# Get one big dtm from corpora

mega_corpus <- mega_tweets %>% 
  VectorSource() %>% 
  Corpus()

mega_corpus <- mega_corpus %>%                # Takes about 6 min on 31 docs
  tm_map(content_transformer(tolower))  %>% 
  tm_map(removePunctuation) %>% 
  tm_map(stripWhitespace) %>% 
  tm_map(removeWords,c(stopwords("english"), custom)) # can use custom list too

mega_dtm <- DocumentTermMatrix(mega_corpus)

#----------------------------------------------------------------------
# Process run sequentially

# Fit LDA for different numbers of topics
num_topics <- 2:20
num_terms <- 20
topic_results <- list()
terms <- list()
for ( k in num_topics ){                # takes 43 min on 18 docs
  topic_results[[k-1]] <- mega_dtm %>% 
    LDA(method = "Gibbs", k = k, control = list(seed = 42))

  terms[[k-1]] <- topic_results[[k-1]] %>% 
    terms(k = num_terms) 
}
#----------------------------------------------------------------------

#----------------------------------------------------------------------
# Parallelizing this task has processing time of 40 min ... no improvement on sequential

library(parallel)
library(doParallel)

fit_LDAs <- function(dtm, k){
  dtm %>% 
    LDA(method = "Gibbs", k = k, control = list(seed = 42))
}

num_topics <- 2:20

registerDoParallel(cores = 3)
topic_results <- foreach(k = num_topics) %do% fit_LDAs(mega_dtm,k)

#----------------------------------------------------------------------

betas <- list()
gammas <- list()
for ( n in 1:length(topic_results) ) {
  betas[[n]] <- topic_results[[n]] %>% tidy(matrix = "beta")
  gammas[[n]] <- topic_results[[n]] %>% tidy(matrix = "gamma") %>% 
    group_by(document) %>% 
    top_n(1, gamma) %>% 
    ungroup()
}

for ( j in 1:length(gammas) ) {
  cat(j+1, "Topic(s)")
  cat("\n") 
  gammas[[j]] %>% arrange(as.numeric(document)) %>% print()
  cat("\n") 
}

for ( j in 1:length(betas) ) {
  cat(j+1, "Topic(s)")
  cat("\n") 
  betas[[j]] %>% print()
  cat("\n") 
}

# Optimize Number of Topics (from https://cran.r-project.org/web/packages/ldatuning/vignettes/topics.html)

library(ldatuning)
result <- FindTopicsNumber(
  mega_dtm,
  topics = seq(from = 2, to = 20, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 77),
  mc.cores = 2L,
  verbose = TRUE
)

FindTopicsNumber_plot(result) # 11 topics then ?

#################################################
####      4) Post-Model Visualization    ###
#################################################

# Top Terms by Topic

library(ggplot2)
library(dplyr)

new_betas <- list()
for ( m in 1:length(betas) ){

  new_betas[[m]] <- betas[[m]] %>% 
    filter(beta > 0.001) %>% 
    arrange(as.numeric(topic))

}

top_terms <- list()
for (k in 1:length(betas)) {

  top_terms[[k]] <- new_betas[[k]] %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    arrange(topic, -beta)

}

for ( t in 1:length(top_terms) ) {
  print(  
    top_terms[[t]] %>%
      mutate(term = reorder(term, beta)) %>%
      ggplot(aes(term, beta, fill = factor(topic))) +
      geom_col(show.legend = FALSE) +
      facet_wrap( ~topic, scales = "free") +
      coord_flip()
  )
}

```

### 2019-03-27 Code/dallin_code_annotations/09_fasttext_clust_EDA.Rmd
Made a folder for annotating Adriel's Code named dallin_code_annotations. I am hoping that doing so will help me better understand the code/model created by Adriel.

---
title: "fastText Clust EDA"
output: github_document
---

# Overview 
These are my annotations on the "fasttext_clust_EDA.R" script written by Adriel

```{r}
library(googlesheets)
library(plotly)
library(broom)
library(caret)
library(cluster)
library(qtlcharts)
library(RPostgreSQL)
library(dbplyr)
source("Code/complaint-prediction/R/clus_func.R")

# source("R/rquery_cormat.R") Note from Dallin: Where is this file?

# connect to db -----------------------------------------------------------

drv <- dbDriver("PostgreSQL")
con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
                 user = "adrielc", password = "byuanalytics58") # This will prompt user
dbListTables(con)

# pull data sample --------------------------------------------------------

Cockroaches <- tbl(con, "Cockroaches")

sample_tweets <- 
  Cockroaches %>% 
  select(tweet_text) %>% 
  mutate(tweet_text = tolower(tweet_text)) %>%
  filter(substr(tweet_text, 1, 4) != "rt @") %>% 
  head(900000) %>% 
  collect()

sample_tweets %>%
  .$tweet_text %>% 
  write_lines("data/tweet_sample_1mil.txt")

# Remove retweets
sample_tweets <- 
  Cockroaches %>% 
  filter(substr(tweet_text, 1, 4) != "RT @") %>% 
  select(tweet_text) %>% 
  head(1500000) %>% 
  mutate(tweet_text = tolower(tweet_text)) %>%
  collect()

sample_tweets %>%
  .$tweet_text %>%
  write_lines("data/tweet_sample_1hM_noRT.txt")
rm(sample_tweets) # After writing the .txt files, we are removing them from the environment with the rm() function

# Remove retweets
sample_tweets <- 
  Cockroaches %>% 
  filter(substr(tweet_text, 1, 4) != "RT @") %>% 
  select(tweet_text) %>% 
  head(2000000) %>% 
  mutate(tweet_text = tolower(tweet_text)) %>%
  collect()

sample_tweets %>%
  .$tweet_text %>%
  write_lines("data/tweet_sample_2M_noRT.txt")
rm(sample_tweets)

# create_clusters ---------------------------------------------------------

file_txt <- "data/tweet_sample_1hM_noRT.txt"

file_model200 <- "data/models/model200.dat"
file_model150 <- "data/models/model150.dat"
file_model100 <- "data/models/model100.dat"
file_model50  <- "data/models/model50.dat"
file_model25  <- "data/models/mode25.dat"

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model200, "-verbose", 1, "-dim", 200))
model200 <- load_model(file_model200)

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model150, "-verbose", 1, "-dim", 150))
model150 <- load_model(file_model150)

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model100, "-verbose", 1, "-dim", 100))
model100 <- load_model(file_model100)

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
model50 <- load_model(file_model50)

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model25, "-verbose", 1, "-dim", 25))
model25 <- load_model(file_model25)

# test word extraction
dict <- get_dictionary(model50)

# test word vectors for specific words
print(get_word_vectors(model50, c("delta", "americanair")))

# Nearest-neighbor queries for words
model_eval("mad", model150, model100, model50, model25, filter_str = "mad") %>% 
  model_eval_plot(20, "mad", "mad")

# Nearest-neighbor queries for words --------------------------------------

nn_words  <- 
  list(c("mad", "mad"),
       c("sad","sad"),
       c("upset", "upset"),
       c("late", "ate"),
       c("delay", "del"),
       c("cancelled", "cancel"),
       c("snow", "snow"),
       c("rain", "rain"),
       c("weather", "weather"))

map(nn_words, function(x) model_eval_plot_wrap(x[1], model200, model150, model100, model50, model25, filter_str = x[2], n = 20))

model_eval_plot_wrap("baggage", model200, model150, model100, model25, filter_str = "bag")
model_eval_plot_wrap("delay", model200, model150, model100, model50, model25, filter_str = "del")
model_eval_plot_wrap("delay", model200, model150, model100, model50, model25)
model_eval_plot_wrap("tarmac", model200, model150, model100, model50, model25, filter_str = "tarmac")

# create list columns with average vectors for tweets ---------------------

sample_tweets <- 
  read_lines("data/tweet_sample_1hM_noRT.txt") %>% 
  tibble(tweet_text)

system.time({
  vec_out <- sample_tweets %>%
    sample_n(5000) %>% 
    mutate(avg_vec_200 = map(tweet_text, avg_word_vec, model = model200),
           avg_vec_150 = map(tweet_text, avg_word_vec, model = model150),
           avg_vec_100 = map(tweet_text, avg_word_vec, model = model100),
           avg_vec_50  = map(tweet_text, avg_word_vec, model = model50),
           avg_vec_25  = map(tweet_text, avg_word_vec, model = model25))
})

test_out <- test_out %>% mutate(avg_vec_25 = map(tweet_text, avg_word_vec, model = model25))

# plot WSS for kmeans solutions -------------------------------------------

set.seed(123)

# Compute and plot wss for k = 1 to k = 15
k.values <- 1:7

# extract wss for 2-7 clusters for each model type
wss_values150 <- map_dbl(k.values, wss_func(2, vec_out))
wss_values100 <- map_dbl(k.values, wss_func(3, vec_out))
wss_values50 <- map_dbl(k.values, wss_func(4, vec_out))
par(mfrow=c(2,2))
plot(k.values, wss_values150,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares",
     main = "Embedding 150")
plot(k.values, wss_values100,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares",
     main = "Embedding 100")
plot(k.values, wss_values50,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares",
     main = "Embedding 50")

# assign clusters to tweets -----------------------------------------------

vec_labeled <- kmeans_assign(test_out, 6:11, 2:6)

# vec_labeled %>% 
#   select(tweet_text, k6_avg_vec_200:k11_avg_vec_25) %>% 
#   write_csv("data/labeled_data_3.csv")

vec_labeled <- read_csv("data/labeled_data_2.csv")

# Randomly sample from the clusters to determine which contain complaints --------

# This labeled data is from "data/labeled_data_2.csv"
# HOW THESE WERE LABELED
# Every cluster gets 1 of 2 labels: def, maybe. No label applied if confident a cluster shouldn't belong
# Each sample of 20 is evaluated with the following heuristics:
# def: If more than 70% of the sample is complaints (percentages are not actually calculated for each cluster, just assumed)
# maybe: if more than 1 complaint is found and is less than 70%

# Here are some examples of complaint types:
## Lost luggage: people are without there stuff and want compensation
## Flight delay: Want some recompense for hotels
## What to do about a missed flight
## Ticket issues
## On the Tarmac waiting
## Poor customer service
## No response from the airline
## Failure in contacting through phone
## Extra/hidden fees

# 3 main reasons that people complain
# Want a response for information
# Want a response for compensation
# Social retaliation

# Interesting note: a lot of complaints contain positive words but are written with sarcasm

# 6 clusters
sample_num_levels(vec_labeled, 7,  20) # 1, 6 - maybe: 2, 4
sample_num_levels(vec_labeled, 8,  20) # 1, 6 - maybe: 4
sample_num_levels(vec_labeled, 9,  20) # 2, 5 - maybe: 4
sample_num_levels(vec_labeled, 10, 20) # 4, 5 - maybe: 3
sample_num_levels(vec_labeled, 11, 20) # 3, 6

# 7 clusters
sample_num_levels(vec_labeled, 12, 20) # 3    - maybe: 2
sample_num_levels(vec_labeled, 13, 20) # 3, 6 - maybe: 7
sample_num_levels(vec_labeled, 14, 20) # 1    - maybe: 6, 7
sample_num_levels(vec_labeled, 15, 20) # 2, 6 - maybe: 7
sample_num_levels(vec_labeled, 16, 20) # 5    - maybe: 3

# 8 clusters
sample_num_levels(vec_labeled, 17, 20) # 1, 4    - maybe: 5, 8
sample_num_levels(vec_labeled, 18, 20) # 2, 3    - maybe: 4, 6
sample_num_levels(vec_labeled, 19, 20) # 1, 3, 7 - maybe: 2, 6
sample_num_levels(vec_labeled, 20, 20) # 3, 4    - mqybe: 6
sample_num_levels(vec_labeled, 21, 20) # 3       - maybe: 1, 8

# 9 clusters
sample_num_levels(vec_labeled, 22, 20) # def: 6, 7, 8 - maybe: 1, 8
sample_num_levels(vec_labeled, 23, 20) # def: 6, 7, 9 - maybe: 1
sample_num_levels(vec_labeled, 24, 20) # def: 4, 5, 7 - maybe: 3
sample_num_levels(vec_labeled, 25, 20) # def: 5, 7, 8 - maybe:
sample_num_levels(vec_labeled, 26, 20) # def: 1, 7, 8 - maybe:

# 10 clusters
sample_num_levels(vec_labeled, 27, 20) # def: 1, 3, 4     - maybe: 6
sample_num_levels(vec_labeled, 28, 20) # def: 3, 4, 7     - maybe: 9 
sample_num_levels(vec_labeled, 29, 20) # def: 2, 4, 5, 7  - maybe:
sample_num_levels(vec_labeled, 30, 20) # def: 1, 6, 8     - maybe: 4, 10
sample_num_levels(vec_labeled, 31, 20) # def: 4, 10       - maybe: 3

# 11 clusters
sample_num_levels(vec_labeled, 32, 20) # def: 2, 3, 6     - maybe: 1
sample_num_levels(vec_labeled, 33, 20) # def: 2, 7, 8, 9  - maybe:
sample_num_levels(vec_labeled, 34, 20) # def: 1, 2, 9     - maybe: 4, 5
sample_num_levels(vec_labeled, 35, 20) # def: 6, 7, 9     - maybe:
sample_num_levels(vec_labeled, 36, 20) # def: 5, 7, 8     - maybe:

# Implement this set logic into getting a decently labeled dataset ------------------

num_def_overlap <- 
  vec_labeled %>% 
  transmute(tweet_text = tweet_text,
            summy = apply(., 1, function(x) {sum(
  # 6 clusters
  x$k6_avg_vec_200 %in% c(1, 6), 
  x$k6_avg_vec_150 %in% c(1, 6), 
  x$k6_avg_vec_100 %in% c(2, 5),
  x$k6_avg_vec_50  %in% c(4, 5), 
  x$k6_avg_vec_25  %in% c(3, 6),

  # 7 clusters
  x$k7_avg_vec_200 %in% c(3), 
  x$k7_avg_vec_150 %in% c(3, 6), 
  x$k7_avg_vec_100 %in% c(1),
  x$k7_avg_vec_50  %in% c(2, 6), 
  x$k7_avg_vec_25  %in% c(5),

  # 8 clusters
  x$k8_avg_vec_200 %in% c(1, 4), 
  x$k8_avg_vec_150 %in% c(2, 3), 
  x$k8_avg_vec_100 %in% c(1, 3, 7),
  x$k8_avg_vec_50  %in% c(3, 4), 
  x$k8_avg_vec_25  %in% c(3),

  # 9 clusters
  x$k9_avg_vec_200 %in% c(6, 7, 8), 
  x$k9_avg_vec_150 %in% c(6, 7, 9), 
  x$k9_avg_vec_100 %in% c(4, 5, 7),
  x$k9_avg_vec_50  %in% c(5, 7, 8), 
  x$k9_avg_vec_25  %in% c(1, 7, 8),

  # 10 clusters
  x$k10_avg_vec_200 %in% c(1, 3, 4), 
  x$k10_avg_vec_150 %in% c(3, 4, 7), 
  x$k10_avg_vec_100 %in% c(2, 4, 5, 7),
  x$k10_avg_vec_50  %in% c(1, 6, 8), 
  x$k10_avg_vec_25  %in% c(4, 10),

  # 11 clusters
  x$k11_avg_vec_200 %in% c(2, 3, 6), 
  x$k11_avg_vec_150 %in% c(2, 7, 8, 9), 
  x$k11_avg_vec_100 %in% c(1, 2, 9),
  x$k11_avg_vec_50  %in% c(6, 7, 9), 
  x$k11_avg_vec_25  %in% c(5, 7, 8)
  )}))

# PLot the number of tweets within a group

hist(num_def_overlap$summy, xlim = c(1, 25), density = sapply(num_def_overlap$tweet_text, str_count, pattern = "\\S+"), breaks = 20)

ggplot(num_def_overlap, aes(x = summy)) +
  geom_density()

length(num_def_overlap[which(num_def_overlap$summy < 2),]$tweet_text) # 1037
sample_n(num_def_overlap[which(num_def_overlap$summy < 2),], 20) #

length(num_def_overlap[which(num_def_overlap$summy > 22),]$tweet_text) # 987
sample_n(num_def_overlap[which(num_def_overlap$summy > 22),], 20)

vec_labeled <- 
  vec_labeled %>% 
  mutate(
    # label a cluster group as probably containing most all complaints
    def_20 = ifelse(
      apply(., 1, function(x) {sum(
        # 6 clusters
        x$k6_avg_vec_200 %in% c(1, 6), 
        x$k6_avg_vec_150 %in% c(1, 6), 
        x$k6_avg_vec_100 %in% c(2, 5),
        x$k6_avg_vec_50  %in% c(4, 5), 
        x$k6_avg_vec_25  %in% c(3, 6),

        # 7 clusters
        x$k7_avg_vec_200 %in% c(3), 
        x$k7_avg_vec_150 %in% c(3, 6), 
        x$k7_avg_vec_100 %in% c(1),
        x$k7_avg_vec_50  %in% c(2, 6), 
        x$k7_avg_vec_25  %in% c(5),

        # 8 clusters
        x$k8_avg_vec_200 %in% c(1, 4), 
        x$k8_avg_vec_150 %in% c(2, 3), 
        x$k8_avg_vec_100 %in% c(1, 3, 7),
        x$k8_avg_vec_50  %in% c(3, 4), 
        x$k8_avg_vec_25  %in% c(3),

        # 9 clusters
        x$k9_avg_vec_200 %in% c(6, 7, 8), 
        x$k9_avg_vec_150 %in% c(6, 7, 9), 
        x$k9_avg_vec_100 %in% c(4, 5, 7),
        x$k9_avg_vec_50  %in% c(5, 7, 8), 
        x$k9_avg_vec_25  %in% c(1, 7, 8),

        # 10 clusters
        x$k10_avg_vec_200 %in% c(1, 3, 4), 
        x$k10_avg_vec_150 %in% c(3, 4, 7), 
        x$k10_avg_vec_100 %in% c(2, 4, 5, 7),
        x$k10_avg_vec_50  %in% c(1, 6, 8), 
        x$k10_avg_vec_25  %in% c(4, 10),

        # 11 clusters
        x$k11_avg_vec_200 %in% c(2, 3, 6), 
        x$k11_avg_vec_150 %in% c(2, 7, 8, 9), 
        x$k11_avg_vec_100 %in% c(1, 2, 9),
        x$k11_avg_vec_50  %in% c(6, 7, 9), 
        x$k11_avg_vec_25  %in% c(5, 7, 8)
      )}) > 20, TRUE, FALSE))

vec_labeled <- 
  vec_labeled %>% 
  mutate(
    # label a group as definitely not containing complaints
    def_not_0_1 = ifelse(
      apply(., 1, function(x) {sum(
        # 6 clusters
        x$k6_avg_vec_200 %in% c(1, 6), 
        x$k6_avg_vec_150 %in% c(1, 6), 
        x$k6_avg_vec_100 %in% c(2, 5),
        x$k6_avg_vec_50  %in% c(4, 5), 
        x$k6_avg_vec_25  %in% c(3, 6),

        # 7 clusters
        x$k7_avg_vec_200 %in% c(3), 
        x$k7_avg_vec_150 %in% c(3, 6), 
        x$k7_avg_vec_100 %in% c(1),
        x$k7_avg_vec_50  %in% c(2, 6), 
        x$k7_avg_vec_25  %in% c(5),

        # 8 clusters
        x$k8_avg_vec_200 %in% c(1, 4), 
        x$k8_avg_vec_150 %in% c(2, 3), 
        x$k8_avg_vec_100 %in% c(1, 3, 7),
        x$k8_avg_vec_50  %in% c(3, 4), 
        x$k8_avg_vec_25  %in% c(3),

        # 9 clusters
        x$k9_avg_vec_200 %in% c(6, 7, 8), 
        x$k9_avg_vec_150 %in% c(6, 7, 9), 
        x$k9_avg_vec_100 %in% c(4, 5, 7),
        x$k9_avg_vec_50  %in% c(5, 7, 8), 
        x$k9_avg_vec_25  %in% c(1, 7, 8),

        # 10 clusters
        x$k10_avg_vec_200 %in% c(1, 3, 4), 
        x$k10_avg_vec_150 %in% c(3, 4, 7), 
        x$k10_avg_vec_100 %in% c(2, 4, 5, 7),
        x$k10_avg_vec_50  %in% c(1, 6, 8), 
        x$k10_avg_vec_25  %in% c(4, 10),

        # 11 clusters
        x$k11_avg_vec_200 %in% c(2, 3, 6), 
        x$k11_avg_vec_150 %in% c(2, 7, 8, 9), 
        x$k11_avg_vec_100 %in% c(1, 2, 9),
        x$k11_avg_vec_50  %in% c(6, 7, 9), 
        x$k11_avg_vec_25  %in% c(5, 7, 8)
      )}) < 2, TRUE, FALSE))

vec_labeled <- 
  vec_labeled %>% 
  mutate(
    # label a group as definitely not containing complaints
    def_22 = ifelse(
      apply(., 1, function(x) {sum(
        # 6 clusters
        x$k6_avg_vec_200 %in% c(1, 6), 
        x$k6_avg_vec_150 %in% c(1, 6), 
        x$k6_avg_vec_100 %in% c(2, 5),
        x$k6_avg_vec_50  %in% c(4, 5), 
        x$k6_avg_vec_25  %in% c(3, 6),

        # 7 clusters
        x$k7_avg_vec_200 %in% c(3), 
        x$k7_avg_vec_150 %in% c(3, 6), 
        x$k7_avg_vec_100 %in% c(1),
        x$k7_avg_vec_50  %in% c(2, 6), 
        x$k7_avg_vec_25  %in% c(5),

        # 8 clusters
        x$k8_avg_vec_200 %in% c(1, 4), 
        x$k8_avg_vec_150 %in% c(2, 3), 
        x$k8_avg_vec_100 %in% c(1, 3, 7),
        x$k8_avg_vec_50  %in% c(3, 4), 
        x$k8_avg_vec_25  %in% c(3),

        # 9 clusters
        x$k9_avg_vec_200 %in% c(6, 7, 8), 
        x$k9_avg_vec_150 %in% c(6, 7, 9), 
        x$k9_avg_vec_100 %in% c(4, 5, 7),
        x$k9_avg_vec_50  %in% c(5, 7, 8), 
        x$k9_avg_vec_25  %in% c(1, 7, 8),

        # 10 clusters
        x$k10_avg_vec_200 %in% c(1, 3, 4), 
        x$k10_avg_vec_150 %in% c(3, 4, 7), 
        x$k10_avg_vec_100 %in% c(2, 4, 5, 7),
        x$k10_avg_vec_50  %in% c(1, 6, 8), 
        x$k10_avg_vec_25  %in% c(4, 10),

        # 11 clusters
        x$k11_avg_vec_200 %in% c(2, 3, 6), 
        x$k11_avg_vec_150 %in% c(2, 7, 8, 9), 
        x$k11_avg_vec_100 %in% c(1, 2, 9),
        x$k11_avg_vec_50  %in% c(6, 7, 9), 
        x$k11_avg_vec_25  %in% c(5, 7, 8)
      )}) > 22, TRUE, FALSE))

# write_csv(select(vec_labeled, tweet_text, def_20, def_not_0_1, def_22), "data/labeled_clusters_train_1.csv")

load("data/vectorized_tweet_sample_5k.dat")
labeled_clusters_train_1 <- read_csv("data/labeled_clusters_train_1.csv")
labels <- read_csv("data/Marketing Research Labeled Tweets_All.csv")

vec_labeled <- cbind(labeled_clusters_train_1, labels)[,-6]

vec_labeled %>% 
  filter(!is.na(label)) %>% 
  dplyr::group_by(def_20) %>% 
  dplyr::summarise(accuracy = sum(label)/sum(vec_labeled$label, na.rm = T))

vec_labeled %>% 
  filter(!is.na(label)) %>% 
  dplyr::group_by(def_22) %>% 
  dplyr::summarise(accuracy = sum(label)/sum(vec_labeled$label, na.rm = T))

vec_labeled %>% 
  filter(!is.na(label)) %>% 
  dplyr::group_by(def_not_0_1) %>% 
  dplyr::summarise(accuracy = sum(label)/sum(vec_labeled$label, na.rm = T))

vec_labeled %>% 
  filter(label == 1,
         def_not_0_1 == TRUE) %>%
  select(tweet_text)

vec_labeled[which(grepl("se niega a dejar", vec_labeled$tweet_text)),]$label

vec_labeled[which(grepl("se niega a dejar", vec_labeled$tweet_text)),]$label

labels[which(grepl("se niega a dejar", labels$tweet_text)),]$label

# plot correlations and proportions ---------------------------------------

labels <- read_csv("data/Marketing Research Labeled Tweets_All.csv")
load("data/vectorized_tweet_sample_5k.dat")

# correlation avg_vec_25 --------------------------------------------------

cor_data_25 <- 
  test_out %>% 
  select(tweet_text, avg_vec_25) %>% 
  unnest(avg_vec_25) %>% 
  filter(tweet_text != "") %>% 
  bind_cols(labels, .) %>% 
  select(-tweet_text1) %>% 
  filter(!is.na(label)) %>% 
  mutate(lebel = as.logical(label))

iplotCorr(cor_data_25[,-c(1,2)], cor_data_25$label, reorder=TRUE, chartOpts = list(scatcolors=c("lightblue", "lightgreen")))

# Contribution analysis ---------------------------------------------------
beta <- apply(cor_data_25[,-c(1,2)], 2, function(y,x) lm(y~x)$coef[2], cor_data_25$label)
pos <- which(beta > 0)
neg <- which(beta < 0)

iplotCorr(cor_data_25[,-c(1,2)], cor_data_25$label, rows=factor(pos), cols=factor(neg), reorder=TRUE)

# Correlation avg_vec_50 --------------------------------------------------

cor_data_50 <- 
  test_out %>% 
  dplyr::select(tweet_text, avg_vec_50) %>% 
  unnest(avg_vec_50) %>% 
  filter(tweet_text != "") %>% 
  bind_cols(labels, .) %>% 
  dplyr::select(-tweet_text1) %>% 
  filter(!is.na(label)) %>% 
  mutate(label = as.logical(label))

iplotCorr(cor_data_50[,-c(1,2)], cor_data_50$label, reorder=TRUE, chartOpts = list(scatcolors=c("lightblue", "lightgreen")))

lm(label ~ V8, data = cor_data_50)$coef[2]

# Contribution analysis ---------------------------------------------------

beta <- apply(cor_data_50[,-c(1,2)], 2, function(x,y) lm(y~x)$coef[2], cor_data_50$label)
pos <- which(beta > 0)
neg <- which(beta < 0)

iplotCorr(cor_data_50[,-c(1,2)], cor_data_50$label, rows=pos, cols=neg, reorder=TRUE)

# Looks like
mod1 <- glm(label ~ V2 + V10 + V2:V10, data = cor_data_50, family = "binomial")
mod2 <- glm(label ~ V2 + V10, data = cor_data_50, family = "binomial")
mod3 <- glm(label ~ V2*V10 + V11:V10 + V34:V48 + V11*V4 + V32, data = cor_data_50, family = "binomial")

mod3 <- glm(label ~ V12 + V34*V48 + V45 + V35 + V2, data = cor_data_50, family = "binomial")

summary(mod1)
summary(mod2)
summary(mod3)

## Test Cases
# tweet_text <- "@mcdo##naldsarabia @emirates @thedubaimall its really crazy, i'm argantina football fan and now i'm the argantini burger fan also 😍"
# tweet_text <- "vuelo d@e a@yer@@@@@ con @vueling??? vistas de!!!!! #acoruña #galicia http://t.co/60rqbl2nc8 http://t.co/60rqbl2nc8 http://t.co/60rqbl2nc8 http://t.co/60rqbl2nc8 http://t.co/60rqbl2nc8"

# featurize that shiz
cor_data_50_feat <- 
  cor_data_50 %>% 
  mutate(hashtags = str_count(tweet_text, "#"), # Count hashtags
         log_mentions = log1p(str_count(tweet_text, "@")), # Count user mentions
         log_links    = log1p(str_count(tweet_text, "http:\\/\\/t.co")), # count links
         question     = str_count(tweet_text, "\\?"), # count question marks 
         exclaim      = str_count(tweet_text, "!")) # count exclamation marks

mod4 <- glm(label ~ V2*V10 + V11:V10 + V34:V48 + V11*V4 + V32 + hashtags + log_mentions + log_links, data = cor_data_50_feat, family = "binomial")

mod5 <- glm(label ~ V12 + V34*V48 + V45 + V35 + V2 + log_mentions + log_links, data = cor_data_50_feat, family = "binomial")
summary(mod5)

accuracy <- list()
for(i in 1:100) {
  cor_data_50_feat_test_train <- 
    cor_data_50_feat %>% 
    mutate(train1 = rbinom(4959, 1, .7))

  mod5_train1 <- 
    cor_data_50_feat_test_train %>% 
    filter(train1 == 1) %>%
    glm(label ~ V12 + V34*V48 + V45 + V35 + V2 + log_mentions + log_links, data = ., family = "binomial")

  out <- cor_data_50_feat_test_train %>% 
    filter(train1 == 0) %>% 
    mutate(fitted = broom::augment(mod5_train1, newdata = ., type.predict = "response")$.fitted,
           fifty_class = if_else(fitted >= 0.5, TRUE, FALSE))

  accuracy[[i]] <- confusionMatrix(factor(as.numeric(out$fifty_class)), factor(as.numeric(out$label)), positive = NULL, dnn = c("Prediction", "Reference"))$overall[1]
}

mean(as.numeric(accuracy))
max(as.numeric(accuracy))
min(as.numeric(accuracy))

# a -----------------------------------------------------------------------

unnest(test_out, avg_vec_25)

cor_data_50_feat_test_train <- 
  cor_data_50_feat %>% 
  mutate(train1 = rbinom(4959, 1, .7))

which(cor_data_50_feat_test_train$train1 == 1)

which(cor_data_50_feat_test_train$train1 == 1)

unnest()

cor_data_50_feat_test_train %>% 
  filter(train1 == 1)

mod5_train1 <- 
  cor_data_50_feat_test_train %>% 
  filter(train1 == 1) %>%
  glm(label ~ V12 + V34*V48 + V45 + V35 + V2 + log_mentions + log_links, data = ., family = "binomial")

out <- cor_data_50_feat_test_train %>% 
  filter(train1 == 0) %>% 
  mutate(fitted = broom::augment(mod5_train1, newdata = ., type.predict = "response")$.fitted, 
         fifty_class = if_else(fitted >= 0.5, TRUE, FALSE))

confusionMatrix(factor(as.numeric(out$fifty_class)), factor(as.numeric(out$label)), positive = NULL, dnn = c("Prediction", "Reference"))$overall[1]

out %>%
  filter(fifty_class == FALSE, label == TRUE) %>% 
  select(tweet_text) %>% 
  sample_n(20)

clus_4_50_mod5_train1 <- kmeans(filter(out, fifty_class == TRUE)[,3:52], centers = 4, iter.max = 30, nstart = 15)

clustered_complaints_mod50_mod5_train1 <- 
  out %>%
  filter(fifty_class == TRUE) %>% 
  mutate(clus_4 = kmeans(.[,3:52], centers = 4, iter.max = 30, nstart = 15)$cluster,
         clus_3 = kmeans(.[,3:52], centers = 3, iter.max = 30, nstart = 15)$cluster,
         clus_2 = kmeans(.[,3:52], centers = 2, iter.max = 30, nstart = 15)$cluster)

clustered_complaints_mod50_mod5_train1 %>% 
  ggplot(aes(x = clus_4, fill = factor(clus_4))) +
  geom_bar()

clustered_complaints_mod50_mod5_train1 %>% 
  ggplot(aes(x = clus_3, fill = factor(clus_4))) +
  geom_bar()

clustered_complaints_mod50_mod5_train1 %>% 
  ggplot(aes(x = clus_2, fill = factor(clus_4))) +
  geom_bar()

clustered_complaints_mod50_mod5_train1 %>% 
  sample_num_levels(sample_col_num = 62, 20)

clustered_complaints <- 
  cor_data_50_feat %>% 
  filter(label == TRUE) %>% 
  transmute(tweet_text = tweet_text,
            clus_2 = kmeans(.[,3:52], centers = 2, iter.max = 30, nstart = 15)$cluster,
            clus_3 = kmeans(.[,3:52], centers = 3, iter.max = 30, nstart = 15)$cluster,
            clus_4 = kmeans(.[,3:52], centers = 4, iter.max = 30, nstart = 15)$cluster,
            clus_5 = kmeans(.[,3:52], centers = 5, iter.max = 30, nstart = 15)$cluster,
            clus_6 = kmeans(.[,3:52], centers = 6, iter.max = 30, nstart = 15)$cluster)

clustered_complaints %>% 
  sample_num_levels(value_col_num = 1, sample_col_num = 6, n = 20)

# Try to ascertain what complaint types we have ---------------------------
## We want to first create clusters that are defined by their distance from certain words
baggage_complaint_words <- c("bag", "luggage", "baggage", "suitcase", "lost", "clothes", "checked", "bags", "losing", "lose")
baggage_complaint_vec <- avg_word_vec(baggage_complaint_words, model50)
delay_complaint_words <- c("delay", "hour", "mechanical", "tarmac", "time", "minute", "cancelled", "announce", "layover")
delay_complaint_vec <- avg_word_vec(delay_complaint_words, model50)
service_complaint_words <- c("service", "customer", "relations", "dirty", "food", "minute", "rep", "phone", "attendant", "rude", "serve", "unprofessional")
service_complain_vec <- avg_word_vec(service_complaint_words, model50)
website_booking_complaint_words <- c("website", "internet", "online", "app", "book", "booking", "reservation", "ticket", "expensive")
website_booking_complaint_vec <- avg_word_vec(website_booking_complaint_words, model50)

labels <- read_csv("data/Marketing Research Labeled Tweets_All.csv")
load("data/vectorized_tweet_sample_5k.dat")

cor_data_50 <- 
  test_out %>% 
  dplyr::select(tweet_text, avg_vec_50) %>% 
  unnest(avg_vec_50) %>% 
  filter(tweet_text != "") %>% 
  bind_cols(labels, .) %>% 
  dplyr::select(-tweet_text1) %>% 
  filter(!is.na(label)) %>% 
  mutate(label = as.logical(label))

cor_data_50 <- 
  cor_data_50 %>% 
  mutate(bag_dist = map_dbl(tweet_text, function(text, vec, model) sqrt(sum((avg_word_vec(text, model)-vec)^2)), baggage_complaint_vec, model50),
         del_dist = map_dbl(tweet_text, function(text, vec, model) sqrt(sum((avg_word_vec(text, model)-vec)^2)), delay_complaint_vec, model50),
         srv_dist = map_dbl(tweet_text, function(text, vec, model) sqrt(sum((avg_word_vec(text, model)-vec)^2)), service_complain_vec, model50),
         web_dist = map_dbl(tweet_text, function(text, vec, model) sqrt(sum((avg_word_vec(text, model)-vec)^2)), website_booking_complaint_vec, model50),
         bag_dist_scale = scale(bag_dist),
         del_dist_scale = scale(del_dist),
         srv_dist_scale = scale(srv_dist),
         web_dist_scale = scale(web_dist))

cor_data_50_clus <- 
  cor_data_50 %>% 
  filter(label == 1) %>% 
  mutate(clus_2 = kmeans(.[,53:56], centers = 2, iter.max = 30, nstart = 15)$cluster,
         clus_3 = kmeans(.[,53:56], centers = 3, iter.max = 30, nstart = 15)$cluster,
         clus_4 = kmeans(.[,53:56], centers = 4, iter.max = 30, nstart = 15)$cluster,
         clus_5 = kmeans(.[,53:56], centers = 5, iter.max = 30, nstart = 15)$cluster,
         clus_6 = kmeans(.[,53:56], centers = 6, iter.max = 30, nstart = 15)$cluster,
         luggage = kmeans(.[,57], centers = 10, iter.max = 30, nstart = 15)$cluster,
         delays  = kmeans(.[,58], centers = 10, iter.max = 30, nstart = 15)$cluster,
         service = kmeans(.[,59], centers = 10, iter.max = 30, nstart = 15)$cluster,
         website = kmeans(.[,60], centers = 10, iter.max = 30, nstart = 15)$cluster)

cor_data_50_clus %>% 
  ggplot(aes(x = luggage, fill = factor(clus_2))) +
  geom_bar()

cor_data_50_clus %>%
  filter(label == 1) %>% 
  sample_num_levels(sample_col_num = 66)

cor_data_50_clus %>% 
  filter(label == 1) %>% 
  ggplot(aes(x = clus_2)) +
  geom_bar()

data(trees)
trees

# Test out principal components -------------------------------------------

cor_data_50.pr <- prcomp(as.matrix(cor_data_50[,3:52]))

PC_cor_data_50 <- as_data_frame(cor_data_50.pr$x)
PC_cor_data_50$label <- factor(cor_data_50$label)
PC_cor_data_50$tweet_text <- cor_data_50$tweet_text

plot_ly(PC_cor_data_50, x = ~PC1, y = ~PC2, z = ~PC3, color = ~label, colors = c('#BF382A', '#0C4B8E'),
        hoverinfo = 'text', text = ~tweet_text) %>% 
  add_markers() %>% 
  layout(scene = list(xaxis = list(title = 'PC1'),
                      yaxis = list(title = 'PC2'),
                      zaxis = list(title = 'PC3')))

scatterplot3d(cor_data_50.pr$x[,1:3], color = factor(cor_data_50$label))

plot(cor_data_50.pr$x[,1], col = factor(cor_data_50$label))

# create a test train pipeline

na_filtered_vec_lab_2 %>% 
  iplotCorr(unnest(.[,5]), .$label, reorder=TRUE)

```

### 2019-03-27 Code/dallin_code_annotations/11_predict_func.Rmd
Made a folder for annotating Adriel's Code named dallin_code_annotations. I am hoping that doing so will help me better understand the code/model created by Adriel.

---
title: "Predict Function"
output: github_document
---

# Overview
These are my annotations on the predict_func.R script written by Adriel.

```{r}
library(tidyverse)
library(fastrtext)
library(stringr)
library(tidytext)

# Testing Models ----------------------------------------------------------
# fasttext.model.50 <- load_model("models/fasttext/model50.dat.bin")
# fasttext.model.50_1 <- load_model("models/model50.dat.bin")
# load("models/prcomp/cor.data.50.pr")
# load("models/classifiers/logit_mod_0.856_acc")

# kTestComplaint <- "@jetblue why are your employees so rude today at dallas-fort worth? tons of attitude on simple questions. #notimpressed"
# kTestNonComplaint <- "@delta I love your service, it's always excellent"

# Featurization -----------------------------------------------------------

TweetFeatures <- function(tweet) {
  # Creates features from the tweet which are used for prediction
  # 
  # Args:
  #   tweet: a single tweet as a string
  # 
  # Returns:
  #   a single-row tibble with the following columns: log.links, log.mentions, count.char, count.space
  tibble(tweet.text = tweet) %>%
    mutate(count.char   = nchar(tweet.text),
           log.mentions = log1p(str_count(tweet.text, "@")), # Count user mentions
           log.links    = log1p(str_count(tweet.text, "http:\\/\\/t.co")), # count links
           count.space  = str_count(tweet.text, " ")) %>% # count exclamation marks
    select(-tweet.text)
}

# Label Prediction -------------------------------------------------------

predict.TweetComplaintPredictor <- function(object, newdata, complaintCutoff = 0) {
  # Given a character vector containing tweets to predict for, this function returns predicted labels for the given tweet.
  #
  # Args:
  #   object: TweetComplaintPredictor model
  #   newdata: A character vector containing tweets  
  #   complaintCutoff: a numeric value specifying the cutoff value for the xgb prediction output 
  #       when considering what value to use to consider a tweet a complaint.
  #
  # Returns:
  #   a string label. Either "Complaint" or "Non-Complaint"
  #

  newdata %>% 
    tibble(tweetText = .) %>% 
    mutate(tweetFeatures = map(tweetText, TweetFeatures)) %>% 
    mutate(fasttextVec = map(tweetText, VectorizeTweet, object$fasttextModel)) %>% 
    mutate(pcaVec = map(fasttextVec, VectorizeTweet, object$pcaModel, object$pcaModelComponentCutoff)) %>% 
    unnest %>% 
    select(-tweetText) %>% 
    sparse.model.matrix(~.-1, .) %>% 
    xgb.DMatrix %>% 
    predict(object$xgbModel, .) %>% 
    map_chr(function(x) ifelse(x > complaintCutoff, "Complaint", "Non-Complaint"))
}

VectorizeTweet <- function(tweet, model, ...) UseMethod("VectorizeTweet", model)

VectorizeTweet.Rcpp_fastrtext <- function(tweet, model, ...) {
  # Computes the word embedding vector for each word in a sentence and then averages them into a single vector
  #
  # Args:
  #   tweet: a single tweet as a string
  #   model: a trained fasttext model used to compute the word embedding vectors
  # 
  # Returns:
  #   a single-row tibble with each embedding vector element as a column. The number of rows is
  #   defined by the dim parameter that was used to train the input fasttext model
  #
  # tokenize the text, return a list of tokens
  tokens <- strsplit(tweet, " ")[[1]]
  # apply get_word_vectors to each token in the vector, return tibble of word vecs, one row for each word
  word.vec.tbl <- tbl_df(get_word_vectors(model, tokens))
  # summarise the word vector tibble into one average tibble
  summarise_all(word.vec.tbl, funs(mean), na.rm = TRUE)
}

VectorizeTweet.prcomp <- function(tweet, model, component, ...) {
  # Computes the principal components from the embedding vectors and returns the first 6
  #
  # Args:
  #   df: a tibble of word embedding vectors
  #   prcomp.mod: a trained prcomp model used to compute principal components of the word embedding vectors
  # 
  # Returns:
  #   a single-row tibble with N principal component variables
  #
  # error handling: embedding vector must be of length 50

  predict(model, newdata = tweet) %>% 
    as_tibble() %>% 
    select(PC1:!!component)
}
```

### 2019-03-27 Code/dallin_code_annotations/12_tweet_complaint_predictor.Rmd
Made a folder for annotating Adriel's Code named dallin_code_annotations. I am hoping that doing so will help me better understand the code/model created by Adriel.

---
title: "Tweet Complaint Predictor"
output: github_document
---

# Overview
These are my annotations on the "TweetComplaintPredictor.r" script written by Adriel

```{r}
# TweetComplaintPredictor class constructor ----------------------------------------
# Class constructor 
newTweetComplaintPredictor <- function(fasttextModel, pcaModel, xgbModel, pcaModelComponentCutoff) {
  component <- enquo(pcaModelComponentCutoff)

  if(class(fasttextModel)[1] != "Rcpp_fastrtext"){
    stop("fasttextModel is not a member of class Rcpp_fastrtext")
  }
  if(class(pcaModel) != "prcomp"){
    stop("pcaModel is not a member of class Rcpp_fastrtext")
  }
  if(class(xgbModel) != "xgb.Booster"){
    stop("xgbModel is not a member of class Rcpp_fastrtext")
  }

  newTweetComplaintPredictor <- list(fasttextModel = fasttextModel,
                                     pcaModel = pcaModel,
                                     xgbModel = xgbModel,
                                     pcaModelComponentCutoff = component)

  class(newTweetComplaintPredictor) <- "TweetComplaintPredictor"

  return(newTweetComplaintPredictor)
}

# Class checker
is.TweetComplaintPredictor <- function(x) inherits(x, "TweetComplaintPredictor")

```

### 2019-03-27 Code/dallin_code_annotations/README.Rmd
Made a folder for annotating Adriel's Code named dallin_code_annotations. I am hoping that doing so will help me better understand the code/model created by Adriel.

---
title: "README"
output: github_document
---
# Dallin Code Annotations
In this folder, I will keep all of my .rmd documents. Some of them will be created by me, but most will take Adriel's code in other folders and annotate it. I hope that by doing so, I will better understand his code, and be able to contribute more to writing the paper on our reasearch. Additionally, I hope these annotations help future RA's understand the code as well.

The numbering of the files is an attempt to be consistent with the tidyverse style guide section 1.1 (found at https://style.tidyverse.org/). As I work more with the code, I will do my best to ensure that the numbering reflects a logical flow for the code.

If the documents only contain a single, massive block of code, this means that I haven't gotten around to annotating that script.

### 2019-03-27 Code/cnn-classifier/R/fasttext_supervised_classifier.R

@@ -4,27 +4,30 @@ library(tidyverse)
 # Prepare data ------------------------------------------------------------
 
 # Create file location where the model will be written to
-file_model <- "models/class_mod_1.dat"
-train_data <- "data/train_data_1.txt"
-test_data <- "data/test_data_1.txt"
+# Dallin Note: Throughout this script, I've adjusted file paths to make them run well on my computer
+file_model <- "Temporary/train_test_data/class_mod_1.dat"
+train_data <- "Temporary/train_test_data/train_data_1.txt"
+test_data <- "Temporary/train_test_data/test_data_1.txt"
 
 # read in the data
-tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>% 
+# tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>% 
+#   filter(nchar(tweet_text) > 5)
+
+# Dallin Note: For my purposes, I'll edit the code directly above and adjust it for my computer
+tweet_data <- read_csv("Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv") %>%
   filter(nchar(tweet_text) > 5)
 
 # format the data to fasttext input requirements
-test_train_data <- 
-  tweet_data %>% 
-  mutate(label = case_when(label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
-                              label == 1 ~ "complaint"),
-            input_lines = paste(label, tweet_text)) %>% 
+test_train_data <- tweet_data %>% 
+  mutate(label = case_when(complaint_label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
+                           complaint_label == 1 ~ "complaint"),
+         input_lines = paste(label, tweet_text)) %>% 
   group_by(label) %>% # get a representative sample of both complaints and non complaints
   mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
   ungroup()
 
 # write train data
-train_data_lines <- 
-  test_train_data %>% 
+train_data_lines <- test_train_data %>% 
   filter(test_train == "train") %>% 
   pull(input_lines) %>% 
   paste0("__label__", .)
@@ -32,8 +35,7 @@ train_data_lines <-
 write_lines(train_data_lines, train_data)
 
 # write test data
[…]

### 2019-03-27 Code/complaint-prediction/R/TweetComplaintPredictor.r

@@ -25,3 +25,5 @@ newTweetComplaintPredictor <- function(fasttextModel, pcaModel, xgbModel, pcaMod
 
 # Class checker
 is.TweetComplaintPredictor <- function(x) inherits(x, "TweetComplaintPredictor")
+
+

### 2019-03-27 Code/complaint-prediction/R/logit_regression_classifier_Best.R

@@ -1,8 +1,8 @@
 library(tidyverse)
 library(qtlcharts)
 library(caret)
-source("R/clus_func.R")
-source("R/logit_classifier_func.R")
+source("Code/complaint-prediction/R/clus_func.R")
+source("Code/complaint-prediction/R/logit_classifier_func.R")
 
 # read in labeled data ----------------------------------------------------
 

### 2019-03-27 Code/dallin_annotations/04_test_rds_connection.Rmd
Wrote more on the test_rds_connection.

---
title: "Test RDS Connection"
output: github_document
---
# Overview
In this document, I will be annotating the code written by Adriel in the script "TestRDSConnection.R."

##### What I understand:
RDS stands for R Data Server. This script helps us log into the RDS and extract the twitter data.

# Libraries
```{r}
library(RPostgreSQL)
library(dbplyr)
library(tidyverse)
```

# Connect to RDS
This code helps us connect to the server and lost the data tables held inside. Our database is apparently a Postgre database
```{r}
# Load drivers to communicate with RDS
drv <- dbDriver("PostgreSQL")
con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
                 user = "adrielc", password = "byuanalytics58") # This will prompt user

# List all tables available within the database
dbListTables(con)
```

### Extract the Data
With the code chunk above, we were able to see the data tables listed in the server. The dataframe we are interested in is called "Cockroaches." We will find that table and save our connection to that dataframe. This will make it easy for us to wrangle the data on the server before it arrives on our laptop. This will be advantageous because the server will likely have more computing power than our laptops.
```{r}
# Create tbl object to reference the table serverside when pulling data
Cockroaches <- tbl(con, "Cockroaches")
```

### Pull Data Sample
Now we will use our connection to wrangle and save the data to our computer.
```{r}
# Get Tweet text for the first 1,500,000 tweets in the DB. Remove retweets (there's a lot)
sample_tweets <- Cockroaches %>% 
  filter(substr(tweet_text, 1, 4) != "RT @") %>% 
  select(tweet_text) %>% 
  head(1500000) %>% 
  mutate(tweet_text = tolower(tweet_text)) %>%
  collect() # all the processing is done server side before being pulled in by collect()
```

### Write Tweets to a .txt File
Now that we have wrangled the data and saved it as an object in our environment, we want to use the write_lines() function to save this data file as a .txt file.
```{r}
# Pull Data Sample --------------------------------------------------------
# Once tweets are pulled in, write the lines to a file.
sample_tweets %>%
  .$tweet_text %>% 
  write_lines("Output/clean_data/tweet_sample_1hM_noRT.txt")
```

# Disconnect
It is always important do sever your connection to a database after you use it. 
```{r}
DBI::dbDisconnect(con)
```

### 2019-03-27 Code/dallin_annotations/08_classifier_construction.Rmd
Wrote more on the test_rds_connection.

---
title: "Classifier Construction"
output: github_document
---

# Overview
These are my annotations of the "classifier-construction.R" script written by Adriel.

```{r}
library(tidyverse)
library(fastrtext)
library(magrittr) # for assignment operator %<>% 
library(plotly)
require(randomForest)
library(Matrix)
source("R/clus_func.R")
source("R/logit_classifier_func.R")

library(xgboost)
library(caret)
library(car)

set.seed(123)

# Fasttext train ----------------------------------------------------------

# train unsupervised fasttext model to learn tweet semantics and word vector representations

# file to read tweets from. Should be a txt file with one tweet per line
file_txt <- "data/tweet_sample_2M_noRT.txt"

# new file to write the trained model to
file_model50  <- "models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat"

# train the unsupervised fasttext model
#fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))

# load the model object we just trained
fasttext_model <- load_model(file_model50)

# Fasttext model evaluation -----------------------------------------------

# Examine the nearest neighbors returned by our trained model. 
# First vector element is the word to look up NN, and the second is a string used to filter the results

nn_words  <- list(c("mad", "mad"),
                  c("sad","sad"),
                  c("upset", "upset"),
                  c("late", "ate"),
                  c("delay", "del"),
                  c("cancelled", "cancel"),
                  c("snow", "snow"),
                  c("rain", "rain"),
                  c("weather", "weather"))

map(nn_words, function(x) model_eval_plot_wrap(x[1], fasttext_model, filter_str = x[2], n = 20))

# Predict and average word vectors for tweets -----------------------------

# read in labeled traing data
train <- read_csv("data/Marketing Research Labeled Tweets All 12-05-18.csv")

# Add extracted text features to the dataset ------------------------------

train %<>% 
  mutate(tweetFeatures = map(tweet_text, TweetFeatures))

# create a list column that contains all of features output by the fasttext model
train %<>% 
  mutate(avg_vec_50 = map(tweet_text, VectorizeTweet, model = fasttext_model))

# PCA on fasttext vectors -------------------------------------------------

# select the average vector column and perform a PCA
train.pr <- train %>%
  select(avg_vec_50) %>% 
  unnest(avg_vec_50) %>% 
  as.matrix() %>% 
  prcomp()

# create a dataframe with the pca output to examine the first 3 components

pca_evaluation <- as_data_frame(train.pr$x)
pca_evaluation$label <- factor(train$complaint_label)
pca_evaluation$tweet_text <- train$tweet_text

# evalute the first three components with a 3d plot

plot_ly(pca_evaluation, x = ~PC1, y = ~PC2, z = ~PC3, color = ~label, colors = c('#BF382A', '#0C4B8E'),
        hoverinfo = 'text', text = ~tweet_text) %>% 
  add_markers() %>% 
  layout(scene = list(xaxis = list(title = 'PC1'),
                      yaxis = list(title = 'PC2'),
                      zaxis = list(title = 'PC3')))

# looks good to me. The complaints seperate well.

# make a scree plot of the components
screeplot(train.pr, type = "line", npcs = 20)

# the first component must be the amount of information about a word learned by the fasttext model
# let's go with 15 components with this model.

# Project word vectors onto PCA -------------------------------------------

train %<>% 
  mutate(avg_vec_50_PCA = map(avg_vec_50, VectorizeTweet, model = train.pr, component = PC4))

save(train.pr, file = "models/fullClassifierOne/prcomp4.dat")

save(train, file = "models/fullClassifierOne/train_data.dat")

rm(list = ls())

load("models/fullClassifierOne/train_data.dat")

trainIndex <- createDataPartition(train$complaint_label, p = .8, 
                                  list = FALSE, 
                                  times = 1)

test_data <- train[-trainIndex,]
test_labels <- test_data %>% select(complaint_label) %>% transmute(label = complaint_label)
train_data <- train[trainIndex,]
train_labels <- train_data %>% select(complaint_label) %>% transmute(label = complaint_label)
train_data_vec <- train_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)
test_data_vec <- test_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)

dtrain <- xgb.DMatrix(sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label))
dtest <- xgb.DMatrix(sparse.model.matrix(~.-1, test_data_vec), label = as.numeric(test_labels$label))
dtest1 <- xgb.DMatrix(sparse.model.matrix(~.-1, test_data_vec))
watchlist <- list(train = dtrain, eval = dtest)

logregobj <- function(preds, dtrain) {
  labels <- getinfo(dtrain, "label")
  preds <- 1/(1 + exp(-preds))
  grad <- preds - labels
  hess <- preds * (1 - preds)
  return(list(grad = grad, hess = hess))
}

evalerror <- function(preds, dtrain) {
  labels <- getinfo(dtrain, "label")
  err <- as.numeric(sum(labels != (preds > 0)))/length(labels)
  return(list(metric = "error", value = err))
}

param <- list(max_depth = 2, eta = 1, silent = 1, nthread = 2, 
              objective = logregobj, eval_metric = evalerror)

bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label), max.depth = 4,
               eta = 0.2, nthread = 2, nrounds = 100, objective = logregobj, eval_metric = evalerror)

test_data$prediction <- predict(bst, dtest1)

predict(bst, dtest1) %>% map_chr(function(x) ifelse(x > 0, "complaint", "non-complaint"))

test_data %<>%
  mutate(predict_label = case_when(prediction > 0 ~ "Complaint",
                                   TRUE ~ "Non-complaint"),
         complaint_label = case_when(complaint_label == 1 ~ "Complaint",
                                   TRUE ~ "Non-complaint")) %>% 
  mutate(accuracy = predict_label == complaint_label)

confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))

save(bst, file = "models/fullClassifierOne/xgb.modelPC4.dat")
xgb.save(bst, 'models/fullClassifierOne/xgb.modelPC4-xgb_version.dat')
save(test_data, file = "models/fullClassifierOne/test_data.dat")

```

### 2019-03-27 Code/dallin_annotations/14_classifier_testing.Rmd
Wrote more on the test_rds_connection.

---
title: "Classifier Testing"
output: github_document
---
# Overview
These are my annotations to the "classifier-testing.R" script written by Adriel.

```{r}
library(fastrtext)
library(Matrix)
library(xgboost)
source("R/predict_func.R")
source("R/TweetComplaintPredictor.r")

load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat")
TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)

predict(TweetComplaintPredictor, "")
```

### 2019-03-27 Code/dallin_annotations/15_json_parse_upload.Rmd
Wrote more on the test_rds_connection.

---
title: "Untitled"
output: github_document
---

# Overview
These are my annotations to the "Json_parse_upload.R" script written by Adriel.

```{r}
library(RPostgreSQL)
library(dbplyr)
library(rjson)
library(RCurl)
library(tidyverse)

# create_df(): ----------------------------------------------------------------
### This function creates one row of a dataframe from a JSON object. This row can be uploaded to a database

create_df <- function(data)
{
  tibble(
    tweet_created_at = null_to_na(data$created_at),
    tweet_id = null_to_na(data$id_str),
    tweet_text = null_to_na(data$text),
    in_reply_to_status_id_str = null_to_na(data$in_reply_to_status_id_str),
    in_reply_to_user_id_str = null_to_na(data$in_reply_to_user_id_str),
    in_reply_to_screen_name = null_to_na(data$in_reply_to_screen_name),
    usr_name = null_to_na(data$user$name),
    usr_screen_name = null_to_na(data$user$screen_name),
    usr_url = null_to_na(data$user$url),
    usr_description = null_to_na(data$user$description),
    usr_protected = null_to_na(data$user$protected),
    usr_followers_count = null_to_na(data$user$followers_count),
    usr_friends_count = null_to_na(data$user$friends_count),
    usr_listed_count = null_to_na(data$user$listed_count),
    usr_created_at = null_to_na(data$user$created_at),
    usr_statuses_count = null_to_na(data$user$statuses_count),
    usr_verified = null_to_na(data$user$verified),
    coordinates = null_to_na(data$coordinates),
    tweet_retweet_count_at_pull_time = null_to_na(data$retweet_count),
    tweet_favorite_count_at_pull_time = null_to_na(data$favorite_count),
    tweet_hastags = null_to_na(data$entities$hashtags),
    tweet_symbols = null_to_na(data$entities$symbols),
    tweet_urls = null_to_na(data$entities$urls),
    tweet_user_mentions = null_to_na(data$entities$user_mentions),
    tweet_sentiment = null_to_na(data$sentiment),
    date = null_to_na(data$date$`$date`),
    oid = null_to_na(data$`_id`$`$oid`)
  )
}

null_to_na <- function(x) ifelse(is.null(x), NA, x)

# data import and upload --------------------------------------------------

raw_data <- "data/tweetsFINAL.json"

data <- fromJSON(sprintf("[%s]", paste(readLines(raw_data, n = 1000),collapse=",")))

out <- map_dfr(data, create_df)

# data_upload -------------------------------------------------------------

# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL")
# creates a connection to the postgres database
# note that "con" will be used later in each connection to the database
con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
                 user = "adrielc", password = "byuanalytics58") # This will prompt user

dataUpload <- read_csv("../DataAcquisitionProject/Nielsen Retail Fact Data.csv")

dbListTables(con)

```

### 2019-03-29 Code/dallin_annotations/08_classifier_construction.Rmd
Updated the documents in dallin_annotations.

@@
 
+# Libraries
 ```{r}
@@
 set.seed(123)
+```
 
+##### Look at working directory
+```{r}
+getwd()
+```
+
+# Train and Load the fastText Model
+Unsupervised fastText models produce word vectors. In other words, the create a mathmatical representation of the word. 
+```{r}
 # Fasttext train ----------------------------------------------------------
-
 # train unsupervised fasttext model to learn tweet semantics and word vector representations
@@
 # file to read tweets from. Should be a txt file with one tweet per line
-file_txt <- "data/tweet_sample_2M_noRT.txt"
+file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"
 
 # new file to write the trained model to
-file_model50  <- "models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat"
+file_model50  <- "../../Temporary/model50-tweet_sample_2M_noRT.dat"
 
@@
 fasttext_model <- load_model(file_model50)
+```
 
+```{r}
 # Fasttext model evaluation -----------------------------------------------

### 2019-03-29 Code/dallin_annotations/16_classifier_testing.Rmd
Updated the documents in dallin_annotations.

---
title: "Classifier Testing"
output: github_document
---
# Overview
These are my annotations to the "classifier-testing.R" script written by Adriel.

This document loads the model, and uses a predict function to test the model on new test tweets. We can see how the model will respond to tweets we find on the internet as well as tweets we make up ourselves.

### What scripts need to function for this code to work?
predict_func.R
* Renamed as 11_predict_func.Rmd
* NOT WORKING

TweetComplaintPredictor.r
* Renamed as 12_tweet_complaint_predictor.Rmd
* NOT WORKING

### Which models need to be loaded for this code to work?
prccomp4.dat 
* I think this is the PCR model
* NOT FOUND

model50-tweet_sample_2M_noRT.dat.bin 
* It looks like this is a fasttext model, but I'm not sure if it is the supervised or unsupervised.
* NOT FOUND

xgb.modelPC4.dat
* This must be the xg boost model that brings the sub-models together.
* NOT FOUND

```{r}
library(fastrtext)
library(Matrix)
library(xgboost)
source("11_predict_func.Rmd") # Formerly "R/predict_func.R" in Adriel's original code
source("tweet_complaint_predictor.Rmd") # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code

load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat")
TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)

predict(TweetComplaintPredictor, "")
```

### 2019-03-29 Code/dallin_annotations/README.Rmd
Wrote more on the test_rds_connection.
Wrote brief summaries on a few of the files in the dallin_annotations folder.

--- 2019-03-27 Code/dallin_code_annotations/README.Rmd
@@
 ---
-# Dallin Code Annotations
+# Dallin Annotations
 In this folder, I will keep all of my .rmd documents.
@@
 If the documents only contain a single, massive block of code, this means that I haven't gotten around to annotating that script.
+
+Below, I have a quick and brief documentation of what I understand about each file.
+
+# Overview of Files
+
+### 01_analyze_complaint_categories.Rmd
+This file analyzes our train/test dataset, documents the label types, visualizes the number of complaints to non-complaints, and visualizes the number of each complaint category.
+Additionally, it runs a tf_idf analysis on the catch-all complaint category to see if another category can be identified.
+
+### 02_create_clustering_function.Rmd
+
+### 03_build_fasttext_classification_model.Rmd
+In this file, I create my own fastText supervised classification model to see how well it can classify on its own (i.e. without the help of a PCA and XGBoost model).
+
+Note: Code still has a few places it needs to be tweaked and isn't fully funcitonal yet--I need to write the .txt files and figure out how to make predictions with the trained model.
+
+### 04_test_rds_connection.Rmd
+This file contains the credentials necessary to log into the R Data Server. It also has brief code for extracting some of the tweets from the database, and it writes the data to a .txt file.
+
+### 05_counting_cockroaches.Rmd
+This file takes airline twitter data and creates a few visualizations (i.e. wordclouds) on the tweet text.
+
+### 06_tweet_object.Rmd
+
+### 07_fasttext_supervised_classifier.Rmd
+This file documents the building of our fastText supervised classifier model.
+
+### 08_classifier_construction.Rmd
+
+### 09_fasttext_clust_EDA.Rmd
+
+### 10_logit_regression_classifier.Rmd
+
+### 11_predict_func.Rmd
+
+### 12_tweet_complaint_predictor.Rmd
+
+### 13_batch_classification.Rmd
+
+### 14_read_tweets_json.Rmd
+
+### 15_json_parse_upload.Rmd
+
+### 16_classifier_testing.Rmd
+This file references the full model, and makes predictions on single tweets. You can use it to see how the model will react with tweets you find online, as well as tweets you write yourself.

### 2019-03-29 Code/dallin_annotations/16_classifier_testing.Rmd
Updated the 16_classifier_testing file.

@@
 ### What scripts need to function for this code to work?
-predict_func.R
-* Renamed as 11_predict_func.Rmd
+##### predict_func.R
+* Renamed as 11_predict_func.Rmd in this folder.
 * NOT WORKING
 
-TweetComplaintPredictor.r
-* Renamed as 12_tweet_complaint_predictor.Rmd
+##### TweetComplaintPredictor.r
+* Renamed as 12_tweet_complaint_predictor.Rmd in this folder.
 * NOT WORKING
@@
 ### Which models need to be loaded for this code to work?
-prccomp4.dat 
-* I think this is the PCR model
-* NOT FOUND
+##### prcomp4.dat 
+* I think this is the PCR model (pr[inciple]comp[onent].dat?)
+* FOUND in Code/complaint-prediction/models/fullClassifierOne/prcomp.dat, as stated in the code.
+* I moved the file to the /Temporary folder
 
-model50-tweet_sample_2M_noRT.dat.bin 
+##### model50-tweet_sample_2M_noRT.dat.bin 
 * It looks like this is a fasttext model, but I'm not sure if it is the supervised or unsupervised.
@@
 
-xgb.modelPC4.dat
+##### xgb.modelPC4.dat
 * This must be the xg boost model that brings the sub-models together.
-* NOT FOUND
+* FOUND in Code/complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat, as stated in the code.
+* Moved to the /Temporary Folder
 
+# Libraries
 ```{r}
@@
 source("tweet_complaint_predictor.Rmd") # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
+```
 
-load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
+##### Reminder of the WD
+```{r}
+getwd()
+```
+
+# Load Models
+```{r}
+load("../../Temporary/prcomp4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
 fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
-load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat")
+load("../../Temporary/xgb.modelPC4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat" in Adriel's original code
 TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)
 
+```
+
+# Test Classifier
+Using this predict() function, we can make predictions about single tweets. All you have to do is type your tweet in the quotations for the second argument. 
+```{r}
 predict(TweetComplaintPredictor, "")
+
 ```

### 2019-04-09 Code/dallin_annotations/02_create_clustering_function.Rmd
More documentation and troubleshooting.

--- 2019-03-27 Code/dallin_code_annotations/02_create_clustering_function.Rmd
@@
 
-### Code I don't understand
+### Code I don't understand, other than that it is a list of many functions created. 
+The functions are: nn_filter, model_eval, GetDotObjectNames, model_eval_plot, model_eval_plot_wrap, and wss_func.
 ```{r}

### 2019-04-09 Code/dallin_annotations/08_classifier_construction.Rmd
More documentation and troubleshooting.

@@
 These are my annotations of the "classifier-construction.R" script written by Adriel.
+
+This file is extremely important because it is where Adriel built the "frankenstein" model.
+
+Here are two important models built by this script:
+model50-tweet_sample_2M_noRT.dat
+xgb.modelPC4-xgb_version.dat
 
@@
 library(Matrix)
-source("R/clus_func.R")
-source("R/logit_classifier_func.R")
+source("../complaint-prediction/R/clus_func.R")
+# source("../complaint-prediction/R/logit_classifier_func.R") This file does not exist
+
+# source("02_create_clusteringifunction.Rmd") New files not yet
 
@@
 # file to read tweets from. Should be a txt file with one tweet per line
-file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"
+# file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"
+file_txt <- "../../Temporary/tweet_sample_1hM_noRT.txt"
 
@@
 # train the unsupervised fasttext model
-#fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
+# fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
 
@@
 # read in labeled traing data
-train <- read_csv("data/Marketing Research Labeled Tweets All 12-05-18.csv")
+train <- read_csv("../../Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")
 
@@
 
-train %<>% 
+train <- train %>% 
   mutate(tweetFeatures = map(tweet_text, TweetFeatures))
@@
 # create a list column that contains all of features output by the fasttext model
-train %<>% 
+train <- train %>%
   mutate(avg_vec_50 = map(tweet_text, VectorizeTweet, model = fasttext_model))

### 2019-04-09 Code/dallin_annotations/09_fasttext_clust_EDA.Rmd
More documentation and troubleshooting.

--- 2019-03-27 Code/dallin_code_annotations/09_fasttext_clust_EDA.Rmd
@@
 library(dbplyr)
-source("Code/complaint-prediction/R/clus_func.R")
+source("../complaint-prediction/R/clus_func.R")
 
@@
 
+getwd()
+
 sample_tweets %>%
   .$tweet_text %>% 
-  write_lines("data/tweet_sample_1mil.txt")
+  write_lines("../../Temporary/tweet_sample_1mil.txt")
 
@@
   .$tweet_text %>%
-  write_lines("data/tweet_sample_1hM_noRT.txt")
+  write_lines("../../Temporary/tweet_sample_1hM_noRT.txt")
 rm(sample_tweets) # After writing the .txt files, we are removing them from the environment with the rm() function
@@
   .$tweet_text %>%
-  write_lines("data/tweet_sample_2M_noRT.txt")
+  write_lines("../../Temporary/tweet_sample_2M_noRT.txt")
 rm(sample_tweets)
@@
 
-file_txt <- "data/tweet_sample_1hM_noRT.txt"
+file_txt <- "../../Temporary/tweet_sample_1hM_noRT.txt"
 
-file_model200 <- "data/models/model200.dat"
-file_model150 <- "data/models/model150.dat"
-file_model100 <- "data/models/model100.dat"
-file_model50  <- "data/models/model50.dat"
-file_model25  <- "data/models/mode25.dat"
+file_model200 <- "../../Temporary/model200.dat"
+file_model150 <- "../../Temporary/model150.dat"
+file_model100 <- "../../Temporary/model100.dat"
+file_model50  <- "../../Temporary/model50.dat"
+file_model25  <- "../../Temporary/mode25.dat"
 
- execute(commands = c("cbow", "-input", file_txt, "-output", file_model200, "-verbose", 1, "-dim", 200))
+ # execute(commands = c("cbow", "-input", file_txt, "-output", file_model200, "-verbose", 1, "-dim", 200))
 model200 <- load_model(file_model200)
 
- execute(commands = c("cbow", "-input", file_txt, "-output", file_model150, "-verbose", 1, "-dim", 150))
+ # execute(commands = c("cbow", "-input", file_txt, "-output", file_model150, "-verbose", 4, "-dim", 150))
 model150 <- load_model(file_model150)
 
- execute(commands = c("cbow", "-input", file_txt, "-output", file_model100, "-verbose", 1, "-dim", 100))
+ # execute(commands = c("cbow", "-input", file_txt, "-output", file_model100, "-verbose", 4, "-dim", 100))
 model100 <- load_model(file_model100)
 
- execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
+ # execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 4, "-dim", 50))
 model50 <- load_model(file_model50)
 
- execute(commands = c("cbow", "-input", file_txt, "-output", file_model25, "-verbose", 1, "-dim", 25))
+ # execute(commands = c("cbow", "-input", file_txt, "-output", file_model25, "-verbose", 4, "-dim", 25))
 model25 <- load_model(file_model25)
@@
 sample_tweets <- 
-  read_lines("data/tweet_sample_1hM_noRT.txt") %>% 
-  tibble(tweet_text)
+  read_lines("../../Temporary/tweet_sample_1hM_noRT.txt") %>% 
+  tibble(tweet_text = .)
 

### 2019-04-09 Code/dallin_annotations/README.Rmd
More documentation and troubleshooting.

@@
 ### 08_classifier_construction.Rmd
+This document contains the code that builds models referenced in other files, namely the model50-tweet_sample_2M_noRT.dat and xgb.modelPC4-xgb_version.dat
 
@@
 ### 11_predict_func.Rmd
+This file contains a lot of useful functions for our model, such as the VectorizeTweet function.
 
 ### 12_tweet_complaint_predictor.Rmd
+tweet_complaint_predictor.Rmd builds a function named newTweetComplaintPredictor, which is referenced in serveral other scripts.
 
@@
 This file references the full model, and makes predictions on single tweets. You can use it to see how the model will react with tweets you find online, as well as tweets you write yourself.
+
+Note: I can't seem to find the logit_classifier_func.R file anywhere. It's referenced in classifier_construction.R

### 2019-04-09 Code/complaint-prediction/R/classifier-construction.R

@@ -4,9 +4,11 @@ library(magrittr) # for assignment operator %<>%
 library(plotly)
 require(randomForest)
 library(Matrix)
-source("R/clus_func.R")
-source("R/logit_classifier_func.R")
+source("Code/complaint-prediction/R/clus_func.R")
+# source("Code/complaint-prediction/R/logit_classifier_func.R") # NOT FOUND. Where is this file?
 
+source("Code/complaint-prediction/R/predict_func.R") # Dallin added this code.
+ 
 
 library(xgboost)
 library(caret)
@@ -14,23 +16,31 @@ library(car)
 
 set.seed(123)
 
+getwd()
+
 
 # Fasttext train ----------------------------------------------------------
-
+# Dallin: In this block, we train the fasttext unsupervised model. This model analyzes the strength of associations 
+# between words, and creates word vectors (mathmatical representations) of each word. Later, you will see that we take
+# the word vectors for each word in a tweet and we average them to create a single "tweet vector." The tweet vector will 
+# become part of our input to the model.
 
 # train unsupervised fasttext model to learn tweet semantics and word vector representations
 
 # file to read tweets from. Should be a txt file with one tweet per line
-file_txt <- "data/tweet_sample_2M_noRT.txt"
+# file_txt <- "data/tweet_sample_2M_noRT.txt" # Original Adriel Code
+file_txt <- "Temporary/tweet_sample_2M_noRT.txt" # My adjustment, given that file paths have changed.
 
 # new file to write the trained model to
-file_model50  <- "models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat"
+# file_model50  <- "models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat" # Original Adriel Code
+file_model50  <- "Temporary/model50-tweet_sample_2M_noRT.dat"
 
 # train the unsupervised fasttext model
 #fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
 
 # load the model object we just trained
-fasttext_model <- load_model(file_model50)
+fasttext_model <- load_model(file_model50) # Original Adriel Code
+
 
 
 # Fasttext model evaluation -----------------------------------------------
@@ -53,18 +63,30 @@ map(nn_words, function(x) model_eval_plot_wrap(x[1], fasttext_model, filter_str 
[…]

### 2019-04-09 Code/complaint-prediction/R/clus_func.R

@@ -125,3 +125,5 @@ sample_num_levels <- function(df, sample_col_num, n = 20) {
     }
   }
 }
+
+

### 2019-04-09 Code/complaint-prediction/R/logit_regression_classifier_Best.R

@@ -208,3 +208,4 @@ logit_mod_0.856_acc <- glm(label ~
 summary(logit_mod_0.856_acc)
 
 save(logit_mod_0.856_acc, file = "models/classifiers/logit_mod_0.856_acc")
+``

### 2019-04-09 Code/rds-data-processing/classifier-testing.R

@@ -1,12 +1,19 @@
 library(fastrtext)
 library(Matrix)
 library(xgboost)
-source("R/predict_func.R")
-source("R/TweetComplaintPredictor.r")
+source("Code/complaint-prediction/R/predict_func.R")
+source("Code/complaint-prediction/R/TweetComplaintPredictor.r")
 
 load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
-fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
-load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat")
+
+# fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
+ fasttextModel <- load_model("Temporary/model50-tweet_sample_2M_noRT.dat.bin") # This is where I've kept the saved models
+
+
+load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat") # This model was built in Code/complaint-prediction/R/classifier-construction.R
+
 TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)
 
 predict(TweetComplaintPredictor, "")
+
+getwd()

### 2019-04-17 Code/dallin_annotations/03_analyze_complaint_categories.Rmd
General reoganization of the dallin_annotations folder. This folder is meant to replace the rest of the code in the repository. It's the same code as before, just renamed and with more documentation.

--- 2019-03-19 Code/01_analyze_complaint_categories.Rmd
@@
 ```{r}
-# Note that the labeled tweet data is kept in my Temporary folder
-data <- read_csv("../Temporary/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")
+# Note that the labeled tweet data is kept in my Temporary folder in the train_test_data folder
+data <- read_csv("../../Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")
 ```

### 2019-04-17 Code/dallin_annotations/09_classifier_testing.Rmd
General reoganization of the dallin_annotations folder. This folder is meant to replace the rest of the code in the repository. It's the same code as before, just renamed and with more documentation.

--- 2019-03-29 Code/dallin_annotations/16_classifier_testing.Rmd
@@
 * Renamed as 11_predict_func.Rmd in this folder.
-* NOT WORKING
+* FOUND
+* WORKING
 
@@
 * Renamed as 12_tweet_complaint_predictor.Rmd in this folder.
+* FOUND
 * NOT WORKING
@@
 * It looks like this is a fasttext model, but I'm not sure if it is the supervised or unsupervised.
-* NOT FOUND
+* FOUND
+* NOT WORKING
+* It must have been large enough that it couldn't be shared on github
+* Found in the classifier_construction file (which is dependent on "R/clus_func.R" and "R/logit_classifier_func.R"
 
@@
 library(xgboost)
-source("11_predict_func.Rmd") # Formerly "R/predict_func.R" in Adriel's original code
+source("../complaint-prediction/R/predict_func.Rmd") # Formerly "R/predict_func.R" in Adriel's original code
 source("tweet_complaint_predictor.Rmd") # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
@@
 fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
+# Model50 was built in fasttext_clust_EDA
+
 load("../../Temporary/xgb.modelPC4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat" in Adriel's original code

### 2019-04-17 Code/dallin_annotations/99_read_tweets_json.Rmd
General reoganization of the dallin_annotations folder. This folder is meant to replace the rest of the code in the repository. It's the same code as before, just renamed and with more documentation.

---
title: "Read Tweets Json"
output: github_document
---

# Overview
These are my annotations to the "read_tweets_Json.R" script written by Adriel.

```{r}
library(RPostgreSQL)
library(dbplyr)

library(R.utils)
library(glue)

library(rjson)
library(RCurl)
library(tidyverse)

# create_df(): ----------------------------------------------------------------
### This function creates one row of a dataframe from a JSON object. This row can be uploaded to a database

create_df <- function(data)
{
  suppressWarnings(
  out <- tibble(
    tweet_created_at = null_to_na(data$created_at),
    tweet_id = null_to_na(data$id_str),
    tweet_text = null_to_na(data$text),
    in_reply_to_status_id_str = null_to_na(data$in_reply_to_status_id_str),
    in_reply_to_user_id_str = null_to_na(data$in_reply_to_user_id_str),
    in_reply_to_screen_name = null_to_na(data$in_reply_to_screen_name),
    usr_name = null_to_na(data$user$name),
    usr_screen_name = null_to_na(data$user$screen_name),
    usr_url = null_to_na(data$user$url),
    usr_description = null_to_na(data$user$description),
    usr_protected = null_to_na(data$user$protected),
    usr_followers_count = null_to_na(data$user$followers_count),
    usr_friends_count = null_to_na(data$user$friends_count),
    usr_listed_count = null_to_na(data$user$listed_count),
    usr_created_at = null_to_na(data$user$created_at),
    usr_statuses_count = null_to_na(data$user$statuses_count),
    usr_verified = null_to_na(data$user$verified),
    coordinates = null_to_na(data$coordinates),
    tweet_retweet_count_at_pull_time = null_to_na(data$retweet_count),
    tweet_favorite_count_at_pull_time = null_to_na(data$favorite_count),
    tweet_hastags = null_to_na(glue::collapse(unlist(map(data$entities$hashtags, function(x) x[[1]])), sep = ", ")),
    tweet_urls = null_to_na(glue::collapse(unlist(map(data$entities$urls, function(x) x[[1]])), sep = ", ")),
    tweet_user_mentions = null_to_na(glue::collapse(unlist(map(data$entities$user_mentions, function(x) x[[1]])), sep = ", ")),
    tweet_sentiment = null_to_na(data$sentiment),
    date = null_to_na(data$date$`$date`),
    oid = null_to_na(data$`_id`$`$oid`)
  ))
  return(out)
}

# null_to_na(): -----------------------------------------------------------
### This function converts nulls to NAs for use in building tibbles

is.null_vec <- Vectorize(function(x){is.null(x)}, "x")

null_to_na <- function(x) {
  if(length(x)==0) {
    return(NA)
  }
  return(x)
}

unlist(map(data[[2]]$entities$, function(x) x[[1]]))

# test data import and upload --------------------------------------------------

raw_data <- "data/tweetsFINAL.json"

time <- c()
seqs <- seq(1000, 10000, by = 1000)
for(seq in 1:length(seqs)){
  time[seq] <- system.time({
    data <- fromJSON(sprintf("[%s]", paste(readLines(raw_data, n = seqs[seq]),collapse=",")))
    out <- map_dfr(data, create_df)
  })
}

# data_upload -------------------------------------------------------------

# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL")
# creates a connection to the postgres database
# note that "con" will be used later in each connection to the database
con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
                 user = "adrielc", password = "byuanalytics58") # This will prompt user

dbListTables(con)

# get number of lines in file ---------------------------------------------

con <- file(raw_data, open = "rb") 
countLines(con, chunkSize = 5e+06)

# upload to database by chunk ---------------------------------------------

seqs <- seq(1730000, 2487767, 10000)
i <- 1
time <- c()
for(seq in seqs) {
  time[i] <- system.time({  
    data <- fromJSON(sprintf("[%s]", paste(read_lines(raw_data, skip = seq, n_max = 10000),collapse=",")))
    upload <- map_dfr(data, create_df) %>%
      distinct(oid, .keep_all = TRUE)
    if(dbExistsTable(con, "Cockroaches")){
      dbWriteTable(con,
                   "Cockroaches",
                   upload,
                   append = T,
                   overwrite = F,
                   row.names = FALSE)
      } else {
        dbWriteTable(con,
                     "Cockroaches",
                     upload,
                     row.names = FALSE)
      }
  })
  i <- i + 1
}

plot(time)

Cockroaches_db <- tbl(con, "Cockroaches")
data_out <- Cockroaches_db %>% summarise(n = n()) %>% collect
data_out

```

### 2019-04-17 Code/complaint-prediction/R/TweetComplaintPredictor.r

@@ -25,5 +25,3 @@ newTweetComplaintPredictor <- function(fasttextModel, pcaModel, xgbModel, pcaMod
 
 # Class checker
 is.TweetComplaintPredictor <- function(x) inherits(x, "TweetComplaintPredictor")
-
-

### 2019-04-17 Code/complaint-prediction/R/classifier-construction.R

@@ -36,7 +36,7 @@ file_txt <- "Temporary/tweet_sample_2M_noRT.txt" # My adjustment, given that fil
 file_model50  <- "Temporary/model50-tweet_sample_2M_noRT.dat"
 
 # train the unsupervised fasttext model
-#fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
+# fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
 
 # load the model object we just trained
 fasttext_model <- load_model(file_model50) # Original Adriel Code
@@ -72,21 +72,25 @@ train <- read_csv("Temporary/train_test_data/Marketing Research Labeled Tweets_ 
 # Add extracted text features to the dataset ------------------------------
 
 train <- train %>% 
-  mutate(tweetFeatures = map(tweet_text, TweetFeatures))
+  mutate(tweetFeatures = map(tweet_text, TweetFeatures)) 
 
 
 # create a list column that contains all of features output by the fasttext model
 train <- train %>%
   mutate(avg_vec_50 = map(tweet_text, VectorizeTweet, model = fasttext_model))
 
-# It looks like there is a problem with the map() function. It doesn't seem to work well with mutate(). 
+# Dallin: It looks like there is a problem with the map() or VectorizeTweet function above. 
+# It doesn't seem to work well with mutate(). 
 # I don't understand how Adriel got this to work. ¯\_(ツ)_/¯
+# The little chunk below is myself troubleshooting an error.
 
-# Dallin: The little chunk below is myself troubleshooting an error.
-train <- train %>%
-  mutate(avg_vec_50 = map(tweet_text, VectorizeTweet(tweet_text, model = fasttext_model)))
+# I tried troubleshooting the problem with this code below, but it didn't work well
+# train <- train %>%
+#      mutate(avg_vec_50 = map(tweet_text, avg_word_vec(text = ., model = fasttext_model)))
 
-new <- VectorizeTweet.Rcpp_fastrtext(train$tweet_text[1], model = fasttext_model)
+# I think I've fixed the problem by going into predict_func.R and removing the tbl_df() function and replacing it
+# with the as_tibble() function. It looks like the documentation is saying that the tbl_df() function has been removed
+# or something?
 
[…]

### 2019-04-17 Code/complaint-prediction/R/clus_func.R

@@ -124,6 +124,3 @@ sample_num_levels <- function(df, sample_col_num, n = 20) {
       print(out)
     }
   }
-}
-
-

### 2019-04-17 Code/dallin_annotations/01_test_rds_connection.R

@@ -1,9 +1,17 @@
+# Overview
+# In this document, I will be annotating the code written by Adriel in the script "TestRDSConnection.R."
+
+##### What I understand:
+# RDS stands for R Data Server. This script helps us log into the RDS and extract the twitter data. 
+
+# Libraries
 library(RPostgreSQL)
 library(dbplyr)
 library(tidyverse)
 
 
 # Connect to RDS ----------------------------------------------------------
+# This code helps us connect to the server and lost the data tables held inside. Our database is apparently a Postgre database
 
 # Load drivers to communicate with RDS
 drv <- dbDriver("PostgreSQL")
@@ -14,11 +22,20 @@ con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
 # List all tables available within the database
 dbListTables(con)
 
+### Extract the Data
+# With the code chunk above, we were able to see the data tables listed in the server. The dataframe we are interested in is called 
+# "Cockroaches." We will find that table and save our connection to that dataframe. This will make it easy for us to wrangle the data on the 
+# server before it arrives on our laptop. This will be advantageous because the server will likely have more computing power than our laptops.
+
 # Create tbl object to reference the table serverside when pulling data
 Cockroaches <- tbl(con, "Cockroaches")
 
 
 # Pull Data Sample --------------------------------------------------------
+
+
+### Pull Data Sample
+# Now we will use our connection to wrangle and save the data to our computer.
 
 # Get Tweet text for the first 1,500,000 tweets in the DB. Remove retweets (there's a lot)
 sample_tweets <- 
@@ -29,10 +46,18 @@ sample_tweets <-
   mutate(tweet_text = tolower(tweet_text)) %>%
   collect() # all the processing is done server side before being pulled in by collect()
 
+
+### Write Tweets to a .txt File
+# Now that we have wrangled the data and saved it as an object in our environment, we want to use the write_lines() function to save 
+# this data file as a .txt file.
+
 # Once tweets are pulled in, write the lines to a file.
 sample_tweets %>%
   .$tweet_text %>% 
   write_lines("Output/clean_data/tweet_sample_1hM_noRT.txt")
+
+# Disconnect
+# It is always important do sever your connection to a database after you use it. 
 
 DBI::dbDisconnect(con)
 

### 2019-04-17 Code/dallin_annotations/05_define_clustering_functions.R

@@ -1,10 +1,11 @@
----
-title: "Create a Clustering Function"
-output: github_document
----
 
-# Libraries
-```{r}
+# Overview ----------------------------------------------------------------
+# This script defines nine different functions that were frequently referenced when building our classification model. When this script is 
+# referenced in other parts of code, it's treated as a package to import these nine functions.
+
+
+# Libraries ---------------------------------------------------------------
+
 library(fastrtext)
 library(tidyverse)
 library(cluster)    # clustering algorithms
@@ -13,15 +14,19 @@ library(dendextend) # for comparing two dendrograms
 library(parallel)
 library(pbapply)
 library(stringr)
-```
 
-# Overview
-In this document, we will be creating several functions that will aid in building our classification model. These functions will be referenced in future scripts to help build our model.
 
-### Average Word Vector Function
-This function will take the word vectors for each word in a tweet, and will average the vectors to create a single vector representing the tweet as a whole. The word vectors will be generated by a fasttext unsupervised model. This will effectively become a mathmatical summary of each tweet, and will be a valuable input to our model.
-```{r}
-# This creates the average word vector to represent each tweet as an embedding vector
+# Avg_word_veg Function ---------------------------------------------------
+# What it does:
+    # An unsupervised fasttext model creates word embeddings for each word in its training dataset. These word embeddings can be thought of 
+    # as mathematical definitions of words. The unsupervised model we trained used a word vector of 50 variables. This function, 
+    # avg_word_vec(), takes the word vectors for every word in a tweet, and averages each of the 50 variables. These averages create a single 
+    # vector that can be thought of as a mathematical summary of the tweet. This single vector becomes a useful input for our PCA model.
+
+# Arguments: 
+    # Text:  A tweet
+    # Model: A trained unsupervised FastText model.
+
 avg_word_vec <- function(text, model) {
   # tokenize the text, return a list of tokens
   vec_of_tokens <- strsplit(text, " ")[[1]]
@@ -32,13 +37,12 @@ avg_word_vec <- function(text, model) {
   # summarise the word vector tibble into one average tibble
[…]

### 2019-04-17 Code/dallin_annotations/06_define_prediction_functions.R

@@ -1,12 +1,11 @@
----
-title: "Predict Function"
-output: github_document
----
 
-# Overview
-These are my annotations on the predict_func.R script written by Adriel.
+# Overview ----------------------------------------------------------------
+# This script defines three different functions that were frequently referenced when building our classification model. When this script is 
+# referenced in other parts of code, it's treated as a package to import these nine functions.
 
-```{r}
+
+# Libraries ---------------------------------------------------------------
+
 library(tidyverse)
 library(fastrtext)
 library(stringr)
@@ -14,6 +13,8 @@ library(tidytext)
 
 
 # Testing Models ----------------------------------------------------------
+# I imagine that Adriel left this section to quickly test his functions as he built them.
+
 # fasttext.model.50 <- load_model("models/fasttext/model50.dat.bin")
 # fasttext.model.50_1 <- load_model("models/model50.dat.bin")
 # load("models/prcomp/cor.data.50.pr")
@@ -22,7 +23,9 @@ library(tidytext)
 # kTestComplaint <- "@jetblue why are your employees so rude today at dallas-fort worth? tons of attitude on simple questions. #notimpressed"
 # kTestNonComplaint <- "@delta I love your service, it's always excellent"
 
-# Featurization -----------------------------------------------------------
+# TweetFeatures Function -----------------------------------------------------------
+
+
 
 TweetFeatures <- function(tweet) {
   # Creates features from the tweet which are used for prediction
@@ -41,7 +44,7 @@ TweetFeatures <- function(tweet) {
 }
 
 
-# Label Prediction -------------------------------------------------------
+# Label Prediction Function -------------------------------------------------------
 
 predict.TweetComplaintPredictor <- function(object, newdata, complaintCutoff = 0) {
   # Given a character vector containing tweets to predict for, this function returns predicted labels for the given tweet.
@@ -70,13 +73,18 @@ predict.TweetComplaintPredictor <- function(object, newdata, complaintCutoff = 0
 }
 
 
+# Vectorize Tweet ---------------------------------------------------------
+# What It Does: This function is very similar to the avg_word_vec() function in 05_define_clustering_functions(), except that it has two
+# classes: one for handling fastText models, and another for handling PCA models. The fastText class takes the word vectors of the full tweet 
[…]

### 2019-04-17 Code/dallin_annotations/08_define_tweet_complaint_predictor_function.r

@@ -1,12 +1,3 @@
----
-title: "Tweet Complaint Predictor"
-output: github_document
----
-
-# Overview
-These are my annotations on the "TweetComplaintPredictor.r" script written by Adriel
-
-```{r}
 # TweetComplaintPredictor class constructor ----------------------------------------
 # Class constructor 
 newTweetComplaintPredictor <- function(fasttextModel, pcaModel, xgbModel, pcaModelComponentCutoff) {
@@ -35,7 +26,4 @@ newTweetComplaintPredictor <- function(fasttextModel, pcaModel, xgbModel, pcaMod
 # Class checker
 is.TweetComplaintPredictor <- function(x) inherits(x, "TweetComplaintPredictor")
 
-
-
-```
 

### 2019-04-17 Code/rds-data-processing/classifier-testing.R
Moved large files to the Temporary folder to allow a push.

@@ -4,16 +4,18 @@ library(xgboost)
 source("Code/complaint-prediction/R/predict_func.R")
 source("Code/complaint-prediction/R/TweetComplaintPredictor.r")
 
-load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
+# load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
+load("Temporary/prcomp4.dat") # Dallin: Location has been edited for where I've kept the model
 
 # fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
  fasttextModel <- load_model("Temporary/model50-tweet_sample_2M_noRT.dat.bin") # This is where I've kept the saved models
 
 
-load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat") # This model was built in Code/complaint-prediction/R/classifier-construction.R
-
+# load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat") # This model was built in Code/complaint-prediction/R/classifier-construction.R
+load("Temporary/xgb.modelPC4.dat")
+ 
 TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)
 
-predict(TweetComplaintPredictor, "")
+predict(TweetComplaintPredictor, "My mom died this week, and the cartel decapitated my father.")
 
-getwd()
+

### 2019-04-19 Code/CountingCockroaches.R
An attempt to resolve problems with committing large files to github.

@@ -1,261 +1,0 @@
-#################################################
-####      1) Data Loading and Preparation     ###
-#################################################
-
-# Can we build this without using tm?
-
-library(tidyverse); library(tidytext); library(tm); library(topicmodels)
-load("/Users/maddatascientist/DATA SCIENCE/Marketing RA/Twitter Subset2.Rdata") # file location dependent on user
-tweets <- twitter_subset
-
-# Format tweets
-tweets <- tweets %>% 
-  mutate(Tweet_Number = row_number()) %>% 
-  select(Tweet_Number, Text = text, Sentiment = sentiment)
-
-# Combine tweets into "mega-tweets" by airline:
-airlines <- list(c("americanair", "american", "american air"), "united", "delta", 
-                 c("southwestair", "southwest") , "klm", "emirates", "indonesiagaruda", "british_airways", 
-                 "usairways", "jetblue", "aircanada", "ryanair", "virginamerica", 
-                 c("alaskaairlines", "alaskaair"), "aerlingus", "easyjet","flyfrontier","porterairlines",
-                 "asercaairlines","singaporeair", "saudiairlines", "saudiairline", "tamairlines",
-                 "cebupacificair","airasia","airfrancefr","koreanairke","deltaassist","aviorairline", 
-                 "lufthansa", "airbus")
-
-library(stringr)
-
-docs <- list()
-for (i in 1:length(airlines)) {     
-  docs[[i]] <- tweets$Text %>%
-    str_subset( str_c( "(?i)", str_c( airlines[[i]] ), collapse = "|" ) ) %>% # The "(?i)" is ignoring case
-    str_c(collapse = " ")
-}
-
-# # #     TAKE OUT ALL AIRLINES     # # #
-for (k in 1:length(docs)) {
-  for (i in 1:length(airlines)) {
-    docs[[k]] <- docs[[k]] %>% 
-      str_replace_all( str_c( "@?(?i)", str_c(airlines[[i]]), collapse = "|" ) , "" ) 
-  }
-}
-
-              # Take Out All "Words" w/ Numbers and All Twitter Handles (optional)
-
-              # docs <- docs %>% 
-                # str_replace_all("[\\s]@[^\\s]*", "") %>% # for Twitter handles
-                # str_replace_all("[^\\s]*\\d.*?\\s", "") # for all words with numbers
-
-
[…]

### 2019-04-19 Code/cnn-classifier/R/fasttext_supervised_classifier.R

@@ -1,77 +1,0 @@
-library(fastrtext)
-library(tidyverse)
-
-# Prepare data ------------------------------------------------------------
-
-# Create file location where the model will be written to
-# Dallin Note: Throughout this script, I've adjusted file paths to make them run well on my computer
-file_model <- "Temporary/train_test_data/class_mod_1.dat"
-train_data <- "Temporary/train_test_data/train_data_1.txt"
-test_data <- "Temporary/train_test_data/test_data_1.txt"
-
-# read in the data
-# tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>% 
-#   filter(nchar(tweet_text) > 5)
-
-# Dallin Note: For my purposes, I'll edit the code directly above and adjust it for my computer
-tweet_data <- read_csv("Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv") %>%
-  filter(nchar(tweet_text) > 5)
-
-# format the data to fasttext input requirements
-test_train_data <- tweet_data %>% 
-  mutate(label = case_when(complaint_label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
-                           complaint_label == 1 ~ "complaint"),
-         input_lines = paste(label, tweet_text)) %>% 
-  group_by(label) %>% # get a representative sample of both complaints and non complaints
-  mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
-  ungroup()
-
-# write train data
-train_data_lines <- test_train_data %>% 
-  filter(test_train == "train") %>% 
-  pull(input_lines) %>% 
-  paste0("__label__", .)
-
-write_lines(train_data_lines, train_data)
-
-# write test data
-test_data_lines <- test_train_data %>% 
-  filter(test_train == "test") %>% 
-  pull(input_lines) %>% 
-  paste0("__label__", .)
-
-write_lines(test_data_lines, test_data)
-
-# create a character vector containing the tweets to test without their labels
-test_labels_without_prefix <- test_train_data %>% 
-  filter(test_train == "test") %>% 
-  pull(label)
-  
-
-# learn model
-execute(commands = c("supervised", "-input", train_data, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
-
-# load model
-model <- load_model(file_model)
-
[…]

### 2019-04-19 Code/complaint-prediction/R/classifier-construction.R

@@ -1,200 +1,0 @@
-library(tidyverse)
-library(fastrtext)
-library(magrittr) # for assignment operator %<>% 
-library(plotly)
-require(randomForest)
-library(Matrix)
-source("Code/complaint-prediction/R/clus_func.R")
-# source("Code/complaint-prediction/R/logit_classifier_func.R") # NOT FOUND. Where is this file?
-
-source("Code/complaint-prediction/R/predict_func.R") # Dallin added this code.
- 
-
-library(xgboost)
-library(caret)
-library(car)
-
-set.seed(123)
-
-getwd()
-
-
-# Fasttext train ----------------------------------------------------------
-# Dallin: In this block, we train the fasttext unsupervised model. This model analyzes the strength of associations 
-# between words, and creates word vectors (mathmatical representations) of each word. Later, you will see that we take
-# the word vectors for each word in a tweet and we average them to create a single "tweet vector." The tweet vector will 
-# become part of our input to the model.
-
-# train unsupervised fasttext model to learn tweet semantics and word vector representations
-
-# file to read tweets from. Should be a txt file with one tweet per line
-# file_txt <- "data/tweet_sample_2M_noRT.txt" # Original Adriel Code
-file_txt <- "Temporary/tweet_sample_2M_noRT.txt" # My adjustment, given that file paths have changed.
-
-# new file to write the trained model to
-# file_model50  <- "models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat" # Original Adriel Code
-file_model50  <- "Temporary/model50-tweet_sample_2M_noRT.dat"
-
-# train the unsupervised fasttext model
-# fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
-
-# load the model object we just trained
-fasttext_model <- load_model(file_model50) # Original Adriel Code
-
-
-
-# Fasttext model evaluation -----------------------------------------------
-
-# Examine the nearest neighbors returned by our trained model. 
-# First vector element is the word to look up NN, and the second is a string used to filter the results
-
-nn_words  <- list(c("mad", "mad"),
-                  c("sad","sad"),
-                  c("upset", "upset"),
-                  c("late", "ate"),
-                  c("delay", "del"),
[…]

### 2019-04-19 Code/complaint-prediction/R/clus_func.R

@@ -1,126 +1,0 @@
-library(fastrtext)
-library(tidyverse)
-library(cluster)    # clustering algorithms
-library(factoextra) # clustering visualization
-library(dendextend) # for comparing two dendrograms
-library(parallel)
-library(pbapply)
-library(stringr)
-
-# This creates the average word vector to represent each tweet as an embedding vector
-avg_word_vec <- function(text, model) {
-  # tokenize the text, return a list of tokens
-  vec_of_tokens <- strsplit(text, " ")[[1]]
-  # apply get_word_vectors to each token in the vector, return matrix of word vecs
-  matrix_of_vecs <- get_word_vectors(model, vec_of_tokens)
-  # convert matrix to a tibble for easy reduction
-  tbl_of_vecs <- tbl_df(matrix_of_vecs) 
-  # summarise the word vector tibble into one average tibble
-  summarise_all(tbl_of_vecs, funs(mean), na.rm = TRUE)
-}
-
-nn_filter <- function(model, token, filter_str, n = 1000) {
-  out <- get_nn(model, token, n)
-  if(!is.na(filter_str)) {
-    tibble(word = names(out), value = out) %>% 
-      filter(!grepl(paste0(".*", filter_str, ".*"), word, ignore.case = T))
-  } else {
-    tibble(word = names(out), value = out)
-  }
-}
-
-model_eval <- function(token, ..., filter_str = NA) {
-  models <- list(...)
-  names(models) <- GetDotObjectNames(...)
-  cl <- detectCores()
-  pblapply(models, nn_filter, token, filter_str, cl = cl)
-}
-
-GetDotObjectNames <- function(...) {
-  strsplit(
-    gsub("[\\(\\)]", 
-         "", 
-         regmatches(
-           deparse(
-             substitute(
-               list(...))), 
-           gregexpr("\\(.*?\\)", 
-                    deparse(
-                      substitute(
-                        list(...)))))[[1]]), 
-    split = ", ")[[1]]
-}
-
-model_eval_plot <- function(eval_list, n = 20, token, filter_str) {
-  out <- lapply(names(eval_list), function(model) {
-    eval_list[[model]] %>% 
-      mutate(model = model)
-  }) %>% 
-    bind_rows() %>% 
-    group_by(model) %>% 
-    top_n(n, value) %>% 
-    ungroup() %>% 
-    arrange(model, value) %>% 
[…]

### 2019-04-19 Code/complaint-prediction/R/fasttext_clust_EDA.R

@@ -1,813 +1,0 @@
-library(googlesheets)
-library(plotly)
-library(broom)
-library(caret)
-library(cluster)
-library(qtlcharts)
-library(RPostgreSQL)
-library(dbplyr)
-source("Code/complaint-prediction/R/clus_func.R")
-
-# source("R/rquery_cormat.R") Note from Dallin: Where is this file?
-
-
-# connect to db -----------------------------------------------------------
-
-
-drv <- dbDriver("PostgreSQL")
-con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
-                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
-                 user = "adrielc", password = "byuanalytics58") # This will prompt user
-dbListTables(con)
-
-
-
-# pull data sample --------------------------------------------------------
-
-
-Cockroaches <- tbl(con, "Cockroaches")
-
-sample_tweets <- 
-  Cockroaches %>% 
-  select(tweet_text) %>% 
-  mutate(tweet_text = tolower(tweet_text)) %>%
-  filter(substr(tweet_text, 1, 4) != "rt @") %>% 
-  head(900000) %>% 
-  collect()
-
-
-sample_tweets %>%
-  .$tweet_text %>% 
-  write_lines("data/tweet_sample_1mil.txt")
-
-
-# Remove retweets
-sample_tweets <- 
-  Cockroaches %>% 
-  filter(substr(tweet_text, 1, 4) != "RT @") %>% 
-  select(tweet_text) %>% 
-  head(1500000) %>% 
-  mutate(tweet_text = tolower(tweet_text)) %>%
-  collect()
-
-
-sample_tweets %>%
-  .$tweet_text %>%
-  write_lines("data/tweet_sample_1hM_noRT.txt")
-rm(sample_tweets) # After writing the .txt files, we are removing them from the environment with the rm() function
-
-
-
-# Remove retweets
-sample_tweets <- 
-  Cockroaches %>% 
-  filter(substr(tweet_text, 1, 4) != "RT @") %>% 
-  select(tweet_text) %>% 
-  head(2000000) %>% 
-  mutate(tweet_text = tolower(tweet_text)) %>%
-  collect()
-
-sample_tweets %>%
-  .$tweet_text %>%
[…]

### 2019-04-19 Code/complaint-prediction/R/predict_func.R

@@ -1,101 +1,0 @@
-library(tidyverse)
-library(fastrtext)
-library(stringr)
-library(tidytext)
-
-
-# Testing Models ----------------------------------------------------------
-# fasttext.model.50 <- load_model("models/fasttext/model50.dat.bin")
-# fasttext.model.50_1 <- load_model("models/model50.dat.bin")
-# load("models/prcomp/cor.data.50.pr")
-# load("models/classifiers/logit_mod_0.856_acc")
-
-# kTestComplaint <- "@jetblue why are your employees so rude today at dallas-fort worth? tons of attitude on simple questions. #notimpressed"
-# kTestNonComplaint <- "@delta I love your service, it's always excellent"
-
-# Featurization -----------------------------------------------------------
-
-TweetFeatures <- function(tweet) {
-  # Creates features from the tweet which are used for prediction
-  # 
-  # Args:
-  #   tweet: a single tweet as a string
-  # 
-  # Returns:
-  #   a single-row tibble with the following columns: log.links, log.mentions, count.char, count.space
-  tibble(tweet.text = tweet) %>%
-    mutate(count.char   = nchar(tweet.text),
-           log.mentions = log1p(str_count(tweet.text, "@")), # Count user mentions
-           log.links    = log1p(str_count(tweet.text, "http:\\/\\/t.co")), # count links
-           count.space  = str_count(tweet.text, " ")) %>% # count exclamation marks
-    select(-tweet.text)
-}
-
-
-# Label Prediction -------------------------------------------------------
-
-predict.TweetComplaintPredictor <- function(object, newdata, complaintCutoff = 0) {
-  # Given a character vector containing tweets to predict for, this function returns predicted labels for the given tweet.
-  #
-  # Args:
-  #   object: TweetComplaintPredictor model
-  #   newdata: A character vector containing tweets  
-  #   complaintCutoff: a numeric value specifying the cutoff value for the xgb prediction output 
-  #       when considering what value to use to consider a tweet a complaint.
-  #
-  # Returns:
-  #   a string label. Either "Complaint" or "Non-Complaint"
-  #
-  
-  newdata %>% 
-    tibble(tweetText = .) %>% 
-    mutate(tweetFeatures = map(tweetText, TweetFeatures)) %>% 
-    mutate(fasttextVec = map(tweetText, VectorizeTweet, object$fasttextModel)) %>% 
[…]

### 2019-04-19 Code/dallin_annotations/01_test_rds_connection.R

@@ -1,63 +1,0 @@
-# Overview
-# In this document, I will be annotating the code written by Adriel in the script "TestRDSConnection.R."
-
-##### What I understand:
-# RDS stands for R Data Server. This script helps us log into the RDS and extract the twitter data. 
-
-# Libraries
-library(RPostgreSQL)
-library(dbplyr)
-library(tidyverse)
-
-
-# Connect to RDS ----------------------------------------------------------
-# This code helps us connect to the server and lost the data tables held inside. Our database is apparently a Postgre database
-
-# Load drivers to communicate with RDS
-drv <- dbDriver("PostgreSQL")
-con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
-                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
-                 user = "adrielc", password = "byuanalytics58") # This will prompt user
-
-# List all tables available within the database
-dbListTables(con)
-
-### Extract the Data
-# With the code chunk above, we were able to see the data tables listed in the server. The dataframe we are interested in is called 
-# "Cockroaches." We will find that table and save our connection to that dataframe. This will make it easy for us to wrangle the data on the 
-# server before it arrives on our laptop. This will be advantageous because the server will likely have more computing power than our laptops.
-
-# Create tbl object to reference the table serverside when pulling data
-Cockroaches <- tbl(con, "Cockroaches")
-
-
-# Pull Data Sample --------------------------------------------------------
-
-
-### Pull Data Sample
-# Now we will use our connection to wrangle and save the data to our computer.
-
-# Get Tweet text for the first 1,500,000 tweets in the DB. Remove retweets (there's a lot)
-sample_tweets <- 
-  Cockroaches %>% 
-  filter(substr(tweet_text, 1, 4) != "RT @") %>% 
-  select(tweet_text) %>% 
-  head(1500000) %>% 
-  mutate(tweet_text = tolower(tweet_text)) %>%
-  collect() # all the processing is done server side before being pulled in by collect()
-
-
-### Write Tweets to a .txt File
-# Now that we have wrangled the data and saved it as an object in our environment, we want to use the write_lines() function to save 
-# this data file as a .txt file.
-
-# Once tweets are pulled in, write the lines to a file.
-sample_tweets %>%
-  .$tweet_text %>% 
-  write_lines("Output/clean_data/tweet_sample_1hM_noRT.txt")
-
[…]

### 2019-04-19 Code/dallin_annotations/05_define_clustering_functions.R

@@ -1,177 +1,0 @@
-
-# Overview ----------------------------------------------------------------
-# This script defines nine different functions that were frequently referenced when building our classification model. When this script is 
-# referenced in other parts of code, it's treated as a package to import these nine functions.
-
-
-# Libraries ---------------------------------------------------------------
-
-library(fastrtext)
-library(tidyverse)
-library(cluster)    # clustering algorithms
-library(factoextra) # clustering visualization
-library(dendextend) # for comparing two dendrograms
-library(parallel)
-library(pbapply)
-library(stringr)
-
-
-# Avg_word_veg Function ---------------------------------------------------
-# What it does:
-    # An unsupervised fasttext model creates word embeddings for each word in its training dataset. These word embeddings can be thought of 
-    # as mathematical definitions of words. The unsupervised model we trained used a word vector of 50 variables. This function, 
-    # avg_word_vec(), takes the word vectors for every word in a tweet, and averages each of the 50 variables. These averages create a single 
-    # vector that can be thought of as a mathematical summary of the tweet. This single vector becomes a useful input for our PCA model.
-
-# Arguments: 
-    # Text:  A tweet
-    # Model: A trained unsupervised FastText model.
-
-avg_word_vec <- function(text, model) {
-  # tokenize the text, return a list of tokens
-  vec_of_tokens <- strsplit(text, " ")[[1]]
-  # apply get_word_vectors to each token in the vector, return matrix of word vecs
-  matrix_of_vecs <- get_word_vectors(model, vec_of_tokens)
-  # convert matrix to a tibble for easy reduction
-  tbl_of_vecs <- tbl_df(matrix_of_vecs) 
-  # summarise the word vector tibble into one average tibble
-  summarise_all(tbl_of_vecs, funs(mean), na.rm = TRUE)
-}
-
-
-# Nn_filter Function ------------------------------------------------------
-
-
-nn_filter <- function(model, token, filter_str, n = 1000) {
-  out <- get_nn(model, token, n)
-  if(!is.na(filter_str)) {
-    tibble(word = names(out), value = out) %>% 
-      filter(!grepl(paste0(".*", filter_str, ".*"), word, ignore.case = T))
-  } else {
[…]

### 2019-04-19 Code/dallin_annotations/08_define_tweet_complaint_predictor_function.r

@@ -1,29 +1,0 @@
-# TweetComplaintPredictor class constructor ----------------------------------------
-# Class constructor 
-newTweetComplaintPredictor <- function(fasttextModel, pcaModel, xgbModel, pcaModelComponentCutoff) {
-  component <- enquo(pcaModelComponentCutoff)
-  
-  if(class(fasttextModel)[1] != "Rcpp_fastrtext"){
-    stop("fasttextModel is not a member of class Rcpp_fastrtext")
-  }
-  if(class(pcaModel) != "prcomp"){
-    stop("pcaModel is not a member of class Rcpp_fastrtext")
-  }
-  if(class(xgbModel) != "xgb.Booster"){
-    stop("xgbModel is not a member of class Rcpp_fastrtext")
-  }
-  
-  newTweetComplaintPredictor <- list(fasttextModel = fasttextModel,
-                                     pcaModel = pcaModel,
-                                     xgbModel = xgbModel,
-                                     pcaModelComponentCutoff = component)
-  
-  class(newTweetComplaintPredictor) <- "TweetComplaintPredictor"
-  
-  return(newTweetComplaintPredictor)
-}
-
-# Class checker
-is.TweetComplaintPredictor <- function(x) inherits(x, "TweetComplaintPredictor")
-
-

### 2019-04-19 Code/rds-data-processing/Json_parse_upload.r

@@ -1,81 +1,0 @@
-library(RPostgreSQL)
-library(dbplyr)
-library(rjson)
-library(RCurl)
-library(tidyverse)
-
-
-
-# create_df(): ----------------------------------------------------------------
-### This function creates one row of a dataframe from a JSON object. This row can be uploaded to a database
-
-
-create_df <- function(data)
-{
-  tibble(
-    tweet_created_at = null_to_na(data$created_at),
-    tweet_id = null_to_na(data$id_str),
-    tweet_text = null_to_na(data$text),
-    in_reply_to_status_id_str = null_to_na(data$in_reply_to_status_id_str),
-    in_reply_to_user_id_str = null_to_na(data$in_reply_to_user_id_str),
-    in_reply_to_screen_name = null_to_na(data$in_reply_to_screen_name),
-    usr_name = null_to_na(data$user$name),
-    usr_screen_name = null_to_na(data$user$screen_name),
-    usr_url = null_to_na(data$user$url),
-    usr_description = null_to_na(data$user$description),
-    usr_protected = null_to_na(data$user$protected),
-    usr_followers_count = null_to_na(data$user$followers_count),
-    usr_friends_count = null_to_na(data$user$friends_count),
-    usr_listed_count = null_to_na(data$user$listed_count),
-    usr_created_at = null_to_na(data$user$created_at),
-    usr_statuses_count = null_to_na(data$user$statuses_count),
-    usr_verified = null_to_na(data$user$verified),
-    coordinates = null_to_na(data$coordinates),
-    tweet_retweet_count_at_pull_time = null_to_na(data$retweet_count),
-    tweet_favorite_count_at_pull_time = null_to_na(data$favorite_count),
-    tweet_hastags = null_to_na(data$entities$hashtags),
-    tweet_symbols = null_to_na(data$entities$symbols),
-    tweet_urls = null_to_na(data$entities$urls),
-    tweet_user_mentions = null_to_na(data$entities$user_mentions),
-    tweet_sentiment = null_to_na(data$sentiment),
-    date = null_to_na(data$date$`$date`),
-    oid = null_to_na(data$`_id`$`$oid`)
-  )
-}
-
-null_to_na <- function(x) ifelse(is.null(x), NA, x)
-
-# data import and upload --------------------------------------------------
-
-
-
-raw_data <- "data/tweetsFINAL.json"
-
[…]

### 2019-04-19 Code/rds-data-processing/batch-classification.R

@@ -1,48 +1,0 @@
-library(RPostgreSQL)
-library(dbplyr)
-library(tidyverse)
-source("complaint-prediction/R/TweetComplaintPredictor.r")
-source("complaint-prediction/R/predict_func.R")
-
-# Connect to RDS ----------------------------------------------------------
-
-# Load drivers to communicate with RDS
-drv <- dbDriver("PostgreSQL")
-con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
-                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
-                 user = "adrielc", password = "byuanalytics58") # This will prompt user
-
-# List all tables available within the database
-dbListTables(con)
-
-# Create tbl object to reference the table serverside when pulling data
-Cockroaches <- tbl(con, "Cockroaches")
-test <- tbl(con, "NielsenRetail")
-
-dbSendQuery(con, "ALTER TABLE \"Cockroaches\" ADD COLUMN complaint_label VARCHAR;")
-
-res <- dbSendQuery(con, "insert into \"NielsenRetail\" (complaint_label) values ('test', 1, 1, 1);")
-
-
-Cockroaches %>% 
-  select(tweet_id, tweet_text) %>% 
-  collect()
-
-sample <- all_tweets %>% head(100)
-
-
-  
-load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
-fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
-load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat")
-TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)
-
-sample %<>% 
-  mutate(prediction = predict(TweetComplaintPredictor, tweet_text))
-
-
-
-
-system.time({sample %<>% 
-    mutate(prediction = predict(TweetComplaintPredictor, tweet_text))
-})

### 2019-04-19 Code/rds-data-processing/classifier-testing.R

@@ -1,21 +1,0 @@
-library(fastrtext)
-library(Matrix)
-library(xgboost)
-source("Code/complaint-prediction/R/predict_func.R")
-source("Code/complaint-prediction/R/TweetComplaintPredictor.r")
-
-# load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
-load("Temporary/prcomp4.dat") # Dallin: Location has been edited for where I've kept the model
-
-# fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
- fasttextModel <- load_model("Temporary/model50-tweet_sample_2M_noRT.dat.bin") # This is where I've kept the saved models
-
-
-# load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat") # This model was built in Code/complaint-prediction/R/classifier-construction.R
-load("Temporary/xgb.modelPC4.dat")
- 
-TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)
-
-predict(TweetComplaintPredictor, "My mom died this week, and the cartel decapitated my father.")
-
-

### 2019-04-19 Code/dallin_annotations/99_batch_classification.Rmd
A second attempt to solve a problem with pushing deleted files that are too big.

---
title: "Batch Classification"
output: github_document
---

# Overview
These are my annotations on the "batch-classification.R" script written by Adriel.

```{r}
library(RPostgreSQL)
library(dbplyr)
library(tidyverse)
source("complaint-prediction/R/TweetComplaintPredictor.r")
source("complaint-prediction/R/predict_func.R")

# Connect to RDS ----------------------------------------------------------

# Load drivers to communicate with RDS
drv <- dbDriver("PostgreSQL")
con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
                 user = "adrielc", password = "byuanalytics58") # This will prompt user

# List all tables available within the database
dbListTables(con)

# Create tbl object to reference the table serverside when pulling data
Cockroaches <- tbl(con, "Cockroaches")
test <- tbl(con, "NielsenRetail")

dbSendQuery(con, "ALTER TABLE \"Cockroaches\" ADD COLUMN complaint_label VARCHAR;")

res <- dbSendQuery(con, "insert into \"NielsenRetail\" (complaint_label) values ('test', 1, 1, 1);")

Cockroaches %>% 
  select(tweet_id, tweet_text) %>% 
  collect()

sample <- all_tweets %>% head(100)

load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat")
TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)

sample %<>% 
  mutate(prediction = predict(TweetComplaintPredictor, tweet_text))

system.time({sample %<>% 
    mutate(prediction = predict(TweetComplaintPredictor, tweet_text))
})
```

### 2019-04-19 Code/dallin_annotations/99_tweet_object.Rmd
A second attempt to solve a problem with pushing deleted files that are too big.

---
title: "Tweet Object"
output: github_document
---
# Overview
These are my annotations on the "tweetObject.R" script written by Adriel.

```{r}
ObjectSample <- list(
  "_id" = 'ObjectId("534769eee4b0efdb7b081251")',
  "created_at" = "Fri Apr 11 04=04=57 +0000 2014",
  "id" = 'NumberLong("454470130765135872")',
  "id_str" = "454470130765135872",
  "text" = "@united is there a service fee to get the miles back if i don't clear? your rules are unclear.",
  "source" = "web",
  "truncated" = FALSE,
  "in_reply_to_status_id" = 'NumberLong("454467945172074497")',
  "in_reply_to_status_id_str" = "454467945172074497",
  "in_reply_to_user_id" = 260907612,
  "in_reply_to_user_id_str" = "260907612",
  "in_reply_to_screen_name" = "united",
  "user" = list(
    "id" = 770550,
    "id_str" = "770550",
    "name" = "Rakesh Agrawal",
    "screen_name" = "rakeshlobster",
    "location" = "San Francisco, CA",
    "url" = "http=//redesignmobile.com",
    "description" = "Global strategy at PayPal. As seen on CNBC, Bloomberg TV and VentureBeat.",
    "protected" = FALSE,
    "followers_count" = 9034,
    "friends_count" = 1672,
    "listed_count" = 410,
    "created_at" = "Tue Feb 13 21=36=08 +0000 2007",
    "favourites_count" = 4807,
    "utc_offset" = -25200,
    "time_zone" = "Pacific Time (US & Canada)",
    "geo_enabled" = TRUE,
    "verified" = FALSE,
    "statuses_count" = 39454,
    "lang" = "en",
    "contributors_enabled" = FALSE,
    "is_translator" = FALSE,
    "is_translation_enabled" = FALSE,
    "profile_background_color" = "0099B9",
    "profile_background_image_url" = "http=//abs.twimg.com/images/themes/theme4/bg.gif",
    "profile_background_image_url_https" = "https=//abs.twimg.com/images/themes/theme4/bg.gif",
    "profile_background_tile" = FALSE,
    "profile_image_url" = "http=//pbs.twimg.com/profile_images/378800000722918071/ce9e53447ed1ee7d90f5e0d1a3b800c5_normal.jpeg",
    "profile_image_url_https" = "https=//pbs.twimg.com/profile_images/378800000722918071/ce9e53447ed1ee7d90f5e0d1a3b800c5_normal.jpeg",
    "profile_link_color" = "0099B9",
    "profile_sidebar_border_color" = "5ED4DC",
    "profile_sidebar_fill_color" = "95E8EC",
    "profile_text_color" = "3C3940",
    "profile_use_background_image" = TRUE,
    "default_profile" = FALSE,
    "default_profile_image" = FALSE,
    "following" = NA,
    "follow_request_sent" = NA,
    "notifications" = NA
    ),
  "geo" = NA,
  "coordinates" = NA,
  "place" = NA,
  "contributors" = NA,
  "retweet_count" = 0,
  "favorite_count" = 0,
  "entities" = list(
    "hashtags" = list(NA),
    "symbols" = list(NA),
    "urls" = list(NA),
    "user_mentions" = list(
        "screen_name" = "united",
        "name" = "United",
        "id" = 260907612,
        "id_str" = "260907612",
        "indices" = list(0,7)
        )
    ),
  "favorited" = FALSE,
  "retweeted" = FALSE,
  "filter_level" = "medium",
  "lang" = "en",
  "sentiment" = 1,
  "date" = 'ISODate("2014-04-11T04=04=57Z")'
)

```

### 2019-04-19 Code/CountingCockroaches.R

@@ -1,0 +1,261 @@
+#################################################
+####      1) Data Loading and Preparation     ###
+#################################################
+
+# Can we build this without using tm?
+
+library(tidyverse); library(tidytext); library(tm); library(topicmodels)
+load("/Users/maddatascientist/DATA SCIENCE/Marketing RA/Twitter Subset2.Rdata") # file location dependent on user
+tweets <- twitter_subset
+
+# Format tweets
+tweets <- tweets %>% 
+  mutate(Tweet_Number = row_number()) %>% 
+  select(Tweet_Number, Text = text, Sentiment = sentiment)
+
+# Combine tweets into "mega-tweets" by airline:
+airlines <- list(c("americanair", "american", "american air"), "united", "delta", 
+                 c("southwestair", "southwest") , "klm", "emirates", "indonesiagaruda", "british_airways", 
+                 "usairways", "jetblue", "aircanada", "ryanair", "virginamerica", 
+                 c("alaskaairlines", "alaskaair"), "aerlingus", "easyjet","flyfrontier","porterairlines",
+                 "asercaairlines","singaporeair", "saudiairlines", "saudiairline", "tamairlines",
+                 "cebupacificair","airasia","airfrancefr","koreanairke","deltaassist","aviorairline", 
+                 "lufthansa", "airbus")
+
+library(stringr)
+
+docs <- list()
+for (i in 1:length(airlines)) {     
+  docs[[i]] <- tweets$Text %>%
+    str_subset( str_c( "(?i)", str_c( airlines[[i]] ), collapse = "|" ) ) %>% # The "(?i)" is ignoring case
+    str_c(collapse = " ")
+}
+
+# # #     TAKE OUT ALL AIRLINES     # # #
+for (k in 1:length(docs)) {
+  for (i in 1:length(airlines)) {
+    docs[[k]] <- docs[[k]] %>% 
+      str_replace_all( str_c( "@?(?i)", str_c(airlines[[i]]), collapse = "|" ) , "" ) 
+  }
+}
+
+              # Take Out All "Words" w/ Numbers and All Twitter Handles (optional)
+
+              # docs <- docs %>% 
+                # str_replace_all("[\\s]@[^\\s]*", "") %>% # for Twitter handles
+                # str_replace_all("[^\\s]*\\d.*?\\s", "") # for all words with numbers
+
+
[…]

### 2019-04-19 Code/cnn-classifier/R/fasttext_supervised_classifier.R

@@ -1,0 +1,77 @@
+library(fastrtext)
+library(tidyverse)
+
+# Prepare data ------------------------------------------------------------
+
+# Create file location where the model will be written to
+# Dallin Note: Throughout this script, I've adjusted file paths to make them run well on my computer
+file_model <- "Temporary/train_test_data/class_mod_1.dat"
+train_data <- "Temporary/train_test_data/train_data_1.txt"
+test_data <- "Temporary/train_test_data/test_data_1.txt"
+
+# read in the data
+# tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>% 
+#   filter(nchar(tweet_text) > 5)
+
+# Dallin Note: For my purposes, I'll edit the code directly above and adjust it for my computer
+tweet_data <- read_csv("Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv") %>%
+  filter(nchar(tweet_text) > 5)
+
+# format the data to fasttext input requirements
+test_train_data <- tweet_data %>% 
+  mutate(label = case_when(complaint_label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
+                           complaint_label == 1 ~ "complaint"),
+         input_lines = paste(label, tweet_text)) %>% 
+  group_by(label) %>% # get a representative sample of both complaints and non complaints
+  mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
+  ungroup()
+
+# write train data
+train_data_lines <- test_train_data %>% 
+  filter(test_train == "train") %>% 
+  pull(input_lines) %>% 
+  paste0("__label__", .)
+
+write_lines(train_data_lines, train_data)
+
+# write test data
+test_data_lines <- test_train_data %>% 
+  filter(test_train == "test") %>% 
+  pull(input_lines) %>% 
+  paste0("__label__", .)
+
+write_lines(test_data_lines, test_data)
+
+# create a character vector containing the tweets to test without their labels
+test_labels_without_prefix <- test_train_data %>% 
+  filter(test_train == "test") %>% 
+  pull(label)
+  
+
+# learn model
+execute(commands = c("supervised", "-input", train_data, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
+
+# load model
+model <- load_model(file_model)
+
[…]

### 2019-04-19 Code/complaint-prediction/R/classifier-construction.R

@@ -1,0 +1,200 @@
+library(tidyverse)
+library(fastrtext)
+library(magrittr) # for assignment operator %<>% 
+library(plotly)
+require(randomForest)
+library(Matrix)
+source("Code/complaint-prediction/R/clus_func.R")
+# source("Code/complaint-prediction/R/logit_classifier_func.R") # NOT FOUND. Where is this file?
+
+source("Code/complaint-prediction/R/predict_func.R") # Dallin added this code.
+ 
+
+library(xgboost)
+library(caret)
+library(car)
+
+set.seed(123)
+
+getwd()
+
+
+# Fasttext train ----------------------------------------------------------
+# Dallin: In this block, we train the fasttext unsupervised model. This model analyzes the strength of associations 
+# between words, and creates word vectors (mathmatical representations) of each word. Later, you will see that we take
+# the word vectors for each word in a tweet and we average them to create a single "tweet vector." The tweet vector will 
+# become part of our input to the model.
+
+# train unsupervised fasttext model to learn tweet semantics and word vector representations
+
+# file to read tweets from. Should be a txt file with one tweet per line
+# file_txt <- "data/tweet_sample_2M_noRT.txt" # Original Adriel Code
+file_txt <- "Temporary/tweet_sample_2M_noRT.txt" # My adjustment, given that file paths have changed.
+
+# new file to write the trained model to
+# file_model50  <- "models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat" # Original Adriel Code
+file_model50  <- "Temporary/model50-tweet_sample_2M_noRT.dat"
+
+# train the unsupervised fasttext model
+# fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
+
+# load the model object we just trained
+fasttext_model <- load_model(file_model50) # Original Adriel Code
+
+
+
+# Fasttext model evaluation -----------------------------------------------
+
+# Examine the nearest neighbors returned by our trained model. 
+# First vector element is the word to look up NN, and the second is a string used to filter the results
+
+nn_words  <- list(c("mad", "mad"),
+                  c("sad","sad"),
+                  c("upset", "upset"),
+                  c("late", "ate"),
+                  c("delay", "del"),
[…]

### 2019-04-19 Code/complaint-prediction/R/clus_func.R

@@ -1,0 +1,126 @@
+library(fastrtext)
+library(tidyverse)
+library(cluster)    # clustering algorithms
+library(factoextra) # clustering visualization
+library(dendextend) # for comparing two dendrograms
+library(parallel)
+library(pbapply)
+library(stringr)
+
+# This creates the average word vector to represent each tweet as an embedding vector
+avg_word_vec <- function(text, model) {
+  # tokenize the text, return a list of tokens
+  vec_of_tokens <- strsplit(text, " ")[[1]]
+  # apply get_word_vectors to each token in the vector, return matrix of word vecs
+  matrix_of_vecs <- get_word_vectors(model, vec_of_tokens)
+  # convert matrix to a tibble for easy reduction
+  tbl_of_vecs <- tbl_df(matrix_of_vecs) 
+  # summarise the word vector tibble into one average tibble
+  summarise_all(tbl_of_vecs, funs(mean), na.rm = TRUE)
+}
+
+nn_filter <- function(model, token, filter_str, n = 1000) {
+  out <- get_nn(model, token, n)
+  if(!is.na(filter_str)) {
+    tibble(word = names(out), value = out) %>% 
+      filter(!grepl(paste0(".*", filter_str, ".*"), word, ignore.case = T))
+  } else {
+    tibble(word = names(out), value = out)
+  }
+}
+
+model_eval <- function(token, ..., filter_str = NA) {
+  models <- list(...)
+  names(models) <- GetDotObjectNames(...)
+  cl <- detectCores()
+  pblapply(models, nn_filter, token, filter_str, cl = cl)
+}
+
+GetDotObjectNames <- function(...) {
+  strsplit(
+    gsub("[\\(\\)]", 
+         "", 
+         regmatches(
+           deparse(
+             substitute(
+               list(...))), 
+           gregexpr("\\(.*?\\)", 
+                    deparse(
+                      substitute(
+                        list(...)))))[[1]]), 
+    split = ", ")[[1]]
+}
+
+model_eval_plot <- function(eval_list, n = 20, token, filter_str) {
+  out <- lapply(names(eval_list), function(model) {
+    eval_list[[model]] %>% 
+      mutate(model = model)
+  }) %>% 
+    bind_rows() %>% 
+    group_by(model) %>% 
+    top_n(n, value) %>% 
+    ungroup() %>% 
+    arrange(model, value) %>% 
[…]

### 2019-04-19 Code/complaint-prediction/R/fasttext_clust_EDA.R

@@ -1,0 +1,813 @@
+library(googlesheets)
+library(plotly)
+library(broom)
+library(caret)
+library(cluster)
+library(qtlcharts)
+library(RPostgreSQL)
+library(dbplyr)
+source("Code/complaint-prediction/R/clus_func.R")
+
+# source("R/rquery_cormat.R") Note from Dallin: Where is this file?
+
+
+# connect to db -----------------------------------------------------------
+
+
+drv <- dbDriver("PostgreSQL")
+con <- dbConnect(drv, dbname = "MarketingAnalyticsClassData",
+                 host = "byumarketinganalytics.chaby6kshgs3.us-east-2.rds.amazonaws.com", port = 5555,
+                 user = "adrielc", password = "byuanalytics58") # This will prompt user
+dbListTables(con)
+
+
+
+# pull data sample --------------------------------------------------------
+
+
+Cockroaches <- tbl(con, "Cockroaches")
+
+sample_tweets <- 
+  Cockroaches %>% 
+  select(tweet_text) %>% 
+  mutate(tweet_text = tolower(tweet_text)) %>%
+  filter(substr(tweet_text, 1, 4) != "rt @") %>% 
+  head(900000) %>% 
+  collect()
+
+
+sample_tweets %>%
+  .$tweet_text %>% 
+  write_lines("data/tweet_sample_1mil.txt")
+
+
+# Remove retweets
+sample_tweets <- 
+  Cockroaches %>% 
+  filter(substr(tweet_text, 1, 4) != "RT @") %>% 
+  select(tweet_text) %>% 
+  head(1500000) %>% 
+  mutate(tweet_text = tolower(tweet_text)) %>%
+  collect()
+
+
+sample_tweets %>%
+  .$tweet_text %>%
+  write_lines("data/tweet_sample_1hM_noRT.txt")
+rm(sample_tweets) # After writing the .txt files, we are removing them from the environment with the rm() function
+
+
+
+# Remove retweets
+sample_tweets <- 
+  Cockroaches %>% 
+  filter(substr(tweet_text, 1, 4) != "RT @") %>% 
+  select(tweet_text) %>% 
+  head(2000000) %>% 
+  mutate(tweet_text = tolower(tweet_text)) %>%
+  collect()
+
+sample_tweets %>%
+  .$tweet_text %>%
[…]

### 2019-04-19 Code/complaint-prediction/R/logit_regression_classifier_Best.R

@@ -1,0 +1,211 @@
+library(tidyverse)
+library(qtlcharts)
+library(caret)
+source("Code/complaint-prediction/R/clus_func.R")
+source("Code/complaint-prediction/R/logit_classifier_func.R")
+
+# read in labeled data ----------------------------------------------------
+
+labeled_data <- read_csv("data/Marketing Research Labeled Tweets_ALL_10-30.csv")
+
+
+# featurize the data ------------------------------------------------------
+
+
+
+
+# add labels to our embedding data -----------------------------------------
+
+cor_data_50 <- 
+  test_out %>% 
+  dplyr::select(tweet_text, avg_vec_50) %>% 
+  unnest(avg_vec_50) %>% 
+  filter(tweet_text != "") %>% 
+  bind_cols(labels, .) %>% 
+  dplyr::select(-tweet_text1) %>% 
+  filter(!is.na(complaint_label)) %>% 
+  mutate(label = as.logical(complaint_label))
+
+# feature engineering -----------------------------------------------------
+
+cor_data_50_feat <- 
+  cor_data_50 %>% 
+  mutate(count.char   = nchar(tweet_text),
+         log.mentions = log1p(str_count(tweet_text, "@")), # Count user mentions
+         log.links    = log1p(str_count(tweet_text, "http:\\/\\/t.co")), # count links
+         count.space  = str_count(tweet_text, " ")) # count exclamation marks
+
+# plot correlations -------------------------------------------------------
+
+iplotCorr(cor_data_50[,-c(1,2)], cor_data_50$label, reorder=TRUE, chartOpts = list(scatcolors=c("lightblue", "lightgreen")))
+
+# Contribution analysis ---------------------------------------------------
+
+beta <- apply(cor_data_50[,-c(1,2)], 2, function(x,y) lm(y~x)$coef[2], cor_data_50$label)
+pos <- which(beta > 0)
+neg <- which(beta < 0)
+
+iplotCorr(cor_data_50[,-c(1,2)], cor_data_50$label, rows=pos, cols=neg, reorder=TRUE)
+
+# PCA for regression ------------------------------------------------------
+
+cor_data_50.pr <- prcomp(as.matrix(cor_data_50[,3:52]))
+
+# save the prcomp model
+cor.data.50.pr <- cor_data_50.pr
+save(cor.data.50.pr, file = "models/prcomp/cor.data.50.pr")
+
[…]

### 2019-04-19 Code/complaint-prediction/R/predict_func.R

@@ -1,0 +1,101 @@
+library(tidyverse)
+library(fastrtext)
+library(stringr)
+library(tidytext)
+
+
+# Testing Models ----------------------------------------------------------
+# fasttext.model.50 <- load_model("models/fasttext/model50.dat.bin")
+# fasttext.model.50_1 <- load_model("models/model50.dat.bin")
+# load("models/prcomp/cor.data.50.pr")
+# load("models/classifiers/logit_mod_0.856_acc")
+
+# kTestComplaint <- "@jetblue why are your employees so rude today at dallas-fort worth? tons of attitude on simple questions. #notimpressed"
+# kTestNonComplaint <- "@delta I love your service, it's always excellent"
+
+# Featurization -----------------------------------------------------------
+
+TweetFeatures <- function(tweet) {
+  # Creates features from the tweet which are used for prediction
+  # 
+  # Args:
+  #   tweet: a single tweet as a string
+  # 
+  # Returns:
+  #   a single-row tibble with the following columns: log.links, log.mentions, count.char, count.space
+  tibble(tweet.text = tweet) %>%
+    mutate(count.char   = nchar(tweet.text),
+           log.mentions = log1p(str_count(tweet.text, "@")), # Count user mentions
+           log.links    = log1p(str_count(tweet.text, "http:\\/\\/t.co")), # count links
+           count.space  = str_count(tweet.text, " ")) %>% # count exclamation marks
+    select(-tweet.text)
+}
+
+
+# Label Prediction -------------------------------------------------------
+
+predict.TweetComplaintPredictor <- function(object, newdata, complaintCutoff = 0) {
+  # Given a character vector containing tweets to predict for, this function returns predicted labels for the given tweet.
+  #
+  # Args:
+  #   object: TweetComplaintPredictor model
+  #   newdata: A character vector containing tweets  
+  #   complaintCutoff: a numeric value specifying the cutoff value for the xgb prediction output 
+  #       when considering what value to use to consider a tweet a complaint.
+  #
+  # Returns:
+  #   a string label. Either "Complaint" or "Non-Complaint"
+  #
+  
+  newdata %>% 
+    tibble(tweetText = .) %>% 
+    mutate(tweetFeatures = map(tweetText, TweetFeatures)) %>% 
+    mutate(fasttextVec = map(tweetText, VectorizeTweet, object$fasttextModel)) %>% 
[…]

### 2019-04-19 Code/rds-data-processing/Json_parse_upload.r

@@ -1,0 +1,81 @@
+library(RPostgreSQL)
+library(dbplyr)
+library(rjson)
+library(RCurl)
+library(tidyverse)
+
+
+
+# create_df(): ----------------------------------------------------------------
+### This function creates one row of a dataframe from a JSON object. This row can be uploaded to a database
+
+
+create_df <- function(data)
+{
+  tibble(
+    tweet_created_at = null_to_na(data$created_at),
+    tweet_id = null_to_na(data$id_str),
+    tweet_text = null_to_na(data$text),
+    in_reply_to_status_id_str = null_to_na(data$in_reply_to_status_id_str),
+    in_reply_to_user_id_str = null_to_na(data$in_reply_to_user_id_str),
+    in_reply_to_screen_name = null_to_na(data$in_reply_to_screen_name),
+    usr_name = null_to_na(data$user$name),
+    usr_screen_name = null_to_na(data$user$screen_name),
+    usr_url = null_to_na(data$user$url),
+    usr_description = null_to_na(data$user$description),
+    usr_protected = null_to_na(data$user$protected),
+    usr_followers_count = null_to_na(data$user$followers_count),
+    usr_friends_count = null_to_na(data$user$friends_count),
+    usr_listed_count = null_to_na(data$user$listed_count),
+    usr_created_at = null_to_na(data$user$created_at),
+    usr_statuses_count = null_to_na(data$user$statuses_count),
+    usr_verified = null_to_na(data$user$verified),
+    coordinates = null_to_na(data$coordinates),
+    tweet_retweet_count_at_pull_time = null_to_na(data$retweet_count),
+    tweet_favorite_count_at_pull_time = null_to_na(data$favorite_count),
+    tweet_hastags = null_to_na(data$entities$hashtags),
+    tweet_symbols = null_to_na(data$entities$symbols),
+    tweet_urls = null_to_na(data$entities$urls),
+    tweet_user_mentions = null_to_na(data$entities$user_mentions),
+    tweet_sentiment = null_to_na(data$sentiment),
+    date = null_to_na(data$date$`$date`),
+    oid = null_to_na(data$`_id`$`$oid`)
+  )
+}
+
+null_to_na <- function(x) ifelse(is.null(x), NA, x)
+
+# data import and upload --------------------------------------------------
+
+
+
+raw_data <- "data/tweetsFINAL.json"
+
[…]

### 2019-04-19 Code/rds-data-processing/classifier-testing.R

@@ -1,0 +1,21 @@
+library(fastrtext)
+library(Matrix)
+library(xgboost)
+source("Code/complaint-prediction/R/predict_func.R")
+source("Code/complaint-prediction/R/TweetComplaintPredictor.r")
+
+# load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
+load("Temporary/prcomp4.dat") # Dallin: Location has been edited for where I've kept the model
+
+# fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
+ fasttextModel <- load_model("Temporary/model50-tweet_sample_2M_noRT.dat.bin") # This is where I've kept the saved models
+
+
+# load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat") # This model was built in Code/complaint-prediction/R/classifier-construction.R
+load("Temporary/xgb.modelPC4.dat")
+ 
+TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)
+
+predict(TweetComplaintPredictor, "My mom died this week, and the cartel decapitated my father.")
+
+

### 2019-04-19 Paper/README.Rmd
Cleaning up the old latex code
Added MIT and Creative Common licenses

@@
 In this paper, we develop a model that uses a variety of observed customer complaints on Twitter to make inference about the severity of service failures.
+
+License: This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-sa/4.0/).
 
@@
 After accounting for differences in firm size, how accurately do these counts measure the true size of the population affected by the service failure (i.e., the reach of the service failure)?
-The counts could \emph{underestimate} the population size because not everyone that experiences a failure tweets about it.
+The counts could underestimate the population size because not everyone that experiences a failure tweets about it.
 However, users could tweet more than once, experience multiple failures, tweet a complaint without experiencing the failure, or be influenced by network effects -- which would all lead to observed counts that \emph{overestimate} the true population size.

### 2019-04-19 Code/dallin_annotations/07_build_classifier.Rmd

--- 2019-04-09 Code/dallin_annotations/08_classifier_construction.Rmd
@@
 library(fastrtext)
-library(magrittr) # for assignment operator %<>% 
+library(magrittr) # for assignment operator %<>%  Dallin: I will try to remove the use of %<>% to comply with the tidyverese stylguide.
 library(plotly)
@@
 library(Matrix)
-source("../complaint-prediction/R/clus_func.R")
+source("05_define_clustering_functions.R")
+source("06_define_prediction_functions.R")
 # source("../complaint-prediction/R/logit_classifier_func.R") This file does not exist
-
-# source("02_create_clusteringifunction.Rmd") New files not yet
 
@@
 # train the unsupervised fasttext model
+# I've commented out the training of this model because it has already been trained and the output has been saved to the Temporary folder.
+
 # fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
@@
 
+# FastText Model Evaluation
+This block looks at a handfull of words and creates a visualization to see how well the fasttext model predicts words similar to those provodied (the words defined as nn_words).
 ```{r}
-# Fasttext model evaluation -----------------------------------------------
-
 # Examine the nearest neighbors returned by our trained model. 
@@
 map(nn_words, function(x) model_eval_plot_wrap(x[1], fasttext_model, filter_str = x[2], n = 20))
+```
 
+# Create Average word Vectors
+Here, our training dataset is brought in.
+With the data loaded, we featureize the tweets and create average tweet vectors.
+The features of the tweets and average vectors are stored inside a list-column to help organize our data well.
+
+```{r}
 # Predict and average word vectors for tweets -----------------------------
@@
 # read in labeled traing data
+# train <- read_csv("data/Marketing Research Labeled Tweets All 12-05-18.csv") This was Adriel's code, but I have the data stored somewhere else.
+
+# I believe the file I'm linking to will be similar to the one that Adriel linked imported above (commented out).
 train <- read_csv("../../Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv") 
+# Update: I tried this and I think it causes problems in the code block under "# create a list column..." (currently line 69)
 
@@
 
-# PCA on fasttext vectors -------------------------------------------------
+# Dallin: It looks like there is a problem with the map() or VectorizeTweet function above. 
+# It doesn't seem to work well with mutate(). 
+# I don't understand how Adriel got this to work. ¯\_(ツ)_/¯
+# The little chunk below is myself troubleshooting an error.
 
+# I tried troubleshooting the problem with this code below, but it didn't work well
+# train <- train %>%
+#      mutate(avg_vec_50 = map(tweet_text, avg_word_vec(text = ., model = fasttext_model)))
+
+# I think I've fixed the problem by going into predict_func.R and removing the tbl_df() function and replacing it
+# with the as_tibble() function. It looks like the documentation is saying that the tbl_df() function has been removed
+# or something?
+```
+
+### Resulting Tweet Vectors
+```{r}
+
+```
+
+# PCA Analysis on the fastText Tweet Vectors
+
+### Train PCA Model
+```{r}
 # select the average vector column and perform a PCA
@@
   prcomp()
+```
 
+### Evaluate the PCA Model with 3D Graph
+```{r}
 # create a dataframe with the pca output to examine the first 3 components
@@
 # looks good to me. The complaints seperate well.
+```
 
+### Scree Plot of Principal Components
+```{r}
 # make a scree plot of the components
@@
 
-# Project word vectors onto PCA -------------------------------------------
+```
 
-train %<>% 
-  mutate(avg_vec_50_PCA = map(avg_vec_50, VectorizeTweet, model = train.pr, component = PC4))
+# Project Word Vectors onto PCA
+Here, we run the VectorizeTweet (PCA class) function on each of the tweet vectors. The VectorizeTweet PCA output summarizes the tweet vector in four principal components.
+```{r}
+train <- train %>% 
+  mutate(avg_vec_50_PCA = map(avg_vec_50, VectorizeTweet, model = train.pr, component = "PC4"))
+```
+
+```{r}
 
@@
 
-logregobj <- function(preds, dtrain) {
-  labels <- getinfo(dtrain, "label")
-  preds <- 1/(1 + exp(-preds))
-  grad <- preds - labels
-  hess <- preds * (1 - preds)
-  return(list(grad = grad, hess = hess))
-}
-
-evalerror <- function(preds, dtrain) {
-  labels <- getinfo(dtrain, "label")
-  err <- as.numeric(sum(labels != (preds > 0)))/length(labels)
-  return(list(metric = "error", value = err))
-}
-
 param <- list(max_depth = 2, eta = 1, silent = 1, nthread = 2, 

### 2019-04-19 Code/dallin_annotations/99_build_standalone_fasttext_classification_model.Rmd

---
title: "Fasttext Classification Model"
output: github_document
---
# Overview
In this file, I will make a fastText model for classification, and see how well it classifies on its own. Our team has already created a fasttext classifier; the purpose of this one is to help me better understand fastText as well as the code written by other team members. I hope that by creating the same classifier as other team members, I will encounter the same problems they did, and learn how to solve them.

##### Update:
I've been struggling to get the test, query, and training .txt files organized. I've also struggled to be able to make predictions using the fastrtext package. That's what I need to work on when I come back to this document.

# Libraries
```{r}
library(tidyverse)
library(fastrtext)
```

# Prepare Data
Our team has created a labeled test/train dataset for our classification model. It includes about 5,000 tweets that have been labeled with a binary classification (complaint, non-complaint) as well as with a more specific categorical label (delay, baggage, rude service, etc.).

We've created the dataset in a spreadsheet, but we need to do some reformatting before the data will be useful for fastText to use. We'll need to read in the data, reformat the labels, randomly assign some tweets to a test set, and others to a training set, and then reformat the data as a character vector instead of a dataframe.

##### Read in the Data
```{r}
data_path <- here::here("Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")

data <- read_csv(data_path)
```

##### Change Complaint Labels
The complaint labels need to be adjusted to be optimal for use in fastText. A label for "baggage" needs to look like "__label__baggage" in order for fastText to recognize it. 
```{r}
data <- data %>% 
  mutate(bi_label = case_when(complaint_label == 0 ~ "__label__non-complaint",
                              complaint_label == 1 ~ "__label__complaint"),
         multi_label = str_c("__label__", complaint_category)
  )

```

##### Randomly Assign Tweets to Test and Train Data
According to R for Data Science, the standard protocal for testing and training a dataset is to use 60% of your data for testing, 20% for a query dataset, and 20% for testing the model. This is the labeling protocol we will follow.
```{r}
set.seed(42)

# Create a vector of the same length as the data, where each integer has a 60% chance of being a 1, 20% chance of a 2, and 20% chance of being a 3.
ss <- sample(1:3, size = nrow(data), replace = TRUE, prob = c(0.6, 0.2, 0.2))

data <- data %>% 
  mutate(set = case_when(ss == 1 ~ "train",
                         ss == 2 ~ "query",
                         ss == 3 ~ "test")
         )
```

##### Make the Character Vectors for Each Dataset
We will create a character vector containing the binary labels, and another containing the multi-categorical labels. 
I need to get the data of these tweets organized into a set of binary labeled data and multi-labeled data. Additionally, I need to get these sets of data into character vectors (.txt files). So far, I've been struggling to organize my data.

In this code, the loop_list creates a list for storing the character vectors we create. 
```{r}
loop_list <- list(1, 2, 3, 4, 5, 6)

# These small tribbles contain the data that differs from loop to loop. I'm hoping that the bi_loop_data will help me create a quick loop for writing the tweets with labels to a character vector.

bi_loop_data <- tribble(
  ~"set",   ~"label_type",
  #-------|--------------|
  "train", "bi_label",
  "query", "bi_label",
  "test",  "bi_label"
)

multi_loop_data <- tribble(
  ~"set",   ~"label_type",
  #-------|--------------|
  "train", "multi_label",
  "query", "multi_label",
  "test",  "multi_label"
)

# This data will be used to identify the paths for each set of data, as well as their name
path_data <- tribble(
  ~ "path",                                         ~ "path_name",
  #-----------------------------------------------|--------------------|
  "../Temporary/train_test_data/binary_train.txt",  "train_bi_path",
  "../Temporary/train_test_data/binary_query.txt",  "query_bi_path",
  "../Temporary/train_test_data/binary_test.txt",   "test_bi_path",
  "../Temporary/train_test_data/multi_train.txt",   "train_multi_path",
  "../Temporary/train_test_data/multi_query.txt",   "query_multi_path",
  "../Temporary/train_test_data/multi_test.txt",    "test_multi_path"
)

# Make the loop for binary data
for (i in 1:nrow(bi_loop_data)) {
  loop_list[[i]] <- data %>%
    filter(set == bi_loop_data$set[i]) %>% 
    mutate(text = paste0(bi_label, " ", tweet_text)) %>% 
    pull(text)
}

# Make the loop for multi-label data
for (i in 1:nrow(multi_loop_data)) {
  loop_list[[i + 3]] <- data %>%
    filter(set == multi_loop_data$set[i]) %>% 
    mutate(text = paste0(multi_label, " ", tweet_text)) %>% 
    pull(text)
}

# Loop to create character vectors/write_lines()
write_lines(loop_list[1],path_data$path[1])

bi_train <- data %>%
    filter(set == "train") %>% 
    mutate(text = paste0(bi_label, " ", tweet_text)) %>% 
    pull(text)

train_data_lines <- test_train_data %>% 
  filter(test_train == "train") %>% 
  pull(input_lines) %>% 
  paste0("__label__", .)

```

# Train Model
Now it's time to train the model using the data we've prepared.
```{r}
bi_model_filepath <- "../Temporary/binary_fasttext_model.dat"
multi_model_filepath <- "../Temporary/multi_fasttext_model.dat"

# Train the Binary fastText Classification Model
  execute(commands = c("supervised", "-input", train_bi_path, "-output", bi_model_filepath, "-dim", 20, "-lr", 1,
                       "-epoch", 20,"-wordNgrams", 2, "-verbose", 1))

  # Train the Multi-Category fastText Classification Model
  execute(commands = c("supervised", "-input", train_multi_path, "-output", multi_model_filepath, "-dim", 20, "-lr", 1,
                       "-epoch", 20,"-wordNgrams", 2, "-verbose", 1))

```

# Test & Analyze Model
```{r}
# Load Models
bi_model <- load_model(bi_model_filepath)
multi_model <- load_model(multi_model_filepath)

# Make the query data an object
query_data <- data %>% 
  filter(set == "query") %>% 
  select(tweet_text, bi_label)

# Make Predictions on Models (Didn't work for me?)
# bi_predictions <- predict(bi_model, sentences = query_bi_path, simplify = TRUE, unlock_empty_predictions = TRUE)

 execute(commands = c("test", bi_model, query_bi_path))
```

### 2019-04-22 Code/dallin_annotations/02_visualize_twitter_data.Rmd
General reoganization of the dallin_annotations folder. This folder is meant to replace the rest of the code in the repository. It's the same code as before, just renamed and with more documentation.
Applied the use of the here::here() function across files 01-09 in dallin_annotations.

--- 2019-03-27 Code/dallin_code_annotations/05_counting_cockroaches.Rmd
@@
 These are my annotations on the "CountingCockroaches.R" file written by Adriel
+
+This file is meant to take our twitter data and produce a few visualizations.
+These visualizations helped us explore the tweets and get a generic grip on what people tweeted about in relation to these airlines.
+Understanding the data better helped us move forward with our analysis and model building.
 
@@
 
+# Libraries
 library(tidyverse); library(tidytext); library(tm); library(topicmodels)
-load("/Users/maddatascientist/DATA SCIENCE/Marketing RA/Twitter Subset2.Rdata") # file location dependent on user
+
+# Load Data
+load(here::here("Data", "Twitter Subset2.Rdata")) # file location dependent on user
 tweets <- twitter_subset

### 2019-04-22 Code/dallin_annotations/04_build_fasttext_supervised_classifier.Rmd
Applied the use of the here::here() function across files 01-09 in dallin_annotations.

--- 2019-03-01 Paper/01_build_classification_model.Rmd
@@
 ---
-title: "Classifier"
+title: "fastText Supervised Classifier"
 output: github_document
@@
 ```{r}
-# file_model <- "Output/models/class_mod_1.dat"
-# train_data_path <- "Output/clean_data/train_data_1.txt"
-# test_data_path <- "Output/clean_data/test_data_1.txt"
+# file_model <- here::here("Output", "models", "class_mod_1.dat")
+# train_data_path <- here::here("Output", "clean_data", "train_data_1.txt")
+# test_data_path <- here::here("Output", "clean_data", "test_data_1.txt")
 ```
@@
 
-# tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>%  
+# tweet_data <- read_csv(here:here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")) %>%  
 #  filter(nchar(tweet_text) > 5)

### 2019-04-22 Code/dallin_annotations/07_build_classifier.Rmd
Applied the use of the here::here() function across files 01-09 in dallin_annotations.

@@
 # file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"
-file_txt <- "../../Temporary/tweet_sample_1hM_noRT.txt"
+file_txt <- here::here("Temporary", "tweet_sample_1hM_noRT.txt")
 
 # new file to write the trained model to
-file_model50  <- "../../Temporary/model50-tweet_sample_2M_noRT.dat"
+file_model50  <- here::here("Temporary", "model50-tweet_sample_2M_noRT.dat")
 
@@
 # I believe the file I'm linking to will be similar to the one that Adriel linked imported above (commented out).
-train <- read_csv("../../Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv") 
+train <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv"))
 # Update: I tried this and I think it causes problems in the code block under "# create a list column..." (currently line 69)
@@
 
-save(train.pr, file = "models/fullClassifierOne/prcomp4.dat")
+save(train.pr, file = here:here("Output", "prcomp4.dat"))
 
-save(train, file = "models/fullClassifierOne/train_data.dat")
+save(train, file = here:here("Output", "train_data.dat"))
 
@@
 
-load("models/fullClassifierOne/train_data.dat")
+load(here:here("Output", "train_data.dat"))
 
@@
 
-save(bst, file = "models/fullClassifierOne/xgb.modelPC4.dat")
-xgb.save(bst, 'models/fullClassifierOne/xgb.modelPC4-xgb_version.dat')
-save(test_data, file = "models/fullClassifierOne/test_data.dat")
+save(bst, file = here:here("Output", "xgb.modelPC4.dat"))
+xgb.save(bst, here:here("Output", "xgb.modelPC4-xgb_version.dat"))
+save(test_data, file = here::here("Output", "test_data.dat"))
 

### 2019-04-22 Code/dallin_annotations/09_classifier_testing.Rmd
Applied the use of the here::here() function across files 01-09 in dallin_annotations.

@@
 library(xgboost)
-source("../complaint-prediction/R/predict_func.Rmd") # Formerly "R/predict_func.R" in Adriel's original code
-source("tweet_complaint_predictor.Rmd") # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
+source(here::here("Code", "dallin_annotations", "06_define_prediction_functions.R")) # Formerly "R/predict_func.R" in Adriel's original code
+source(here::here("Code", "dallin_annotations", "08_define_tweet_complaint_predictor_function.R")) # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
 ```
@@
 getwd()
+
+here:here()
 ```
@@
 ```{r}
-load("../../Temporary/prcomp4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
-fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
+load(here::here("Output", "prcomp4.dat")) # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
+fasttextModel <- load_model(here:here("Output", "model50-tweet_sample_2M_noRT.dat.bin"))
 # Model50 was built in fasttext_clust_EDA

### 2019-04-22 Code/dallin_annotations/01_test_rds_connection.R

@@ -53,8 +53,8 @@ sample_tweets <-
 
 # Once tweets are pulled in, write the lines to a file.
 sample_tweets %>%
-  .$tweet_text %>% 
-  write_lines("Output/clean_data/tweet_sample_1hM_noRT.txt")
+  .$tweet_text %>%
+  write_lines(here::here("Output", "clean_data", "tweet_sample_1hM_noRT.txt"))
 
 # Disconnect
 # It is always important do sever your connection to a database after you use it. 

### 2019-04-23 Code/dallin_annotations/07_build_classifier.Rmd
Added more documentation to file 07

@@
 # Train and Load the fastText Model
-Unsupervised fastText models produce word vectors. In other words, the create a mathmatical representation of the word. 
+Unsupervised fastText models produce word vectors. In other words, the create a mathmatical representation of the word. These word vectors will be used later to 
 ```{r}
@@
 # file to read tweets from. Should be a txt file with one tweet per line
-# file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"
 file_txt <- here::here("Temporary", "tweet_sample_1hM_noRT.txt")
@@
 # train the unsupervised fasttext model
-# I've commented out the training of this model because it has already been trained and the output has been saved to the Temporary folder.
-
+# Note: I've commented out the training of this model because it has already been trained and the output has been saved to the Temporary folder.
 # fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
@@
   mutate(avg_vec_50 = map(tweet_text, VectorizeTweet, model = fasttext_model))
-
-# Dallin: It looks like there is a problem with the map() or VectorizeTweet function above. 
-# It doesn't seem to work well with mutate(). 
-# I don't understand how Adriel got this to work. ¯\_(ツ)_/¯
-# The little chunk below is myself troubleshooting an error.
-
-# I tried troubleshooting the problem with this code below, but it didn't work well
-# train <- train %>%
-#      mutate(avg_vec_50 = map(tweet_text, avg_word_vec(text = ., model = fasttext_model)))
-
-# I think I've fixed the problem by going into predict_func.R and removing the tbl_df() function and replacing it
-# with the as_tibble() function. It looks like the documentation is saying that the tbl_df() function has been removed
-# or something?
 ```
 
-### Resulting Tweet Vectors
+### Analyzing the Outputs of What We Did Above
+The two sections below are the outputs of the code we ran above. for the example tweet first tweet, shown below.
 ```{r}
+train$tweet_text[[1]]
+```
 
+##### Resulting Tweet Features
+This is the output of the tweetFeatures() function.
+It just makes a small table of data explaining features of each tweet, such as the number of spaces, the number of exclamation points, the number of characters, etc.
+The data table shown below is the output for just one tweet.
+This small data table is then stored inside a list-column of the train data.
+```{r}
+train$tweetFeatures[[1]]
+```
+
+##### Resulting Tweet Vectors
+Similar to the output above, this is the output of the VectorizeTweet() function for just one tweet.
+If you are familiar with word vectors, you will notice that this small data table looks similar to a single word vector.
+This vector, however, is a compilation of every word vector from each word in a given tweet.
+With the example tweet above, the VectorizeTweet() function finds the word vector for the words "two," "airports," "one," "greeen," etc.
+The VectorizeTweet() function takes the word vector for each word in the tweet and averages each column.
+In theory, this should provide a mathematical summary for the entire tweet.
+```{r}
+train$avg_vec_50[[1]]
 ```
@@
 ### Train PCA Model
+This block of code trains the PCA model exclusively on the avg_vec_50 variable (the average tweet vector for each tweet).
 ```{r}
@@
 ### Evaluate the PCA Model with 3D Graph
+Here, we create a dataframe with the PCA output for each tweet, paired with the tweet labels and tweet text.
+The data is then plotted with the three PCA variables on the axes, and color mapped to complaint type.
+With this visualization, we can see that the PCA model groups complaints and non-complaints well.
 ```{r}

### 2019-04-23 Paper/paper.Rmd
Added more documentation to file 07

@@
 
-To use our model, we feed a set of tweets into a PCA model and a FastText classification model.
+To use our model, we fed a set of tweets into a PCA model and a FastText classification model.
 The output of these two models is then fed into our XGBoost model, which makes a binary prediction for the tweet as a complaint or non-complaint.
@@
 ## Overview
-In this section, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
+In this section, we'll document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
 
@@
 The idea behind PCA is that a complex multi-dimensional problem can be boiled down to a single-dimensional problem.
-For example, what if you had a model that tried to predict a student's grade on a test by looking at how many hours the student studied, how many lectures the student attended, how many hours of sleep they got, what cereal they eat for breakfast, and how many siblings they have.
+For example, let's say you had a model that tried to predict a student's grade on a test by looking at how many hours the student studied, how many lectures the student attended, how many hours of sleep they got, what cereal they eat for breakfast, and how many siblings they have.
 While all of these factors could arguably have an affect on the student's test grade, I would expect the "hours studied" and "lectures attended" variables to have the strongest correlation to test.
@@
 Quick Explanation of PCA: https://www.youtube.com/watch?v=HMOI_lkzW08
-https://www.youtube.com/watch?v=_UVHneBUBW0
+Deeper Explanation of PCA: https://www.youtube.com/watch?v=_UVHneBUBW0
 

### 2019-04-23 Code/dallin_annotations/06_define_prediction_functions.R

@@ -39,7 +39,8 @@ TweetFeatures <- function(tweet) {
     mutate(count.char   = nchar(tweet.text),
            log.mentions = log1p(str_count(tweet.text, "@")), # Count user mentions
            log.links    = log1p(str_count(tweet.text, "http:\\/\\/t.co")), # count links
-           count.space  = str_count(tweet.text, " ")) %>% # count exclamation marks
+           count.space  = str_count(tweet.text, " "),
+           count.excla = str_count(tweet.text, "!")) %>% # count exclamation marks
     select(-tweet.text)
 }
 

### 2019-04-26 Code/dallin_annotations/07_build_classifier.Rmd
Explained the PCA and XGBoost aspects of our model.

@@
 output: github_document
+allow_html_dependencies: true
 ---
@@
 library(Matrix)
+library(xgboost)
+library(caret)
+library(car)
+```
+
+```{r}
 source("05_define_clustering_functions.R")
@@
 # source("../complaint-prediction/R/logit_classifier_func.R") This file does not exist
+```
 
-library(xgboost)
-library(caret)
-library(car)
-
+```{r}
 set.seed(123)
@@
 
+# Dallin: This visualization of the PCA model was commented out because it caused problems with knitting.
+
 pca_evaluation <- as_data_frame(train.pr$x)
@@
 ### Scree Plot of Principal Components
+PCA models compress multi-dimensional issues into smaller "principal components." They identify trends and relationships in data, and these trends are summarized in "principal components." These principal components are responsible for describing a certain portion of the variance seen in the data.
+
+We are using this scree plot to analyze how many principle components can summarize the variance in our data well.
+The scree plot shows that with only two principal components, a large portion of the variance in the data can be described, and little of the remaining variance remains.
+
+When using our PCA model to make predictions, we want a model that is as simple as possible while describing the data well.
+In terms of PCA, this generally means that you want to use only a few principal components to describe the majority of variance in the data.
+The scree plot shown below helps do this by informing us how many principal components we should use to effectivly describe our training data.
+
+The scree plot shows variances (in other words, variance undescribed by the model) on the y-axis, and principal components on the x-axis.
+For example, with only one principal component, a large amount of variance remains in the data.
+With two principal components, however, we see that the amount of undescribed variance drops considerably.
+The rule of thumb with the scree plot is to identify the "elbow" (where the slope of the line starts to flatten out), and choose a number of principal components based on number of principal components at that point.
+Using this plot, for example, we will use the first four principal components of the model.
+Using four principal components will help us achieve a model that is both simple, and accurate.
+Using more than four principal components will result in significantly diminished returns -- it will slow down our model without providing a significant improvement to our model's predictive ability.
 ```{r}
@@
 # let's go with 15 components with this model.
+# Dallin: Do we want to go with 15 components? Not sure why...
 
@@
 
+### Output of VectorizeTweet() Function (PCA Class)
+Each principal component can be thought of as a single, compressed dimension.
+The values shown below represent the magnitude of the tweet along that single dimension.
+Plotting these values should result in a plot similar to the 3D scatter plot shown above.
 ```{r}
+train$avg_vec_50_PCA[[1]]
+```
 
-save(train.pr, file = here:here("Output", "prcomp4.dat"))
+# Save the Model Files
+Here, we save our PCA model (prcomp4.dat) and our training dataset (train_data.dat -- a dataset containing tweet text, along with its respecive tweet vector and PCA values).
 
-save(train, file = here:here("Output", "train_data.dat"))
+We then remove these models from the environment and reload them (this has helped ensure that our resulting output is truely independent.)
+```{r}
+save(train.pr, file = here::here("Output", "prcomp4.dat"))
+save(train, file = here::here("Output", "train_data.dat"))
 
@@
 
-load(here:here("Output", "train_data.dat"))
+load(here::here("Output", "train_data.dat"))
+```
 
+# Train the XGboost Model
+
+### Create a Training Index
+We need to separate our dataset (train_data.dat) into training data and test data for our xgboost model.
+The code below creates a list that randomly selects 80% of our dataset for training, leaving 20% of it for testing.
+```{r}
 trainIndex <- createDataPartition(train$complaint_label, p = .8, 
@@
                                   times = 1)
+```
 
+### Group the Testing and Training Datasets
+For each dataset (testing and training) we are creating a set of data containing the complaint labels associated with the tweet, as well as set containing the tweet's features, the tweet vector and the PCA output of the model.
+```{r}
 test_data <- train[-trainIndex,]
 test_labels <- test_data %>% select(complaint_label) %>% transmute(label = complaint_label)
+test_data_vec <- test_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)
+
 train_data <- train[trainIndex,]
@@
 train_data_vec <- train_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)
-test_data_vec <- test_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)
-
-dtrain <- xgb.DMatrix(sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label))
-dtest <- xgb.DMatrix(sparse.model.matrix(~.-1, test_data_vec), label = as.numeric(test_labels$label))
-dtest1 <- xgb.DMatrix(sparse.model.matrix(~.-1, test_data_vec))
-watchlist <- list(train = dtrain, eval = dtest)
-
-param <- list(max_depth = 2, eta = 1, silent = 1, nthread = 2, 
-              objective = logregobj, eval_metric = evalerror)
-
-bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label), max.depth = 4,
-               eta = 0.2, nthread = 2, nrounds = 100, objective = logregobj, eval_metric = evalerror)
-
-test_data$prediction <- predict(bst, dtest1)
-
-predict(bst, dtest1) %>% map_chr(function(x) ifelse(x > 0, "complaint", "non-complaint"))
-
-test_data %<>%
-  mutate(predict_label = case_when(prediction > 0 ~ "Complaint",
-                                   TRUE ~ "Non-complaint"),
-         complaint_label = case_when(complaint_label == 1 ~ "Complaint",
-                                   TRUE ~ "Non-complaint")) %>% 
-  mutate(accuracy = predict_label == complaint_label)
-
-confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))
-
-save(bst, file = here:here("Output", "xgb.modelPC4.dat"))
-xgb.save(bst, here:here("Output", "xgb.modelPC4-xgb_version.dat"))
-save(test_data, file = here::here("Output", "test_data.dat"))
 
 ```
+
+### Create Dense Matrices for XGBoost
+XGBoost models need matrices as inputs, not dataframes or tibbles.
+Here, we take our testing and training data, and turn it into a matrix instead.
+To make it easy to keep track of our matrices, we have stored both the training and test matrices in a single list (called watchlist).
+
+UPDATE: It looks like we don't even use these matrices later on..?
+Nevermind. dtest1 is needed.
+```{r}
+# I don't think the lines I have commented out are actually necessary for the model 
+# dtrain <- xgb.DMatrix(sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label))
+# dtest  <- xgb.DMatrix(sparse.model.matrix(~.-1, test_data_vec), label = as.numeric(test_labels$label))
+dtest1 <- xgb.DMatrix(sparse.model.matrix(~.-1, test_data_vec))
+# watchlist <- list(train = dtrain, eval = dtest)
+```
+
+### Set the Parameters of the Model and Begin Training
+
+```{r}
+# NOTE: All code below is commented out because this code had trouble knitting
+
+# bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label), max.depth = 4,
+#                eta = 0.2, nthread = 2, nrounds = 100, objective = logregobj, eval_metric = evalerror)
+```
+
+# Analyze the Model
+
+### Get Predictions from the Model
+Here, we let the model make predictions on our test dataset. We then compare the predictions to our actual labels to help us understand accuracy. 
+```{r}
+# test_data$prediction <- predict(bst, dtest1)
+# 
+# predict(bst, dtest1) %>% map_chr(function(x) ifelse(x > 0, "complaint", "non-complaint"))
+#   
+# 
+# test_data <- test_data %>% 
+#   mutate(predict_label = case_when(prediction > 0 ~ "Complaint",
+#                                    TRUE ~ "Non-complaint"),
+#          complaint_label = case_when(complaint_label == 1 ~ "Complaint",
+#                                    TRUE ~ "Non-complaint")) %>% 
+#   mutate(accuracy = predict_label == complaint_label)
+```
+
+### Look at the Confusion Matrix
+This Confusion matrix helps us see how many false postives and false negatives we had.
+For example, there were 85 instances where a tweet was predicted as a complaint, but it was not (false positive), and 38 instances where a complaint was not predicted to be a complaint, when it actually was (false negative).
+Overall, the model had an 87.59% accuracy, which seems pretty good to me.
+```{r}
+# confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))
+
+# The document had trouble knitting after knitting, so I've copied and pasted the output of the code from the line above.
+
+# Confusion Matrix and Statistics
+# 
+#                Reference
+# Prediction      Complaint Non-complaint
+#   Complaint           205            85
+#   Non-complaint        38           663
+#                                           
+#                Accuracy : 0.8759          
+#                  95% CI : (0.8537, 0.8958)
+#     No Information Rate : 0.7548          
+#     P-Value [Acc > NIR] : < 2.2e-16       
+#                                           
+#                   Kappa : 0.6852          
+#                                           
+#  Mcnemar's Test P-Value : 3.359e-05       
+#                                           
+#             Sensitivity : 0.8436          
+#             Specificity : 0.8864          
+#          Pos Pred Value : 0.7069          
+#          Neg Pred Value : 0.9458          
+#              Prevalence : 0.2452          
+#          Detection Rate : 0.2069          
+#    Detection Prevalence : 0.2926          
+#       Balanced Accuracy : 0.8650          
+#                                           
+#        'Positive' Class : Complaint   
+```
+
+### Save the Model
+```{r}
+# save(bst, file = here::here("Output", "xgb.modelPC4.dat"))
+# xgb.save(bst, here::here("Output", "xgb.modelPC4-xgb_version.dat"))
+# save(test_data, file = here::here("Output", "test_data.dat"))
+```

### 2019-04-26 Paper/paper.Rmd
Explained the PCA and XGBoost aspects of our model.

@@
 The output of these two models is then fed into our XGBoost model, which makes a binary prediction for the tweet as a complaint or non-complaint.
+I believe that the idea behind this "frankenstein model" is to use the perspectives of various styles of models to gain an accurate consensus on the data -- somewhat similar to the concept behind random forests.
 
@@
 
-## Useful Resources:
+## Details of the Use of PCA in Our Model
+We wanted to incorporate a PC analysis in our model, hoping that the perspective of a unique model type would aid our model's accuracy.
+As input, the PCA model needs numerical data, so we needed to convert our character data (tweet text) into numerical data.
+To do this, we used a fastText model again.
+Unlike the fastText model above, however, we decided to use an unsupervised fastText model for producing word vectors.
+
+Ultimately, we used PCA because we wanted to take our text data and process it in a way it could become quantitative data, believing that this would be a better format as an input for our XGBoost model.
+It is important to note that the PCA model was not capable of predicting complaints vs non-complaints, and never "saw" training labels when we trained it (it was unsupervised).
+Rather, it processed the textual data to provide quantitative data that grouped complaints and non-complaints fairly well, despite being unaware of the labels.
+
+### Using a fastText Unsupervised Model for Word Vectors
+This model, trained on the tweet text from our training dataset of nearly 5,000 tweets, learns the associations of words by analyzing how frequently pairs of words appear near each other.
+After running this analysis, the model can produce a word vector for any word -- even words it hadn't seen before.
+
+What are these word vectors?
+They represent a mathematical definition of a word.
+Via a method that is beyond the level of depth we'd like to explain in this paper, the output of this model (a vector containing 50 numbers for each word queried) is a representation of the associations one word has with all other words used in a corpus.
+Our model was specifically trained to produce word vectors of length 50, but this was simply a parameter we found to be most effective for our purposes (we explored this in the code fasttext_clust_EDA.R).
+Similar to the PCA model, it is important to note that this model that never "saw" our training labels (i.e.
+it was unsupervised), and was never capable of predicting complaints and non-complaints.
+Rather, it processed the textual data to provide a quantitative input for our principal component analysis.
+
+These word vectors also function well with additions and subtractions.
+For example, with word vectors, king - man + woman = queen.
+This fact is very useful to us, because it means that if we average the vectors for each word in a tweet, we should end up with a summary of a tweet in a single vector.
+We created a function that averaged word vectors, named "VectorizeTweet()." The function takes a single tweet, breaks its text down into a dataframe of each word used in the tweet, fetches the word vector for each word in the dataframe, and then averages each column of the vectors.
+This vectorized tweet summary became the numerical input for our PC analysis.
+
+### Analysis of Principal Components
+Once we had a list-column of average tweet vectors (avg_vec_50), we analyzed its principal components.
+We started with a 3D visualization of the first three principal components, coloring the tweets by their complaint/non-complaint labels, and found that the complaints and non-complaints grouped well.
+We also looked at a scree plot and found that four principal components would be effective enough to describe the variance in our data well.
+
+Once we saw that we should use four principal components, we then trained the PCA model using our dataset of about 5,000 tweets, and used the model to find the values for the four principal components for eqch tweet.
+This provided another numerical input we used in our next model, the XGboost model.
+
+## Useful Resources for PCA:
 Quick Explanation of PCA: https://www.youtube.com/watch?v=HMOI_lkzW08
-Deeper Explanation of PCA: https://www.youtube.com/watch?v=_UVHneBUBW0
+Slightly Deeper Explanation of PCA: https://www.youtube.com/watch?v=_UVHneBUBW0
 
@@
 
-## Useful Resources:
+## Our Use of the XGBoost Model
+At this point, we had three sets of quantitative data on our tweets as inputs for our XGboost model: averaged tweet vectors, PCA outputs for four principal components, and a set of tweet features.
+I haven't mentioned the tweet features yet, but it was a simple step we took to gather crude data on the tweet.
+We created a function that calculated various details on a tweet, such as the number of spaces, the number of characters, and the number of exclamation points used in a tweet.
+After we ran this function on each tweet, the data was stored in a list-column called tweetFeatures.
+
+We partitioned our dataset of 5,000 tweets (now processed to include tweet features, a tweet vector, and four principal component values) so that 80% was designated for training, and 20% was designated for testing.
+We then transformed our tibble of data into a dense matrix (the format required for XGBoost).
+We trained the XGBoost model, allowed the model to make predictions on our test dataset, and then compared the resulting predictions against our testing dataset's labels using a confusion matrix.
+We found our XGBoost model to be 87.59% accurate, with 85 false positives, and 38 false negatives.
+
+## Useful Resources for XGBoost:
 When I was first learning about XGBoost, I found these youtube videos to be helpful in explaining the very basic concepts behind boosted trees.

### 2019-05-02 Code/dallin_annotations/04_build_fasttext_supervised_classifier.Rmd
Made edits and knitted file 04. I used the error = TRUE argument in the code chunks to show code actions previously hidden. Made a new visualization about predictions.

--- 2019-03-01 Code/01_build_classification_model.Rmd
@@
 ---
-title: "Classifier"
+title: "fastText Supervised Classifier"
 output: github_document
 ---
+
+```{r include=FALSE} knitr::opts_chunk$set(error = TRUE) ```
 
@@
 library(tidyverse)
+
+set.seed(42)
 ```
@@
 In our case, we want to store the model in Output/models and name the model class_mod_1.dat.
-Within R, we'll refer to this file path as file_model.
+Within R, we'll refer to this file path as model_path.
 
@@
 ```{r}
-file_model <- "Output/models/class_mod_1.dat"
-train_data_path <- "Output/clean_data/train_data_1.txt"
-test_data_path <- "Output/clean_data/test_data_1.txt"
+model_path <- here::here("Output", "models", "class_mod_1.dat")
+train_data_path <- here::here("Output", "clean_data", "train_data_1.txt")
+test_data_path <- here::here("Output", "clean_data", "test_data_1.txt")
 ```
@@
 
-# tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>%  
-#  filter(nchar(tweet_text) > 5)
+tweet_data <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")) %>%
+ filter(nchar(tweet_text) > 5)
 ```
@@
 ```{r}
-# test_train_data <- 
-#   tweet_data %>% 
-#   mutate(label = case_when(label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
-#                               label == 1 ~ "complaint"),
-#             input_lines = paste(label, tweet_text)) %>% 
-#   group_by(label) %>% # get a representative sample of both complaints and non complaints
-#   mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
-#   ungroup()
+test_train_data <- tweet_data %>%
+  mutate(label = case_when(complaint_label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
+                              complaint_label == 1 ~ "complaint"),
+            input_lines = paste(label, tweet_text)) %>%
+  group_by(label) %>% # get a representative sample of both complaints and non complaints
+  mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
+  ungroup()
 ```
@@
 # write train data
-# train_data_lines <- 
-#   test_train_data %>% 
-#   filter(test_train == "train") %>% 
-#   pull(input_lines) %>% 
-#   paste0("__label__", .)
-# 
-# write_lines(train_data_lines, train_data_path)
-# 
-# # write test data
-# test_data_lines <- 
-#   test_train_data %>% 
-#   filter(test_train == "test") %>% 
-#   pull(input_lines) %>% 
-#   paste0("__label__", .)
-# 
-# write_lines(test_data_lines, test_data_path)
+train_data_lines <- test_train_data %>%
+  filter(test_train == "train") %>%
+  pull(input_lines) %>%
+  paste0("__label__", .)
+
+write_lines(train_data_lines, train_data_path)
+
+# write test data
+test_data_lines <- test_train_data %>%
+  filter(test_train == "test") %>%
+  pull(input_lines) %>%
+  paste0("__label__", .)
+
+write_lines(test_data_lines, test_data_path)
 
@@
 # train model
-execute(commands = c("supervised", "-input", train_data_path, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
+execute(commands = c("supervised", "-input", train_data_path, "-output", model_path, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
 
 # load model
-model <- load_model(file_model)
+model <- load_model(model_path)
 ```
@@
 predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
+
 head(predictions, 5)
@@
 This will help us confirm that our model worked as expected.
+The predictions are shorter than the test dataset, so I'm not sure what happened.
+According to some errors I've seen, I think it's because a few tweets use vocabulary that was not included in the training dataset.
 ```{r}
@@
 
-## Accuracy
+A second attempt to make predictions:
+```{r error = TRUE}
+tested <- test_train_data %>% 
+  filter(test_train == "test") %>% 
+  mutate(prediction = predict(model, tweet_text, unlock_empty_predictions = TRUE)) %>% 
+  unnest(prediction) %>% 
+  mutate(rounded_prediction = round(prediction),
+         correct            = case_when(complaint_label == rounded_prediction ~ TRUE,
+                                        complaint_label != rounded_prediction ~ FALSE))
+```
+
+Visualization of Outputs:
+From this graph, apparently I messed up somewhere in making predictions, because the predictions being made seem to have no correlation with the actual complaint label.
+It could be that, or the fastText model needs significantly more text to train and be accurate.
+```{r}
+tested %>% 
+  ggplot(aes(x = row_number(tweet_text), y = prediction, color = complaint_label, alpha = 0.1)) +
+  geom_point()
+```
+
+Is the list "predictions" the same as the "prediction" variable in tested?
+```{r}
+are_they_same <- c(tested$prediction[[3]],
+                   predictions[[3]],
+                   tested$prediction[[300]],
+                   predictions[[300]])
+
+(are_they_same)
+```
+The predictions are exactly the same from both sets, so I guess the classifier was just bad?
+
+I'll try to use our fasttext model using bash.
+Navigate to the right directory of the model:
+```{bash error = TRUE}
+cd ../../Output/models/class_mod_1.bin
+ls
+```
+
+```{bash error = TRUE}
+./fasttext predict ../../Output/models/class_mod_1.bin - @delta you are the worst airline. Thanks for delaying my flight
+```
+This didn't work
+
+Second attempt to make predictions using bash
+```{bash error = TRUE}
+cd ../../Output/models
+
+./fasttext predict class_mod_1.bin - @delta you are the worst airline. Thanks for delaying my flight
+```
+
+Third attempt to make predictions using bash.
+```{bash error = TRUE}
+cd ../../../../../../fasttext/fastText-0.2.0
+ls
+```
+
+f## Accuracy
 Let's look at how accurately the model predicted names
-```{r}
+```{r error = TRUE}
 # Compute accuracy
@@
 Hamming loss is most useful when applied to multi-classifiers because when it is done with binary classifiers (such as ours), it is simply equal to 1 - accuracy.
-```{r}
+```{r error = TRUE}
 # because there is only one category by observation, hamming loss will be the same

### 2019-05-02 Code/dallin_annotations/07_build_classifier.Rmd
I used error = TRUE to reveal code that had been commented-out (i.e. the confusion matrix).

@@
 
-# bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label), max.depth = 4,
-#                eta = 0.2, nthread = 2, nrounds = 100, objective = logregobj, eval_metric = evalerror)
+bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label), max.depth = 4,
+               eta = 0.2, nthread = 2, nrounds = 100, objective = logregobj, eval_metric = evalerror)
 ```
@@
 ```{r}
-# test_data$prediction <- predict(bst, dtest1)
-# 
-# predict(bst, dtest1) %>% map_chr(function(x) ifelse(x > 0, "complaint", "non-complaint"))
-#   
-# 
-# test_data <- test_data %>% 
-#   mutate(predict_label = case_when(prediction > 0 ~ "Complaint",
-#                                    TRUE ~ "Non-complaint"),
-#          complaint_label = case_when(complaint_label == 1 ~ "Complaint",
-#                                    TRUE ~ "Non-complaint")) %>% 
-#   mutate(accuracy = predict_label == complaint_label)
+test_data$prediction <- predict(bst, dtest1)
+
+predict(bst, dtest1) %>% map_chr(function(x) ifelse(x > 0, "complaint", "non-complaint"))
+
+test_data <- test_data %>%
+  mutate(predict_label = case_when(prediction > 0 ~ "Complaint",
+                                   TRUE ~ "Non-complaint"),
+         complaint_label = case_when(complaint_label == 1 ~ "Complaint",
+                                   TRUE ~ "Non-complaint")) %>%
+  mutate(accuracy = predict_label == complaint_label)
 ```
@@
 ```{r}
-# confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))
+confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))
 

### 2019-05-02 Paper/paper.Rmd
I included a few edits to my own phrasing and explanation of the model. I also included  a few more visualizations and code chunks that helped explain the model's performance and accuracy.

@@
 ---
-title: "Classifier"
+title: "Classifier Explanation"
 output: github_document
 ---
+```{r include = FALSE}
+library(tidyverse)
+library(caret)
+library(xgboost)
+library(Matrix)
+
+train <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv"))
+```
 # The Classification Model
@@
 
-While there are a massive number of methods to perform this task, our team has identified three tools to aid us in our classification: Principal Component Analysis (PCA), FastText, and XGBoost.
+While many methods available can aid us in this task, our team has identified three tools to help us perform our classification: Principal Component Analysis (PCA), fastText, and XGBoost.
 Using these three tools, we've created a "frankenstein model" that incorporates all three tools listed above.
-The model has been trained on 2,500 tweets labeled 0 for "non-complaint" and 1 for "complaint." We have then tested the model on a similarly-sized dataset.
+The model has been tested and trained on `r nrow(train) # the number of tweets in our training dataset` tweets labeled 0 for "non-complaint" and 1 for "complaint." We partitioned the data so that about 80% was used for training, and 20% for testing.
 
-To use our model, we fed a set of tweets into a PCA model and a FastText classification model.
-The output of these two models is then fed into our XGBoost model, which makes a binary prediction for the tweet as a complaint or non-complaint.
+To use our model, we fed a set of tweets into a PCA model.
+The output of the PCA model (unsupervised) was then fed into an XGBoost model (supervised).
+Simultaneously, we fed the same set of tweets into a fastText classification model (supervised).
+The frankenstien model then compares predictions of the XGBoost and fastText models, and makes a final prediction.
 I believe that the idea behind this "frankenstein model" is to use the perspectives of various styles of models to gain an accurate consensus on the data -- somewhat similar to the concept behind random forests.
@@
 
-# The FastText Sub-Model
+# The fastText Sub-Model
 ## Overview
-In this section, we'll document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
+In this section, we will document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
 
@@
 
-!!!!!! Considering that this is such a large dataset, it might be worthwhile to use -loss hs (hierarchical softmax) to speed up the training. It should not significantly affect accuracy.
-
 ```{r}
@@
 We started with a 3D visualization of the first three principal components, coloring the tweets by their complaint/non-complaint labels, and found that the complaints and non-complaints grouped well.
+
+![3D visualization of first three principal components.](../Figures/3D_PCA.png)
+
 We also looked at a scree plot and found that four principal components would be effective enough to describe the variance in our data well.
+
+![Scree plot.](../Figures/screeplot.png)
 
@@
 
+```{r include = FALSE}
+source(here::here("Code", "dallin_annotations", "06_define_prediction_functions.R"))
+
+load(here::here("Output", "train_data.dat"))
+
+trainIndex <- createDataPartition(train$complaint_label, p = .8, 
+                                  list = FALSE, 
+                                  times = 1)
+
+test_data <- train[-trainIndex,]
+test_labels <- test_data %>% select(complaint_label) %>% transmute(label = complaint_label)
+test_data_vec <- test_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)
+
+train_data <- train[trainIndex,]
+train_labels <- train_data %>% select(complaint_label) %>% transmute(label = complaint_label)
+train_data_vec <- train_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)
+
+dtest1 <- xgb.DMatrix(sparse.model.matrix(~.-1, test_data_vec))
+
+bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), label = as.numeric(train_labels$label), max.depth = 4,
+               eta = 0.2, nthread = 2, nrounds = 100, objective = logregobj, eval_metric = evalerror)
+
+test_data$prediction <- predict(bst, dtest1)
+
+predict(bst, dtest1) %>% map_chr(function(x) ifelse(x > 0, "complaint", "non-complaint"))
+
+test_data <- test_data %>%
+  mutate(predict_label = case_when(prediction > 0 ~ "Complaint",
+                                   TRUE ~ "Non-complaint"),
+         complaint_label = case_when(complaint_label == 1 ~ "Complaint",
+                                   TRUE ~ "Non-complaint")) %>%
+
+    mutate(accuracy = predict_label == complaint_label)
+```
+
+Confusion matrix output:
+```{r}
+confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))
+```
+
 ## Useful Resources for XGBoost:

### 2019-05-02 Code/dallin_annotations/09_classifier_testing.Rmd
I cleaned up some comments that didn't seem necessary to me.

@@
 ##### predict_func.R
-* Renamed as 11_predict_func.Rmd in this folder.
+* Renamed as 06_define_prediction_functions.R in this folder.
 * FOUND
@@
 ##### TweetComplaintPredictor.r
-* Renamed as 12_tweet_complaint_predictor.Rmd in this folder.
+* Renamed as 08_define_tweet_complaint_predictor_function.R in this folder.
 * FOUND
@@
 library(xgboost)
-source(here::here("Code", "dallin_annotations", "06_define_prediction_functions.R")) # Formerly "R/predict_func.R" in Adriel's original code
-source(here::here("Code", "dallin_annotations", "08_define_tweet_complaint_predictor_function.R")) # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
+
+source(here::here("Code", "dallin_annotations", "06_define_prediction_functions.R"))
+source(here::here("Code", "dallin_annotations", "08_define_tweet_complaint_predictor_function.R"))
 ```
@@
 ```{r}
-load(here::here("Output", "prcomp4.dat")) # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
-fasttextModel <- load_model(here:here("Output", "model50-tweet_sample_2M_noRT.dat.bin"))
-# Model50 was built in fasttext_clust_EDA
+load(here::here("Output", "prcomp4.dat"))
+fasttextModel <- load_model(here::here("Output", "model50-tweet_sample_2M_noRT.dat.bin"))
+load(here::here("Output", "xgb.modelPC4.dat"))
 
-load("../../Temporary/xgb.modelPC4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat" in Adriel's original code
-TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)
-
+TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, "PC4")
 ```
@@
 ```{r}
-predict(TweetComplaintPredictor, "")
+predict(TweetComplaintPredictor, "Hey why do dogs bark at mailmen?")
 
 ```
+
+Dallin: practicing with the new model
+```{r}
+train %>% 
+  head(10)
+
+```

### 2019-05-08 Paper/paper.Rmd
Added more documentation for XGBoost, I also clarified the use of the fastText classification model.

@@
 
-To use our model, we fed a set of tweets into a PCA model.
+To use our model, we fed a set of tweets into a fastText word representations model (unsupervised).
+After summarizing the ouput of this model, we take the fastText model output and send it through a PCA model.
 The output of the PCA model (unsupervised) was then fed into an XGBoost model (supervised).
-Simultaneously, we fed the same set of tweets into a fastText classification model (supervised).
-The frankenstien model then compares predictions of the XGBoost and fastText models, and makes a final prediction.
+The XGBoost model then compares predictions of the PCA and fastText models, and makes a final prediction.
 I believe that the idea behind this "frankenstein model" is to use the perspectives of various styles of models to gain an accurate consensus on the data -- somewhat similar to the concept behind random forests.
@@
 
-# The fastText Sub-Model
+In our repository, you will also find that we train and test a fastText classification model (supervised).
+This model is simply another attempt to create a classification model, and can be thought of as a baseline comparison to the frankenstien model.
+
+# The fastText Classification Model
 ## Overview
@@
 
+XGBoost Documentation: https://xgboost.readthedocs.io/en/latest/R-package/xgboostPresentation.html
 Decision Trees: https://www.youtube.com/watch?v=7VeUPuFGJHk

### 2019-05-08 Code/dallin_annotations/04_build_fasttext_supervised_classifier.Rmd
Created a visualization of the accuracy of the fastText model, along with a few notes explaining our thought process behind making the model.

@@
 In this R Markdown, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
+
+The supervised model built in this script is not used in the "frankenstien model." Instead, it is a standalone classification model.
+This is a way for us to compare the frankenstien model's performance to a "baseline."
 
@@
 
-!!!!!!!!!! I'm still not sure how we are using the test_labels_without_prefix. If its not the test data, what is it?
-
 ```{r}
@@
 
-This will help us confirm that our model worked as expected.
-The predictions are shorter than the test dataset, so I'm not sure what happened.
-According to some errors I've seen, I think it's because a few tweets use vocabulary that was not included in the training dataset.
+Below we compare the length of the list of predictions to the length of the testing dataset. Ideally, these should have the same length. This will help us confirm that our model worked as expected.
+
 ```{r}
@@
 
-A second attempt to make predictions:
-```{r error = TRUE}
+Unexpectedly, the predictions are shorter than the test dataset, so I'm not sure what happened.
+According to some errors I've seen, I think it's because a few tweets use vocabulary that was not included in the training dataset.
+
+Below, we merge the predictions with our testing dataset, preparing the data for visualizations.
+```{r}
+new_predictions <- attributes(predictions)$names
+
 tested <- test_train_data %>% 
@@
   unnest(prediction) %>% 
-  mutate(rounded_prediction = round(prediction),
-         correct            = case_when(complaint_label == rounded_prediction ~ TRUE,
-                                        complaint_label != rounded_prediction ~ FALSE))
+  mutate(new_predictions = new_predictions,
+         correct = case_when(label == new_predictions ~ TRUE,
+                             label != new_predictions ~ FALSE))
 ```
@@
 Visualization of Outputs:
-From this graph, apparently I messed up somewhere in making predictions, because the predictions being made seem to have no correlation with the actual complaint label.
-It could be that, or the fastText model needs significantly more text to train and be accurate.
+Below, we have a bar graph of our testing data and the model's predictions.
+The columns represent the labels from our testing dataset.
+The fill is the model's predictions.
+We see that the model seems to make a lot of false positives, but provides almost no false negatives.
 ```{r}
 tested %>% 
-  ggplot(aes(x = row_number(tweet_text), y = prediction, color = complaint_label, alpha = 0.1)) +
-  geom_point()
+  ggplot(aes(x = label, fill = new_predictions)) +
+  geom_bar()
 ```
 
-Is the list "predictions" the same as the "prediction" variable in tested?
+## Accuracy
+Let's look at how accurately the model predicted binary complaints.
 ```{r}
-are_they_same <- c(tested$prediction[[3]],
-                   predictions[[3]],
-                   tested$prediction[[300]],
-                   predictions[[300]])
+tested %>% 
+  summarise(accuracy = mean(correct))
+```
+It looks like this model is about 60% accurate.
+This isn't great, but it's better than flipping a coin.
+Perhaps the model will perform significantly better with a larger dataset for training and testing.
 
-(are_they_same)
-```
-The predictions are exactly the same from both sets, so I guess the classifier was just bad?
-
-I'll try to use our fasttext model using bash.
-Navigate to the right directory of the model:
-```{bash error = TRUE}
-cd ../../Output/models/class_mod_1.bin
-ls
-```
-
-```{bash error = TRUE}
-./fasttext predict ../../Output/models/class_mod_1.bin - @delta you are the worst airline. Thanks for delaying my flight
-```
-This didn't work
-
-Second attempt to make predictions using bash
-```{bash error = TRUE}
-cd ../../Output/models
-
-./fasttext predict class_mod_1.bin - @delta you are the worst airline. Thanks for delaying my flight
-```
-
-Third attempt to make predictions using bash.
-```{bash error = TRUE}
-cd ../../../../../../fasttext/fastText-0.2.0
-ls
-```
-
-f## Accuracy
-Let's look at how accurately the model predicted names
 ```{r error = TRUE}
@@
 ```
-
-# Analysis

### 2019-05-08 Code/dallin_annotations/11_build_multi_classifier.Rmd
Built and analyzed a classifier for multiple complaint categories. This uses the same foundation as the "frankenstein model" in file 07_build_classifier.Rmd

---
title: "Building a Frankenstien Classification Model for Multiple Complaint Labels"
output: github_document
---

# Overview
In this document, I will try to make a classification model similar to the one in 07_build_classifier.Rmd. The difference here will be that I will attempt to build a classification model meant to predict based on a set of many complaint categories.

# Libraries and Scripts
```{r echo = FALSE}
library(tidyverse)
library(fastrtext)
library(magrittr)
library(plotly)
require(randomForest)
library(Matrix)
library(xgboost)
library(caret)
library(car)

set.seed(42)

source("05_define_clustering_functions.R")
source("06_define_prediction_functions.R")
```

## Load the Training Dataset
This dataset was created in file 07_build_classifier.Rmd
```{r}
load(here::here("Output", "train_data.dat"))
```

Modify the training dataset to make it ready for a multi classification
```{r}
train <- train %>% 
  mutate(complaint_category_name = complaint_category) %>% 
  mutate(complaint_category = case_when(complaint_category_name == "non_complaint"         ~ 1,
                                        complaint_category_name == "delay_delay"           ~ 2,
                                        complaint_category_name == "event_specific"        ~ 3,
                                        complaint_category_name == "event_vague"           ~ 4,
                                        complaint_category_name == "human_service_rude"    ~ 5,
                                        complaint_category_name == "baggage"               ~ 6,
                                        complaint_category_name == "app_failure"           ~ 7,
                                        complaint_category_name == "delay_cancel"          ~ 8,
                                        complaint_category_name == "human_service_hold"    ~ 9,
                                        complaint_category_name == "delay_tarmac"          ~ 10,
                                        complaint_category_name == "wishlist"              ~ 11,
                                        complaint_category_name == "check_failure"         ~ 12))
```

I will make sure that the mutated data matches the original data.
```{r}
train %>% 
  count(complaint_category_name, complaint_category, sort = TRUE) %>% 
  mutate(complaint_category_name = reorder(complaint_category_name, n))
```
We see that every datapoint has been matched, so we're good!

## Partition the Dataset
```{r}
trainIndex <- createDataPartition(train$complaint_category, p = .8, 
                                  list = FALSE, 
                                  times = 1)

test_data <- train[-trainIndex,]
test_labels <- test_data %>% select(complaint_category) %>% transmute(label = complaint_category)
test_data_vec <- test_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)

train_data <- train[trainIndex,]
train_labels <- train_data %>% select(complaint_category) %>% transmute(label = complaint_category)
train_data_vec <- train_data %>%  select(tweetFeatures, avg_vec_50, avg_vec_50_PCA) %>% unnest %>% mutate_all(as.numeric)
```

## Create Dense Matricies for XGBoost
```{r}
dtest1 <- xgb.DMatrix(sparse.model.matrix(~.-1, test_data_vec))
```

## Set the Parameters of the Model and Begin Training
```{r error = TRUE}
bst <- xgboost(data = sparse.model.matrix(~.-1, train_data_vec), 
               label = as.factor(train_labels$label),
               max.depth = 4, 
               eta = 0.2, 
               nthread = 2, 
               nrounds = 100, 
               num_class = 13,
               objective = "multi:softmax",
               eval_metric = evalerror)
```
The train-error does not improve with iterations, which is concerning to me.

`# Get Predictions on the Model
```{r error = TRUE}
test_data$prediction <- predict(bst, dtest1)

predict(bst, dtest1)
```

!!!!! I messed up on the predictions and will need to come back to this to see how to fix it.

```{r error = TRUE}
test_data %>% 
  ggplot(aes(x = as.factor(complaint_category), fill = as.factor(prediction))) +
  geom_bar() +
  coord_flip()
```
We see that the model isn't especially accurate, but also that for many test labels, the majority of the predicitions (that aren't non complaints) are correct (i.e. 1 matches 1, 2 matches 2, 4 matches 4, etc.). The model could definitely be improved, but it performs better than rolling the dice.

## Accuracy
```{r}
test_data <- test_data %>% 
  mutate(correct = complaint_category == prediction)

test_data %>% 
  summarise(mean(correct))
```
The model is 76% accurate, which is suprisingly good! It definitely has room for improvement though. I would guess that the model's ability to correctly estimate the majority of non complaints has helped the model perform well.

How does the model perform when we focus solely on complaints though?

Visualization of complaint categories:
```{r}
test_data %>% 
  filter(complaint_category != 1) %>% 
  ggplot(aes(x = as.factor(complaint_category), fill = as.factor(prediction))) +
  geom_bar() +
  coord_flip()
```

Accuracy of non-complaint predictions:
```{r}
test_data %>% 
  filter(complaint_category != 1) %>% 
  summarise(mean(correct))
```
It appears that when predicting non-complaints, the model is only accurate about 25% of the time. This is very poor, but better than rolling the dice.

```{r error = TRUE}
confusionMatrix(factor(test_data$complaint_category), factor(test_data$prediction))
```

### 2019-05-08 Code/dallin_annotations/10_build_fasttext_multi_classifier.Rmd
Built a fastText classifier for multiple complaint categories (similar to the classifier built in file 04). This model isn't very accurate, but it's a start.

---
title: "Building a fastText Classifier for Multiple Labels (Supervised)"
output: github_document
---
# Overview
In this document, I create a fastText classification model that predicts complaints by the various complaint categories we created in our test/train dataset. This model is very simple, and uses fastText exclusively for classification.

## Load Packages
```{r}
library(fastrtext)
library(tidyverse)

set.seed(42)
```

Set the paths to the model, testing, and training data. Once the data and models are created, this is where they will be saved.
```{r}
model_path <- here::here("Output", "models", "fasttext_multi_class_model.dat")
train_data_path <- here::here("Output", "clean_data", "rain_multi_data_1.txt")
test_data_path <- here::here("Output", "clean_data", "test_multi_data_1.txt")
```

## Read in the Data
```{r}
tweet_data <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")) %>%
 filter(nchar(tweet_text) > 5)
```

## Partition Data for Testing and Training
```{r}
test_train_data <- tweet_data %>%
  mutate(input_lines = paste(complaint_category, tweet_text)) %>%
  group_by(complaint_category) %>% # get a representative sample of both complaints and non complaints
  mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
  ungroup()
```

## Create .txt Files
As input, the fastText model needs to take the testing and training data as .txt files.
```{r}
# write train data
train_data_lines <- test_train_data %>%
  filter(test_train == "train") %>%
  pull(input_lines) %>%
  paste0("__label__", .)

write_lines(train_data_lines, train_data_path)

# write test data
test_data_lines <- test_train_data %>%
  filter(test_train == "test") %>%
  pull(input_lines) %>%
  paste0("__label__", .)

write_lines(test_data_lines, test_data_path)

# create a character vector containing the tweets to test without their labels
test_labels_without_prefix <-
  test_train_data %>%
  filter(test_train == "test") %>%
  pull(complaint_category)
```

## Train the fastText Classification Model (Supervised, Multiple Categories)
```{r}
# train model
execute(commands = c("supervised", "-input", train_data_path, "-output", model_path, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))

# load model
model <- load_model(model_path)
```

## Review Model
```{r}
predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)

head(predictions, 5)
```

Below we compare the length of the list of predictions to the length of the testing dataset. Ideally, these should have the same length. This will help us confirm that our model worked as expected.
```{r}
length(predictions)
length(test_labels_without_prefix)
length(test_data_lines)
```
Similar to the previous fastText model, it appears the model would not make predictions on a few of the tweets in the testing dataset. This is likely due to the size of our training dataset as well as the variance in vocabulary for tweets.

Below, we merge the predictions with our testing dataset, preparing the data for visualizations.
```{r}
new_predictions <- attributes(predictions)$names

tested <- test_train_data %>% 
  filter(test_train == "test") %>% 
  mutate(prediction = predict(model, tweet_text, unlock_empty_predictions = TRUE)) %>% 
  unnest(prediction) %>% 
  mutate(new_predictions = new_predictions,
         correct = case_when(complaint_category == new_predictions ~ TRUE,
                             complaint_category != new_predictions ~ FALSE))
```

## Visualize Predictions
```{r}
tested %>% 
  ggplot(aes(x = complaint_category, fill = new_predictions)) +
  geom_bar() +
  coord_flip()
```

## Accuracy
```{r}
tested %>% 
  summarise(accuracy = mean(correct))
```
This model does not seem very accurate at all, but it is still better than rolling the dice.

### 2019-05-08 Code/dallin_annotations/07_build_classifier.Rmd
Included a visualization of the model's accuracy, and included error = TRUE in many of the code blocks.

@@
 # Libraries
-```{r}
+```{r echo = FALSE}
 library(tidyverse)
@@
 # Create Average word Vectors
-Here, our training dataset is brought in.
-With the data loaded, we featureize the tweets and create average tweet vectors.
-The features of the tweets and average vectors are stored inside a list-column to help organize our data well.
-
+Similar to the previous model, we need to create average tweet vectors for each tweet.
 ```{r}
 # Predict and average word vectors for tweets -----------------------------
-
-# read in labeled traing data
-# train <- read_csv("data/Marketing Research Labeled Tweets All 12-05-18.csv") This was Adriel's code, but I have the data stored somewhere else.
 
@@
 With this visualization, we can see that the PCA model groups complaints and non-complaints well.
-```{r}
+```{r error = TRUE}
 # create a dataframe with the pca output to examine the first 3 components
@@
 load(here::here("Output", "train_data.dat"))
+
+source("05_define_clustering_functions.R")
+source("06_define_prediction_functions.R")
+
 ```
@@
 
-```{r}
+```{r error = TRUE}
 # NOTE: All code below is commented out because this code had trouble knitting
@@
 Here, we let the model make predictions on our test dataset. We then compare the predictions to our actual labels to help us understand accuracy. 
-```{r}
+```{r error = TRUE}
 test_data$prediction <- predict(bst, dtest1)
@@
 
+Visualization of the Test Data
+```{r}
+test_data %>% 
+  ggplot(aes(x = complaint_label, fill = predict_label)) +
+  geom_bar()
+```
+
 ### Look at the Confusion Matrix
@@
 Overall, the model had an 87.59% accuracy, which seems pretty good to me.
-```{r}
+```{r error = TRUE}
 confusionMatrix(factor(test_data$complaint_label), factor(test_data$predict_label))

### 2019-05-08 Code/dallin_annotations/06_define_prediction_functions.R
Just added a note to the use of the logregobj function.

@@ -130,6 +130,7 @@ VectorizeTweet.prcomp <- function(tweet, model, component, ...) {
 
 # Logregobj Function ------------------------------------------------------
 # Dallin: Logistic Regression on Object (I think?)
+# This is the objective function used by the xgboost model (i.e. instead of a linear regression)
 
 logregobj <- function(preds, dtrain) {
   labels <- getinfo(dtrain, "label")

### 2019-05-10 Code/dallin_annotations/11_build_multi_classifier.Rmd
Added a description to the dataset used (which was drawn from the 07 file).

@@
 ## Load the Training Dataset
-This dataset was created in file 07_build_classifier.Rmd
+This dataset was created in file 07_build_classifier.Rmd.
+This dataset contains tweets that have been processed by unsupervised models (a fastText word embeddings model, and a PCR model trained on the fastText word embeddings).
+These unsupervised models were trained on millions of tweets instead of a few thousand, so we expect them to perform well on phrases and words that were not included in the relatively small labeled training dataset of a few thousand tweets.
 ```{r}

### 2019-05-24 Paper/paper.Rmd
Made revisions to the paper.

@@
 ---
-```{r include = FALSE}
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(error = TRUE)
+```
+
+``` {r include = FALSE}
 library(tidyverse)
@@
 # The Classification Model
-A key component to successfuly using twitter data to assess service failures is the ability to classify tweets as complaints and non-complaints.
-If our team can accurately classify a tweet, we will be capable of tackling the greater issue of judging how serious the complaint is, and whether or not a company needs to take action.
+In order to successfuly use twitter data to assess service failures, we need the ability to simply classify tweets as complaints and non-complaints.
+If our team can accurately classify a tweet, we will be capable of tackling the greater issue of judging how serious the complaint is, and deciding whether or not a company needs to take action.
 
-While many methods available can aid us in this task, our team has identified three tools to help us perform our classification: Principal Component Analysis (PCA), fastText, and XGBoost.
+While many available methods can aid us in this task, our team has identified three tools to help us perform our classification: principal component analysis (PCA), fastText, and XGBoost.
 Using these three tools, we've created a "frankenstein model" that incorporates all three tools listed above.
@@
 
-To use our model, we fed a set of tweets into a fastText word representations model (unsupervised).
-After summarizing the ouput of this model, we take the fastText model output and send it through a PCA model.
+To use our model, we began by feeding a set of tweets into a fastText word representations model (unsupervised).
+This model allowed us to use the words of a tweet to create a quantitative summary of each tweet.
+We took the fastText model output and sent it through a PCA model.
 The output of the PCA model (unsupervised) was then fed into an XGBoost model (supervised).
-The XGBoost model then compares predictions of the PCA and fastText models, and makes a final prediction.
-I believe that the idea behind this "frankenstein model" is to use the perspectives of various styles of models to gain an accurate consensus on the data -- somewhat similar to the concept behind random forests.
+The XGBoost model compared the output of the PCA and fastText models, observed a few other details (data we called "tweet features"), and then used its training to predict whether the tweet was a complaint or non-complaint.
 
@@
 
-In our repository, you will also find that we train and test a fastText classification model (supervised).
+In our repository, you will also find that we train and test a fastText classification model.
+fastText provides two methods for analyzing text data: creating word embeddings (using an unsupervised approach) and classifying text (using a supervised approach).
+This second model relies on the latter method to create a standalone model.
 This model is simply another attempt to create a classification model, and can be thought of as a baseline comparison to the frankenstien model.
+In our analysis, it appeared that the frankenstien model outperformed this fastText classification model.
 
-# The fastText Classification Model
-## Overview
-In this section, we will document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
+# The fastText and PCA Sub-Models
+In this section, we explain how we used both fastText and PCA unsupervised models to provide a numerical summary of each tweet. This numerical summary was used as input to the XGBoost model.
 
-## Load Packages
-```{r}
-# library(fastrtext)
-# library(tidyverse)
-```
+## Intro to fastText Unsupervised Models for Word Embeddings
 
-## Define Functions
-No functions have been defined in this file.
-
-## About fastText
-fastText was designed by Facebook and it allows us to build models for both classification and word embeddings.
-Classification refers to analyzing a set of text, and labeling it according to the topics it closely relates to.
-Word embeddings help us predict which words are most closely related to a single word of interest.
-
-fastText boasts that it can perform classification and the creation of word embeddings faster than other tools used for comparable activities (like Word2vec and GloVe) without sacrificing accuracy.
-This is what drew our team's attention to this method from the beginning.
-
-If you are unfamiliar with Fasttext, we'd reccomend getting to know it better by following along with the tutorials found at https://fasttext.cc/docs/en/supervised-tutorial.html.
-The tutorial run entirely from the terminal (a.k.a.
-the command line, shell, bash, command prompt), so if you're uncomfortable navigating your computer from the terminal, it would be worthwhile to find some tutorials on navigating directories within your terminal before beginning to learn fastText.
-If you'd like to learn more about how fastText works, this post found on Medium is also helpful https://towardsdatascience.com/fasttext-under-the-hood-11efc57b2b3.
-
-Finally, if you don't conceptually understand word embeddings and classification, we reccomend doing a bit of research to get a better grip on those ideas before proceding.
-
-## Execute Code
-
-### List File Paths of Model and Data
-To build our fasttext classification model, we begin by defining where we want to store our fastText model once we've trained it.
-In our case, we want to store the model in Output/models and name the model class_mod_1.dat.
-Within R, we'll refer to this file path as file_model.
-
-As a data input for training our model, we already have two text files: train_data_1.txt and test_data_1.txt.
-The file paths to these text files (already built) will be referred to as train_data and test_data.
-
-```{r}
-# file_model <- "Output/models/class_mod_1.dat"
-# train_data_path <- "Output/clean_data/train_data_1.txt"
-# test_data_path <- "Output/clean_data/test_data_1.txt"
-```
-
-### Read in the Data
-We have our training and test data kept in one csv file. We'll read it in after we've filtered all short tweets (with greater than five characters). We'll name this object tweet_data.
-```{r}
-# This code (and all code below) is broken because we don't have access to a tweet_sample_5k_full.csv file.
-
-# tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>%  
-#  filter(nchar(tweet_text) > 5)
-```
-
-### Format the Training Data
-For any supervised learning model (such as complaint classification), our training and test datasets need to have data labeled with the "correct" answers.
-This will allow our model to "learn" the correct answers, and it will hopefully help our model accurately predict correct answers.
-
-For our fastText model, we need to make sure each tweet is preceded by a label (in our case, the labels will be "complaint" and "non-complaint".
-fastText labels have two underscores before and after the label.
-For example, our complaint labels need to look like this: __label__complaint.
-Furthermore, the data we feed into the fastText model needs to be a character vector (like a .txt file), not a dataframe.
-We'll have to do some formatting before we get to that point.
-
-Now that we have access to the data, we'll edit a variable named "label." Currently the labels are 0 for non-complaints and 1 for complaints.
-When we're done, we'll replace the 0's and 1's with their respective terms.
-Additionally, the label and text need to be in the same cell, so we'll make a new variable that concotenates the text and the label toghether.
-
-Finally, we need to randomly and evenly tag our data: half of it will become training, and half of it will become test data.
-
-```{r}
-# test_train_data <- 
-#   tweet_data %>% 
-#   mutate(label = case_when(label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
-#                               label == 1 ~ "complaint"),
-#             input_lines = paste(label, tweet_text)) %>% 
-#   group_by(label) %>% # get a representative sample of both complaints and non complaints
-#   mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
-#   ungroup()
-```
-
-#### Create the .txt Files
-As mentioned earlier, we need to create a text file of our training and test datasets because the fastText model only takes character vectors as inputs.
-With our data labeled both for training/test and complaint/non-complaint, we're ready to do this.
-We will use the write_lines() function to do this.
-The train_data_path is the file location we specified earlier in this script.
-
-!!!!!!!!!! I'm still not sure how we are using the test_labels_without_prefix. If its not the test data, what is it?
-
-```{r}
-# write train data
-# train_data_lines <- 
-#   test_train_data %>% 
-#   filter(test_train == "train") %>% 
-#   pull(input_lines) %>% 
-#   paste0("__label__", .)
-# 
-# write_lines(train_data_lines, train_data_path)
-# 
-# # write test data
-# test_data_lines <- 
-#   test_train_data %>% 
-#   filter(test_train == "test") %>% 
-#   pull(input_lines) %>% 
-#   paste0("__label__", .)
-# 
-# write_lines(test_data_lines, test_data_path)
-
-# create a character vector containing the tweets to test without their labels
-# test_labels_without_prefix <- 
-#   test_train_data %>% 
-#   filter(test_train == "test") %>% 
-#   pull(label)
-```
-
-### Train the Model
-The package we are using (fastrtext) uses the execute() function to train the model.
-This function makes more sense if you've followed the fastText tutorials, but put simply, it concotenates the arguments into a single command which is then run in the terminal.
-
-After we train the model, we'll load the model into our environment.
-
-"supervised" specifies that this is a supervised model (classification, as opposed to creating word vectors). 
-"-input" specifies the file location of the training text files.
-"-output" specifies the file location where we want to place our model, once it has finished training.
-
-You can find more information about the parameters of the model (such as -dim, -lr, and -epoch) here: https://fasttext.cc/docs/en/options.html.
-
-```{r}
-# train model
-# execute(commands = c("supervised", "-input", train_data_path, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
-# 
-# # load model
-# model <- load_model(file_model)
-```
-
-### Review Model:
-We'll want to see how a few of the predictions turned out. 
-```{r}
-# prediction are returned as a list with words and probabilities
-# predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
-# head(predictions, 5)
-```
-
-This will help us confirm that our model worked as expected.
-```{r}
-# length(predictions)
-# length(test_labels_without_prefix)
-# length(test_data_lines)
-```
-
-### Accuracy
-Let's look at how accurately the model predicted names
-```{r}
-# # Compute accuracy
-# mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
-```
-
-Here, we'll look at the hamming loss, and a few of the predictions.
-
-The hamming loss is the number of wrong labels over the total number of labels.
-Hamming loss is most useful when applied to multi-classifiers because when it is done with binary classifiers (such as ours), it is simply equal to 1 - accuracy.
-```{r}
-# # because there is only one category by observation, hamming loss will be the same
-# get_hamming_loss(as.list(test_labels_without_prefix), predictions)
-# 
-# # test predictions
-# predictions <- predict(model, sentences = test_to_write)
-# print(head(predictions, 5))
-# 
-# # you can get flat list of results when you are retrieving only one label per observation
-# print(head(predict(model, sentences = test_to_write, simplify = TRUE)))
-```
-
-## Analysis
-
-# The PCA Sub-Model
-## Intro to PCA
-The idea behind PCA is that a complex multi-dimensional problem can be boiled down to a single-dimensional problem.
-For example, let's say you had a model that tried to predict a student's grade on a test by looking at how many hours the student studied, how many lectures the student attended, how many hours of sleep they got, what cereal they eat for breakfast, and how many siblings they have.
-While all of these factors could arguably have an affect on the student's test grade, I would expect the "hours studied" and "lectures attended" variables to have the strongest correlation to test.
-A PCA model would notice the most important variables of a model, and simplify the model to focus on just two "principle components" (note that it still incorporates the other variables in the model, but these variables have been "simplified" or "compressed")
-
-With a PCA model, similar results will cluster together, and clusterings can help with classification.
-With our student example, we would see "A" students cluster together, "B" students to cluster together, etc.
-While this example might seem like a simple explanation, PCA analysis can be very useful when large amounts of data are available, but you don't know which variables are most important in your classification.
-
-For our purposes, we should be able to use PCA analysis by taking large ammounts of data we collect on tweets (their features, their average word vector, etc.) and see a clustering of complaints and non-complaints, without worrying about which features or variables of a tweet are best for classification.
-
-## Details of the Use of PCA in Our Model
-We wanted to incorporate a PC analysis in our model, hoping that the perspective of a unique model type would aid our model's accuracy.
-As input, the PCA model needs numerical data, so we needed to convert our character data (tweet text) into numerical data.
-To do this, we used a fastText model again.
-Unlike the fastText model above, however, we decided to use an unsupervised fastText model for producing word vectors.
-
-Ultimately, we used PCA because we wanted to take our text data and process it in a way it could become quantitative data, believing that this would be a better format as an input for our XGBoost model.
-It is important to note that the PCA model was not capable of predicting complaints vs non-complaints, and never "saw" training labels when we trained it (it was unsupervised).
-Rather, it processed the textual data to provide quantitative data that grouped complaints and non-complaints fairly well, despite being unaware of the labels.
-
-### Using a fastText Unsupervised Model for Word Vectors
-This model, trained on the tweet text from our training dataset of nearly 5,000 tweets, learns the associations of words by analyzing how frequently pairs of words appear near each other.
-After running this analysis, the model can produce a word vector for any word -- even words it hadn't seen before.
+The fastText sub-model, trained on the tweet text from over a million tweets, learned the associations of words by analyzing how frequently pairs of words appear near each other.
+After running this analysis, the model can produce a word vector for any word -- even words it has not seen before.
 
@@
 They represent a mathematical definition of a word.
-Via a method that is beyond the level of depth we'd like to explain in this paper, the output of this model (a vector containing 50 numbers for each word queried) is a representation of the associations one word has with all other words used in a corpus.
-Our model was specifically trained to produce word vectors of length 50, but this was simply a parameter we found to be most effective for our purposes (we explored this in the code fasttext_clust_EDA.R).
-Similar to the PCA model, it is important to note that this model that never "saw" our training labels (i.e.
-it was unsupervised), and was never capable of predicting complaints and non-complaints.
+Via a method that is beyond the level of depth we'd like to explain in this paper, the output of this model (a vector containing 50 numbers for each word queried) represents the associations one word has with all other words used in a corpus.
+We trained our model to produce word vectors of length 50, but this was simply a parameter we found most effective for our purposes (we explored this in the code fasttext_clust_EDA.R).
+It is important to note that this model never "saw" our training labels (i.e.
+it was unsupervised), and could not predict complaints and non-complaints.
 Rather, it processed the textual data to provide a quantitative input for our principal component analysis.
 
-These word vectors also function well with additions and subtractions.
+An important aspect of these word vectors is that they function well with addition and subtraction.
 For example, with word vectors, king - man + woman = queen.
-This fact is very useful to us, because it means that if we average the vectors for each word in a tweet, we should end up with a summary of a tweet in a single vector.
-We created a function that averaged word vectors, named "VectorizeTweet()." The function takes a single tweet, breaks its text down into a dataframe of each word used in the tweet, fetches the word vector for each word in the dataframe, and then averages each column of the vectors.
+This detail is very useful to us, because it means that we can average the vectors for each word in a tweet and end up with a summary of a tweet in a single vector.
+To perform this, we created a function that averaged word vectors, named "VectorizeTweet( )." The function takes a single tweet, breaks its text down into a dataframe of each word used in the tweet, fetches the word vector for each word in the dataframe, and then averages each column of the vectors.
 This vectorized tweet summary became the numerical input for our PC analysis.
+The result of the VectorizeTweet( ) function is shown below, where each line corresponds to a single tweet.
+
+```{r echo = FALSE}
+load(file = "../Output/train.Rdata")
+
+train %>%
+  select(avg_vec_50) %>% 
+  unnest()
+```
+
+## Intro to PCA
+The idea behind PCA is that a complex multi-dimensional problem can be boiled down to a single-dimensional problem.
+For example, let's say you had a model that tried to predict a student's grade on a test by looking at how many hours the student studied, how many lectures the student attended, how many hours of sleep the student got, what cereal the student eats for breakfast, and how many siblings a student has.
+While all of these factors could arguably have an affect on the student's test grade, I would expect the "hours studied" and "lectures attended" variables to have the strongest correlation to their grade.
+A PCA model would notice the most important variables of a model, and simplify the model to focus on just two "principle components" (note that it still incorporates the other variables in the model, but these variables have been "simplified" or "compressed").
+
+With a PCA model, similar results will cluster together, and clusterings can help with classification.
+With our student example, we would expect to see "A" students cluster together, "B" students to cluster together, etc.
+While this example might seem like a simple explanation, PCA analysis can be very useful when large amounts of data are available, but you do not know which variables are most important in making predictions.
+In our scenario, PCA was useful because we had a lot of data that was meaningful, but difficult to interpret (the vectorized tweets).
+During training, our PCA model analyzed the fifty variables of the vectorized tweets, and detected patterns and relationships.
+The model described these pattterns and relationships as functions that take in several datapoints, and return a single datapoint that summarizes all input datapoints.
+These functions are what we refer to as principle components.
+The list of principle component functions (PC1, PC2, PC3...) are prioritized so that the first principle component describes the most variation in the data, the second component describes the next largest trend in variation, and so on.
+When all of the principle components are combined, nearly all of the variation in the data can be explained (this is visualized in the elbow plot below).
+
+In reality, these principle components are purely mathematical and can't be interpreted; however, we can make a simplified explanation of these components that can help us better understand them.
+For the purpose of explaining PCA in an easy-to-understand, we can imagine that the first principle component describes a trend that explains a large number of tweet complaints (like a positive or negative sentiment score), and that the second principle component describes another large characteristic that makes a tweet a complaint (such as the inclusion of words like "delay," "poor," and "terrible").
+
+## Details of the Use of PCA in Our Model
+Ultimately, we used PCA because we wanted to take our text data and process it in a way it could become quantitative data, believing that this would be a better format as an input for our XGBoost model.
+We trained our PCA model on two sets of data: the vectorized tweet variables (using the fastText unsupervised model) and "tweet features." The tweet features have not been mentioned until now, but it was simply a set of data that included the number of exclamation points, words, and spaces used in a tweet.
+We created a function called "TweetFeatures( )" which collected this data.
+
+It is important to note that the PCA model was not capable of predicting complaints vs non-complaints, and never "saw" training labels when we trained it (it was unsupervised).
+Rather, it processed the textual data to provide quantitative data that grouped complaints and non-complaints fairly well, despite being "unaware" of the labels.
+
+After running the PC Analysis, we were able to see a clustering of complaints and non-complaints, without worrying about which features or variables of a tweet are best for classification (visualized below).
 
 ### Analysis of Principal Components
-Once we had a list-column of average tweet vectors (avg_vec_50), we analyzed its principal components.
-We started with a 3D visualization of the first three principal components, coloring the tweets by their complaint/non-complaint labels, and found that the complaints and non-complaints grouped well.
+Once we trained our PCA model, we were interested in seeing if it could reasonably separate complaints from non-complaints despite the absence of labeled data.
+We did this by creating a 3D visualization of the first three principal components, coloring the tweets by their complaint/non-complaint labels, and found that the complaints and non-complaints grouped well.
 
@@
 
-We also looked at a scree plot and found that four principal components would be effective enough to describe the variance in our data well.
+After seeing that our PCA model helped group complaints and non-complaints well, we wondered how many of those principle component variables we should include as input to the XGBoost model.
+To do this, we used a scree plot.
+The scree plot shows variances undescribed by the model on the y-axis, and principal components on the x-axis.
+For example, with only one principal component, a large amount of variance remains in the data.
+With two principal components, however, we see that the amount of undescribed variance drops considerably.
+The rule of thumb with the scree plot is to identify the "elbow" (where the slope of the line starts to flatten out), and choose a number of principal components based on number of principal components at that point.
+Using this plot we determined that we would use the first four principal components of the model.
+Using four principal components helped us achieve a model that is both simple, and accurate.
+Using more than four principal components would result in significantly diminished returns -- it would slow down our model without providing a significant improvement to our model's predictive ability.
 
@@
 
-Once we saw that we should use four principal components, we then trained the PCA model using our dataset of about 5,000 tweets, and used the model to find the values for the four principal components for eqch tweet.
+Once we saw that we should use four principal components, we used the model to find the values for the four principal components for each tweet.
 This provided another numerical input we used in our next model, the XGboost model.
+The results are shown below.
+
+```{r echo = FALSE}
+train %>% 
+  select(avg_vec_50_PCA) %>% 
+  unnest()
+```
 
@@
 We found our XGBoost model to be 87.59% accurate, with 85 false positives, and 38 false negatives.
+A visualization and confusion matrix output are shown below.
+
+![Scree plot.](../Figures/bi_classifier_test_results.png)
 
@@
 MIT lecture on Boosting: https://www.youtube.com/watch?v=UHBmv7qCey4
+
+# The fastText Classification Model
+## Overview
+In this section, we will document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.
+
+The supervised model built in this script is not used in the "frankenstien model." Instead, it is a standalone classification model.
+This is a way for us to compare the frankenstien model's performance to a "baseline."
+
+# Load Packages
+```{r echo = FALSE}
+library(fastrtext)
+library(tidyverse)
+
+set.seed(42)
+```
+
+## About fastText
+fastText was designed by Facebook and it allows us to build models for both classification and word embeddings.
+Classification refers to analyzing a set of text, and labeling it according to the topics it closely relates to.
+Word embeddings help us predict which words are most closely related to a single word of interest.
+
+fastText boasts that it can perform classification and the creation of word embeddings faster than other tools used for comparable activities (like Word2vec and GloVe) without sacrificing accuracy.
+This is what drew our team's attention to this method from the beginning.
+
+If you are unfamiliar with Fasttext, we'd reccomend getting to know it better by following along with the tutorials found at https://fasttext.cc/docs/en/supervised-tutorial.html.
+The tutorial run entirely from the terminal (a.k.a.
+the command line, shell, bash, command prompt), so if you're uncomfortable navigating your computer from the terminal, it would be worthwhile to find some tutorials on navigating directories within your terminal before beginning to learn fastText.
+If you'd like to learn more about how fastText works, this post found on Medium is also helpful https://towardsdatascience.com/fasttext-under-the-hood-11efc57b2b3.
+
+Finally, if you don't conceptually understand word embeddings and classification, we reccomend doing a bit of research to get a better grip on those ideas before proceding.
+
+## Execute Code
+
+### List File Paths of Model and Data
+To build our fasttext classification model, we begin by defining where we want to store our fastText model once we've trained it.
+In our case, we want to store the model in Output/models and name the model class_mod_1.dat.
+Within R, we'll refer to this file path as model_path.
+
+As a data input for training our model, we already have two text files: train_data_1.txt and test_data_1.txt.
+The file paths to these text files (already built) will be referred to as train_data and test_data.
+
+```{r}
+model_path <- here::here("Output", "models", "class_mod_1.dat")
+train_data_path <- here::here("Output", "clean_data", "train_data_1.txt")
+test_data_path <- here::here("Output", "clean_data", "test_data_1.txt")
+```
+
+### Read in the Data
+We have our training and test data kept in one csv file. We'll read it in after we've filtered all short tweets (with greater than five characters). We'll name this object tweet_data.
+```{r}
+# This code (and all code below) is broken because we don't have access to a tweet_sample_5k_full.csv file.
+
+tweet_data <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")) %>%
+ filter(nchar(tweet_text) > 5)
+```
+
+### Format the Training Data
+For any supervised learning model (such as complaint classification), our training and test datasets need to have data labeled with the "correct" answers.
+This will allow our model to "learn" the correct answers, and it will hopefully help our model accurately predict correct answers.
+
+For our fastText model, we need to make sure each tweet is preceded by a label (in our case, the labels will be "complaint" and "non-complaint".
+fastText labels have two underscores before and after the label.
+For example, our complaint labels need to look like this: __label__complaint.
+Furthermore, the data we feed into the fastText model needs to be a character vector (like a .txt file), not a dataframe.
+We'll have to do some formatting before we get to that point.
+
+Now that we have access to the data, we'll edit a variable named "label." Currently the labels are 0 for non-complaints and 1 for complaints.
+When we're done, we'll replace the 0's and 1's with their respective terms.
+Additionally, the label and text need to be in the same cell, so we'll make a new variable that concotenates the text and the label toghether.
+
+Finally, we need to randomly and evenly tag our data: half of it will become training, and half of it will become test data.
+
+```{r}
+test_train_data <- tweet_data %>%
+  mutate(label = case_when(complaint_label == 0 ~ "non-complaint", # each line (tweet) is preceded by a label to be predicted
+                              complaint_label == 1 ~ "complaint"),
+            input_lines = paste(label, tweet_text)) %>%
+  group_by(label) %>% # get a representative sample of both complaints and non complaints
+  mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
+  ungroup()
+```
+
+#### Create the .txt Files
+As mentioned earlier, we need to create a text file of our training and test datasets because the fastText model only takes character vectors as inputs.
+With our data labeled both for training/test and complaint/non-complaint, we're ready to do this.
+We will use the write_lines() function to do this.
+The train_data_path is the file location we specified earlier in this script.
+
+```{r}
+# write train data
+train_data_lines <- test_train_data %>%
+  filter(test_train == "train") %>%
+  pull(input_lines) %>%
+  paste0("__label__", .)
+
+write_lines(train_data_lines, train_data_path)
+
+# write test data
+test_data_lines <- test_train_data %>%
+  filter(test_train == "test") %>%
+  pull(input_lines) %>%
+  paste0("__label__", .)
+
+write_lines(test_data_lines, test_data_path)
+
+# create a character vector containing the tweets to test without their labels
+test_labels_without_prefix <-
+  test_train_data %>%
+  filter(test_train == "test") %>%
+  pull(label)
+```
+
+### Train the Model
+The package we are using (fastrtext) uses the execute() function to train the model.
+This function makes more sense if you've followed the fastText tutorials, but put simply, it concotenates the arguments into a single command which is then run in the terminal.
+
+After we train the model, we'll load the model into our environment.
+
+"supervised" specifies that this is a supervised model (classification, as opposed to creating word vectors). 
+"-input" specifies the file location of the training text files.
+"-output" specifies the file location where we want to place our model, once it has finished training.
+
+You can find more information about the parameters of the model (such as -dim, -lr, and -epoch) here: https://fasttext.cc/docs/en/options.html.
+
+```{r}
+# train model
+execute(commands = c("supervised", "-input", train_data_path, "-output", model_path, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
+
+# load model
+model <- load_model(model_path)
+```
+
+### Review Model:
+We'll want to see how a few of the predictions turned out. 
+```{r}
+# prediction are returned as a list with words and probabilities
+predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
+
+head(predictions, 5)
+```
+
+Below we compare the length of the list of predictions to the length of the testing dataset. Ideally, these should have the same length. This will help us confirm that our model worked as expected.
+
+```{r}
+length(predictions)
+length(test_labels_without_prefix)
+length(test_data_lines)
+```
+
+Unexpectedly, the predictions are shorter than the test dataset, so I'm not sure what happened.
+According to some errors I've seen, I think it's because a few tweets use vocabulary that was not included in the training dataset.
+
+Below, we merge the predictions with our testing dataset, preparing the data for visualizations.
+```{r}
+new_predictions <- attributes(predictions)$names
+
+tested <- test_train_data %>% 
+  filter(test_train == "test") %>% 
+  mutate(prediction = predict(model, tweet_text, unlock_empty_predictions = TRUE)) %>% 
+  unnest(prediction) %>% 
+  mutate(new_predictions = new_predictions,
+         correct = case_when(label == new_predictions ~ TRUE,
+                             label != new_predictions ~ FALSE))
+```
+
+Visualization of Outputs:
+Below, we have a bar graph of our testing data and the model's predictions.
+The columns represent the labels from our testing dataset.
+The fill is the model's predictions.
+We see that the model seems to make a lot of false positives, but provides almost no false negatives.
+```{r}
+tested %>% 
+  ggplot(aes(x = label, fill = new_predictions)) +
+  geom_bar()
+```
+
+### Accuracy
+
+```{r}
+tested %>% 
+  summarise(accuracy = mean(correct))
+```
+It looks like this model is about 60% accurate.
+This isn't great, but it's better than flipping a coin.
+Perhaps the model will perform significantly better with a larger dataset for training and testing.
+
+```{r error = TRUE}
+# Compute accuracy
+mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
+```
+
+Here, we'll look at the hamming loss, and a few of the predictions.
+
+The hamming loss is the number of wrong labels over the total number of labels.
+Hamming loss is most useful when applied to multi-classifiers because when it is done with binary classifiers (such as ours), it is simply equal to 1 - accuracy.
+```{r error = TRUE}
+# because there is only one category by observation, hamming loss will be the same
+get_hamming_loss(as.list(test_labels_without_prefix), predictions)
+
+# test predictions
+predictions <- predict(model, sentences = test_to_write)
+print(head(predictions, 5))
+
+# you can get flat list of results when you are retrieving only one label per observation
+print(head(predict(model, sentences = test_to_write, simplify = TRUE)))
+```

### 2019-05-30 Code/07_build_classifier.Rmd
Restructured the folders of the project. The folder formerly labeled as "dallin_annotations" has now become the "Code" folder. The "dallin_annotations" folder contained all of the R and python scripts in Code, but renamed and organized scripts according to the tidyverse styleguide. All other files in the folder formerly named "Code" have been deleted (they were redundant).

--- 2019-05-08 Code/dallin_annotations/07_build_classifier.Rmd
@@
 
-The scree plot shows variances (in other words, variance undescribed by the model) on the y-axis, and principal components on the x-axis.
+The scree plot shows variances undescribed by the model on the y-axis, and principal components on the x-axis.
 For example, with only one principal component, a large amount of variance remains in the data.
@@
 # save(test_data, file = here::here("Output", "test_data.dat"))
+save(train, file = ../../Output/train.Rdata) # Save the training file so it can be referenced in the paper
 ```

### 2019-05-30 Code/10_build_fasttext_multi_classifier.Rmd
Restructured the folders of the project. The folder formerly labeled as "dallin_annotations" has now become the "Code" folder. The "dallin_annotations" folder contained all of the R and python scripts in Code, but renamed and organized scripts according to the tidyverse styleguide. All other files in the folder formerly named "Code" have been deleted (they were redundant).

---
title: "Building a fastText Classifier for Multiple Complaint Categories (Supervised)"
output: github_document
---
# Overview
In this document, I create a fastText classification model that predicts complaints by the various complaint categories we created in our test/train dataset. This model is very simple, and uses fastText exclusively for classification.

# Building the First fastText Classifier for Multiple Complaint Categories

## Preparation
In this section, we will load necesary libraries, and prepare our data for training a model by reading it in, partitioning it, and converting the data to necessary .txt files.
### Libraries
```{r}
library(fastrtext)
library(tidyverse)

set.seed(42)
```

Here, I set the paths to the model, testing, and training data. Once the data and models are created, this is where they will be saved.
```{r}
model_path <- here::here("Output", "models", "fasttext_multi_class_model.dat")
train_data_path <- here::here("Output", "clean_data", "rain_multi_data_1.txt")
test_data_path <- here::here("Output", "clean_data", "test_multi_data_1.txt")
```

### Prepare Data
##### Read in the Data
```{r}
tweet_data <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")) %>%
 filter(nchar(tweet_text) > 5)
```

##### Partition Data for Testing and Training
```{r}
test_train_data <- tweet_data %>%
  mutate(input_lines = paste(complaint_category, tweet_text)) %>%
  group_by(complaint_category) %>% # get a representative sample of both complaints and non complaints
  mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
  ungroup()
```

##### Create .txt Files
As input, the fastText model needs to take the testing and training data as .txt files.
```{r}
# write train data
train_data_lines <- test_train_data %>%
  filter(test_train == "train") %>%
  pull(input_lines) %>%
  paste0("__label__", .)

write_lines(train_data_lines, train_data_path)

# write test data
test_data_lines <- test_train_data %>%
  filter(test_train == "test") %>%
  pull(input_lines) %>%
  paste0("__label__", .)

write_lines(test_data_lines, test_data_path)

# create a character vector containing the tweets to test without their labels
test_labels_without_prefix <-
  test_train_data %>%
  filter(test_train == "test") %>%
  pull(complaint_category)
```

## Train the fastText Classification Model (Supervised, Multiple Categories)
```{r}
# train model
execute(commands = c("supervised", "-input", train_data_path, "-output", model_path, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))

# load model
model <- load_model(model_path)
```

## Review Model
```{r}
predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)

head(predictions, 5)
```

Below we compare the length of the list of predictions to the length of the testing dataset. Ideally, these should have the same length. This will help us confirm that our model worked as expected.
```{r}
length(predictions)
length(test_labels_without_prefix)
length(test_data_lines)
```
Similar to the previous fastText model, it appears the model would not make predictions on a few of the tweets in the testing dataset. This is likely due to the size of our training dataset as well as the variance in vocabulary for tweets.

Below, we merge the predictions with our testing dataset, preparing the data for visualizations.
```{r}
new_predictions <- attributes(predictions)$names

tested <- test_train_data %>% 
  filter(test_train == "test") %>% 
  mutate(prediction = predict(model, tweet_text, unlock_empty_predictions = TRUE)) %>% 
  unnest(prediction) %>% 
  mutate(new_predictions = new_predictions,
         correct = case_when(complaint_category == new_predictions ~ TRUE,
                             complaint_category != new_predictions ~ FALSE))
```

### Visualize Predictions
```{r}
tested %>% 
  ggplot(aes(x = complaint_category, fill = new_predictions)) +
  geom_bar() +
  coord_flip()
```

### Accuracy
The graph above is a little bit busy, so here is one that simplifies predictions into correct and incorrect.
```{r}
tested %>% 
  ggplot(aes(x = complaint_category, fill = correct)) +
  geom_bar() +
  coord_flip() +
  labs(title = "Correct and Incorrect Predictions by Category")
```

Here is the measured accuracy of the model.
```{r}
tested %>% 
  summarise(accuracy = mean(correct))
```
This model does not seem very accurate at all, but it is still better than rolling the dice.

# Building a Second fastText Classification Model with Condensed Complaint Categories

The classification of the tweets above was extremely poor, and I think it could be due to the size of our training dataset relative to the quantity of categories. I believe that if we shrunk the categories down to about 6 or so, we might have better luck classifying the data.

I will condense the complaint categories into smaller chunks, and hopefully, this will result in better data for training and testing our model.

## Preparation
In this section, we will clean the environment, re-load our test/train data, condense complaint categories, partition the data for testing and training, create a location to save our data and models, and create necessary .txt files for training and testing the model.

### Clean the Environment
To ensure that we are working with data independent from the section above, we will remove all objects in the environment, and re-load the libraries we need.
```{r}
rm(list = ls())

library(fastrtext)
library(tidyverse)

set.seed(42)
```

### Prepare Data
#### Load the Training/Test Data
This is our labeled test/train dataset with about 5,000 tweets, binary complaint labels, and categorical complaint labels.
```{r}
tweet_data <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")) %>%
 filter(nchar(tweet_text) > 5)
```

#### Condense the Complaint Categories

##### View the Complaint Categories
This visualization will help us see how many categories we currently have, and will help us decide which categories to condense.
```{r}
tweet_data %>% 
  count(complaint_category, sort = TRUE) %>% 
  mutate(complaint_category = reorder(complaint_category, n)) %>% 
  ggplot(aes(x = complaint_category, n)) +
  geom_col() +
  coord_flip() +
  labs(title = "Complaint Categories by Count")
```

Looking at this chart, it appears that we could condense delay_ into a single category, and human_service_ into a single category. app_failure, wishlist, and check_failure could all go into event_specific. This seems to make the most intuitive sense to me.

##### Perform Condensing on Complaint Categories
```{r}
tweet_data <- tweet_data %>% 
  mutate(complaint_category_new = case_when(complaint_category == "non_complaint" ~ "non_complaint", 
                                            complaint_category == "baggage" ~ "baggage",
                                            complaint_category == "event_vague" ~ "event_vague",
                                            str_detect(complaint_category, "delay") == TRUE ~ "delay",
                                            str_detect(complaint_category, "event_specific") == TRUE ~ "event_specific",
                                            str_detect(complaint_category, "app") == TRUE ~ "event_specific",
                                            str_detect(complaint_category, "wish") == TRUE ~ "event_specific",
                                            str_detect(complaint_category, "failure") == TRUE ~ "event_specific",
                                            str_detect(complaint_category, "human_service") == TRUE ~ "human_service"))
```

##### Visualize Condensing of Complaint Categories
```{r}
tweet_data %>% 
  count(complaint_category_new, sort = TRUE) %>% 
  mutate(complaint_category_new = reorder(complaint_category_new, n)) %>% 
  ggplot(aes(x = complaint_category_new, n)) +
  geom_col() +
  coord_flip() +
  labs(title = "Condensed Complaint Categories by Count")
```

We've now condensed the complaint categories down to `r tweet_data %>% count(complaint_category_new) %>% nrow()` categories. Hopefully, this will help our classifier train well.

#### Partition the Data for the Second Model
Here, we split the data so that 80% of it is dedicated towards training, and 20% is dedicated for testing.
```{r}
test_train_data <- tweet_data %>%
  mutate(input_lines = paste(complaint_category_new, tweet_text)) %>%
  group_by(complaint_category_new) %>% # get a representative sample of both complaints and non complaints
  mutate(test_train = c("test", "train")[rbinom(n(), 1, 0.8) + 1]) %>% # assign test train splits
  ungroup()
```

#### Create a Location for Saving the data and Second Model
```{r}
model_path_2 <- here::here("Output", "models", "fasttext_multi_class_model_2.dat")
train_data_path_2 <- here::here("Output", "clean_data", "train_multi_data_2.txt")
test_data_path_2 <- here::here("Output", "clean_data", "test_multi_data_2.txt")
```

#### Create .txt Files for the Second Model
As input, the fastText model needs to take the testing and training data as .txt files.
```{r}
# write train data
train_data_lines <- test_train_data %>%
  filter(test_train == "train") %>%
  pull(input_lines) %>%
  paste0("__label__", .)

write_lines(train_data_lines, train_data_path_2)

# write test data
test_data_lines <- test_train_data %>%
  filter(test_train == "test") %>%
  pull(input_lines) %>%
  paste0("__label__", .)

write_lines(test_data_lines, test_data_path_2)

# create a character vector containing the tweets to test without their labels
test_labels_without_prefix <-
  test_train_data %>%
  filter(test_train == "test") %>%
  pull(complaint_category_new)
```

## Train the Second fastText Classification Model (Supervised, Condensed Categories)
```{r}
# train model
execute(commands = c("supervised", "-input", train_data_path_2, "-output", model_path_2, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))

# load model
model <- load_model(model_path_2)
```

## Review Second Model
```{r}
predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)

head(predictions, 5)
```

Below we compare the length of the list of predictions to the length of the testing dataset. Ideally, these should have the same length. This will help us confirm that our model worked as expected.
```{r}
length(predictions)
length(test_labels_without_prefix)
length(test_data_lines)
```
Similar to the previous fastText model, it appears the model would not make predictions on a few of the tweets in the testing dataset. This is likely due to the size of our training dataset as well as the variance in vocabulary for tweets.

Below, we merge the predictions with our testing dataset, preparing the data for visualizations.
```{r}
new_predictions <- attributes(predictions)$names

tested <- test_train_data %>% 
  filter(test_train == "test") %>% 
  mutate(prediction = predict(model, tweet_text, unlock_empty_predictions = TRUE)) %>% 
  unnest(prediction) %>% 
  mutate(new_predictions = new_predictions,
         correct = case_when(complaint_category_new == new_predictions ~ TRUE,
                             complaint_category_new != new_predictions ~ FALSE))
```

### Visualize Predictions of Second Model
```{r}
tested %>% 
  ggplot(aes(x = complaint_category_new, fill = new_predictions)) +
  geom_bar() +
  coord_flip() +
  labs(title = "Labeled Tweets and Respective Predictions")
```

### Accuracy of Second Model
If the graph above was too busy, here is another graph that simplifies everything down to correct and incorrect predictions. As indicated, the coral predictions were false, while the turquoise predictions were correct.

```{r}
tested %>% 
  ggplot(aes(x = complaint_category_new, fill = correct)) +
  geom_bar() +
  coord_flip() +
  labs(title = "Correct and Incorrect Predictions by Category")
```

```{r}
tested %>% 
  summarise(accuracy = mean(correct))
```
Surprisingly to me, this model does not perform much better than the first model in this document, which predicted on twelve different complaint categories.

### 2019-05-30 Code/11_build_multi_classifier.Rmd
Restructured the folders of the project. The folder formerly labeled as "dallin_annotations" has now become the "Code" folder. The "dallin_annotations" folder contained all of the R and python scripts in Code, but renamed and organized scripts according to the tidyverse styleguide. All other files in the folder formerly named "Code" have been deleted (they were redundant).

--- 2019-05-10 Code/dallin_annotations/11_build_multi_classifier.Rmd
@@
 In this document, I will try to make a classification model similar to the one in 07_build_classifier.Rmd.
-The difference here will be that I will attempt to build a classification model meant to predict based on a set of many complaint categories.
+The difference here will be that the classification model will predict based on a set of several complaint categories.
 
@@
 This dataset contains tweets that have been processed by unsupervised models (a fastText word embeddings model, and a PCR model trained on the fastText word embeddings).
-These unsupervised models were trained on millions of tweets instead of a few thousand, so we expect them to perform well on phrases and words that were not included in the relatively small labeled training dataset of a few thousand tweets.
+These unsupervised models were trained on millions of tweets instead of a few thousand, so we expect them to perform well on phrases and words that were not included in the relatively small labeled training dataset of about five thousand tweets.
 ```{r}
@@
 ```
-It appears that when predicting non-complaints, the model is only accurate about 25% of the time. This is very poor, but better than rolling the dice.
+It appears that when predicting non-complaints, the model is only accurate about 25% of the time.
+This is very poor, but better than rolling the dice.
+Regardless, I wouldn't put a lot of trust in its predictions.
 

### 2019-05-30 Code/99_logit_regression_classifier.Rmd
Restructured the folders of the project. The folder formerly labeled as "dallin_annotations" has now become the "Code" folder. The "dallin_annotations" folder contained all of the R and python scripts in Code, but renamed and organized scripts according to the tidyverse styleguide. All other files in the folder formerly named "Code" have been deleted (they were redundant).

---
title: "Logit Regression Classifier Best"
output: github_document
---

# Overview
These are my annotations on the "logit_regression_classifier_Best.R" script written by Adriel.

```{r}
library(tidyverse)
library(qtlcharts)
library(caret)
source("Code/complaint-prediction/R/clus_func.R")
source("Code/complaint-prediction/R/logit_classifier_func.R")

# read in labeled data ----------------------------------------------------

labeled_data <- read_csv("data/Marketing Research Labeled Tweets_ALL_10-30.csv")

# featurize the data ------------------------------------------------------

# add labels to our embedding data -----------------------------------------

cor_data_50 <- 
  test_out %>% 
  dplyr::select(tweet_text, avg_vec_50) %>% 
  unnest(avg_vec_50) %>% 
  filter(tweet_text != "") %>% 
  bind_cols(labels, .) %>% 
  dplyr::select(-tweet_text1) %>% 
  filter(!is.na(complaint_label)) %>% 
  mutate(label = as.logical(complaint_label))

# feature engineering -----------------------------------------------------

cor_data_50_feat <- 
  cor_data_50 %>% 
  mutate(count.char   = nchar(tweet_text),
         log.mentions = log1p(str_count(tweet_text, "@")), # Count user mentions
         log.links    = log1p(str_count(tweet_text, "http:\\/\\/t.co")), # count links
         count.space  = str_count(tweet_text, " ")) # count exclamation marks

# plot correlations -------------------------------------------------------

iplotCorr(cor_data_50[,-c(1,2)], cor_data_50$label, reorder=TRUE, chartOpts = list(scatcolors=c("lightblue", "lightgreen")))

# Contribution analysis ---------------------------------------------------

beta <- apply(cor_data_50[,-c(1,2)], 2, function(x,y) lm(y~x)$coef[2], cor_data_50$label)
pos <- which(beta > 0)
neg <- which(beta < 0)

iplotCorr(cor_data_50[,-c(1,2)], cor_data_50$label, rows=pos, cols=neg, reorder=TRUE)

# PCA for regression ------------------------------------------------------

cor_data_50.pr <- prcomp(as.matrix(cor_data_50[,3:52]))

# save the prcomp model
cor.data.50.pr <- cor_data_50.pr
save(cor.data.50.pr, file = "models/prcomp/cor.data.50.pr")

screeplot(cor.data.50.pr, type = "line")
# elbow at 6 components. Use 6 components for enriching our model

# Build model -------------------------------------------------------------

PC6_cor_data_50 <- 
  cor_data_50.pr$x %>% 
  as_tibble() %>% 
  select(PC1:PC6)

cor_data_50_feat <- 
  cor_data_50_feat %>%
  bind_cols(PC6_cor_data_50)

beta <- apply(cor_data_50_feat[,-c(1,2)], 2, function(x,y) lm(y~x)$coef[2], cor_data_50$label)
pos <- which(beta > 0)
neg <- which(beta < 0)

cor_data_50_feat %>% 
  select(complaint_label, V1:V50) %>% 
  glm(complaint_label ~ ., data = ., family = "binomial") %>% 
  summary()

iplotCorr(cor_data_50_feat[,-c(1,2)], cor_data_50_feat$label, rows=pos, cols=neg, reorder=TRUE)

# Build model -------------------------------------------------------------

df <- cor_data_50_feat

test_mod <- function(df, testing = FALSE){
  mod <- glm(label ~
               PC2 +
               PC3 +
               PC5 +
               # PC6 + 
               # PC1:PC5 +
               # PC2:PC5 +
               # PC3:PC6 +
               V1 +
               V2 +
               V9 +
               V10 +
               V15 +
               V26 +
               V34 +
               V37 +
               V45 +
               # V46 +
               V48 + 
               V50 +
               # V15:V4 +
               # V34:V31 +
               # V22:V42 +
               # V27:V31 +
               V10:V50 +
               V34:V48 +
               V14:V34 +
               # PC1:V50 +
               # PC1:V35 +
               PC1:V33 +
               PC2:V9 +
               # PC3:V6 +
               PC3:V26 + 
               PC6:V27 +
               # log_mentions + 
               log.links + 
               log.mentions:PC1 + 
               count.char:PC1 + # This one does a lot of the heavy lifting
               count.char:PC4 +
               count.space:PC1,
             data = df, family = "binomial")
  if(testing == TRUE){
    print(summary(mod)) 
  }
  return(mod)
}

accuracy <- list()
for(i in 1:100) { 
  cor_data_50_feat_test_train <- 
    cor_data_50_feat %>% 
    mutate(train1 = rbinom(4958, 1, .75))

  mod1_train1 <- 
    cor_data_50_feat_test_train %>% 
    filter(train1 == 1) %>%
    test_mod()

  out <- cor_data_50_feat_test_train %>% 
    filter(train1 == 0) %>% 
    mutate(fitted = broom::augment(mod1_train1, newdata = ., type.predict = "response")$.fitted,
           fifty_class = if_else(fitted >= 0.5, TRUE, FALSE))

  accuracy[[i]] <- confusionMatrix(factor(as.numeric(out$fifty_class)), factor(as.numeric(out$label)), positive = NULL, dnn = c("Prediction", "Reference"))$overall[1]
}

mean(as.numeric(accuracy))
max(as.numeric(accuracy))
min(as.numeric(accuracy))

# Best so far: 0.8548388

# Save the best performing model ------------------------------------------

logit_mod_0.856_acc <- glm(label ~
      PC2 +
      PC3 +
      PC5 +
      # PC6 + 
      # PC1:PC5 +
      # PC2:PC5 +
      # PC3:PC6 +
      V1 +
      V2 +
      V9 +
      V10 +
      V15 +
      V26 +
      V34 +
      V37 +
      V45 +
      # V46 +
      V48 + 
      V50 +
      # V15:V4 +
      # V34:V31 +
      # V22:V42 +
      # V27:V31 +
      V10:V50 +
      V34:V48 +
      V14:V34 +
      # PC1:V50 +
      # PC1:V35 +
      PC1:V33 +
      PC2:V9 +
      # PC3:V6 +
      PC3:V26 + 
      PC6:V27 +
      # log_mentions + 
      log.links + 
      log.mentions:PC1 +
        count.char:PC1 + # This one does a lot of the heavy lifting
        count.char:PC4 +
        count.space:PC1,
    data = cor_data_50_feat, family = "binomial")

summary(logit_mod_0.856_acc)

save(logit_mod_0.856_acc, file = "models/classifiers/logit_mod_0.856_acc")

```

### 2019-05-30 Code/README.Rmd
Restructured the folders of the project. The folder formerly labeled as "dallin_annotations" has now become the "Code" folder. The "dallin_annotations" folder contained all of the R and python scripts in Code, but renamed and organized scripts according to the tidyverse styleguide. All other files in the folder formerly named "Code" have been deleted (they were redundant).

@@
 ---
-title: "Code"
+title: "README"
 output: github_document
 ---
+# Dallin Annotations
+In this folder, I will keep all of my .rmd documents.
+Some of them will be created by me, but most will take Adriel's code in other folders and annotate it.
+I hope that by doing so, I will better understand his code, and be able to contribute more to writing the paper on our reasearch.
+Additionally, I hope these annotations help future RA's understand the code as well.
 
-## Description
+The numbering of the files is an attempt to be consistent with the tidyverse style guide section 1.1 (found at https://style.tidyverse.org/).
+As I work more with the code, I will do my best to ensure that the numbering reflects a logical flow for the code.
 
-Each script should do something specific (like tidyverse functions), have a descriptive name, and include number prefixes if they are meant to be run in a certain order (e.g., `01_import_data.R`, `02_clean_data.R`).
+If the documents only contain a single, massive block of code, this means that I haven't gotten around to annotating that script.
 
-## Project Workflow
+Below, I have a quick and brief documentation of what I understand about each file.
 
-* Use RStudio projects.
-* Use `here::here()` to specify files paths.
-* Use tidyverse functions as much as possible.
-* Try and follow the [tidyverse style guide](https://style.tidyverse.org).
+# Overview of Files
+Note: Files prefaced by 99_ are files that I don't understand completely, and seem to be more related to data wrangling than model building.
+
+### 01_test_rds_connection.R
+This file contains the credentials necessary to log into the R Data Server. It also has brief code for extracting some of the tweets from the database, and it writes the data to a .txt file.
+
+### 02_visualize_twitter_data.R
+This file takes airline twitter data and creates a few visualizations (i.e. wordclouds) on the tweet text. It was formerly called CountingCockroaches.R.
+
+### 03_analyze_complaint_categories.Rmd
+This file analyzes our train/test dataset, documents the label types, visualizes the number of complaints to non-complaints, and visualizes the number of each complaint category.
+Additionally, it runs a tf_idf analysis on the catch-all complaint category to see if another category can be identified.
+
+### 04_build_fasttext_supervised_classifier.Rmd
+This file documents the building of our fastText supervised classifier model.
+
+### 05_define_culstering_functions.R
+This file was formerly called clus_func.R.
+It contains the code defining a few functions.
+These functions will be referenced in future scripts to help build our model.
+One especially important function here is the avg_word_vec function.
+
+##### Average Word Vector Function
+This function will take the word vectors for each word in a tweet, and will average the vectors to create a single vector representing the tweet as a whole.
+The word vectors will be generated by a fasttext unsupervised model.
+This will effectively become a mathmatical summary of each tweet, and will be a valuable input to our model.
+
+### 06_define_prediction_functions.R
+This file was formerly called predict_func.R. It contains a lot of useful functions for our model. Two important functions defined here are the VectorizeTweet() and TweetFeatures() functions.
+
+##### VectorizeTweet Function.
+This function has two classes: one for use with a unsupervised fastText model, and another for use with a PCA model trained on the output of the VectorizeTweet() function.
+This class is functionally identical to the avg_word_vec() function (as far as I understand--looking at the code they should do the exact same thing, so I'm not entirely sure why we have two nearly identical functions).
+
+The first class (used with an unsupervised fastText model) breaks a tweet down into individual words, and finds the word vectors associated with each of these words.
+After these word vectors are stored in a dataframe, each variable of the dataframe is averaged to produce a single vector (the same size as an individual word vector).
+This "tweet vector" can be thought of as a mathematical summary of the tweet.
+
+The second class (used with a PCA model trained on the output of the first class), produces a tibble with the first n principal components of the tweet vector (where n is defined by the user).
+
+##### TweetFeatures Function
+This function creates a simple summary of a tweet's features (i.e.
+the number of exclamation points, the number of links used, and the number of times this user has been mentioned previously in the data).
+
+### 07_build_classifier.Rmd
+This document was formerly called classifier_construction.R.
+It contains the code that builds models referenced in other files, namely the model50-tweet_sample_2M_noRT.dat and xgb.modelPC4-xgb_version.dat.
+The xgb.modelPC4-xgb_version.dat model is the full, frankenstein model we have built.
+When I reference "the model," or the "frankenstein model," this is the model I am referring to.
+
+Note: I can't seem to find the logit_classifier_func.R file anywhere. It's referenced in classifier_construction.R
+
+### 08_define_tweet_complaint_predictor_function.R
+tweet_complaint_predictor.Rmd builds a function named newTweetComplaintPredictor, which is referenced in serveral other scripts. This function uses our model to predict
+
+### 09_classifier_testing.Rmd
+This file references the full model, and makes predictions on single tweets. You can use it to see how the model will react with tweets you find online, as well as tweets you write yourself.
+
+### 99_batch_classification.Rmd
+### 99_build_standalone_fasttext_classification_model.Rmd
+In this file, I create my own fastText supervised classification model to see how well it can classify on its own (i.e.
+without the help of a PCA and XGBoost model).
+This will be a good base to compare against our own xgboost model built in 07_construct_classifier.Rmd
+
+Note: Code still has a few places it needs to be tweaked and isn't fully funcitonal yet--I need to write the .txt files and figure out how to make predictions with the trained model.
+
+### 99_fasttext_clust_EDA.Rmd
+### 99_json_parse_upload.Rmd
+### 99_logit_regression_classifier.Rmd
+### 99_read_tweets_json.Rmd
+### 99_tweet_object.Rmd

### 2019-05-30 Code/complaint-prediction/R/TweetComplaintPredictor.R

@@ -1,27 +1,0 @@
-# TweetComplaintPredictor class constructor ----------------------------------------
-# Class constructor 
-newTweetComplaintPredictor <- function(fasttextModel, pcaModel, xgbModel, pcaModelComponentCutoff) {
-  component <- enquo(pcaModelComponentCutoff)
-  
-  if(class(fasttextModel)[1] != "Rcpp_fastrtext"){
-    stop("fasttextModel is not a member of class Rcpp_fastrtext")
-  }
-  if(class(pcaModel) != "prcomp"){
-    stop("pcaModel is not a member of class Rcpp_fastrtext")
-  }
-  if(class(xgbModel) != "xgb.Booster"){
-    stop("xgbModel is not a member of class Rcpp_fastrtext")
-  }
-  
-  newTweetComplaintPredictor <- list(fasttextModel = fasttextModel,
-                                     pcaModel = pcaModel,
-                                     xgbModel = xgbModel,
-                                     pcaModelComponentCutoff = component)
-  
-  class(newTweetComplaintPredictor) <- "TweetComplaintPredictor"
-  
-  return(newTweetComplaintPredictor)
-}
-
-# Class checker
-is.TweetComplaintPredictor <- function(x) inherits(x, "TweetComplaintPredictor")

### 2019-05-30 Code/rds-data-processing/read_tweets_Json.R

@@ -1,135 +1,0 @@
-library(RPostgreSQL)
-library(dbplyr)
-
-library(R.utils)
-library(glue)
-
-library(rjson)
-library(RCurl)
-library(tidyverse)
-
-
-
-# create_df(): ----------------------------------------------------------------
-### This function creates one row of a dataframe from a JSON object. This row can be uploaded to a database
-
-
-create_df <- function(data)
-{
-  suppressWarnings(
-  out <- tibble(
-    tweet_created_at = null_to_na(data$created_at),
-    tweet_id = null_to_na(data$id_str),
-    tweet_text = null_to_na(data$text),
-    in_reply_to_status_id_str = null_to_na(data$in_reply_to_status_id_str),
-    in_reply_to_user_id_str = null_to_na(data$in_reply_to_user_id_str),
-    in_reply_to_screen_name = null_to_na(data$in_reply_to_screen_name),
-    usr_name = null_to_na(data$user$name),
-    usr_screen_name = null_to_na(data$user$screen_name),
-    usr_url = null_to_na(data$user$url),
-    usr_description = null_to_na(data$user$description),
-    usr_protected = null_to_na(data$user$protected),
-    usr_followers_count = null_to_na(data$user$followers_count),
-    usr_friends_count = null_to_na(data$user$friends_count),
-    usr_listed_count = null_to_na(data$user$listed_count),
-    usr_created_at = null_to_na(data$user$created_at),
-    usr_statuses_count = null_to_na(data$user$statuses_count),
-    usr_verified = null_to_na(data$user$verified),
-    coordinates = null_to_na(data$coordinates),
-    tweet_retweet_count_at_pull_time = null_to_na(data$retweet_count),
-    tweet_favorite_count_at_pull_time = null_to_na(data$favorite_count),
-    tweet_hastags = null_to_na(glue::collapse(unlist(map(data$entities$hashtags, function(x) x[[1]])), sep = ", ")),
-    tweet_urls = null_to_na(glue::collapse(unlist(map(data$entities$urls, function(x) x[[1]])), sep = ", ")),
-    tweet_user_mentions = null_to_na(glue::collapse(unlist(map(data$entities$user_mentions, function(x) x[[1]])), sep = ", ")),
-    tweet_sentiment = null_to_na(data$sentiment),
-    date = null_to_na(data$date$`$date`),
-    oid = null_to_na(data$`_id`$`$oid`)
-  ))
-  return(out)
-}
-
-
[…]

### 2019-05-30 Code/twitterDataExample/tweetObject.R

@@ -1,79 +1,0 @@
-ObjectSample <- list(
-  "_id" = 'ObjectId("534769eee4b0efdb7b081251")',
-  "created_at" = "Fri Apr 11 04=04=57 +0000 2014",
-  "id" = 'NumberLong("454470130765135872")',
-  "id_str" = "454470130765135872",
-  "text" = "@united is there a service fee to get the miles back if i don't clear? your rules are unclear.",
-  "source" = "web",
-  "truncated" = FALSE,
-  "in_reply_to_status_id" = 'NumberLong("454467945172074497")',
-  "in_reply_to_status_id_str" = "454467945172074497",
-  "in_reply_to_user_id" = 260907612,
-  "in_reply_to_user_id_str" = "260907612",
-  "in_reply_to_screen_name" = "united",
-  "user" = list(
-    "id" = 770550,
-    "id_str" = "770550",
-    "name" = "Rakesh Agrawal",
-    "screen_name" = "rakeshlobster",
-    "location" = "San Francisco, CA",
-    "url" = "http=//redesignmobile.com",
-    "description" = "Global strategy at PayPal. As seen on CNBC, Bloomberg TV and VentureBeat.",
-    "protected" = FALSE,
-    "followers_count" = 9034,
-    "friends_count" = 1672,
-    "listed_count" = 410,
-    "created_at" = "Tue Feb 13 21=36=08 +0000 2007",
-    "favourites_count" = 4807,
-    "utc_offset" = -25200,
-    "time_zone" = "Pacific Time (US & Canada)",
-    "geo_enabled" = TRUE,
-    "verified" = FALSE,
-    "statuses_count" = 39454,
-    "lang" = "en",
-    "contributors_enabled" = FALSE,
-    "is_translator" = FALSE,
-    "is_translation_enabled" = FALSE,
-    "profile_background_color" = "0099B9",
-    "profile_background_image_url" = "http=//abs.twimg.com/images/themes/theme4/bg.gif",
-    "profile_background_image_url_https" = "https=//abs.twimg.com/images/themes/theme4/bg.gif",
-    "profile_background_tile" = FALSE,
-    "profile_image_url" = "http=//pbs.twimg.com/profile_images/378800000722918071/ce9e53447ed1ee7d90f5e0d1a3b800c5_normal.jpeg",
[…]

### 2019-07-31 Code/Code for Rethinking and Quap.R
Cleaned up regression (now called ecology_model) estimated with quap()

@@ -1,17 +1,0 @@
-# in order to insall all package, install rtools from
-# https://cran.r-project.org/bin/windows/Rtools/
-# install Rtools35.exe
-
-install.packages("usethis")
-library(usethis)
-install.packages("rstan", repos = "https://cloud.r-project.org/", dependencies = TRUE)
-library(rstan)
-install.packages(c("coda","mvtnorm","devtools"))
-library(devtools)
-devtools::install_github("rmcelreath/rethinking",ref="Experimental")
-library(rethinking)
-
-?quap
-
-
-#lets try again

### 2019-07-31 Code/Model beg.R

@@ -1,62 +1,0 @@
-# Simulating Data ---------------------------------------------------------
-# Load packages.
-library(rethinking)
-library(devtools)
-library(usethis)
-
-# Simulate explanatory variables.
-length_of_tweet <- sample(10:280, size = 1000 , replace = TRUE ) # Length of tweet.
-past <- sample(0:1 , size = 1000 , replace = TRUE )              # Have they tweeted about this in the past.
-re_tweet <- runif(1000, min=0, max=5)                            # How many times has this re-tweeted.
-# followers <- sample(0:1000, size=1000, replace=TRUE)             # How many followers they have.
-followers <- sample(0:1000, size=1000, replace=TRUE)             # How many followers they have.
-
-# Specify parameter values.
-b0 <- 1
-bl <- 5
-bp <- 10
-br <- -3
-bf <- 2
-error <- rnorm(1000, 0, 1) 
-
-# Generate y.
-mydata <- b0 + bl * length_of_tweet + bp * past + br * re_tweet + bf * followers + error
-
-# Combine into data frame.
-d <- data.frame(mydata, length_of_tweet, past, re_tweet, followers)
-
-# Estimation --------------------------------------------------------------
-# Run quap.
-twitter <- quap(
-  alist( 
-    mydata ~ dnorm(mu, sigma) , 
-    mu <- bl*length_of_tweet + bp*past + br*re_tweet + bf*followers , 
-    bl ~ dnorm(0, .25), 
-    bp ~ dnorm(0, .25), 
-    br ~ dnorm(0, .25), 
-    bf ~ dnorm(0, .25), 
-    sigma ~ dexp(1) 
-  ), 
-  data = d
-)
-
-# Evaluating model fit.
-precis(twitter_scaled)
-plot(twitter_scaled)
-
-#trying to run the model without "weights"
-plot(mydata_scaled)
-
-impact <- lm(mydata_scaled~followers_scaled, data=d_scaled)
-
-plot(impact)
-
-#Adam 
-
-#McKenna
-
-WAIC(twitter_scaled)
-
-compare(twitter, twitter_scaled)
-
-

### 2019-07-31 Code/ecology_model.R

@@ -1,0 +1,47 @@
+# Stan/Rethinking Setup ---------------------------------------------------
+# 1. Install Stan, a compiler, and rstan: github.com/stan-dev/rstan/wiki/RStan-Getting-Started.
+# 2. Install "experimental" version of the rethinking packages:
+#    devtools::install_github("rmcelreath/rethinking", ref = "Experimental")
+
+# Simulating Data ---------------------------------------------------------
+# Load packages.
+library(rethinking)
+
+# Simulate explanatory variables.
+length <- sample(10:280, size = 1000 , replace = TRUE ) # Length of tweet.
+past <- sample(0:1 , size = 1000 , replace = TRUE )     # Have they tweeted about this in the past?
+retweet <- runif(1000, min=0, max=5)                    # How many times has this been retweeted.
+followers <- sample(0:1000, size=1000, replace=TRUE)    # How many followers they have.
+
+# Specify parameter values.
+b0 <- 1
+bl <- 5
+bp <- 10
+br <- -3
+bf <- 2
+error <- rnorm(1000, 0, 1) 
+
+# Generate y.
+mydata <- b0 + bl * length + bp * past + br * retweet + bf * followers + error
+
+# Combine into data frame.
+data <- data.frame(mydata, length, past, retweet, followers)
+
+# Estimation --------------------------------------------------------------
+# Run quap.
+out <- quap(
+  alist( 
+    mydata ~ dnorm(mu, sigma) , 
+    mu <- bl * length + bp * past + br * retweet + bf * followers , 
+    bl ~ dnorm(0, .25), 
+    bp ~ dnorm(0, .25), 
+    br ~ dnorm(0, .25), 
+    bf ~ dnorm(0, .25), 
+    sigma ~ dexp(1) 
+  ), 
+  data = data
+)
+
+# Model output.
+out
+

### 2019-07-31 Code/ecology_model.R
Added URL for experimental version of rethinking

@@ -1,7 +1,6 @@
 # Stan/Rethinking Setup ---------------------------------------------------
-# 1. Install Stan, a compiler, and rstan: github.com/stan-dev/rstan/wiki/RStan-Getting-Started.
-# 2. Install "experimental" version of the rethinking packages:
-#    devtools::install_github("rmcelreath/rethinking", ref = "Experimental")
+# 1. Install Stan, a compiler, and rstan: github.com/stan-dev/rstan/wiki/RStan-Getting-Started
+# 2. Install rethinking package: https://github.com/rmcelreath/rethinking/tree/Experimental
 
 # Simulating Data ---------------------------------------------------------
 # Load packages.

### 2019-08-02 Paper/README.Rmd

@@
 ---
-title: "Counting the Cockroaches in the Walls or I Know Why the Caged Bird Tweets: Assessing the Severity of Service Failures Through Social Chatter"
+title: "Counting the Cockroaches in the Walls: Assessing the Severity of Service Failures Through Social Chatter"
 output: github_document
@@
 In this paper, we develop a model that uses a variety of observed customer complaints on Twitter to make inference about the severity of service failures.
+
+Keywords: Social Media, Bayesian Inference, Classification Customer Satisfaction, Services Marketing, Text Analysis
 

### 2019-08-15 Code/Stan-introduction.Rmd
Stan introduction files added and edits to the ecology model.

---
title: "Stan Introduction"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The Need for Stan

Part of the difficulty of Bayesian statistics for us is the R is not equipped to handle some of the necessary procedures. For example, sampling from a posterior distribution is an essential part of Bayesian inference, but if we are using MCMC or a variation of it as part of our sampling (and we likely are) writing the code in R can be long and comlicated. Even running the code neccessary may take an impractical amount of time.

Stan is a programming language seperate from R designed to help in Bayesian analysis. Stan removes the dozens of lines of code that we would have needed to write, and instead asks for us to fill in three basics blocks of information: 'data', 'parameters', and 'model'.

We'll explain more about each of these components and show how to use Stan within Rstudio with the example code below.

```{r}
# Run all R code in a new R script file called RStan_introduction
# The package below will install Stan to Rstudio, and you will be able to create Stan files.
install.packages("rstan", repos = "https://cloud.r-project.org/", dependencies = TRUE)
```

```{r}
pkgbuild::has_build_tools(debug = TRUE) 
#This line should return output 'TRUE'

```

```{r}
library(rstan)
#If this is your first Rstan installation, restart R. 
#If the installation has not gone correctly, a more in depth guide can be found at
#https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started
```

Now we should have rstan installed. Restart R! As with most new packages, this should get everything we need working.

Go to the file tab in the top left corner of Rstudio. Select new file. You should now see 'Stan file' in this list. Select it, and return here.

If Stan file is not an option, something went wrong in setup. Return to this website https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started for more help.

If the Stan file is now open, perfect, save it as my_stan_model and leave it there for now. We need to make some fake data for our Stan model.

# Create our data

```{r}
N = 100
Y = rnorm(N, 1.6, 0.2)
hist(Y)
```

So we have some very simple data that will work for our stan model. We have 100 data points, the data is normally distributed around a mean of 1.6, and has a standard deviation of 0.2. From here we will start building stan in your new stan file.

Clear any default text out of your Stan file and paste the following.

# Build Stan model

Stan files use double slash marks for comments // 
Lines within blocks should end with a semi colon ;.
After the model block, leave one line underneath it.

***
data {

}

parameters {

}

model {

}

***

These are the blocks I referred to earlier, and are the most used. There are others you'll learn about later.
Lets start with the first, data. Pretty straitforward, we need to tell the model what data we're working with. Down below you'll see how we format it.

***
data {  
  int N;  
  real Y[N];  
}

parameters {

}

model {

}

***

First we include our sample size. int because we are dealing with integers, a discrete count. Second, our observations, Y[N]. Real because our data are continuous. N is in brackets to tell stan that we have an array of data points for N individuals (100 in this case).

***
data {  
  int N;  
  real Y[N];  
}

parameters {  
  real mu;  
  real<lower=0> sigma;  
}

model {

}

***

Our model section includes the parameters we are trying to estimate from our data. In our simple model here, we only are worried about mu and sigma. Both are continuous, so type real, but we want to make sure the model knows that sigma cannot be negative. Thus we add in the <lower=0> modifier. That's it for parameters.

***
data {  
  int N;   
  real Y[N];  
}

parameters {  
  real mu;  
  real<lower=0> sigma;  
}

model {  
  for(i in 1:N)  
   Y[i] ~ normal(mu, sigma);  
  mu ~ normal(1.7, 0.3)  
  sigma ~ cauchy(0, 1);  
}

***

The model block gets a little more complicated, as will parameters and data in more complicated models that we will see later. For right now, this will do. We start by defining our likelyhood here, in which we make a for loop that will run all points of our data Y, assuming a normal distribution. Then we define our priors for both our parameters, mu and sigma. In this code, we assume a prior very close to our data, but tweek the numbers here to see how priors interact with the likelyhood.

# Using our Stan model in R

Lets return to our Rscript.

Since we already have the rstan library loaded, we can run our data through the stan model and look at some of the important results.

```{r}
mymodeldata = list(
  N = 100,
  Y = rnorm(N, 1.6, 0.2)
)
fit = stan(
  file = here::here("my_stan_model.stan"),
  data = mymodeldata,
  seed = 42
)
```

The function stan can be manipulated in greater detail, but the only details we need to worry about now are correctly calling the stan model, entering our data as a list, and the seed just to make sure results are consistent and anyone running the code can know they ran everything corectly.

The here::here line will be useful as we navigate directories in Github. For now, assuming that your Rscript and Stan file are in the same directory or project on your computer, you should only need to correctly spell the name of your Stan file.

Now the object fit contains the results of running our data through our model. Let's check them out.
```{r}
print(fit)
```
Here we can see the estimated means for our parameters and diagnose our model for issues with convergence. You will learn more abot that later, but the model seems to have run correctly here. We can also look at the posterior with the following code.
```{r}
parametermu = extract(fit)$mu
hist(parametermu)
```
Here we have a posterior distribtution for mu. Since our prior and simulated data were very similar, we see a very tight distribution, but again, try it with different means for both the sample and the prior, and see how the data interracts.

# Conclusion

This has been a very simple introdution to help you create a Stan model and using R to run data through it. Your future Stan models will be a lot more complex, but this example should help you see how models differ and the impact new code has going forward.

### 2019-08-16 Code/Stan-introduction.Rmd
Rmarkdown outputed to a Github Doc

@@
 title: "Stan Introduction"
-output:
-  html_document: default
-  word_document: default
-  pdf_document: default
+output: github_document
 ---
@@
 fit = stan(
-  file = here::here("my_stan_model.stan"),
+  file = here::here("Code", "my_stan_model.stan"),
   data = mymodeldata,

### 2019-08-26 Code/Stan-introduction.Rmd
adding code chunks for stan code
added chains code and explanation, and other minor edits.

@@
 
-***
+```
 data {
@@
 
-***
+```
 
@@
 
-***
+```
 data {  
@@
 model {  
+//This for loop is our likelyhood
   for(i in 1:N)  
    Y[i] ~ normal(mu, sigma);  
+//These are our priors
   mu ~ normal(1.7, 0.3)  
@@
   data = mymodeldata,
-  seed = 42
+  seed = 42,
+  chains = 4
 )
@@
 
-Now the object fit contains the results of running our data through our model. Let's check them out.
+The chains code is helpful for making your code run more efficiently and checking for accuracy.
+We will go into more detail later, but for now you should run 4 chains, assuming your computer has 4 cores.
+If your not sure how many cores you have, you can usually find that information in your computer settings, or you can run this code.
+
+```
+install.packages("parellel")
+library(parallel)
+detectCores()
+```
+R will detect the number of cores on your PC.
+
+Now the object 'fit' contains the results of running our data through our model. Let's check them out.
 ```{r}

### 2019-10-17 Code/postratification_code.Rmd
Begginings of a postratification model for our MRP model.

---
title: "Postratification Code"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Postratification code

We are looking into an MRP model for Counting Cockroaches and we want to learn what postratification is and if we can do it in our model.

The documents we study are currently together on a google doc

```{r}
library(tidyverse)

vote_yes <- c(rep(0, 25*(1-0.76)), 
              rep(1, 25*0.76),
              rep(0, 50*(1-0.3)),
              rep(1, 50*0.3))
vote_yes

```

### 2019-10-21 Code/postratification_code.Rmd
commit

@@
 vote_yes
+mean(vote_yes)
 
 ```
+
+That is our population. We will now make a sample with subgroups.
+
+```{r}
+poll_data <- tibble(
+  group = c(rep("A", 25), rep("B", 10)),
+  yes = c(rep(1, 19), rep(0, 6), rep(1, 3), rep(0, 7))
+)
+poll_data %>%
+  group_by(group) %>%
+  summarise(count = n())
+```
+
+Here are our subgroups and how many our represented in our sample. It does not match the proportions found in our population.
+
+```{r}
+Census <- tibble(
+  group = c("A", "B"),
+  pop = c(25, 50)
+)
+Census
+mean(poll_data$yes)
+```
+
+Our mean for the sample varies from our population, so we stratify.
+
+```{r}
+group_support <- poll_data %>%
+  group_by(group) %>%
+  summarise(perc_support = mean(yes))
+group_support
+
+overall_support <- group_support %>%
+  summarise(total_support = sum(perc_support * Census$pop/sum(Census$pop)))
+overall_support
+```

### 2019-11-22 Code/mrp/mrp-vignette.Rmd
Trying to translate the stan complex to stan simple.

---
title: "MPR case study 2"
author: "McKenna Weech"
date: "11/7/2019"
output: github_document
---
original: http://mc-stan.org/rstanarm/articles/mrp.html

```{r}
library(rstanarm)
library(ggplot2)
library(bayesplot)
theme_set(bayesplot::theme_default())
library(dplyr)
library(tidyr)
```

Here is the code that they use to make their '''simulate_mrp_data''' function
```{r}
simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5) 
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }

  # Now let's adjust for the probability of response
  p_response_baseline <- 0.01
  p_response_male <- c(2, 0.8) / 2.8
  p_response_eth <- c(1, 1.2, 2.5) / 4.7
  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
  p_response_inc <- c(1, 0.9, 0.8) / 2.7
  p_response_state <- rbeta(50, 1, 1)
  p_response_state <- p_response_state / sum(p_response_state)
  p_response <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    p_response[j] <-
      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
  }
  people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)

  ## For respondent i, people[i] is that person's poststrat cell,
  ## some number between 1 and 32
  n_cell <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    n_cell[j] <- sum(people == j)
  }

  coef_male <- c(0,-0.3)
  coef_eth <- c(0, 0.6, 0.9)
  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
  coef_income <- c(0,-0.2, 0.6)
  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
  true_popn <- data.frame(poststrat[, 1:5], cat_pref = rep(NA, prod(J)))
  for (j in 1:prod(J)) {
    true_popn$cat_pref[j] <- plogis(
      coef_male[poststrat[j, 1] + 1] +
        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
      )
  }

  #male or not, eth, age, income level, state, city
  y <- rbinom(n, 1, true_popn$cat_pref[people])
  male <- poststrat[people, 1]
  eth <- poststrat[people, 2]
  age <- poststrat[people, 3]
  income <- poststrat[people, 4]
  state <- poststrat[people, 5]

  sample <- data.frame(cat_pref = y, 
                       male, age, eth, income, state, 
                       id = 1:length(people))

  #Make all numeric:
  for (i in 1:ncol(poststrat)) {
    poststrat[, i] <- as.numeric(poststrat[, i])
  }
  for (i in 1:ncol(true_popn)) {
    true_popn[, i] <- as.numeric(true_popn[, i])
  }
  for (i in 1:ncol(sample)) {
    sample[, i] <- as.numeric(sample[, i])
  }
  list(
    sample = sample,
    poststrat = poststrat,
    true_popn = true_popn
  )
}
```
Wow.

Okay back to the case study. 
```{r}
mrp_sim <- simulate_mrp_data(n=1200)
str(mrp_sim)
sample <- mrp_sim[["sample"]]
rbind(head(sample), tail(sample))
```
Using the function to simulate data.

```{r}
poststrat <- mrp_sim[["poststrat"]]
rbind(head(poststrat), tail(poststrat))
```

```{r}
fit <- stan_glmer(cat_pref ~ factor(male) + factor(male) * factor(age) + (1 | state) + (1 | age) + (1 | eth) + (1 | income), 
                  family = binomial(link = "logit"), 
                  data = sample)

library(rstanarm)
example(fit)
rstan::get_stanmodel(fit$stanfit)
```
```{r}
print(fit)
```
```{r}
posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat) 
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N) 
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```
```{r}
sample_popn_pref <- mean(sample$cat_pref)
round(sample_popn_pref, 3)
```
```{r, eval=FALSE}
compare2 <- compare2 +
  geom_hline(yintercept = model_popn_pref[1], colour = '#2ca25f', size = 1) +
  geom_text(aes(x = 5.2, y = model_popn_pref[1] + .025), label = "MRP", colour = '#2ca25f')
bayesplot_grid(compare, compare2, 
               grid_args = list(nrow = 1, widths = c(8, 1)))

```
```{r}
true_ponp_pref <- sum(true_popn$cat_pref * poststrat$N) / sum(poststrat$N) 
round(ttrue_popn_pref, 3)
```

### 2019-11-22 Code/mrp/mrp case study .R

@@ -67,3 +67,21 @@ d.total.ave
 apipop %>% as.tibble() %>%
   summarise(mean(api00))
 
+### MRP with rstanarm 
+
+library(rstanarm)
+library(bayesplot)
+theme_set(bayesplot::theme_default())
+library(dplyr)
+library(tidyr)
+
+
+
+
+
+
+
+
+
+
+

### 2019-12-13 Code/postratification_code.Rmd

@@
 ```
+
+```{r}
+install.packages("rstanarm")
+library(rstanarm)
+```
+
+```{r}
+simulate_mrp_data <- function(n) {
+  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
+  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
+  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
+  count <- 0
+  for (i1 in 1:J[1]){
+    for (i2 in 1:J[2]){
+      for (i3 in 1:J[3]){
+        for (i4 in 1:J[4]){
+          for (i5 in 1:J[5]){
+              count <- count + 1
+              # Fill them in so we know what category we are referring to
+              poststrat[count, 1:5] <- c(i1-1, i2, i3,i4,i5) 
+          }
+        }
+      }
+    }
+  }
+  # Proportion in each sample in the population
+  p_male <- c(0.52, 0.48)
+  p_eth <- c(0.5, 0.2, 0.3)
+  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
+  p_income<-c(.50,.35,.15)
+  p_state_tmp<-runif(50,10,20)
+  p_state<-p_state_tmp/sum(p_state_tmp)
+  poststrat$N<-0
+  for (j in 1:prod(J)){
+    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
+      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
+  }
+
+  # Now let's adjust for the probability of response
+  p_response_baseline <- 0.01
+  p_response_male <- c(2, 0.8) / 2.8
+  p_response_eth <- c(1, 1.2, 2.5) / 4.7
+  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
+  p_response_inc <- c(1, 0.9, 0.8) / 2.7
+  p_response_state <- rbeta(50, 1, 1)
+  p_response_state <- p_response_state / sum(p_response_state)
+  p_response <- rep(NA, prod(J))
+  for (j in 1:prod(J)) {
+    p_response[j] <-
+      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
+      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
+      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
+  }
+  people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
+
+  ## For respondent i, people[i] is that person's poststrat cell,
+  ## some number between 1 and 32
+  n_cell <- rep(NA, prod(J))
+  for (j in 1:prod(J)) {
+    n_cell[j] <- sum(people == j)
+  }
+
+  coef_male <- c(0,-0.3)
+  coef_eth <- c(0, 0.6, 0.9)
+  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
+  coef_income <- c(0,-0.2, 0.6)
+  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
+  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
+                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
+  true_popn <- data.frame(poststrat[, 1:5], cat_pref = rep(NA, prod(J)))
+  for (j in 1:prod(J)) {
+    true_popn$cat_pref[j] <- plogis(
+      coef_male[poststrat[j, 1] + 1] +
+        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
+        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
+        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
+      )
+  }
+
+  #male or not, eth, age, income level, state, city
+  y <- rbinom(n, 1, true_popn$cat_pref[people])
+  male <- poststrat[people, 1]
+  eth <- poststrat[people, 2]
+  age <- poststrat[people, 3]
+  income <- poststrat[people, 4]
+  state <- poststrat[people, 5]
+
+  sample <- data.frame(cat_pref = y, 
+                       male, age, eth, income, state, 
+                       id = 1:length(people))
+
+  #Make all numeric:
+  for (i in 1:ncol(poststrat)) {
+    poststrat[, i] <- as.numeric(poststrat[, i])
+  }
+  for (i in 1:ncol(true_popn)) {
+    true_popn[, i] <- as.numeric(true_popn[, i])
+  }
+  for (i in 1:ncol(sample)) {
+    sample[, i] <- as.numeric(sample[, i])
+  }
+  list(
+    sample = sample,
+    poststrat = poststrat,
+    true_popn = true_popn
+  )
+}
+```
+
+```{r}
+mrp_sim <- simulate_mrp_data(n=1200)
+str(mrp_sim)
+```

### 2019-12-20 Code/03_analyze_complaint_categories.Rmd

--- 2019-03-19 Code/01_analyze_complaint_categories.Rmd
@@
 ```{r}
-# Note that the labeled tweet data is kept in my Temporary folder
-data <- read_csv("../Temporary/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")
+# Note that the labeled tweet data is kept in my Temporary folder in the train_test_data folder
+data <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv"))
 ```

### 2019-12-30 Code/mrp/mrp-vignette.Rmd
Trying to extract stan code from rstanarm

@@
 
-Here is the code that they use to make their '''simulate_mrp_data''' function
+Here is the code that they use to make their funtion. 
 ```{r}
@@
 ```
-Wow.
 
-Okay back to the case study. 
+Running the function to get simulated data. 
 ```{r}
-mrp_sim <- simulate_mrp_data(n=1200)
+mrp_sim <- simulate_mrp_data(n=100)
 str(mrp_sim)
+
 sample <- mrp_sim[["sample"]]
-rbind(head(sample), tail(sample))
+poststrat <- mrp_sim[["poststrat"]]
+true_popn <- mrp_sim[["true_popn"]]
 ```
-Using the function to simulate data.
-
 ```{r}
-poststrat <- mrp_sim[["poststrat"]]
-rbind(head(poststrat), tail(poststrat))
+fit <- stan_glmer(
+  cat_pref ~ factor(male) + factor(male) * factor(age) + 
+    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
+  family = binomial(link = "logit"),
+  data = sample
+)
 ```
 
+Now I am trying to put the data into a list that we can input into stan. 
 ```{r}
-fit <- stan_glmer(cat_pref ~ factor(male) + factor(male) * factor(age) + (1 | state) + (1 | age) + (1 | eth) + (1 | income), 
-                  family = binomial(link = "logit"), 
-                  data = sample)
+stan_data <- list( 
+  K = 5,
 
-library(rstanarm)
-example(fit)
-rstan::get_stanmodel(fit$stanfit)
+  )
+
+# This is the RStanrm function that they use
+
+# fit <- stan_glmer(
+#   cat_pref ~ factor(male) + factor(male) * factor(age) + 
+#     (1 | state) + (1 | age) + (1 | eth) + (1 | income),
+#   family = binomial(link = "logit"),
+#   data = sample
+# )
 ```
-```{r}
-print(fit)
-```
-```{r}
-posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat) 
-poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N) 
-model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
-round(model_popn_pref, 3)
-```
-```{r}
-sample_popn_pref <- mean(sample$cat_pref)
-round(sample_popn_pref, 3)
-```
-```{r, eval=FALSE}
-compare2 <- compare2 +
-  geom_hline(yintercept = model_popn_pref[1], colour = '#2ca25f', size = 1) +
-  geom_text(aes(x = 5.2, y = model_popn_pref[1] + .025), label = "MRP", colour = '#2ca25f')
-bayesplot_grid(compare, compare2, 
-               grid_args = list(nrow = 1, widths = c(8, 1)))
-
-```
-```{r}
-true_ponp_pref <- sum(true_popn$cat_pref * poststrat$N) / sum(poststrat$N) 
-round(ttrue_popn_pref, 3)
-```

### 2020-01-17 Code/mrp/Case Study .Rmd
Adding in code to do poststratification

--- 2019-12-30 Code/mrp/mrp-vignette.Rmd
@@
 ---
-title: "MPR case study 2"
+title: "MRP Case Study"
 author: "McKenna Weech"
-date: "11/7/2019"
+date: "1/17/2020"
 output: github_document
 ---
-original: http://mc-stan.org/rstanarm/articles/mrp.html
 
-```{r}
+Load packages 
+```{r message = FALSE}
 library(rstanarm)
@@
 
-Here is the code that they use to make their funtion. 
+First we will simulate data. 
 ```{r}
@@
                            c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
-  true_popn <- data.frame(poststrat[, 1:5], cat_pref = rep(NA, prod(J)))
+  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
   for (j in 1:prod(J)) {
@@
 
-  sample <- data.frame(cat_pref = y, 
+  sample <- data.frame(service_failure = y, 
                        male, age, eth, income, state, 
@@
 
-Running the function to get simulated data. 
+Next we can view the data
 ```{r}
@@
 ```
-```{r}
-fit <- stan_glmer(
-  cat_pref ~ factor(male) + factor(male) * factor(age) + 
-    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
-  family = binomial(link = "logit"),
-  data = sample
-)
+
+### Begine Bayseian Work Flow (Modeling) 
+We are woking towards building a model that can predict the severity of a service failure baised on consumer feedback.
+The case study will work to build a simple model and impliment postratification to generalize findings in a sample to a larger population.
+The model we will focus on here will start as a simple binomial model but we will hopefully build it up.
+We will be using code taken from Lauren Kenndey and Jonah Gabry's vignette on postratification see: http://mc-stan.org/rstanarm/articles/mrp.html
+
+We will be lookig at the following pices of data about each "customer"
+
+* gender
+* age (group)
+* income (group)
+* state
+
+All of the variables are categorical variables.
+
+WE NEED A MODEL
+
+I HATE RSTANARM -- JUST SAYING
+
+### Postratification 
+Note: for now I have set these chuncks to eval = false because we don
+t have a poststrat_prob yet so it freaks out
+
+For the postratification portion we take the estimate that we get from the model times poststrat$/N / sum(postsrat$N)
+
+```{r eval = FALSE}
+poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
+model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
+round(model_popn_pref, 3)
 ```
 
-Now I am trying to put the data into a list that we can input into stan. 
-```{r}
-stan_data <- list( 
-  K = 5,
+Becasue we are using simulated data we can see how our poststratified predictions compare to the true population
 
-  )
+```{r eval = FALSE}
+sample_popn_pref <- mean(sample$cat_pref)
+round(sample_popn_pref, 3)
 
-# This is the RStanrm function that they use
-
-# fit <- stan_glmer(
-#   cat_pref ~ factor(male) + factor(male) * factor(age) + 
-#     (1 | state) + (1 | age) + (1 | eth) + (1 | income),
-#   family = binomial(link = "logit"),
-#   data = sample
-# )
+compare2 <- compare2 +
+  geom_hline(yintercept = model_popn_pref[1], colour = '#2ca25f', size = 1) +
+  geom_text(aes(x = 5.2, y = model_popn_pref[1] + .025), label = "MRP", colour = '#2ca25f')
+bayesplot_grid(compare, compare2, 
+               grid_args = list(nrow = 1, widths = c(8, 1)))
 ```

### 2020-01-23 Code/mrp/Case Study .Rmd
Case Study introduction draft

@@
 
-Load packages 
+Firms employ a variety of passive listening platforms (e.g., customer comment cards, help lines, social media) that elicit a variety of complaints.
+Since these complaints are self-selected, it isn’t obvious if complaints are widespread or genuinely indicative of systemic service failures.
+In other words, how can can a firm know when complaints can be ignored and when they need to addressed?
+This issue is related to a larger class of problems where the goal is to make inference about the size of a population from a non-random sample (e.g., the German tank problem).
+In this paper, we develop a model that uses a variety of observed customer complaints on Twitter to make inference about the severity of service failures.
+
+## Describe the model conceptually
+
+It has been said that if you observe a cockroach on your floor, there are likely thousands inside the walls of your home.
+Following this analogy, our hope is to count the cockroaches we can see and calculate how many are hiding in the walls.
+
+For the first portion of this case, we will be making a model around simulated data.
+Each observation will represent a single tweet, and we will be scoring them for satisfaction.
+We will use a multiple hierarchal linear model to predict satisfaction from the other known variables.
+Once we have the model predicting well on our simulated data, we will fit it to our real data, and from there use our real data satisfaction scores to measure service or product failure severity.
+
+Along with making a model, we will also be using poststratification to correct the weights in our simulated sample and real data to more correctly represent the population.
+This will be explained in greater detail as we postratify in this first iteration of the model, so we can explain and see the benefit of a full multiple regression with postratification model (MRP).
+
+To begin, we will start by generating our simulated data. It will run through an initial simple linear model and postratification.
+
+# Iteration 1: Simulation Data and Simple Model
+
+This initial block of code, we will just be loading in the needed packages and settings to make our sample and model code run.
+
 ```{r message = FALSE}
+library(tidyverse) #Load packages
+library(rstan)
 library(rstanarm)
@@
 library(tidyr)
+library(tidybayes)
+
+options(mc.cores = parallel::detectCores()) # Set Stan to use all availible cores
+rstan_options(auto_write = TRUE) # Don't recompile Stan code that hasn't changed
 ```
 
-First we will simulate data. 
+For this first iteration of modeling, we will be generating our own data. We will generate a population, and sample from it in order to build an MRP model.
+
+We will be modeling our populations `satisfaction`.
+This will eventually translate into measuring service severity when we apply our model to our real data.
+We will be looking at common characteristics like `gender`, `ethnicity`, `income`, `age`, and `state`.
+
+The following code will make a function `simulate_mrp_data` that will help us make our simulated data, and sample from it in such a way that we can use and see the value in postratification.
+
 ```{r}
@@
 
-Next we can view the data
-```{r}
-mrp_sim <- simulate_mrp_data(n=100)
-str(mrp_sim)
-
-sample <- mrp_sim[["sample"]]
-poststrat <- mrp_sim[["poststrat"]]
-true_popn <- mrp_sim[["true_popn"]]
-```
-
 ### Begine Bayseian Work Flow (Modeling) 

### 2020-01-24 Code/mrp/Case Study .Rmd
looking into rstanarm

--- 2020-01-17 Code/mrp/Case Study .Rmd
@@
 
-```{r eval = FALSE}
+```{r eval = FALSE2}
 poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
@@
 
-Becasue we are using simulated data we can see how our poststratified predictions compare to the true population
+Because we are using simulated data we can see how our poststratified predictions compare to the true population
 

### 2020-01-24 Code/mrp/mrp-vignette.Rmd
Trying to understand rstanarm
looking into rstanarm

@@
 ```
+
+```{r}
+sample
+```
+
 ```{r}
 fit <- stan_glmer(
-  cat_pref ~ factor(male) + factor(male) * factor(age) + 
-    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
+  cat_pref ~ factor(male) + factor(male) * factor(age) + # gender factor and a gender ~ age interaction factor
+    (1 | state) + (1 | age) + (1 | eth) + (1 | income), # random intercept with fixed means
   family = binomial(link = "logit"),
@@
 )
+```
+
+For information on the priors used.
+```{r}
+prior_summary.stanreg
 ```

### 2020-01-24 Code/mrp/Case Study .Rmd
Case Study intro draft v2

@@
 ```{r message = FALSE}
-library(tidyverse) #Load packages
-library(rstan)
-library(rstanarm)
-library(ggplot2)
-library(bayesplot)
-theme_set(bayesplot::theme_default())
-library(dplyr)
-library(tidyr)
-library(tidybayes)
-
-options(mc.cores = parallel::detectCores()) # Set Stan to use all availible cores
-rstan_options(auto_write = TRUE) # Don't recompile Stan code that hasn't changed
+# library(tidyverse) #Load packages
+# library(rstan)
+# library(rstanarm)
+# library(ggplot2)
+# library(bayesplot)
+# theme_set(bayesplot::theme_default())
+# library(dplyr)
+# library(tidyr)
+# library(tidybayes)
+# 
+# options(mc.cores = parallel::detectCores()) # Set Stan to use all availible cores
+# rstan_options(auto_write = TRUE) # Don't recompile Stan code that hasn't changed
 ```
@@
 ```{r}
-simulate_mrp_data <- function(n) {
-  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
-  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
-  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
-  count <- 0
-  for (i1 in 1:J[1]){
-    for (i2 in 1:J[2]){
-      for (i3 in 1:J[3]){
-        for (i4 in 1:J[4]){
-          for (i5 in 1:J[5]){
-              count <- count + 1
-              # Fill them in so we know what category we are referring to
-              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5) 
-          }
-        }
-      }
-    }
-  }
-  # Proportion in each sample in the population
-  p_male <- c(0.52, 0.48)
-  p_eth <- c(0.5, 0.2, 0.3)
-  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
-  p_income<-c(.50,.35,.15)
-  p_state_tmp<-runif(50,10,20)
-  p_state<-p_state_tmp/sum(p_state_tmp)
-  poststrat$N<-0
-  for (j in 1:prod(J)){
-    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
-      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
-  }
-
-  # Now let's adjust for the probability of response
-  p_response_baseline <- 0.01
-  p_response_male <- c(2, 0.8) / 2.8
-  p_response_eth <- c(1, 1.2, 2.5) / 4.7
-  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
-  p_response_inc <- c(1, 0.9, 0.8) / 2.7
-  p_response_state <- rbeta(50, 1, 1)
-  p_response_state <- p_response_state / sum(p_response_state)
-  p_response <- rep(NA, prod(J))
-  for (j in 1:prod(J)) {
-    p_response[j] <-
-      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
-      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
-      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
-  }
-  people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
-
-  ## For respondent i, people[i] is that person's poststrat cell,
-  ## some number between 1 and 32
-  n_cell <- rep(NA, prod(J))
-  for (j in 1:prod(J)) {
-    n_cell[j] <- sum(people == j)
-  }
-
-  coef_male <- c(0,-0.3)
-  coef_eth <- c(0, 0.6, 0.9)
-  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
-  coef_income <- c(0,-0.2, 0.6)
-  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
-  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
-                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
-  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
-  for (j in 1:prod(J)) {
-    true_popn$cat_pref[j] <- plogis(
-      coef_male[poststrat[j, 1] + 1] +
-        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
-        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
-        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
-      )
-  }
-
-  #male or not, eth, age, income level, state, city
-  y <- rbinom(n, 1, true_popn$cat_pref[people])
-  male <- poststrat[people, 1]
-  eth <- poststrat[people, 2]
-  age <- poststrat[people, 3]
-  income <- poststrat[people, 4]
-  state <- poststrat[people, 5]
-
-  sample <- data.frame(service_failure = y, 
-                       male, age, eth, income, state, 
-                       id = 1:length(people))
-
-  #Make all numeric:
-  for (i in 1:ncol(poststrat)) {
-    poststrat[, i] <- as.numeric(poststrat[, i])
-  }
-  for (i in 1:ncol(true_popn)) {
-    true_popn[, i] <- as.numeric(true_popn[, i])
-  }
-  for (i in 1:ncol(sample)) {
-    sample[, i] <- as.numeric(sample[, i])
-  }
-  list(
-    sample = sample,
-    poststrat = poststrat,
-    true_popn = true_popn
-  )
-}
+# simulate_mrp_data <- function(n) {
+#   J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
+#   poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
+#   colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
+#   count <- 0
+#   for (i1 in 1:J[1]){
+#     for (i2 in 1:J[2]){
+#       for (i3 in 1:J[3]){
+#         for (i4 in 1:J[4]){
+#           for (i5 in 1:J[5]){
+#               count <- count + 1
+#               # Fill them in so we know what category we are referring to
+#               poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5) 
+#           }
+#         }
+#       }
+#     }
+#   }
+#   # Proportion in each sample in the population
+#   p_male <- c(0.52, 0.48)
+#   p_eth <- c(0.5, 0.2, 0.3)
+#   p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
+#   p_income<-c(.50,.35,.15)
+#   p_state_tmp<-runif(50,10,20)
+#   p_state<-p_state_tmp/sum(p_state_tmp)
+#   poststrat$N<-0
+#   for (j in 1:prod(J)){
+#     poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
+#       p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
+#   }
+#   
+#   # Now let's adjust for the probability of response
+#   p_response_baseline <- 0.01
+#   p_response_male <- c(2, 0.8) / 2.8
+#   p_response_eth <- c(1, 1.2, 2.5) / 4.7
+#   p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
+#   p_response_inc <- c(1, 0.9, 0.8) / 2.7
+#   p_response_state <- rbeta(50, 1, 1)
+#   p_response_state <- p_response_state / sum(p_response_state)
+#   p_response <- rep(NA, prod(J))
+#   for (j in 1:prod(J)) {
+#     p_response[j] <-
+#       p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
+#       p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
+#       p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
+#   }
+#   people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
+#   
+#   ## For respondent i, people[i] is that person's poststrat cell,
+#   ## some number between 1 and 32
+#   n_cell <- rep(NA, prod(J))
+#   for (j in 1:prod(J)) {
+#     n_cell[j] <- sum(people == j)
+#   }
+#   
+#   coef_male <- c(0,-0.3)
+#   coef_eth <- c(0, 0.6, 0.9)
+#   coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
+#   coef_income <- c(0,-0.2, 0.6)
+#   coef_state <- c(0, round(rnorm(49, 0, 1), 1))
+#   coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
+#                            c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
+#   true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
+#   for (j in 1:prod(J)) {
+#     true_popn$cat_pref[j] <- plogis(
+#       coef_male[poststrat[j, 1] + 1] +
+#         coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
+#         coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
+#         coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
+#       )
+#   }
+#   
+#   #male or not, eth, age, income level, state, city
+#   y <- rbinom(n, 1, true_popn$cat_pref[people])
+#   male <- poststrat[people, 1]
+#   eth <- poststrat[people, 2]
+#   age <- poststrat[people, 3]
+#   income <- poststrat[people, 4]
+#   state <- poststrat[people, 5]
+#   
+#   sample <- data.frame(service_failure = y, 
+#                        male, age, eth, income, state, 
+#                        id = 1:length(people))
+#   
+#   #Make all numeric:
+#   for (i in 1:ncol(poststrat)) {
+#     poststrat[, i] <- as.numeric(poststrat[, i])
+#   }
+#   for (i in 1:ncol(true_popn)) {
+#     true_popn[, i] <- as.numeric(true_popn[, i])
+#   }
+#   for (i in 1:ncol(sample)) {
+#     sample[, i] <- as.numeric(sample[, i])
+#   }
+#   list(
+#     sample = sample,
+#     poststrat = poststrat,
+#     true_popn = true_popn
+#   )
+# }
 ```
-
-### Begine Bayseian Work Flow (Modeling) 
-We are woking towards building a model that can predict the severity of a service failure baised on consumer feedback.
-The case study will work to build a simple model and impliment postratification to generalize findings in a sample to a larger population.
-The model we will focus on here will start as a simple binomial model but we will hopefully build it up.
-We will be using code taken from Lauren Kenndey and Jonah Gabry's vignette on postratification see: http://mc-stan.org/rstanarm/articles/mrp.html
-
-We will be lookig at the following pices of data about each "customer"
-
-* gender
-* age (group)
-* income (group)
-* state
-
-All of the variables are categorical variables.
-
-WE NEED A MODEL
-
-I HATE RSTANARM -- JUST SAYING
 
@@
 
-```{r eval = FALSE2}
-poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
-model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
-round(model_popn_pref, 3)
+```{r eval = FALSE}
+# poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
+# model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
+# round(model_popn_pref, 3)
 ```
@@
 ```{r eval = FALSE}
-sample_popn_pref <- mean(sample$cat_pref)
-round(sample_popn_pref, 3)
-
-compare2 <- compare2 +
-  geom_hline(yintercept = model_popn_pref[1], colour = '#2ca25f', size = 1) +
-  geom_text(aes(x = 5.2, y = model_popn_pref[1] + .025), label = "MRP", colour = '#2ca25f')
-bayesplot_grid(compare, compare2, 
-               grid_args = list(nrow = 1, widths = c(8, 1)))
+# sample_popn_pref <- mean(sample$cat_pref)
+# round(sample_popn_pref, 3)
+# 
+# compare2 <- compare2 +
+#   geom_hline(yintercept = model_popn_pref[1], colour = '#2ca25f', size = 1) +
+#   geom_text(aes(x = 5.2, y = model_popn_pref[1] + .025), label = "MRP", colour = '#2ca25f')
+# bayesplot_grid(compare, compare2, 
+#                grid_args = list(nrow = 1, widths = c(8, 1)))
 ```

### 2020-01-31 Code/mrp/Case Study .Rmd
Adding hierarchal stan model and mark down file

--- 2020-01-24 Code/mrp/Case Study .Rmd
@@
   for (j in 1:prod(J)) {
-    true_popn$cat_pref[j] <- plogis(
+    true_popn$satisfaction[j] <- plogis(
       coef_male[poststrat[j, 1] + 1] +
@@
   #male or not, eth, age, income level, state, city
-  y <- rbinom(n, 1, true_popn$cat_pref[people])
+  y <- rbinom(n, 1, true_popn$satisfaction[people])
   male <- poststrat[people, 1]
@@
 
-### Begine Bayseian Work Flow (Modeling) 
-We are woking towards building a model that can predict the severity of a service failure baised on consumer feedback.
-The case study will work to build a simple model and impliment postratification to generalize findings in a sample to a larger population.
-The model we will focus on here will start as a simple binomial model but we will hopefully build it up.
-We will be using code taken from Lauren Kenndey and Jonah Gabry's vignette on postratification see: http://mc-stan.org/rstanarm/articles/mrp.html
+```{r echo=FALSE}
 
-We will be lookig at the following pices of data about each "customer"
+J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
+  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
+  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
+  count <- 0
+  for (i1 in 1:J[1]){
+    for (i2 in 1:J[2]){
+      for (i3 in 1:J[3]){
+        for (i4 in 1:J[4]){
+          for (i5 in 1:J[5]){
+              count <- count + 1
+              # Fill them in so we know what category we are referring to
+              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
+          }
+        }
+      }
+    }
+  }
+  # Proportion in each sample in the population
+  p_male <- c(0.52, 0.48)
+  p_eth <- c(0.5, 0.2, 0.3)
+  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
+  p_income<-c(.50,.35,.15)
+  p_state_tmp<-runif(50,10,20)
+  p_state<-p_state_tmp/sum(p_state_tmp)
+  poststrat$N<-0
+  for (j in 1:prod(J)){
+    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
+      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
+  }
 
-* gender
-* age (group)
-* income (group)
-* state
+  # Now let's adjust for the probability of response
+  p_response_baseline <- 0.01
+  p_response_male <- c(2, 0.8) / 2.8
+  p_response_eth <- c(1, 1.2, 2.5) / 4.7
+  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
+  p_response_inc <- c(1, 0.9, 0.8) / 2.7
+  p_response_state <- rbeta(50, 1, 1)
+  p_response_state <- p_response_state / sum(p_response_state)
+  p_response <- rep(NA, prod(J))
+  for (j in 1:prod(J)) {
+    p_response[j] <-
+      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
+      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
+      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
+  }
 
-All of the variables are categorical variables.
+```
 
-WE NEED A MODEL
+Now that we have our simulated data, we now need our hierarchal stan model.
 
-I HATE RSTANARM -- JUST SAYING
+```{}
+
+// Index values, observations, and covariates.
+data {
+  int<lower = 1> N;                      // Number of observations.
+  int<lower = 1> K;                      // Number of groups.
+  int<lower = 1> I;                      // Number of observation-level covariates.
+
+  real satisfaction[N];                        // Vector of observations.
+  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
+  int eth[N];                               // Vector of ethnicity covariates.
+  int age[N];                               // Vector of age covariates.
+  int income[N];                          // Vector of income covariates.
+  int state[N];                          // Vector of state covariates.
+
+  real gamma_mean;                       // Mean for the hyperprior on gamma.
+  real<lower = 0> gamma_var;             // Variance for the hyperprior on gamma.
+  real<lower = 0> tau_min;               // Minimum for the hyperprior on tau.
+  real<lower = 0> tau_max;               // Maximum for the hyperprior on tau.
+  real<lower = 0> sigma_min;             // Minimum for the hyperprior on tau.
+  real<lower = 0> sigma_max;             // Maximum for the hyperprior on tau.
+}
+
+// Parameters and hyperparameters.
+parameters {
+  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
+  vector[K] beta;                        // Vector of observation-level price coefficients.
+  real gamma;                            // Mean of the population model.
+  real<lower=0> tau;                     // Variance of the population model.
+  real<lower=0> sigma;                   // Variance of the observation model.
+}
+
+// Hierarchical regression.
+model {
+  // Declare mu for use in the linear model.
+  vector[N] mu;
+
+  // Hyperpriors and prior.
+  gamma ~ normal(gamma_mean, gamma_var);
+  tau ~ uniform(tau_min, tau_max);
+  sigma ~ uniform(sigma_min, sigma_max);
+
+  // Population model and likelihood.
+  for (k in 1:K) {
+    alpha[k,] ~ normal(gamma, tau);
+    beta[k] ~ normal(gamma, tau);
+  }
+  for (n in 1:N) {
+    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
+    income[n] + beta[male[n]] * state[n];
+  }
+  cat_pref ~ normal(mu, sigma);
+}
+
+// Generate predictions using the posterior.
+generated quantities {
+  vector[N] mu_pc;                       // Declare mu for predicted linear model.
+  real cat_pref_pc[N];                     // Vector of predicted observations.
+
+  // Generate posterior prediction distribution.
+  for (n in 1:N) {
+    mu_pc[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
+    income[n] + beta[male[n]] * state[n];
+    cat_pref_pc[n] = normal_rng(mu_pc[n], sigma);
+  }
+}
+
+```
+
+As we will also need to do some prior and posterior checks, and for that we will need the generative model.
+
+```{}
+
+// Index values, observations, covariates, and hyperior values.
+data {
+  int<lower = 1> N;                      // Number of observations.
+  int<lower = 1> K;                      // Number of groups.
+  int<lower = 1> I;                      // Number of observation-level covariates.
+
+  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
+  int eth[N];                               // Vector of ethnicity covariates.
+  int age[N];                               // Vector of age covariates.
+  int income[N];                          // Vector of income covariates.
+  int state[N];                          // Vector of state covariates.
+
+  real gamma_mean;                       // Mean for the hyperprior on gamma.
+  real<lower = 0> gamma_var;             // Variance for the hyperprior on gamma.
+  real<lower = 0> tau_min;               // Minimum for the hyperprior on tau.
+  real<lower = 0> tau_max;               // Maximum for the hyperprior on tau.
+  real<lower = 0> sigma_min;             // Minimum for the hyperprior on tau.
+  real<lower = 0> sigma_max;             // Maximum for the hyperprior on tau.
+}
+
+// Generate data according to the hierarchical regression.
+generated quantities {
+  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
+  vector[K] beta;                        // Vector of observation-level price coefficients.
+  real gamma;                            // Mean of the population model.
+  real<lower=0> tau;                     // Variance of the population model.
+  real<lower=0> sigma;                   // Variance of the observation model.
+
+  vector[N] mu;                          // Declare mu for linear model.
+  real cat_pref[N];                        // Vector of observations.
+
+  gamma = normal_rng(gamma_mean, gamma_var);
+  tau = uniform_rng(tau_min, tau_max);
+  sigma = uniform_rng(sigma_min, sigma_max);
+
+  // Draw parameter values and generate data.
+  for (k in 1:K) {
+    for (i in 1:(I - 1)) {
+      alpha[k, i] = normal_rng(gamma, tau);
+    }
+    beta[k] = normal_rng(gamma, tau);
+  }
+  for (n in 1:N) {
+    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
+    income[n] + beta[male[n]] * state[n];
+    cat_pref[n] = normal_rng(mu[n], sigma);
+  }
+}
+
+```
 
@@
 
-```{r eval = FALSE2}
+```{r eval = FALSE}
 poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
@@
 ```{r eval = FALSE}
-sample_popn_pref <- mean(sample$cat_pref)
+sample_popn_pref <- mean(sample$satisfaction)
 round(sample_popn_pref, 3)

### 2020-01-31 Code/mrp/Case Study .Rmd
Stan code added but not running. Working on fixes.

@@
 
+  coef_male <- c(0,-0.3)
+  coef_eth <- c(0, 0.6, 0.9)
+  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
+  coef_income <- c(0,-0.2, 0.6)
+  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
+  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
+                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
+  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
+  for (j in 1:prod(J)) {
+    true_popn$satisfaction[j] <- plogis(
+      coef_male[poststrat[j, 1] + 1] +
+        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
+        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
+        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
+      )
+  }
 ```
@@
 
+```{r}
+sim_values <- list(
+  N = 6300,                                       # Number of observations.
+  K = 2,                                         # Number of groups.
+  I = 65,                                         # Number of observation-level covariates.
+
+  male = sample(2, 6300, replace = TRUE),            # Vector of group assignments.
+  eth = sample(3, 6300, replace = TRUE),       # Vector of brands covariates.
+  age = sample(7, 6300, replace = TRUE),        # Vector of price covariates.
+  income = sample(3, 6300, replace = TRUE),
+  state = sample(50, 6300, replace = TRUE),
+
+  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
+  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
+  tau_min = 0,                                   # Minimum for the hyperprior on tau.
+  tau_max = .1,                                   # Maximum for the hyperprior on tau.
+  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
+  sigma_max = .1                                  # Maximum for the hyperprior on tau.
+)
+# Generate data.
+sim_data <- stan(
+  file = here::here("Code/mrp/generate_data.stan"),
+  data = sim_values,
+  iter = 10,
+  chains = 1,
+  seed = 42,
+  algorithm = "Fixed_param"
+)
+```
+
+```{r}
+# Extract the simulated data.
+prior_pc <- tibble(
+  cat_pref = as.vector(extract(sim_data)$cat_pref)
+)
+# Plot the prior predictive distribution.
+prior_pc %>% 
+  ggplot(aes(x = cat_pref)) +
+  geom_density()
+```
+
+```{r}
+# # Specify data.
+# data <- list(
+#   N = nrow(true_popn),                     # Number of observations.
+#   K = 2,                    # Number of groups.
+#   I = 65,                                # Number of observation-level covariates.
+#   
+#   cat_pref = true_popn$cat_pref,               # Vector of observations.
+#   male = as.numeric(as.factor(true_popn$male)),            # Vector of group assignments.
+#   eth = true_popn$eth,       # Vector of brands covariates.
+#   age = true_popn$age,        # Vector of price covariates.
+#   income = true_popn$income,
+#   state = true_popn$state,
+#   
+#   gamma_mean = 0.5,                                # Mean for the hyperprior on gamma.
+#   gamma_var = .2,                                 # Variance for the hyperprior on gamma.
+#   tau_min = 0,                                   # Minimum for the hyperprior on tau.
+#   tau_max = 1,                                   # Maximum for the hyperprior on tau.
+#   sigma_min = 0,                                 # Minimum for the hyperprior on tau.
+#   sigma_max = 1                                 # Maximum for the hyperprior on tau.
+# )
+# # Calibrate the model.
+# model03 <- stan(
+#   file = here::here("Code/mrp/hierarchical_model.stan"),
+#   data = data,
+#   control = list(adapt_delta = 0.99),
+#   seed = 42
+# )
+```
+
+```{r}
+# Posterior predictive check.
+# post_pc03 <- tibble(
+#   # Extract the posterior predicted values.
+#   intent = as.vector(extract(model03)$cat_pref_pc)
+# )
+# # Plot the posterior predictive distribution.
+# ggplot(post_pc03, aes(x = intent)) +
+#   geom_histogram() +
+#   xlim(1, 10) 
+# ggplot(purchase_intent, aes(x = intent)) +
+#   geom_histogram() +
+#   xlim(1, 10) 
+```
+
+```{r}
+# model03 %>%
+#   gather_draws(alpha[n, i]) %>%
+#   unite(.variable, .variable, n, i) %>%
+#   ggplot(aes(x = .value, y = .variable)) +
+#   geom_halfeyeh(.width = .95) +
+#   facet_wrap(
+#     ~ .variable,
+#     nrow = data$K,
+#     ncol = (data$I - 1),
+#     scales = "free"
+#   )
+```
+
+```{r}
+# Plot the betas.
+# model03 %>%
+#   gather_draws(beta[i]) %>%
+#   unite(.variable, .variable, i) %>%
+#   ggplot(aes(x = .value, y = .variable)) +
+#   geom_halfeyeh(.width = .95) +
+#   facet_wrap(
+#     ~ .variable,
+#     nrow = data$K,
+#     ncol = 1,
+#     scales = "free"
+#   )
+```
+
 ### Postratification 

### 2020-02-14 Code/mrp/Case Study .Rmd
starting to look at creating a list as an input to the stan code
Modifications to hierarchal model with new sample data.

@@
 
+```{r}
+mrp_sim <- simulate_mrp_data(n=1200)
+sample <- mrp_sim[["sample"]]
+
+print(sample)
+```
+
 ```{r echo=FALSE}
-
-J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
-  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
-  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
-  count <- 0
-  for (i1 in 1:J[1]){
-    for (i2 in 1:J[2]){
-      for (i3 in 1:J[3]){
-        for (i4 in 1:J[4]){
-          for (i5 in 1:J[5]){
-              count <- count + 1
-              # Fill them in so we know what category we are referring to
-              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
-          }
-        }
-      }
-    }
-  }
-  # Proportion in each sample in the population
-  p_male <- c(0.52, 0.48)
-  p_eth <- c(0.5, 0.2, 0.3)
-  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
-  p_income<-c(.50,.35,.15)
-  p_state_tmp<-runif(50,10,20)
-  p_state<-p_state_tmp/sum(p_state_tmp)
-  poststrat$N<-0
-  for (j in 1:prod(J)){
-    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
-      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
-  }
-
-  # Now let's adjust for the probability of response
-  p_response_baseline <- 0.01
-  p_response_male <- c(2, 0.8) / 2.8
-  p_response_eth <- c(1, 1.2, 2.5) / 4.7
-  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
-  p_response_inc <- c(1, 0.9, 0.8) / 2.7
-  p_response_state <- rbeta(50, 1, 1)
-  p_response_state <- p_response_state / sum(p_response_state)
-  p_response <- rep(NA, prod(J))
-  for (j in 1:prod(J)) {
-    p_response[j] <-
-      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
-      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
-      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
-  }
-
-  coef_male <- c(0,-0.3)
-  coef_eth <- c(0, 0.6, 0.9)
-  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
-  coef_income <- c(0,-0.2, 0.6)
-  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
-  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
-                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
-  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
-  for (j in 1:prod(J)) {
-    true_popn$satisfaction[j] <- plogis(
-      coef_male[poststrat[j, 1] + 1] +
-        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
-        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
-        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
-      )
-  }
+# 
+# J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
+#   poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
+#   colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
+#   count <- 0
+#   for (i1 in 1:J[1]){
+#     for (i2 in 1:J[2]){
+#       for (i3 in 1:J[3]){
+#         for (i4 in 1:J[4]){
+#           for (i5 in 1:J[5]){
+#               count <- count + 1
+#               # Fill them in so we know what category we are referring to
+#               poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
+#           }
+#         }
+#       }
+#     }
+#   }
+#   # Proportion in each sample in the population
+#   p_male <- c(0.52, 0.48)
+#   p_eth <- c(0.5, 0.2, 0.3)
+#   p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
+#   p_income<-c(.50,.35,.15)
+#   p_state_tmp<-runif(50,10,20)
+#   p_state<-p_state_tmp/sum(p_state_tmp)
+#   poststrat$N<-0
+#   for (j in 1:prod(J)){
+#     poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
+#       p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
+#   }
+# 
+#   # Now let's adjust for the probability of response
+#   p_response_baseline <- 0.01
+#   p_response_male <- c(2, 0.8) / 2.8
+#   p_response_eth <- c(1, 1.2, 2.5) / 4.7
+#   p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
+#   p_response_inc <- c(1, 0.9, 0.8) / 2.7
+#   p_response_state <- rbeta(50, 1, 1)
+#   p_response_state <- p_response_state / sum(p_response_state)
+#   p_response <- rep(NA, prod(J))
+#   for (j in 1:prod(J)) {
+#     p_response[j] <-
+#       p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
+#       p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
+#       p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
+#   }
+# 
+#   coef_male <- c(0,-0.3)
+#   coef_eth <- c(0, 0.6, 0.9)
+#   coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
+#   coef_income <- c(0,-0.2, 0.6)
+#   coef_state <- c(0, round(rnorm(49, 0, 1), 1))
+#   coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
+#                            c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
+#   true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
+#   for (j in 1:prod(J)) {
+#     true_popn$satisfaction[j] <- plogis(
+#       coef_male[poststrat[j, 1] + 1] +
+#         coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
+#         coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
+#         coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
+#       )
+#   }
 ```
@@
 
-  real satisfaction[N];                        // Vector of observations.
+  real service_failure[N];                        // Vector of observations.
   int<lower = 1, upper = K> male[N];        // Vector of group assignments.
-  int eth[N];                               // Vector of ethnicity covariates.
-  int age[N];                               // Vector of age covariates.
+  int age[N];                               // Vector of ethnicity covariates.
+  int eth[N];                               // Vector of age covariates.
   int income[N];                          // Vector of income covariates.
@@
 parameters {
-  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
-  vector[K] beta;                        // Vector of observation-level price coefficients.
+  matrix[K, (I - 1)] alpha;              // Matrix of observation-level gender coefficients.
+  vector[K] beta;                        // Vector of all other observation-level coefficients.
   real gamma;                            // Mean of the population model.
@@
   for (n in 1:N) {
-    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
+    mu[n] = alpha[male[n], age[n]] + beta[male[n]] * eth[n] + beta[male[n]] * 
     income[n] + beta[male[n]] * state[n];
   }
-  cat_pref ~ normal(mu, sigma);
+  service_failure ~ normal(mu, sigma);
 }
@@
   vector[N] mu_pc;                       // Declare mu for predicted linear model.
-  real cat_pref_pc[N];                     // Vector of predicted observations.
+  real service_failure_pc[N];                     // Vector of predicted observations.
 
@@
   for (n in 1:N) {
-    mu_pc[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
+    mu_pc[n] = alpha[male[n], age[n]] + beta[male[n]] * eth[n] + beta[male[n]] * 
     income[n] + beta[male[n]] * state[n];
-    cat_pref_pc[n] = normal_rng(mu_pc[n], sigma);
+    service_failure_pc[n] = normal_rng(mu_pc[n], sigma);
   }

### 2020-02-14 Code/mrp/Case Study .Rmd
Now that we have successfully sampled from our postratification code, we need to start building a logistic linear model.

@@
 
-We will be modeling our populations `satisfaction`.
+We will be modeling our populations `service_failure`.
 This will eventually translate into measuring service severity when we apply our model to our real data.
@@
 ```{r}
+
 mrp_sim <- simulate_mrp_data(n=1200)
@@
 
-print(sample)
+head(sample)
+
+```
+
+We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model
+
+# Hierarchal Logit Model
+
+```{}
+
+ data {
+   // Define variables in data
+   // Number of observations (an integer)
+   int<lower=0> N;
+   // Number of parameters
+   int<lower=0> p;
+   // Variables
+   int death[N];
+   int<lower=0>  qsmk[N];
+   int<lower=0>  sex[N];
+   real<lower=0> age[N];
+   int<lower=0>  race[N];
+   real<lower=0> smokeyrs[N];
+ }
+
+ parameters {
+   // Define parameters to estimate
+   real beta[p];
+ }
+
+ transformed parameters  {
+   // Probability trasformation from linear predictor
+   real<lower=0> odds[N];
+   real<lower=0, upper=1> prob[N];
+
+   for (i in 1:N) {
+     odds[i] <- exp(beta[1] + beta[2]*qsmk[i] + beta[3]*sex[i] + beta[4]*age[i] + beta[5]*race[i] + beta[6]*smokeyrs[i]);
+     prob[i] <- odds[i] / (odds[i] + 1);
+   }
+ }
+
+ model {
+   // Prior part of Bayesian inference (flat if unspecified)
+
+  // Likelihood part of Bayesian inference
+    death ~ bernoulli(prob);
+}
+
 ```
@@
 generated quantities {
-  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
-  vector[K] beta;                        // Vector of observation-level price coefficients.
+  matrix[K, (I - 1)] alpha;              // Matrix of observation-level gender coefficients.
+  vector[K] beta;                        // Vector of all other observation-level coefficients.
   real gamma;                            // Mean of the population model.
@@
   vector[N] mu;                          // Declare mu for linear model.
-  real cat_pref[N];                        // Vector of observations.
+  real service_failure[N];                        // Vector of observations.
 
@@
     income[n] + beta[male[n]] * state[n];
-    cat_pref[n] = normal_rng(mu[n], sigma);
+    service_failure[n] = normal_rng(mu[n], sigma);
   }
@@
 ```{r}
+
 sim_values <- list(
@@
 )
+
 ```
@@
 ```{r}
+
 # Extract the simulated data.
 prior_pc <- tibble(
-  cat_pref = as.vector(extract(sim_data)$cat_pref)
+  service_failure = as.vector(extract(sim_data)$service_failure)
 )
@@
 prior_pc %>% 
-  ggplot(aes(x = cat_pref)) +
+  ggplot(aes(x = service_failure)) +
   geom_density()
+
 ```
 
-```{r}
+```{r echo=FALSE}
+
 # # Specify data.
@@
 # )
+
 ```
 
-```{r}
+```{r echo=FALSE}
 # Posterior predictive check.
@@
 
-```{r}
+```{r echo=FALSE}
 # model03 %>%
@@
 
-```{r}
+```{r echo=FALSE}
 # Plot the betas.
@@
 
-```{r eval = FALSE}
+```{ echo=FALSE}
 poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
@@
 
-```{r eval = FALSE}
+```{ echo=FALSE}
 sample_popn_pref <- mean(sample$satisfaction)

### 2020-02-14 Code/mrp/Case Study .Rmd
Updating

--- 2020-01-31 Code/mrp/Case Study .Rmd
@@
 title: "MRP Case Study"
-author: "McKenna Weech"
+author: "McKenna Weech, Adam Hettinger, and Hannah Thompson"
 date: "1/17/2020"
@@
 }
+```
+
+```{r}
+mrp_sim <- simulate_mrp_data(n=1200)
+sample <- mrp_sim[["sample"]]
+
+print(sample)
 ```

### 2020-02-14 Code/mrp/mrp-vignette.Rmd
Updating

@@
               poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5) 
+          }
+        }
+      }
+    }
+  }
+  # Proportion in each sample in the population
+  p_male <- c(0.52, 0.48)
+  p_eth <- c(0.5, 0.2, 0.3)
+  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
+  p_income<-c(.50,.35,.15)
+  p_state_tmp<-runif(50,10,20)
+  p_state<-p_state_tmp/sum(p_state_tmp)
+  poststrat$N<-0
+  for (j in 1:prod(J)){
+    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
+      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
+  }
+
+  # Now let's adjust for the probability of response
+  p_response_baseline <- 0.01
+  p_response_male <- c(2, 0.8) / 2.8
+  p_response_eth <- c(1, 1.2, 2.5) / 4.7
+  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
+  p_response_inc <- c(1, 0.9, 0.8) / 2.7
+  p_response_state <- rbeta(50, 1, 1)
+  p_response_state <- p_response_state / sum(p_response_state)
+  p_response <- rep(NA, prod(J))
+  for (j in 1:prod(J)) {
+    p_response[j] <-
+      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
+      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
+      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
+  }
+  people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
+
+  ## For respondent i, people[i] is that person's poststrat cell,
+  ## some number between 1 and 32
+  n_cell <- rep(NA, prod(J))
+  for (j in 1:prod(J)) {
+    n_cell[j] <- sum(people == j)
+  }
+
+  coef_male <- c(0,-0.3)
+  coef_eth <- c(0, 0.6, 0.9)
+  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
+  coef_income <- c(0,-0.2, 0.6)
+  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
+  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
+                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
+  true_popn <- data.frame(poststrat[, 1:5], cat_pref = rep(NA, prod(J)))
+  for (j in 1:prod(J)) {
+    true_popn$cat_pref[j] <- plogis(
+      coef_male[poststrat[j, 1] + 1] +
+        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
+        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
+        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
+      )
+  }
+
+  #male or not, eth, age, income level, state, city
+  y <- rbinom(n, 1, true_popn$cat_pref[people])
+  male <- poststrat[people, 1]
+  eth <- poststrat[people, 2]
+  age <- poststrat[people, 3]
+  income <- poststrat[people, 4]
+  state <- poststrat[people, 5]
+
+  sample <- data.frame(cat_pref = y, 
+                       male, age, eth, income, state, 
+                       id = 1:length(people))
+
+  #Make all numeric:
+  for (i in 1:ncol(poststrat)) {
+    poststrat[, i] <- as.numeric(poststrat[, i])
+  }
+  for (i in 1:ncol(true_popn)) {
+    true_popn[, i] <- as.numeric(true_popn[, i])
+  }
+  for (i in 1:ncol(sample)) {
+    sample[, i] <- as.numeric(sample[, i])
+  }
+  list(
+    sample = sample,
+    poststrat = poststrat,
+    true_popn = true_popn
+  )
+}
+```
+```{r}
+simulate_mrp_data <- function(n) {
+  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
+  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
+  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
+  count <- 0
+  for (i1 in 1:J[1]){
+    for (i2 in 1:J[2]){
+      for (i3 in 1:J[3]){
+        for (i4 in 1:J[4]){
+          for (i5 in 1:J[5]){
+              count <- count + 1
+              # Fill them in so we know what category we are referring to
+              poststrat[count, 1:5] <- c(i1-1, i2, i3,i4,i5) 
           }

### 2020-03-10 Code/mrp/Case Study .Rmd
Updating stan code.

--- 2020-02-14 Code/mrp/Case Study .Rmd
@@
 mrp_sim <- simulate_mrp_data(n=1200)
+
 sample <- mrp_sim[["sample"]]
+poststrat <- mrp_sim[["poststrat"]]
+true_popn <- mrp_sim[["true_popn"]]
 
 head(sample)
+
+```
+```{r}
+stan_data <- list( 
+  N = nrow(sample), 
+  service_failure = sample$service_failure,
+  male = sample$male, 
+  age = sample$age,
+  eth = sample$eth, 
+  income = sample$income, 
+  state = sample$state)
+```
+
+```{r}
+fit <- stan(
+  file = here::here("Code", "mrp", "logit_simple.stan"),
+  data = stan_data,
+  seed = 42
+)
+
+```
+```{r}
+fit %>%
+  mcmc_trace(
+    pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'),
+    n_warmup = 500,
+    facet_args = list(nrow = 2, labeller = label_parsed)
+  )
+
+print(fit, pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'))
+```
+```{r}
 
@@
 sim_data <- stan(
-  file = here::here("Code/mrp/generate_data.stan"),
+  file = here::here("Code", "mrp", "generate_data.stan"),
   data = sim_values,
@@
 
+Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working.
+
+```{r}
+stan_values <- list(
+  N = 1200,                                       # Number of observations.
+  K = 2,                                         # Number of groups.
+  I = 65,                                         # Number of observation-level covariates.
+
+  male = sample$male,                 
+  eth = sample$eth,      
+  age = sample$age,        
+  income = sample$income,
+  state = sample$state,
+  service_failure = sample$service_failure
+)
+
+```
+
+```{r}
+fit3 <- stan(
+  file = here::here("Code", "mrp", "logit_simple.stan"),
+  data = stan_values,
+  seed = 42
+)
+```
+
 ### Postratification 

### 2020-03-10 Code/mrp/Case Study (McKenna) .Rmd
Splitting up the case study
Cleaning up the code.

--- 2020-03-10 Code/mrp/Case Study .Rmd
@@
 ---
-title: "MRP Case Study"
-author: "McKenna Weech, Adam Hettinger, and Hannah Thompson"
-date: "1/17/2020"
-output: github_document
+title: "Case Study (McKenna)"
+author: "McKenna Weech"
+date: "3/10/2020"
+output: html_document
 ---
@@
 
-# Hierarchal Logit Model
-
-```{}
-
- data {
-   // Define variables in data
-   // Number of observations (an integer)
-   int<lower=0> N;
-   // Number of parameters
-   int<lower=0> p;
-   // Variables
-   int death[N];
-   int<lower=0>  qsmk[N];
-   int<lower=0>  sex[N];
-   real<lower=0> age[N];
-   int<lower=0>  race[N];
-   real<lower=0> smokeyrs[N];
- }
-
- parameters {
-   // Define parameters to estimate
-   real beta[p];
- }
-
- transformed parameters  {
-   // Probability trasformation from linear predictor
-   real<lower=0> odds[N];
-   real<lower=0, upper=1> prob[N];
-
-   for (i in 1:N) {
-     odds[i] <- exp(beta[1] + beta[2]*qsmk[i] + beta[3]*sex[i] + beta[4]*age[i] + beta[5]*race[i] + beta[6]*smokeyrs[i]);
-     prob[i] <- odds[i] / (odds[i] + 1);
-   }
- }
-
- model {
-   // Prior part of Bayesian inference (flat if unspecified)
-
-  // Likelihood part of Bayesian inference
-    death ~ bernoulli(prob);
-}
-
-```
-
-```{r echo=FALSE}
-# 
-# J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
-#   poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
-#   colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
-#   count <- 0
-#   for (i1 in 1:J[1]){
-#     for (i2 in 1:J[2]){
-#       for (i3 in 1:J[3]){
-#         for (i4 in 1:J[4]){
-#           for (i5 in 1:J[5]){
-#               count <- count + 1
-#               # Fill them in so we know what category we are referring to
-#               poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
-#           }
-#         }
-#       }
-#     }
-#   }
-#   # Proportion in each sample in the population
-#   p_male <- c(0.52, 0.48)
-#   p_eth <- c(0.5, 0.2, 0.3)
-#   p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
-#   p_income<-c(.50,.35,.15)
-#   p_state_tmp<-runif(50,10,20)
-#   p_state<-p_state_tmp/sum(p_state_tmp)
-#   poststrat$N<-0
-#   for (j in 1:prod(J)){
-#     poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
-#       p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
-#   }
-# 
-#   # Now let's adjust for the probability of response
-#   p_response_baseline <- 0.01
-#   p_response_male <- c(2, 0.8) / 2.8
-#   p_response_eth <- c(1, 1.2, 2.5) / 4.7
-#   p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
-#   p_response_inc <- c(1, 0.9, 0.8) / 2.7
-#   p_response_state <- rbeta(50, 1, 1)
-#   p_response_state <- p_response_state / sum(p_response_state)
-#   p_response <- rep(NA, prod(J))
-#   for (j in 1:prod(J)) {
-#     p_response[j] <-
-#       p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
-#       p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
-#       p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
-#   }
-# 
-#   coef_male <- c(0,-0.3)
-#   coef_eth <- c(0, 0.6, 0.9)
-#   coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
-#   coef_income <- c(0,-0.2, 0.6)
-#   coef_state <- c(0, round(rnorm(49, 0, 1), 1))
-#   coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
-#                            c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
-#   true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
-#   for (j in 1:prod(J)) {
-#     true_popn$satisfaction[j] <- plogis(
-#       coef_male[poststrat[j, 1] + 1] +
-#         coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
-#         coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
-#         coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
-#       )
-#   }
-```
-
-Now that we have our simulated data, we now need our hierarchal stan model.
-
-```{}
-
-// Index values, observations, and covariates.
-data {
-  int<lower = 1> N;                      // Number of observations.
-  int<lower = 1> K;                      // Number of groups.
-  int<lower = 1> I;                      // Number of observation-level covariates.
-
-  real service_failure[N];                        // Vector of observations.
-  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
-  int age[N];                               // Vector of ethnicity covariates.
-  int eth[N];                               // Vector of age covariates.
-  int income[N];                          // Vector of income covariates.
-  int state[N];                          // Vector of state covariates.
-
-  real gamma_mean;                       // Mean for the hyperprior on gamma.
-  real<lower = 0> gamma_var;             // Variance for the hyperprior on gamma.
-  real<lower = 0> tau_min;               // Minimum for the hyperprior on tau.
-  real<lower = 0> tau_max;               // Maximum for the hyperprior on tau.
-  real<lower = 0> sigma_min;             // Minimum for the hyperprior on tau.
-  real<lower = 0> sigma_max;             // Maximum for the hyperprior on tau.
-}
-
-// Parameters and hyperparameters.
-parameters {
-  matrix[K, (I - 1)] alpha;              // Matrix of observation-level gender coefficients.
-  vector[K] beta;                        // Vector of all other observation-level coefficients.
-  real gamma;                            // Mean of the population model.
-  real<lower=0> tau;                     // Variance of the population model.
-  real<lower=0> sigma;                   // Variance of the observation model.
-}
-
-// Hierarchical regression.
-model {
-  // Declare mu for use in the linear model.
-  vector[N] mu;
-
-  // Hyperpriors and prior.
-  gamma ~ normal(gamma_mean, gamma_var);
-  tau ~ uniform(tau_min, tau_max);
-  sigma ~ uniform(sigma_min, sigma_max);
-
-  // Population model and likelihood.
-  for (k in 1:K) {
-    alpha[k,] ~ normal(gamma, tau);
-    beta[k] ~ normal(gamma, tau);
-  }
-  for (n in 1:N) {
-    mu[n] = alpha[male[n], age[n]] + beta[male[n]] * eth[n] + beta[male[n]] * 
-    income[n] + beta[male[n]] * state[n];
-  }
-  service_failure ~ normal(mu, sigma);
-}
-
-// Generate predictions using the posterior.
-generated quantities {
-  vector[N] mu_pc;                       // Declare mu for predicted linear model.
-  real service_failure_pc[N];                     // Vector of predicted observations.
-
-  // Generate posterior prediction distribution.
-  for (n in 1:N) {
-    mu_pc[n] = alpha[male[n], age[n]] + beta[male[n]] * eth[n] + beta[male[n]] * 
-    income[n] + beta[male[n]] * state[n];
-    service_failure_pc[n] = normal_rng(mu_pc[n], sigma);
-  }
-}
-
-```
-
-As we will also need to do some prior and posterior checks, and for that we will need the generative model.
-
-```{}
-
-// Index values, observations, covariates, and hyperior values.
-data {
-  int<lower = 1> N;                      // Number of observations.
-  int<lower = 1> K;                      // Number of groups.
-  int<lower = 1> I;                      // Number of observation-level covariates.
-
-  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
-  int eth[N];                               // Vector of ethnicity covariates.
-  int age[N];                               // Vector of age covariates.
-  int income[N];                          // Vector of income covariates.
-  int state[N];                          // Vector of state covariates.
-
-  real gamma_mean;                       // Mean for the hyperprior on gamma.
-  real<lower = 0> gamma_var;             // Variance for the hyperprior on gamma.
-  real<lower = 0> tau_min;               // Minimum for the hyperprior on tau.
-  real<lower = 0> tau_max;               // Maximum for the hyperprior on tau.
-  real<lower = 0> sigma_min;             // Minimum for the hyperprior on tau.
-  real<lower = 0> sigma_max;             // Maximum for the hyperprior on tau.
-}
-
-// Generate data according to the hierarchical regression.
-generated quantities {
-  matrix[K, (I - 1)] alpha;              // Matrix of observation-level gender coefficients.
-  vector[K] beta;                        // Vector of all other observation-level coefficients.
-  real gamma;                            // Mean of the population model.
-  real<lower=0> tau;                     // Variance of the population model.
-  real<lower=0> sigma;                   // Variance of the observation model.
-
-  vector[N] mu;                          // Declare mu for linear model.
-  real service_failure[N];                        // Vector of observations.
-
-  gamma = normal_rng(gamma_mean, gamma_var);
-  tau = uniform_rng(tau_min, tau_max);
-  sigma = uniform_rng(sigma_min, sigma_max);
-
-  // Draw parameter values and generate data.
-  for (k in 1:K) {
-    for (i in 1:(I - 1)) {
-      alpha[k, i] = normal_rng(gamma, tau);
-    }
-    beta[k] = normal_rng(gamma, tau);
-  }
-  for (n in 1:N) {
-    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
-    income[n] + beta[male[n]] * state[n];
-    service_failure[n] = normal_rng(mu[n], sigma);
-  }
-}
-
-```
-
 ```{r}
@@
 
-```
-
-```{r echo=FALSE}
-
-# # Specify data.
-# data <- list(
-#   N = nrow(true_popn),                     # Number of observations.
-#   K = 2,                    # Number of groups.
-#   I = 65,                                # Number of observation-level covariates.
-#   
-#   cat_pref = true_popn$cat_pref,               # Vector of observations.
-#   male = as.numeric(as.factor(true_popn$male)),            # Vector of group assignments.
-#   eth = true_popn$eth,       # Vector of brands covariates.
-#   age = true_popn$age,        # Vector of price covariates.
-#   income = true_popn$income,
-#   state = true_popn$state,
-#   
-#   gamma_mean = 0.5,                                # Mean for the hyperprior on gamma.
-#   gamma_var = .2,                                 # Variance for the hyperprior on gamma.
-#   tau_min = 0,                                   # Minimum for the hyperprior on tau.
-#   tau_max = 1,                                   # Maximum for the hyperprior on tau.
-#   sigma_min = 0,                                 # Minimum for the hyperprior on tau.
-#   sigma_max = 1                                 # Maximum for the hyperprior on tau.
-# )
-# # Calibrate the model.
-# model03 <- stan(
-#   file = here::here("Code/mrp/hierarchical_model.stan"),
-#   data = data,
-#   control = list(adapt_delta = 0.99),
-#   seed = 42
-# )
-
-```
-
-```{r echo=FALSE}
-# Posterior predictive check.
-# post_pc03 <- tibble(
-#   # Extract the posterior predicted values.
-#   intent = as.vector(extract(model03)$cat_pref_pc)
-# )
-# # Plot the posterior predictive distribution.
-# ggplot(post_pc03, aes(x = intent)) +
-#   geom_histogram() +
-#   xlim(1, 10) 
-# ggplot(purchase_intent, aes(x = intent)) +
-#   geom_histogram() +
-#   xlim(1, 10) 
-```
-
-```{r echo=FALSE}
-# model03 %>%
-#   gather_draws(alpha[n, i]) %>%
-#   unite(.variable, .variable, n, i) %>%
-#   ggplot(aes(x = .value, y = .variable)) +
-#   geom_halfeyeh(.width = .95) +
-#   facet_wrap(
-#     ~ .variable,
-#     nrow = data$K,
-#     ncol = (data$I - 1),
-#     scales = "free"
-#   )
-```
-
-```{r echo=FALSE}
-# Plot the betas.
-# model03 %>%
-#   gather_draws(beta[i]) %>%
-#   unite(.variable, .variable, i) %>%
-#   ggplot(aes(x = .value, y = .variable)) +
-#   geom_halfeyeh(.width = .95) +
-#   facet_wrap(
-#     ~ .variable,
-#     nrow = data$K,
-#     ncol = 1,
-#     scales = "free"
-#   )
 ```

### 2020-03-20 Code/mrp/Case Study .Rmd
This is a working hierarchal multinomial logit model. I am working on making it more interpretable. This comes from the ART forum 2017.

--- 2020-02-14 Code/mrp/Case Study .Rmd
@@
 ```{r message = FALSE}
+
 library(tidyverse) #Load packages
@@
 library(tidybayes)
-
 options(mc.cores = parallel::detectCores()) # Set Stan to use all availible cores
@@
   }
-
   # Now let's adjust for the probability of response
@@
   people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
-
   ## For respondent i, people[i] is that person's poststrat cell,
@@
   }
-
   coef_male <- c(0,-0.3)
@@
   }
-
   #male or not, eth, age, income level, state, city
@@
   state <- poststrat[people, 5]
-
   sample <- data.frame(service_failure = y,
@@
                        id = 1:length(people))
-
   #Make all numeric:
@@
 sample <- mrp_sim[["sample"]]
-
-print(sample)
+poststrat <- mrp_sim[["poststrat"]]
+true_popn <- mrp_sim[["true_popn"]]
+head(sample)
 ```
 
-```{r echo=FALSE}
-
-J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
-  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
-  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
-  count <- 0
-  for (i1 in 1:J[1]){
-    for (i2 in 1:J[2]){
-      for (i3 in 1:J[3]){
-        for (i4 in 1:J[4]){
-          for (i5 in 1:J[5]){
-              count <- count + 1
-              # Fill them in so we know what category we are referring to
-              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
-          }
-        }
-      }
-    }
-  }
-  # Proportion in each sample in the population
-  p_male <- c(0.52, 0.48)
-  p_eth <- c(0.5, 0.2, 0.3)
-  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
-  p_income<-c(.50,.35,.15)
-  p_state_tmp<-runif(50,10,20)
-  p_state<-p_state_tmp/sum(p_state_tmp)
-  poststrat$N<-0
-  for (j in 1:prod(J)){
-    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
-      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
-  }
-
-  # Now let's adjust for the probability of response
-  p_response_baseline <- 0.01
-  p_response_male <- c(2, 0.8) / 2.8
-  p_response_eth <- c(1, 1.2, 2.5) / 4.7
-  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
-  p_response_inc <- c(1, 0.9, 0.8) / 2.7
-  p_response_state <- rbeta(50, 1, 1)
-  p_response_state <- p_response_state / sum(p_response_state)
-  p_response <- rep(NA, prod(J))
-  for (j in 1:prod(J)) {
-    p_response[j] <-
-      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
-      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
-      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
-  }
-
-  coef_male <- c(0,-0.3)
-  coef_eth <- c(0, 0.6, 0.9)
-  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
-  coef_income <- c(0,-0.2, 0.6)
-  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
-  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
-                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
-  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
-  for (j in 1:prod(J)) {
-    true_popn$satisfaction[j] <- plogis(
-      coef_male[poststrat[j, 1] + 1] +
-        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
-        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
-        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
-      )
-  }
+```{r}
+stan_data <- list( 
+  N = nrow(sample), 
+  service_failure = sample$service_failure,
+  male = sample$male, 
+  age = sample$age,
+  eth = sample$eth, 
+  income = sample$income, 
+  state = sample$state)
 ```
 
-Now that we have our simulated data, we now need our hierarchal stan model.
+We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model
+
+# Hierarchal Logit Model
 
@@
 
-// Index values, observations, and covariates.
 data {
-  int<lower = 1> N;                      // Number of observations.
-  int<lower = 1> K;                      // Number of groups.
-  int<lower = 1> I;                      // Number of observation-level covariates.
-
-  real satisfaction[N];                        // Vector of observations.
-  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
-  int eth[N];                               // Vector of ethnicity covariates.
-  int age[N];                               // Vector of age covariates.
-  int income[N];                          // Vector of income covariates.
-  int state[N];                          // Vector of state covariates.
-
-  real gamma_mean;                       // Mean for the hyperprior on gamma.
-  real<lower = 0> gamma_var;             // Variance for the hyperprior on gamma.
-  real<lower = 0> tau_min;               // Minimum for the hyperprior on tau.
-  real<lower = 0> tau_max;               // Maximum for the hyperprior on tau.
-  real<lower = 0> sigma_min;             // Minimum for the hyperprior on tau.
-  real<lower = 0> sigma_max;             // Maximum for the hyperprior on tau.
+  int<lower=2> C; // # of alternatives (choices) in each scenario
+  int<lower=1> K; // # of covariates of alternatives
+  int<lower=1> R; // # of respondents
+  int<lower=1> S; // # of scenarios per respondent
+  int<lower=0> G; // # of respondent covariates 
+  int<lower=1,upper=C> Y[R, S]; // observed choices
+  matrix[C, K] X[R, S]; // matrix of attributes for each obs
+  matrix[G, R] Z; // vector of covariates for each respondent
 }
 
-// Parameters and hyperparameters.
 parameters {
-  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
-  vector[K] beta;                        // Vector of observation-level price coefficients.
-  real gamma;                            // Mean of the population model.
-  real<lower=0> tau;                     // Variance of the population model.
-  real<lower=0> sigma;                   // Variance of the observation model.
+  matrix[K, R] Beta;
+  matrix[K, G] Theta;
+  corr_matrix[K] Omega;
+  vector<lower=0>[K] tau;
 }
 
-// Hierarchical regression.
-model {
-  // Declare mu for use in the linear model.
-  vector[N] mu;
-
-  // Hyperpriors and prior.
-  gamma ~ normal(gamma_mean, gamma_var);
-  tau ~ uniform(tau_min, tau_max);
-  sigma ~ uniform(sigma_min, sigma_max);
-
-  // Population model and likelihood.
-  for (k in 1:K) {
-    alpha[k,] ~ normal(gamma, tau);
-    beta[k] ~ normal(gamma, tau);
-  }
-  for (n in 1:N) {
-    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
-    income[n] + beta[male[n]] * state[n];
-  }
-  cat_pref ~ normal(mu, sigma);
+transformed parameters {
+  cov_matrix[K] Sigma = quad_form_diag(Omega, tau);
 }
 
-// Generate predictions using the posterior.
-generated quantities {
-  vector[N] mu_pc;                       // Declare mu for predicted linear model.
-  real cat_pref_pc[N];                     // Vector of predicted observations.
-
-  // Generate posterior prediction distribution.
-  for (n in 1:N) {
-    mu_pc[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
-    income[n] + beta[male[n]] * state[n];
-    cat_pref_pc[n] = normal_rng(mu_pc[n], sigma);
-  }
-}
-
-```
-
-As we will also need to do some prior and posterior checks, and for that we will need the generative model.
-
-```{}
-
-// Index values, observations, covariates, and hyperior values.
-data {
-  int<lower = 1> N;                      // Number of observations.
-  int<lower = 1> K;                      // Number of groups.
-  int<lower = 1> I;                      // Number of observation-level covariates.
-
-  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
-  int eth[N];                               // Vector of ethnicity covariates.
-  int age[N];                               // Vector of age covariates.
-  int income[N];                          // Vector of income covariates.
-  int state[N];                          // Vector of state covariates.
-
-  real gamma_mean;                       // Mean for the hyperprior on gamma.
-  real<lower = 0> gamma_var;             // Variance for the hyperprior on gamma.
-  real<lower = 0> tau_min;               // Minimum for the hyperprior on tau.
-  real<lower = 0> tau_max;               // Maximum for the hyperprior on tau.
-  real<lower = 0> sigma_min;             // Minimum for the hyperprior on tau.
-  real<lower = 0> sigma_max;             // Maximum for the hyperprior on tau.
-}
-
-// Generate data according to the hierarchical regression.
-generated quantities {
-  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
-  vector[K] beta;                        // Vector of observation-level price coefficients.
-  real gamma;                            // Mean of the population model.
-  real<lower=0> tau;                     // Variance of the population model.
-  real<lower=0> sigma;                   // Variance of the observation model.
-
-  vector[N] mu;                          // Declare mu for linear model.
-  real cat_pref[N];                        // Vector of observations.
-
-  gamma = normal_rng(gamma_mean, gamma_var);
-  tau = uniform_rng(tau_min, tau_max);
-  sigma = uniform_rng(sigma_min, sigma_max);
-
-  // Draw parameter values and generate data.
-  for (k in 1:K) {
-    for (i in 1:(I - 1)) {
-      alpha[k, i] = normal_rng(gamma, tau);
-    }
-    beta[k] = normal_rng(gamma, tau);
-  }
-  for (n in 1:N) {
-    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
-    income[n] + beta[male[n]] * state[n];
-    cat_pref[n] = normal_rng(mu[n], sigma);
+model {
+  //priors
+  to_vector(Theta) ~ normal(0, 10);
+  tau ~ cauchy(0, 2.5); 
+  Omega ~ lkj_corr(2);
+  //likelihood
+  for (r in 1:R) {
+    Beta[,r] ~ multi_normal(Theta*Z[,r], Sigma);	
+    for (s in 1:S)
+      Y[r,s] ~ categorical_logit(X[r,s]*Beta[,r]);
   }
@@
 ```{r}
-sim_values <- list(
-  N = 6300,                                       # Number of observations.
-  K = 2,                                         # Number of groups.
-  I = 65,                                         # Number of observation-level covariates.
+# ========== Load libraries and set options ==========
+library(rstan)
+library(MASS)
+library(shinystan)
 
-  male = sample(2, 6300, replace = TRUE),            # Vector of group assignments.
-  eth = sample(3, 6300, replace = TRUE),       # Vector of brands covariates.
-  age = sample(7, 6300, replace = TRUE),        # Vector of price covariates.
-  income = sample(3, 6300, replace = TRUE),
-  state = sample(50, 6300, replace = TRUE),
+# writes a compiled Stan program to the disk to avoid recompiling
+rstan_options(auto_write=TRUE) 
+# allows Stan chains to run in parallel on multiprocessor machines
+options(mc.cores = parallel::detectCores())
 
-  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
-  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
-  tau_min = 0,                                   # Minimum for the hyperprior on tau.
-  tau_max = .1,                                   # Maximum for the hyperprior on tau.
-  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
-  sigma_max = .1                                  # Maximum for the hyperprior on tau.
-)
-# Generate data.
-sim_data <- stan(
-  file = here::here("Code/mrp/generate_data.stan"),
-  data = sim_values,
-  iter = 10,
-  chains = 1,
-  seed = 42,
-  algorithm = "Fixed_param"
-)
+# ========== Test Stan with synthetic data ============
+
+# function to generate mnl data
+generate_hmnl_data <- function(R=100, S=30, C=3, 
+                               Theta=matrix(rep(1, 8), nrow=2), 
+                               Sigma=diag(0.1, 4)){
+  K <- ncol(Theta)
+  G <- nrow(Theta)
+  Y <- array(dim=c(R, S))
+  X <- array(rnorm(R*S*C*K), dim=c(R, S, C, K)) # normal covariates
+  Z <- array(dim=c(G, R))
+  Z[1,] <- 1  # intercept
+  if (G > 1) {
+    Z[2:G,] <- rnorm(R*(G-1)) # normal covariates
+  }
+  Beta <- array(dim=c(K, R))
+  for (r in 1:R) {
+    Beta[,r] <- mvrnorm(n=1, mu=Z[,r]%*%Theta, Sigma=Sigma)
+    for (s in 1:S)
+      Y[r,s] <- sample(x=C, size=1, prob=exp(X[r,s,,]%*%Beta[,r])) # logit formula
+   }
+  list(R=R, S=S, C=C, K=K, G=G, Y=Y, X=X, Z=Z, 
+       beta.true=beta, Theta.true=Theta, Sigma.true=Sigma)
+}
+
+d1 <- generate_hmnl_data()
+str(d1)
+
+test.stan <- stan(file="hmnl.stan", data=d1, iter=1000, chains=4)
+
+plot(test.stan, plotfun="trace", pars=("Theta"))
+
+plot(test.stan, plotfun="trace", pars=c("tau"))
+
+plot(test.stan, plotfun="trace", pars=("Omega"))
+
+plot(test.stan, pars=c("Theta", "tau", "Omega"))
+
+plot(test.stan, pars=c("Theta", "Sigma"))
+
+summary(test.stan, pars=c("Theta"))$summary
+
+summary(test.stan, pars=c("tau"))$summary
+
+summary(test.stan, pars=c("Omega"))$summary
 ```
@@
 ```{r}
-# Extract the simulated data.
-prior_pc <- tibble(
-  cat_pref = as.vector(extract(sim_data)$cat_pref)
-)
-# Plot the prior predictive distribution.
-prior_pc %>% 
-  ggplot(aes(x = cat_pref)) +
-  geom_density()
+# ========= Read in Chocolate Data and Prep for Stan ==========
+rm(list=ls()) # tidy up
+choc.df <- read.csv("cbc_chocolate.csv")
+
+# Coding the chocolate data (this ought to be a function)
+choc.contrasts <- list(Brand = "contr.sum", Type = "contr.sum")
+choc.coded <- model.matrix(~ Brand + Type, data = choc.df, contrasts = choc.contrasts)
+choc.coded <- choc.coded[,2:ncol(choc.coded)] # remove intercept
+# Fix the bad labels from contr.sum
+choc.names <- c("BrandDove", "BrandGhirardelli", "BrandGodiva", "BrandHersheys", 
+                "TypeDark", "TypeDarkNuts", "TypeMilk", "TypeMilkNuts")
+colnames(choc.coded) <- choc.names
+choc.df <- cbind(choc.df, choc.coded)
+
+head(choc.df)
+
+# Munge into Stan list
+R <- length(unique(choc.df$Ind))
+S <- length(unique(choc.df$Trial))
+C <- max(choc.df$Alt)
+K <- 9
+Y <- array(dim=c(R, S))
+X <- array(rnorm(R*S*C*K), dim=c(R, S, C, K)) 
+Z <- array(1, dim=c(1, R)) # intercept only
+for (r in 1:R) { # respondents
+  for (s in 1:S){ # choice scenarios
+    scenario <- choc.df[choc.df$Ind==unique(choc.df$Ind)[r] & 
+                        choc.df$Trial==unique(choc.df$Trial)[s], ]
+    X[r,s,,] <- data.matrix(scenario[,c(7, 9:16)]) # price and coded brand and type
+    Y[r,s] <- scenario$Alt[as.logical(scenario$Chosen)]
+  }
+}
+
+choc.standata <- list(C=C, K=K, R=R, S=S, G=1, Y=Y, X=X, Z=Z)
+str(choc.standata)
+
+rm(Y, X, Z, R, S, r, s, C, K, choc.contrasts, scenario, choc.coded)
+
 ```
@@
 ```{r}
-# # Specify data.
-# data <- list(
-#   N = nrow(true_popn),                     # Number of observations.
-#   K = 2,                    # Number of groups.
-#   I = 65,                                # Number of observation-level covariates.
-#   
-#   cat_pref = true_popn$cat_pref,               # Vector of observations.
-#   male = as.numeric(as.factor(true_popn$male)),            # Vector of group assignments.
-#   eth = true_popn$eth,       # Vector of brands covariates.
-#   age = true_popn$age,        # Vector of price covariates.
-#   income = true_popn$income,
-#   state = true_popn$state,
-#   
-#   gamma_mean = 0.5,                                # Mean for the hyperprior on gamma.
-#   gamma_var = .2,                                 # Variance for the hyperprior on gamma.
-#   tau_min = 0,                                   # Minimum for the hyperprior on tau.
-#   tau_max = 1,                                   # Maximum for the hyperprior on tau.
-#   sigma_min = 0,                                 # Minimum for the hyperprior on tau.
-#   sigma_max = 1                                 # Maximum for the hyperprior on tau.
-# )
-# # Calibrate the model.
-# model03 <- stan(
-#   file = here::here("Code/mrp/hierarchical_model.stan"),
-#   data = data,
-#   control = list(adapt_delta = 0.99),
-#   seed = 42
-# )
+
+# ========== Run Stan and Check Convergence =========
+choc.stan <- stan(file="hmnl.stan", data=choc.standata)
+
+plot(choc.stan, plotfun="trace", pars=("Theta"))
+
+plot(choc.stan, plotfun="trace", pars=c("tau"))
+
+plot(choc.stan, plotfun="trace", pars=c("Omega[1,2]"))
+
+plot(choc.stan, plotfun="trace", pars=paste("Beta[", 1:9, ",1]", sep="")) # resp 1
+
+summary(choc.stan)$summary[,c("Rhat", "n_eff")]
+
+# Convergence checking gets tedious with a lot of parameters, so automate
+check_fit <- function(fit) {
+  summ <- summary(fit)$summary
+  range_rhat <- range(summ[ , 'Rhat'])
+  rhat_ok <- 0.99 <= range_rhat[1] && range_rhat[2] <= 1.1
+  range_neff <- range(summ[ , 'n_eff'])
+  neff_ok <- range_neff[1] >= 400
+  sp <- rstan::get_sampler_params(fit, inc_warmup=FALSE)
+  max_divergent <- max(sapply(sp, function(p){ sum(p[ , 'divergent__']) }))
+  no_divergent <- max_divergent == 0
+
+  list(ok = rhat_ok && neff_ok && no_divergent,
+       range_rhat = range_rhat,
+       range_neff = range_neff,
+       max_divergent = max_divergent)
+}
+
+check_fit(choc.stan)
 ```
@@
 ```{r}
-# Posterior predictive check.
-# post_pc03 <- tibble(
-#   # Extract the posterior predicted values.
-#   intent = as.vector(extract(model03)$cat_pref_pc)
-# )
-# # Plot the posterior predictive distribution.
-# ggplot(post_pc03, aes(x = intent)) +
-#   geom_histogram() +
-#   xlim(1, 10) 
-# ggplot(purchase_intent, aes(x = intent)) +
-#   geom_histogram() +
-#   xlim(1, 10) 
+# ========== Summarize Posterior ==========
+choc.names
+plot(choc.stan, pars=c("Theta", "tau"))
+
+plot(choc.stan, pars=c("Omega"))
+
+plot(choc.stan, pars=paste("Beta[", 1:9, ",1]", sep="")) + ggtitle("Respondent 1: Likes Milk Chocolate")
+
+plot(choc.stan, pars=paste("Beta[", 1:9, ",2]", sep="")) + ggtitle("Respondent 2: Likes Dark Chocolate")
+
+launch_shinystan(choc.stan)
+
+# ========== Simulate Shares from Model =========
+# function for computing shares from beta.draws for an hmnl model
+shares.hmnl.post <- function(beta.draws, X) # X is attribute matrix for scenario
+{
+  R <- dim(beta.draws)[3]  # respondents
+  D <- dim(beta.draws)[1]  # draws
+  shares <- array(NA, dim=c(nrow(X), R, D))
+  for (d in 1:D) {
+    for (r in 1:R) {
+      beta <- beta.draws[d,,r] 
+      V <- exp(X %*% beta)  
+      shares[,r,d] <- V/sum(V)
+    }
+  }
+  shares
+}
+
+choc.standata$X[1,1,,] # note option 2 is dark
+shares <- shares.hmnl.post(extract(choc.stan, pars=c("Beta"))$Beta, 
+                          choc.standata$X[1,1,,])
+str(shares)
+
+apply(shares, 1, quantile, probs=c(0.5, 0.025, 0.975))
+apply(shares, 1:2, quantile, probs=c(0.5, 0.025, 0.975))
+
 ```
-
-```{r}
-# model03 %>%
-#   gather_draws(alpha[n, i]) %>%
-#   unite(.variable, .variable, n, i) %>%
-#   ggplot(aes(x = .value, y = .variable)) +
-#   geom_halfeyeh(.width = .95) +
-#   facet_wrap(
-#     ~ .variable,
-#     nrow = data$K,
-#     ncol = (data$I - 1),
-#     scales = "free"
-#   )
-```
-
-```{r}
-# Plot the betas.
-# model03 %>%
-#   gather_draws(beta[i]) %>%
-#   unite(.variable, .variable, i) %>%
-#   ggplot(aes(x = .value, y = .variable)) +
-#   geom_halfeyeh(.width = .95) +
-#   facet_wrap(
-#     ~ .variable,
-#     nrow = data$K,
-#     ncol = 1,
-#     scales = "free"
-#   )
-```
-
-### Postratification 
-Note: for now I have set these chuncks to eval = false because we don
-t have a poststrat_prob yet so it freaks out
-
-For the postratification portion we take the estimate that we get from the model times poststrat$/N / sum(postsrat$N)
-
-```{r eval = FALSE}
-poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
-model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
-round(model_popn_pref, 3)
-```
-
-Because we are using simulated data we can see how our poststratified predictions compare to the true population
-
-```{r eval = FALSE}
-sample_popn_pref <- mean(sample$satisfaction)
-round(sample_popn_pref, 3)
-
-compare2 <- compare2 +
-  geom_hline(yintercept = model_popn_pref[1], colour = '#2ca25f', size = 1) +
-  geom_text(aes(x = 5.2, y = model_popn_pref[1] + .025), label = "MRP", colour = '#2ca25f')
-bayesplot_grid(compare, compare2,
-               grid_args = list(nrow = 1, widths = c(8, 1)))
-```

### 2020-03-20 Code/mrp/Case Study (McKenna) .Rmd

@@
 ```{r}
+# Run stan code. 
 fit3 <- stan(
-  file = here::here("Code", "mrp", "logit_simple.stan"),
+  file = here::here("Code", "mrp", "sim_regression.stan"),
   data = stan_values,
@@
 )
+```
+
+```{r}
+# Check trace plots.
+fit3 %>%
+  mcmc_trace(
+    pars = c("beta1", "beta2", "beta3", "beta4", "beta5"),
+    n_warmup = 500,
+    facet_args = list(nrow = 2, labeller = label_parsed)
+  )
+```
+
+```{r}
+# Recover parameter values.
+par_values <- tibble(
+  .variable = c("mu", "tau"),
+  values = c(sim_values$mu, sim_values$tau),
+)
+```
+
+```{r}
+fit3 %>%
+  gather_draws(beta1, beta2, beta3, beta4, beta5) %>%
+  ggplot(aes(x = .value, y = .variable)) +
+  geom_halfeyeh(.width = .95) +
+  facet_wrap(
+    ~ .variable,
+    nrow = 2,
+    scales = "free"
+  )
+
+fit3_summary <- summary(fit3)
+
+fit3_summary
 ```

### 2020-03-20 Code/mrp/brms code.Rmd

---
title: "Why BRMS Doesn't Work"
author: "McKenna Weech"
date: "2/27/2020"
output: word_document
---

```{r}
# Load packages
library(brms)
```

```{r}
#Let's grab some data 
sample <- mrp_sim[["sample"]]

#And let try and get data from brms.
make_standata(formula =
                cat_pref ~ factor(male) + factor(male) * factor(age) + # gender factor and a gender ~ age interaction factor
                (1 | state) + (1 | age) + (1 | eth) + (1 | income), # random intercept with fixed means
              family = binomial(link = "logit"),
              data = sample)
```

We can also see the stan code that it is writing. 
```{r}
make_stancode(formula =
                cat_pref ~ factor(male) + factor(male) * factor(age) + # gender factor and a gender ~ age interaction factor
                (1 | state) + (1 | age) + (1 | eth) + (1 | income), # random intercept with fixed means
              family = binomial(link = "logit"),
              data = sample )
```

### 2020-03-20 Code/mrp/mrp-vignette.Rmd

--- 2020-01-24 Code/mrp/mrp-vignette.Rmd
@@
 ```
+```{r}
+simulate_mrp_data <- function(n) {
+  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
+  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
+  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
+  count <- 0
+  for (i1 in 1:J[1]){
+    for (i2 in 1:J[2]){
+      for (i3 in 1:J[3]){
+        for (i4 in 1:J[4]){
+          for (i5 in 1:J[5]){
+              count <- count + 1
+              # Fill them in so we know what category we are referring to
+              poststrat[count, 1:5] <- c(i1-1, i2, i3,i4,i5) 
+          }
+        }
+      }
+    }
+  }
+  # Proportion in each sample in the population
+  p_male <- c(0.52, 0.48)
+  p_eth <- c(0.5, 0.2, 0.3)
+  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
+  p_income<-c(.50,.35,.15)
+  p_state_tmp<-runif(50,10,20)
+  p_state<-p_state_tmp/sum(p_state_tmp)
+  poststrat$N<-0
+  for (j in 1:prod(J)){
+    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
+      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
+  }
+  # Now let's adjust for the probability of response
+  p_response_baseline <- 0.01
+  p_response_male <- c(2, 0.8) / 2.8
+  p_response_eth <- c(1, 1.2, 2.5) / 4.7
+  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
+  p_response_inc <- c(1, 0.9, 0.8) / 2.7
+  p_response_state <- rbeta(50, 1, 1)
+  p_response_state <- p_response_state / sum(p_response_state)
+  p_response <- rep(NA, prod(J))
+  for (j in 1:prod(J)) {
+    p_response[j] <-
+      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
+      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
+      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
+  }
+  people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
+  ## For respondent i, people[i] is that person's poststrat cell,
+  ## some number between 1 and 32
+  n_cell <- rep(NA, prod(J))
+  for (j in 1:prod(J)) {
+    n_cell[j] <- sum(people == j)
+  }
+  coef_male <- c(0,-0.3)
+  coef_eth <- c(0, 0.6, 0.9)
+  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
+  coef_income <- c(0,-0.2, 0.6)
+  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
+  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
+                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
+  true_popn <- data.frame(poststrat[, 1:5], cat_pref = rep(NA, prod(J)))
+  for (j in 1:prod(J)) {
+    true_popn$cat_pref[j] <- plogis(
+      coef_male[poststrat[j, 1] + 1] +
+        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
+        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
+        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
+      )
+  }
+
+  #male or not, eth, age, income level, state, city
+  y <- rbinom(n, 1, true_popn$cat_pref[people])
+  male <- poststrat[people, 1]
+  eth <- poststrat[people, 2]
+  age <- poststrat[people, 3]
+  income <- poststrat[people, 4]
+  state <- poststrat[people, 5]
+  sample <- data.frame(cat_pref = y, 
+                       male, age, eth, income, state, 
+                       id = 1:length(people))
+  #Make all numeric:
+  for (i in 1:ncol(poststrat)) {
+    poststrat[, i] <- as.numeric(poststrat[, i])
+  }
+  for (i in 1:ncol(true_popn)) {
+    true_popn[, i] <- as.numeric(true_popn[, i])
+  }
+  for (i in 1:ncol(sample)) {
+    sample[, i] <- as.numeric(sample[, i])
+  }
+  list(
+    sample = sample,
+    poststrat = poststrat,
+    true_popn = true_popn
+  )
+}
+```
 
@@
 mrp_sim <- simulate_mrp_data(n=100)
+
+save(mrp_sim, file = "mrp_sim.RData")
+
 str(mrp_sim)

### 2020-03-20 Code/mrp/Case-Study-.Rmd
cleaning up report presentation

--- 2020-03-20 Code/mrp/Case Study .Rmd
@@
 
-```{r}
-mrp_sim <- simulate_mrp_data(n=1200)
-sample <- mrp_sim[["sample"]]
-poststrat <- mrp_sim[["poststrat"]]
-true_popn <- mrp_sim[["true_popn"]]
-head(sample)
-```
-
-```{r}
-stan_data <- list( 
-  N = nrow(sample), 
-  service_failure = sample$service_failure,
-  male = sample$male, 
-  age = sample$age,
-  eth = sample$eth, 
-  income = sample$income, 
-  state = sample$state)
-```
-
 We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model
@@
 
+#<<<<<<< HEAD
 plot(test.stan, pars=c("Theta", "tau", "Omega"))
+
+sim_values <- list(
+  N = 6300,                                       # Number of observations.
+  K = 2,                                         # Number of groups.
+  I = 65,                                         # Number of observation-level covariates.
+
+  male = sample(2, 6300, replace = TRUE),            # Vector of group assignments.
+  eth = sample(3, 6300, replace = TRUE),       # Vector of brands covariates.
+  age = sample(7, 6300, replace = TRUE),        # Vector of price covariates.
+  income = sample(3, 6300, replace = TRUE),
+  state = sample(50, 6300, replace = TRUE),
+
+  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
+  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
+  tau_min = 0,                                   # Minimum for the hyperprior on tau.
+  tau_max = .1,                                   # Maximum for the hyperprior on tau.
+  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
+  sigma_max = .1                                  # Maximum for the hyperprior on tau.
+)
+# Generate data.
+sim_data <- stan(
+  file = here::here("Code", "mrp", "generate_data.stan"),
+  data = sim_values,
+  iter = 10,
+  chains = 1,
+  seed = 42,
+  algorithm = "Fixed_param"
+)
+#>>>>>>> 4c5892d01716983cac2179c618db12208c13fe69
 
@@
 
+#<<<<<<< HEAD
 plot(choc.stan, plotfun="trace", pars=c("tau"))
+#=======
+```
+Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working.
 
+```{}
+stan_values <- list(
+  N = 1200,                                       # Number of observations.
+  K = 2,                                         # Number of groups.
+  I = 65,                                         # Number of observation-level covariates.
+
+  male = sample$male,                 
+  eth = sample$eth,      
+  age = sample$age,        
+  income = sample$income,
+  state = sample$state,
+  service_failure = sample$service_failure
+)
+
+```
+
+```{}
+fit3 <- stan(
+  file = here::here("Code", "mrp", "logit_simple.stan"),
+  data = stan_values,
+  seed = 42
+)
+```
+
+>>>>>>> 4c5892d01716983cac2179c618db12208c13fe69
+
+```{r}
 plot(choc.stan, plotfun="trace", pars=c("Omega[1,2]"))

### 2020-04-09 Code/mrp/Case Study (McKenna) .Rmd
Working on simple logit model

--- 2020-03-10 Code/mrp/Case Study (McKenna) .Rmd
@@
 ```
-```{r}
+```{r, eval = FALSE}
 fit %>%
@@
 ```
-```{r}
-
-```
 
@@
 
+Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working. 
 ```{r}
+ matrix <- sample %>% 
+  select(male, age, eth, income, state)
 
-sim_values <- list(
-  N = 6300,                                       # Number of observations.
-  K = 2,                                         # Number of groups.
-  I = 65,                                         # Number of observation-level covariates.
-
-  male = sample(2, 6300, replace = TRUE),            # Vector of group assignments.
-  eth = sample(3, 6300, replace = TRUE),       # Vector of brands covariates.
-  age = sample(7, 6300, replace = TRUE),        # Vector of price covariates.
-  income = sample(3, 6300, replace = TRUE),
-  state = sample(50, 6300, replace = TRUE),
-
-  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
-  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
-  tau_min = 0,                                   # Minimum for the hyperprior on tau.
-  tau_max = .1,                                   # Maximum for the hyperprior on tau.
-  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
-  sigma_max = .1                                  # Maximum for the hyperprior on tau.
-)
-# Generate data.
-sim_data <- stan(
-  file = here::here("Code", "mrp", "generate_data.stan"),
-  data = sim_values,
-  iter = 10,
-  chains = 1,
-  seed = 42,
-  algorithm = "Fixed_param"
-)
-
+x <- as.matrix(matrix)
 ```
@@
 ```{r}
-
-# Extract the simulated data.
-prior_pc <- tibble(
-  service_failure = as.vector(extract(sim_data)$service_failure)
-)
-# Plot the prior predictive distribution.
-prior_pc %>% 
-  ggplot(aes(x = service_failure)) +
-  geom_density()
-
-```
-
-Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working.
-
-```{r}
-stan_values <- list(
+stan_data <- list(
   N = 1200,                                       # Number of observations.
-  K = 2,                                         # Number of groups.
-  I = 65,                                         # Number of observation-level covariates.
+  K = 6300,                                       # Number of groups.
+  g = sample(6300, 1200, replace = TRUE),         # Vector of group assignments
 
@@
 ```{r}
-fit3 <- stan(
-  file = here::here("Code", "mrp", "logit_simple.stan"),
-  data = stan_values,
+data_list <- list(
+  D <- 5,                                    # Number of variables. 
+  N <- 1200,                                 # Number of observations.
+  L <- 6300,                                 # Number of groups. 
+  y <- sample$service_failure,               # Outcome variables. 
+  ll <- sample(6300, 1200, replace = TRUE),  # Group assignment. 
+  x <- as.matrix(matrix)                     # Vector of predictors. 
+)
+```
+
+```{r, eval = FALSE}
+fit <- stan(
+  file = here::here("Code", "mrp", "logit_hier.stan"),
+  data = data_list,
   seed = 42

### 2020-04-10 Code/mrp/Case Study (McKenna) .Rmd
Loading in data

@@
 library(tidybayes)
+library(here)
 
@@
 
-```{r}
+```{r, eval = FALSE}
 simulate_mrp_data <- function(n) {
@@
 
-mrp_sim <- simulate_mrp_data(n=1200)
-
-sample <- mrp_sim[["sample"]]
-poststrat <- mrp_sim[["poststrat"]]
-true_popn <- mrp_sim[["true_popn"]]
-
-head(sample)
+sample <- read_csv(here("code", "mrp", "data", "sample.csv"))
+proststrat <- read_csv(here("code", "mrp", "data", "poststrat.csv"))
+true_popn <- read_csv(here("code", "mrp", "data", "true_popn.csv"))
 
@@
   ll <- sample(6300, 1200, replace = TRUE),  # Group assignment. 
-  x <- as.matrix(matrix)                     # Vector of predictors. 
+  x <- as.matrix(matrix)                     # Matrix of predictors. 
 )

### 2020-04-24 Code/mrp/Case Study (McKenna) .Rmd
Cleaning up the case study to make it easier to follow.

@@
 
-For this first iteration of modeling, we will be generating our own data. We will generate a population, and sample from it in order to build an MRP model.
+For this first iteration of modeling, we will be generating our own data.
+We will generate a population, and sample from it in order to build an MRP model.
+The function will also generate an MRP table to use later to poststratify.
 
@@
 The following code will make a function `simulate_mrp_data` that will help us make our simulated data, and sample from it in such a way that we can use and see the value in postratification.
+
+We include the function here just for reference. The outputs have been previously saved out as "sample", "postrat", and "true_popn".
 
@@
 
+Here we will import our data generated by the function.
+
 ```{r}
 
-sample <- read_csv(here("code", "mrp", "data", "sample.csv"))
-proststrat <- read_csv(here("code", "mrp", "data", "poststrat.csv"))
-true_popn <- read_csv(here("code", "mrp", "data", "true_popn.csv"))
+sample <- read_csv(here:here("code", "mrp", "data", "sample.csv"))
+proststrat <- read_csv(here:here("code", "mrp", "data", "poststrat.csv"))
+true_popn <- read_csv(here:here("code", "mrp", "data", "true_popn.csv"))
 
 ```
+We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model
+
+In this section we are working througha couple different model versions heading to the hierarichal model.
+
+Here we are looking at running a simple logit model.
+
 ```{r}
@@
 
-We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model
-
 Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working. 
@@
 ```
+
+This is me thinking about what format we want the data in.
 
@@
 ```
+
+Here we are trying to do a higherarical logit.
 

### 2020-05-06 Code/MRP-Hannah/Case Study (Hannah).Rmd
updates citations

--- 2020-04-09 Code/mrp/Case Study (McKenna) .Rmd
@@
 ---
-title: "Case Study (McKenna)"
-author: "McKenna Weech"
+title: "Case Study (Hannah)"
+author: "Hannah Thompson"
 date: "3/10/2020"
@@
 ```{r}
+sample <- read_csv(here("code", "mrp", "data", "sample.csv"))
+proststrat <- read_csv(here("code", "mrp", "data", "poststrat.csv"))
+true_popn <- read_csv(here("code", "mrp", "data", "true_popn.csv"))
+```
+
+```{r}
 stan_data <- list( 
@@
 )
+```
 
-```
-```{r, eval = FALSE}
+```{r}
 fit %>%
   mcmc_trace(
-    pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'),
-    n_warmup = 500,
+    pars = c("alpha","beta1", "beta2", "beta3", "beta4"),
+    n_warmup = 5,
     facet_args = list(nrow = 2, labeller = label_parsed)
@@
 ```
+```{r}
+
+```
 
@@
 
-Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working. 
 ```{r}
- matrix <- sample %>% 
-  select(male, age, eth, income, state)
 
-x <- as.matrix(matrix)
+sim_values <- list(
+  N = 6300,                                       # Number of observations.
+  K = 2,                                         # Number of groups.
+  I = 65,                                         # Number of observation-level covariates.
+
+  male = sample(2, 6300, replace = TRUE),            # Vector of group assignments.
+  eth = sample(3, 6300, replace = TRUE),       # Vector of brands covariates.
+  age = sample(7, 6300, replace = TRUE),        # Vector of price covariates.
+  income = sample(3, 6300, replace = TRUE),
+  state = sample(50, 6300, replace = TRUE),
+
+  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
+  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
+  tau_min = 0,                                   # Minimum for the hyperprior on tau.
+  tau_max = .1,                                   # Maximum for the hyperprior on tau.
+  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
+  sigma_max = .1                                  # Maximum for the hyperprior on tau.
+)
+# Generate data.
+sim_data <- stan(
+  file = here::here("Code", "mrp", "generate_data.stan"),
+  data = sim_values,
+  iter = 10,
+  chains = 1,
+  seed = 42,
+  algorithm = "Fixed_param"
+)
+
 ```
@@
 ```{r}
-stan_data <- list(
+
+# Extract the simulated data.
+prior_pc <- tibble(
+  service_failure = as.vector(extract(sim_data)$service_failure)
+)
+# Plot the prior predictive distribution.
+prior_pc %>% 
+  ggplot(aes(x = service_failure)) +
+  geom_density()
+
+```
+
+Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working.
+
+```{r}
+stan_values <- list(
   N = 1200,                                       # Number of observations.
-  K = 6300,                                       # Number of groups.
-  g = sample(6300, 1200, replace = TRUE),         # Vector of group assignments
+  K = 2,                                         # Number of groups.
+  I = 65,                                         # Number of observation-level covariates.
 
@@
 ```{r}
-data_list <- list(
-  D <- 5,                                    # Number of variables. 
-  N <- 1200,                                 # Number of observations.
-  L <- 6300,                                 # Number of groups. 
-  y <- sample$service_failure,               # Outcome variables. 
-  ll <- sample(6300, 1200, replace = TRUE),  # Group assignment. 
-  x <- as.matrix(matrix)                     # Vector of predictors. 
-)
-```
-
-```{r, eval = FALSE}
-fit <- stan(
-  file = here::here("Code", "mrp", "logit_hier.stan"),
-  data = data_list,
+fit3 <- stan(
+  file = here::here("Code", "mrp", "logit_simple.stan"),
+  data = stan_values,
   seed = 42

### 2020-05-06 Code/MRP-Hannah/Random Thoughts and Trys.Rmd
updates citations

---
title: "Thoughts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

setwd('~/Dropbox/MRP Files/MRP Primer')
rm(list=ls(all=TRUE))

## MRP Script

library("arm")
library("foreign")

#read in megapoll and attach
marriage.data <- read.dta("gay_marriage_megapoll.dta", convert.underscore = TRUE)

#read in state-level dataset

Statelevel <- read.dta("state_level_update.dta",convert.underscore = TRUE)
Statelevel <- Statelevel[order(Statelevel$sstate.initnum),]

#read in Census data
Census <- read.dta("poststratification 2000.dta",convert.underscore = TRUE)
Census <- Census[order(Census$cstate),]
Census$cstate.initnum <-  match(Census$cstate, Statelevel$sstate)

#Create index variables

  #At level of megapoll

marriage.data$race.female <- (marriage.data$female *3) + marriage.data$race.wbh# from 1 for white males to 6 for hispanic females
marriage.data$age.edu.cat <- 4 * (marriage.data$age.cat -1) + marriage.data$edu.cat# from 1 for 18-29 with low edu to 16 for 65+ with high edu
marriage.data$p.evang.full <- Statelevel$p.evang[marriage.data$state.initnum]# proportion of evangelicals in respondent's state
marriage.data$p.mormon.full <-Statelevel$p.mormon[marriage.data$state.initnum]# proportion of mormon's in respondent's state
marriage.data$p.relig.full <- marriage.data$p.evang.full + marriage.data$p.mormon.full# combined evangelical + mormom proportions
marriage.data$p.kerry.full <- Statelevel$kerry.04[marriage.data$state.initnum]# kerry's % of 2-party vote in respondent's state in 2004

  #At census level (same coding as above for all variables)

Census$crace.female <- (Census$cfemale *3) + Census$crace.WBH 
Census$cage.edu.cat <- 4 * (Census$cage.cat -1) + Census$cedu.cat 
Census$cp.evang.full<-  Statelevel$p.evang[Census$cstate.initnum]
Census$cp.mormon.full <- Statelevel$p.mormon[Census$cstate.initnum]
Census$cp.relig.full <- Census$cp.evang.full + Census$cp.mormon.full
Census$cp.kerry.full <-  Statelevel$kerry.04[Census$cstate.initnum]

#run individual-level opinion model

individual.model <- glmer(formula = yes.of.all ~ (1|race.female) + (1|age.cat) 
  + (1|edu.cat) + (1|age.edu.cat) + (1|state) + (1|region) + (1|poll) + p.relig.full 
        + p.kerry.full,data=marriage.data, family=binomial(link="logit"))
display(individual.model)

#examine random effects and standard errors for race-female
ranef(individual.model)$race.female
se.ranef(individual.model)$race.female

#create vector of state ranefs and then fill in missing ones
state.ranefs <- array(NA,c(51,1))
dimnames(state.ranefs) <- list(c(Statelevel$sstate),"effect")
for(i in Statelevel$sstate){
    state.ranefs[i,1] <- ranef(individual.model)$state[i,1]
}
state.ranefs[,1][is.na(state.ranefs[,1])] <- 0 #set states with missing REs (b/c not in data) to zero

#create a prediction for each cell in Census data
cellpred <- invlogit( fixef(individual.model)["(Intercept)"]
            + ranef(individual.model)$race.female[Census$crace.female,1]
            + ranef(individual.model)$age.cat[Census$cage.cat,1]
            + ranef(individual.model)$edu.cat[Census$cedu.cat,1]
            + ranef(individual.model)$age.edu.cat[Census$cage.edu.cat,1]
            + state.ranefs[Census$cstate,1]
            + ranef(individual.model)$region[Census$cregion,1]   
            + (fixef(individual.model)["p.relig.full"] *Census$cp.relig.full)
            + (fixef(individual.model)["p.kerry.full"] *Census$cp.kerry.full)
               )

#weights the prediction by the freq of cell                                       
cellpredweighted <- cellpred * Census$cpercent.state

#calculates the percent within each state (weighted average of responses)
statepred <- 100* as.vector(tapply(cellpredweighted,Census$cstate,sum))
statepred

# install.packages("devtools")
devtools::install_github("romainfrancois/bibtex")

bib <- read.bib( package = "bibtex" )
15

### 2020-05-06 Code/MRP-Hannah/Stan Complex Hannah.Rmd
updates citations

// S4 class stanmodel 'bernoulli' coded as follows:
// include /pre/Columbia_copyright.stan
// include /pre/license.stan

// GLM for a Bernoulli outcome
functions {
// include /functions/common_functions.stan
// include /functions/bernoulli_likelihoods.stan
}
data {
  // dimensions
  int<lower=0> K;        // number of predictors
  int<lower=0> N[2];     // number of observations where y = 0 and y = 1 respectively
  vector[K] xbar;        // vector of column-means of rbind(X0, X1)
  int<lower=0,upper=1> dense_X; // flag for dense vs. sparse
  matrix[N[1],K] X0[dense_X];   // centered (by xbar) predictor matrix | y = 0
  matrix[N[2],K] X1[dense_X];   // centered (by xbar) predictor matrix | y = 1

  int<lower=0, upper=1> clogit; // 1 iff the number of successes is fixed in each stratum
  int<lower=0> J; // number of strata (possibly zero)
  int<lower=1,upper=J> strata[clogit == 1 ? N[1] + N[2] : 0];

  // stuff for the sparse case
  int<lower=0> nnz_X0;                       // number of non-zero elements in the implicit X0 matrix
  vector[nnz_X0] w_X0;                       // non-zero elements in the implicit X0 matrix
  int<lower=0, upper = K - 1> v_X0[nnz_X0];  // column indices for w_X0
  // where the non-zeros start in each row of X0
  int<lower=0, upper = rows(w_X0) + 1> u_X0[dense_X ? 0 : N[1] + 1]; 
  int<lower=0> nnz_X1;                       // number of non-zero elements in the implicit X1 matrix
  vector[nnz_X1] w_X1;                       // non-zero elements in the implicit X1 matrix
  int<lower=0, upper = K - 1> v_X1[nnz_X1];  // column indices for w_X1
  // where the non-zeros start in each row of X1
  int<lower=0, upper = rows(w_X1) + 1> u_X1[dense_X ? 0 : N[2] + 1]; 
  // declares prior_PD, has_intercept, link, prior_dist, prior_dist_for_intercept
#include /data/data_glm.stan

  int<lower=0> K_smooth;
  matrix[N[1], K_smooth] S0;
  matrix[N[2], K_smooth] S1;
  int<lower=1> smooth_map[K_smooth];

  int<lower=5,upper=5> family;

  // weights
  int<lower=0,upper=1> has_weights;  // 0 = No, 1 = Yes
  vector[has_weights ? N[1] : 0] weights0;
  vector[has_weights ? N[2] : 0] weights1;

  // offset
  int<lower=0,upper=1> has_offset;  // 0 = No, 1 = Yes
  vector[has_offset ? N[1] : 0] offset0;
  vector[has_offset ? N[2] : 0] offset1;

  // declares prior_{mean, scale, df}, prior_{mean, scale, df}_for_intercept, prior_{mean, scale, df}_for_aux
// include /data/hyperparameters.stan
  // declares t, p[t], l[t], q, len_theta_L, shape, scale, {len_}concentration, {len_}regularization
// include /data/glmer_stuff.stan

  // more glmer stuff
  int<lower=0> num_non_zero[2];     // number of non-zero elements in the Z matrices
  vector[num_non_zero[1]] w0;       // non-zero elements in the implicit Z0 matrix
  vector[num_non_zero[2]] w1;       // non-zero elements in the implicit Z1 matrix
  int<lower=0, upper = q - 1> v0[num_non_zero[1]]; // column indices for w0
  int<lower=0, upper = q - 1> v1[num_non_zero[2]]; // column indices for w1
  // where the non-zeros start in each row of Z0
  int<lower=0, upper = rows(w0) + 1> u0[t > 0 ? N[1] + 1 : 0];  
  // where the non-zeros start in each row of Z1
  int<lower=0, upper = rows(w1) + 1> u1[t > 0 ? N[2] + 1 : 0];  
  int<lower=0, upper=1> special_case;     // whether we only have to deal with (1|group)
}
transformed data {
  int NN = N[1] + N[2];
  real aux = not_a_number();
  int<lower=1> V0[special_case ? t : 0,N[1]] = make_V(N[1], special_case ? t : 0, v0);
  int<lower=1> V1[special_case ? t : 0,N[2]] = make_V(N[2], special_case ? t : 0, v1);
  int<lower=0> successes[clogit ? J : 0];
  int<lower=0> failures[clogit ? J : 0];
  int<lower=0> observations[clogit ? J : 0];

  int can_do_bernoullilogitglm = link == 1 && clogit == 0 && has_offset == 0 && prior_PD == 0 && dense_X == 1 && has_weights == 0 && t == 0;
  matrix[can_do_bernoullilogitglm ? NN : 0, can_do_bernoullilogitglm ? K + K_smooth : 0] XS;
  int y[can_do_bernoullilogitglm ? NN : 0];

  // defines hs, len_z_T, len_var_group, delta, pos
// include /tdata/tdata_glm.stan
  for (j in 1:J) {
    successes[j] = 0;
    failures[j] = 0;
  }
  if (J > 0) for (i in 1:N[2]) successes[strata[i]] += 1;
  if (J > 0) for (i in (N[2] + 1):NN) failures[strata[i]] +=  1;
  for (j in 1:J) observations[j] = failures[j] + successes[j];

  if (can_do_bernoullilogitglm) {
    XS = K_smooth > 0 ? append_col(append_row(X0[1], X1[1]), append_row(S0, S1)) : append_row(X0[1], X1[1]);
    y = append_array(rep_array(0, N[1]), rep_array(1, N[2]));
  }
}
parameters {
  real<upper=(link == 4 ? 0.0 : positive_infinity())> gamma[has_intercept];
  // declares z_beta, global, local, z_b, z_T, rho, zeta, tau
// include /parameters/parameters_glm.stan
}
transformed parameters {
  // defines beta, b, theta_L
// include /tparameters/tparameters_glm.stan
  if (t > 0) {
    if (special_case) {
      int start = 1;
      theta_L = scale .* tau;
      if (t == 1) b = theta_L[1] * z_b;
      else for (i in 1:t) {
        int end = start + l[i] - 1;
        b[start:end] = theta_L[i] * z_b[start:end];
        start = end + 1;
      }
    }
    else {
      theta_L = make_theta_L(len_theta_L, p, 
                             1.0, tau, scale, zeta, rho, z_T);
      b = make_b(z_b, theta_L, p, l);
    }
  }
}
model {
  if (can_do_bernoullilogitglm) {
    vector[K + K_smooth] coeff = K_smooth > 0 ? append_row(beta, beta_smooth) : beta;
    target += bernoulli_logit_glm_lpmf(y | XS, has_intercept ? gamma[1] : 0.0, coeff);
  } else if (prior_PD == 0) {
    // defines eta0, eta1
// include /model/make_eta_bern.stan
    if (has_intercept == 1) {
      if (link != 4) {
        eta0 += gamma[1];
        eta1 += gamma[1];
      }
      else {
        real shift = fmax(max(eta0), max(eta1));
        eta0 += gamma[1] - shift;
        eta1 += gamma[1] - shift;
      }
    }
    // Log-likelihood
    if (clogit) { 
      real dummy = ll_clogit_lp(eta0, eta1, successes, failures, observations);
    }
    else if (has_weights == 0) {
      real dummy = ll_bern_lp(eta0, eta1, link, N);
    }
    else {  // weighted log-likelihoods
      target += dot_product(weights0, pw_bern(0, eta0, link));
      target += dot_product(weights1, pw_bern(1, eta1, link));
    }
  }

// include /model/priors_glm.stan
  if (t > 0) {
    real dummy = decov_lp(z_b, z_T, rho, zeta, tau, 
                          regularization, delta, shape, t, p);
  }
}
generated quantities {
  real mean_PPD = compute_mean_PPD ? 0 : negative_infinity();
  real alpha[has_intercept];

  if (has_intercept == 1) {
    if (dense_X) alpha[1] = gamma[1] - dot_product(xbar, beta);
    else alpha[1] = gamma[1];
  }

  if (compute_mean_PPD) {
    vector[N[1]] pi0;
    vector[N[2]] pi1;
    // defines eta0, eta1
// include /model/make_eta_bern.stan
    if (has_intercept == 1) {
      if (link != 4) {
        eta0 += gamma[1];
        eta1 += gamma[1];
      }      
      else {
        real shift;
        shift = fmax(max(eta0), max(eta1));
        eta0 += gamma[1] - shift;
        eta1 += gamma[1] - shift;
        alpha[1] -= shift;
      }
    }
    if (clogit) for (j in 1:J) mean_PPD += successes[j]; // fixed by design
    else {
      pi0 = linkinv_bern(eta0, link);
      pi1 = linkinv_bern(eta1, link);
      for (n in 1:N[1]) mean_PPD += bernoulli_rng(pi0[n]);
      for (n in 1:N[2]) mean_PPD += bernoulli_rng(pi1[n]);
    }
    mean_PPD /= NN;
  }
}

### 2020-05-06 Code/mrp/Case Study (McKenna) .Rmd
Inserted downes mrp model as well as the stan user guide mrp model. Edited for case study format.

--- 2020-04-09 Code/mrp/Case Study (McKenna) .Rmd
@@
 
-Firms employ a variety of passive listening platforms (e.g., customer comment cards, help lines, social media) that elicit a variety of complaints.
-Since these complaints are self-selected, it isn’t obvious if complaints are widespread or genuinely indicative of systemic service failures.
-In other words, how can can a firm know when complaints can be ignored and when they need to addressed?
-This issue is related to a larger class of problems where the goal is to make inference about the size of a population from a non-random sample (e.g., the German tank problem).
-In this paper, we develop a model that uses a variety of observed customer complaints on Twitter to make inference about the severity of service failures.
+## Intro 
+Multi-level regression and post-stratification helps to infer treatment size for a whole population from a non-representative sample.
+Using population knowlege sample are classified into cells baised off of choosen classification variables.
+Heirarchical bayesian models are used to infer(?) treatment within cells and population knowlege is used to weight each cell according to their prevelance within the total population.
 
-## Describe the model conceptually
+## Data/Categories/Cells
+Categorical classification variables are choosen and cell are assigned baised off of category classification.
+For example, if one variable is gender consisting of two categories (male and other) and one varibale is age consisting of two categories (0-50 and 50-100) then there would be four cells: male 0-50, male 50-100, other 0-50, and other 50-100.
 
-It has been said that if you observe a cockroach on your floor, there are likely thousands inside the walls of your home.
-Following this analogy, our hope is to count the cockroaches we can see and calculate how many are hiding in the walls.
+In this case study there are four classification variables choosen: age, income, ethnicity, gender, and state.
+Each vairbale is tranforemed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).
 
-For the first portion of this case, we will be making a model around simulated data.
-Each observation will represent a single tweet, and we will be scoring them for satisfaction.
-We will use a multiple hierarchal linear model to predict satisfaction from the other known variables.
-Once we have the model predicting well on our simulated data, we will fit it to our real data, and from there use our real data satisfaction scores to measure service or product failure severity.
+Data is generated using a function from...(find referance)
 
-Along with making a model, we will also be using poststratification to correct the weights in our simulated sample and real data to more correctly represent the population.
-This will be explained in greater detail as we postratify in this first iteration of the model, so we can explain and see the benefit of a full multiple regression with postratification model (MRP).
+## Model
 
-To begin, we will start by generating our simulated data. It will run through an initial simple linear model and postratification.
-
-# Iteration 1: Simulation Data and Simple Model
-
-This initial block of code, we will just be loading in the needed packages and settings to make our sample and model code run.
-
-```{r message = FALSE}
+```{r message = FALSE, echo = FALSE}
 library(tidyverse) #Load packages
@@
 
-For this first iteration of modeling, we will be generating our own data. We will generate a population, and sample from it in order to build an MRP model.
-
-We will be modeling our populations `service_failure`.
-This will eventually translate into measuring service severity when we apply our model to our real data.
-We will be looking at common characteristics like `gender`, `ethnicity`, `income`, `age`, and `state`.
-
-The following code will make a function `simulate_mrp_data` that will help us make our simulated data, and sample from it in such a way that we can use and see the value in postratification.
-
-```{r}
+```{r, eval = FALSE, echo = FALSE}
+# Data generating function for referance. 
 simulate_mrp_data <- function(n) {
@@
 
-```{r}
+```{r, message = FALSE, echo = FALSE}
 
-mrp_sim <- simulate_mrp_data(n=1200)
-
-sample <- mrp_sim[["sample"]]
-poststrat <- mrp_sim[["poststrat"]]
-true_popn <- mrp_sim[["true_popn"]]
-
-head(sample)
-
-```
-```{r}
-stan_data <- list( 
-  N = nrow(sample), 
-  service_failure = sample$service_failure,
-  male = sample$male, 
-  age = sample$age,
-  eth = sample$eth, 
-  income = sample$income, 
-  state = sample$state)
-```
-
-```{r}
-fit <- stan(
-  file = here::here("Code", "mrp", "logit_simple.stan"),
-  data = stan_data,
-  seed = 42
-)
-
-```
-```{r, eval = FALSE}
-fit %>%
-  mcmc_trace(
-    pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'),
-    n_warmup = 500,
-    facet_args = list(nrow = 2, labeller = label_parsed)
-  )
-
-print(fit, pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'))
-```
-
-We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model
-
-Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working. 
-```{r}
- matrix <- sample %>% 
-  select(male, age, eth, income, state)
-
-x <- as.matrix(matrix)
-```
-
-```{r}
-stan_data <- list(
-  N = 1200,                                       # Number of observations.
-  K = 6300,                                       # Number of groups.
-  g = sample(6300, 1200, replace = TRUE),         # Vector of group assignments
-
-  male = sample$male,                 
-  eth = sample$eth,      
-  age = sample$age,        
-  income = sample$income,
-  state = sample$state,
-  service_failure = sample$service_failure
-)
+# Import data. 
+sample <- read_csv(here::here("code", "mrp", "data", "sample.csv"))
+proststrat <- read_csv(here::here("code", "mrp", "data", "poststrat.csv"))
+true_popn <- read_csv(here::here("code", "mrp", "data", "true_popn.csv"))
 
@@
 
+This case study will use generated data.
+The data is broken up into three data tables: sample, postratification, and population.
+The postratification table shows the population density of each cell and is used to weight the outcome results from the sample.
+Because the data is generated we also have a generated population that we can use to check the accuracy of the model.
+
+First we will build a model to predict the our outcome for each cell. Then we will use the postratification table to correctly weight each cell to predict outcome for the whole population.
+
+We will use bayesian hierchical modeling to take advantage of partical pooling to account for empty cells.
+
+#### McKenna's logit model  
 ```{r}
@@
   ll <- sample(6300, 1200, replace = TRUE),                  # Group assignment. 
-  x <- as.matrix(matrix)                     # Vector of predictors. 
+  x <- matrix(sample %>% 
+                select(male, age, eth, income, state))       # Matrix of predictors. 
 )
+
+D <- 5
+N <- 1200
+L <- 6300
+y <- sample$service_failure
+ll <- sample(6300, 1200, replace = TRUE)
+
 ```
@@
   file = here::here("Code", "mrp", "logit_hier.stan"),
-  data = data_list,
+  data = "data_list",
   seed = 42
@@
 ```
+#### Downes logit model 
+```{r}
+# Observations. 
+outcome <- sample$service_failure
+male <- sample$male
+age <- sample$age 
+eth <- sample$eth 
+income <- sample$income
+state <- sample$state
 
-### Postratification 
-Note: for now I have set these chuncks to eval = false because we don
-t have a poststrat_prob yet so it freaks out
+# Number of categories. 
+n <- length(outcome)
+n_male <- max(male)
+n_age <- max(age)
+n_eth <- max(eth)
+n_income <- max(income)
+n_state <- max(state)
 
-For the postratification portion we take the estimate that we get from the model times poststrat$/N / sum(postsrat$N)
+# Define parameters for Hamiltonian Monte Carlo algorithm
+n_iter <- 1000
+n_chain <- 4
+n_sim <- (n_iter * n_chain)/2
 
-```{ echo=FALSE}
-poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
-model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
-round(model_popn_pref, 3)
 ```
 
+```{r, eval = FALSE}
+stanfit_final <- stan(file= "downes_copy.stan",
+                        data=c("n","n_age","n_male","n_eth","n_income","n_state",
+                               "outcome","age","male","eth","income","state"), 
+                        iter=n_iter, chains=n_chain)
+```
+#### Stan user guide logit model 
+```{r}
+stan_data <- list( 
+  age <- sample$age, 
+  eth <- sample$eth, 
+  income <- sample$income, 
+  male <- sample$male, 
+  state <- sample$state, 
+  Y <- sample$service_failure, 
+  N <- length(Y))
+```
+
+```{r, eval = FALSE}
+stanfit_final <- stan(file= "stan_mrp.stan",
+                        data= "stan_data", 
+                        iter=n_iter, chains=n_chain)
+```
+
+## Postratification
+
+Postratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people
+
+$$\omega=\displaystyle\frac{$$\sum_{j=1}^{J}\beta_{j}*N_{j}$$}{$$\sum_{j=1}^{J}N_{j}$$}$$
+Postratification can be performed in stan using the generated quantities block.
+
+```{r, eval = FALSE}
+generated quantities {
+  real expect_pos = 0;
+  int total = 0;
+  for (b in 1:7)
+    for (c in 1:3)
+      for (d in 1:3)
+        for (f in 1:2)
+          for (g in 1:50) {
+        total += P[b, c, d, f, g];
+        expect_pos
+          += P[b, c, d, f, g]
+             * inv_logit(b0 + a_age[b] + a_eth[c] + a_income[d] + a_male[f] + a_state[g]);
+      }
+  real<lower = 0, upper = 1> phi = expect_pos / total;
+}           
+```
+
+## Compare to Population 
 Because we are using simulated data we can see how our poststratified predictions compare to the true population
-
-```{ echo=FALSE}
-sample_popn_pref <- mean(sample$satisfaction)
-round(sample_popn_pref, 3)
-
-compare2 <- compare2 +
-  geom_hline(yintercept = model_popn_pref[1], colour = '#2ca25f', size = 1) +
-  geom_text(aes(x = 5.2, y = model_popn_pref[1] + .025), label = "MRP", colour = '#2ca25f')
-bayesplot_grid(compare, compare2,
-               grid_args = list(nrow = 1, widths = c(8, 1)))
-```

### 2020-05-06 Code/MRP-Hannah/Citations.Rmd

---
title: "Citations"
author: "Hannah Thompson"
date: "5/6/2020"
output: html_document
bibliography: bibliography.bibtex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

https://timmastny.rbind.io/blog/multilevel-mrp-tidybayes-brms-stan/  
@misc{ Mastny17
       author = "Tim Mastny"
       title = "MRP Using brms and tidybayes",
       year = "2017" }

https://timmastny.rbind.io/blog/poststratification-with-dplyr/ 
@misc{ @Mastny17,
       author = "Tim Mastny",
       title = "Poststratification Primer with dplyr",
       year = "2017" }

https://cran.r-project.org/web/packages/rstanarm/vignettes/mrp.html
@misc{ @Kennedy_Gabry20,
       author = "Lauren Kennedy", "Jonah Gabry",
       title = "MRP with rstanarm",
       year = "2020" }

https://github.com/gelman/mrp-stan
@misc{ @Gelman14,
       author = "Andrew Gelman",
       title = "gelman/mrp-stan",
       year = "2014" }

https://www.r-bloggers.com/gelmans-mrp-in-r-what-is-this-all-about/
@misc{ Gutiérrez17,
       author = "Gutiérrez, Andrés",
       title = "Gelman's MrP in R – What is this all about?",
       year = "2017" }

http://www.stat.columbia.edu/~gelman/research/unpublished/MRT(1).pdf
@misc{ @gelman_lax_phillips_gabry_trangucci_2018,
       author = "Gelman, Andrew and Lax, Jeffrey and Phillips, Justin and Gabry, Jonah and Trangucci, Robert",
       title = "Using Multilevel Regression and Poststratification to Estimate Dynamic Public Opinion",
       year = "2018" }

https://github.com/gelman/mrp-stan/blob/master/models/turnout_simple_post.stan
@misc{ @Gelman14,
       author = "Andrew Gelman",
       title = "gelman/mrp-stan",
       year = "2014" }

http://www.stat.columbia.edu/~gelman/research/unpublished/modelweighting.pdf
@misc{ @si_trangucci_gabry_gelman_2018,
       author = "Si, Yajuan and Trangucci, Rob and Gabry, Jonah and Gelman, Andrew",
       title = "Bayesian hierarchical weighting adjustment and survey inference",
       year = "2018" }

https://cran.r-project.org/web/packages/rstanarm/vignettes/pooling.html
@misc{ @carpenter_gabry_goodrich_2020,
       author = "Carpenter, Bob and Gabry, Jonah and Goodrich, Ben",
       title = "Hierarchical Partial Pooling for Repeated Binary Trials",
       year = "2020" }

https://academic.oup.com/aje/article/187/8/1780/4964985
@article{ @Nobody06,
       author = "Downes, Marnie and Gurrin, Lyle C and English, Dallas R and Pirkis, Jane and Currier, Dianne and Spittal, Matthew J and Carlin, John B",
       title = "Multilevel Regression and Poststratification: A Modeling Approach to Estimating Population Quantities From Highly Selected Survey Samples",
       year = "2018" }

https://github.com/danilofreire/r-scripts/blob/master/stan-logistic-regression.R 
@misc{ @kennedy_gabry_2019,
       author = "Kennedy, Lauren and Gabry, Jonah",
       title = "MRP with rstanarm",
       year = "2019" }

https://mc-stan.org/docs/2_18/stan-users-guide/hierarchical-logistic-regression.html
@misc{ @Freire15,
       author = "Danila Freire",
       title = "Stan Logistic Regression",
       year = "2015" }

https://mc-stan.org/docs/2_18/stan-users-guide/hierarchical-logistic-regression.html

@manual{ @StanGuide,
       author = "Team, Stan Development",
       title = "Stan User's Guide" }

### 2020-05-13 Code/mrp/Case Study (McKenna) .Rmd
Changed the section names.
Adjusting data lists for stan models.

@@
 
-## Data/Categories/Cells
+## Data 
 Categorical classification variables are choosen and cell are assigned baised off of category classification.
@@
 ```{r}
+predictors <- sample %>% 
+  select(male, age, eth, income, state)
+
+pred <- as.matrix(predictors, byrow = TRUE)
+```
+
+```{r}
 data_list <- list(
-  D <- 5,                                                    # Number of variables. 
-  N <- 1200,                                                 # Number of observations.
-  L <- 6300,                                                 # Number of groups. 
-  y <- sample$service_failure,                               # Outcome variables. 
-  ll <- sample(6300, 1200, replace = TRUE),                  # Group assignment. 
-  x <- matrix(sample %>% 
-                select(male, age, eth, income, state))       # Matrix of predictors. 
+  D = 5,                                              # Number of variables. 
+  N = 1200,                                           # Number of observations.
+  L = 6300,                                           # Number of groups. 
+  y = sample$service_failure,                         # Outcome variables. 
+  ll = sample(6300, 1200, replace = TRUE),            # Group assignment. 
+  x = predictors                                      # Matrix of predictors. 
 )
-
-D <- 5
-N <- 1200
-L <- 6300
-y <- sample$service_failure
-ll <- sample(6300, 1200, replace = TRUE)
-
 ```
@@
 # Observations. 
-outcome <- sample$service_failure
-male <- sample$male
-age <- sample$age 
-eth <- sample$eth 
-income <- sample$income
-state <- sample$state
-
-# Number of categories. 
-n <- length(outcome)
-n_male <- max(male)
-n_age <- max(age)
-n_eth <- max(eth)
-n_income <- max(income)
-n_state <- max(state)
+downes_list <- list(
+  outcome = sample$service_failure,
+  male = sample$male,
+  age = sample$age, 
+  eth = sample$eth, 
+  income = sample$income,
+  state = sample$state,
+  n = length(sample$service_failure), 
+  n_male = max(sample$male),
+  n_age = max(sample$age),
+  n_eth = max(sample$eth),
+  n_income = max(sample$income),
+  n_state = max(sample$state)
+)
 
@@
 ```{r, eval = FALSE}
-stanfit_final <- stan(file= "downes_copy.stan",
-                        data=c("n","n_age","n_male","n_eth","n_income","n_state",
-                               "outcome","age","male","eth","income","state"), 
-                        iter=n_iter, chains=n_chain)
+stanfit_final <- stan(file = "downes_copy.stan",
+                        data = downes_list, 
+                        iter = n_iter, chains = n_chain)
 ```
@@
 stan_data <- list( 
-  age <- sample$age, 
-  eth <- sample$eth, 
-  income <- sample$income, 
-  male <- sample$male, 
-  state <- sample$state, 
-  Y <- sample$service_failure, 
-  N <- length(Y))
+  age = sample$age, 
+  eth = sample$eth, 
+  income = sample$income, 
+  male = sample$male, 
+  state = sample$state, 
+  Y = sample$service_failure, 
+  N = length(sample$service_failure))
 ```

### 2020-05-18 Code/mrp/Case Study (McKenna) .Rmd
Addressing errors in McKenna Logit model

@@
 #### McKenna's logit model  
+- The issue here is the way that the matrix of predictors is being specified, I think 
 ```{r}
@@
 
-pred <- as.matrix(predictors, byrow = TRUE)
+pred <- as.matrix(predictors)
+
+# pred <- list()
+# for (n in 1:nrow(predictors)) {
+#   pred[[n]] <- matrix(as.numeric(predictors[n,]))
+# }
 ```
@@
   N = 1200,                                           # Number of observations.
-  L = 6300,                                           # Number of groups. 
+  L = 5,                                              # Number of groups. 
   y = sample$service_failure,                         # Outcome variables. 
-  ll = sample(6300, 1200, replace = TRUE),            # Group assignment. 
-  x = predictors                                      # Matrix of predictors. 
+  ll = sample(5, 1200, replace = TRUE),               # Group assignment. 
+  x = pred                                            # Matrix of predictors. 
 )
@@
                         data = downes_list, 
-                        iter = n_iter, chains = n_chain)
+                        iter = n_iter, chains = 1)
 ```
@@
   Y = sample$service_failure, 
-  N = length(sample$service_failure))
+  N = length(sample$service_failure)
+  )
 ```

### 2020-05-20 Code/mrp/Case Study (McKenna) .Rmd
Editing intro to case study

@@
 
-In this case study there are four classification variables choosen: age, income, ethnicity, gender, and state.
-Each vairbale is tranforemed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).
+In this case study there are five classification variables choosen: age, income, ethnicity, gender, and state.
+Each variable is tranforemed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).
 

### 2020-06-03 Code/mrp/Case Study (McKenna) .Rmd
knitting to markdown
commit for example
Initial clean-up

@@
 date: "3/10/2020"
-output: html_document
+output: github_document
 ---
 
-## Intro 
 Multi-level regression and post-stratification helps to infer treatment size for a whole population from a non-representative sample.
-Using population knowlege sample are classified into cells baised off of choosen classification variables.
-Heirarchical bayesian models are used to infer(?) treatment within cells and population knowlege is used to weight each cell according to their prevelance within the total population.
+Using population knowledge sample are classified into cells based off of chosen classification variables.
+Hierarchical Bayesian models are used to infer(?) treatment within cells and population knowlege is used to weight each cell according to their prevalence within the total population.
 
 ## Data
-Categorical classification variables are choosen and cell are assigned baised off of category classification.
-For example, if one variable is gender consisting of two categories (male and other) and one varibale is age consisting of two categories (0-50 and 50-100) then there would be four cells: male 0-50, male 50-100, other 0-50, and other 50-100.
+
+Categorical classification variables are chosen and cell are assigned baised off of category classification.
+For example, if one variable is gender consisting of two categories (male and other) and one variable is age consisting of two categories (0-50 and 50-100) then there would be four cells: male 0-50, male 50-100, other 0-50, and other 50-100.
 
 In this case study there are five classification variables choosen: age, income, ethnicity, gender, and state.
-Each variable is tranforemed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).
+Each variable is transformed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).
 
-Data is generated using a function from...(find referance)
+Data is generated using a function from...(find reference).
 
@@
 rstan_options(auto_write = TRUE) # Don't recompile Stan code that hasn't changed
-```
 
-```{r, eval = FALSE, echo = FALSE}
 # Data generating function for referance. 
@@
 
-# Import data. 
+# Importing the data. 
 sample <- read_csv(here::here("code", "mrp", "data", "sample.csv"))

### 2020-06-03 Code/mrp/Case Study (McKenna) .Rmd
McKenna's logit model runs

@@
 
-options(mc.cores = parallel::detectCores()) # Set Stan to use all availible cores
-rstan_options(auto_write = TRUE) # Don't recompile Stan code that hasn't changed
+options(mc.cores = parallel::detectCores()) # Set Stan to use all available cores.
+rstan_options(auto_write = TRUE)            # Don't recompile Stan code that hasn't changed.
 
-# Data generating function for referance. 
+# Data generating function for reference. 
 simulate_mrp_data <- function(n) {
@@
 }
-```
-
-```{r, message = FALSE, echo = FALSE}
 
@@
 true_popn <- read_csv(here::here("code", "mrp", "data", "true_popn.csv"))
-
 ```
@@
 This case study will use generated data.
-The data is broken up into three data tables: sample, postratification, and population.
-The postratification table shows the population density of each cell and is used to weight the outcome results from the sample.
+The data is broken up into three data tables: sample, post-stratification, and population.
+The post-stratification table shows the population density of each cell and is used to weight the outcome results from the sample.
 Because the data is generated we also have a generated population that we can use to check the accuracy of the model.
 
-First we will build a model to predict the our outcome for each cell. Then we will use the postratification table to correctly weight each cell to predict outcome for the whole population.
+First we will build a model to predict the our outcome for each cell. Then we will use the post-stratification table to correctly weight each cell to predict outcome for the whole population.
 
-We will use bayesian hierchical modeling to take advantage of partical pooling to account for empty cells.
+We will use Bayesian hierarchical modeling to take advantage of partial pooling to account for empty cells.
 
-#### McKenna's logit model  
-- The issue here is the way that the matrix of predictors is being specified, I think 
+### McKenna's logit model
+
 ```{r}
@@
 
-pred <- as.matrix(predictors)
-
-# pred <- list()
-# for (n in 1:nrow(predictors)) {
-#   pred[[n]] <- matrix(as.numeric(predictors[n,]))
-# }
-```
-
-```{r}
 data_list <- list(
@@
   ll = sample(5, 1200, replace = TRUE),               # Group assignment. 
-  x = pred                                            # Matrix of predictors. 
+  x = predictors                                      # Matrix of predictors. 
 )
@@
   file = here::here("Code", "mrp", "logit_hier.stan"),
-  data = "data_list",
+  data = data_list,
   seed = 42 
@@
 ```
+
 #### Downes logit model
+
 ```{r}

### 2020-06-03 Code/mrp/Case Study (McKenna) .Rmd
Downes logit model runs

@@
   outcome = sample$service_failure,
-  male = sample$male,
+  male = sample$male + 1,
   age = sample$age, 
@@
   n = length(sample$service_failure), 
-  n_male = max(sample$male),
+  n_male = max(sample$male) + 1,
   n_age = max(sample$age),
@@
 )
-
-# Define parameters for Hamiltonian Monte Carlo algorithm
-n_iter <- 1000
-n_chain <- 4
-n_sim <- (n_iter * n_chain)/2
-
 ```
@@
 ```{r, eval = FALSE}
-stanfit_final <- stan(file = "downes_copy.stan",
+fit <- stan(
+  file = here::here("Code", "mrp", "downes_copy.stan"),
   data = downes_list,
-                        iter = n_iter, chains = 1)
+  seed = 42 
+)
 ```
+
 #### Stan user guide logit model
+
 ```{r}

### 2020-06-17 Cases/mrp/Case Study (McKenna) .Rmd
Reorganizing case study and files.

--- 2020-06-03 Code/mrp/Case Study (McKenna) .Rmd
@@
 ```{r, eval = FALSE}
-stanfit_final <- stan(file= "stan_mrp.stan",
-                        data= "stan_data", 
-                        iter=n_iter, chains=n_chain)
+fit <- stan(
+  file = here::here("Code", "mrp", "stan_mrp.stan"),
+  data = stan_data,
+  seed = 42 
+)
 ```
 
-## Postratification
+## Post-Stratification
 
-Postratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people
+Post-stratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people
 
 $$\omega=\displaystyle\frac{$$\sum_{j=1}^{J}\beta_{j}*N_{j}$$}{$$\sum_{j=1}^{J}N_{j}$$}$$
-Postratification can be performed in stan using the generated quantities block.
+Post-stratification can be performed in stan using the generated quantities block.
 
@@
 ## Compare to Population
-Because we are using simulated data we can see how our poststratified predictions compare to the true population
+
+Because we are using simulated data we can see how our poststratified predictions compare to the true population.

### 2020-06-17 Code/mrp/mrp case study .R

@@ -1,87 +1,0 @@
-from the blog post: https://timmastny.rbind.io/blog/poststratification-with-dplyr/
-
-library(tidyverse)
-library(rstan)
-library(bayesplot)
-library(tidybayes)
-
-### Example 1 with voting data 
-vote_yes <- c(rep(0, 25*(1-0.76)), 
-              rep(1, 25*0.76),
-              rep(0, 50*(1-0.3)),
-              rep(1, 50*0.3))
-vote_yes
-
-mean(vote_yes)
-
-poll_data <- tibble(
-  group = c(rep("A", 25), rep("B", 10)),
-  yes = c(rep(1, 19), rep(0, 6), rep(1, 3), rep(0, 7))
-)
-poll_data %>%
-  group_by(group) %>%
-  summarise(count = n())
-
-Census <- tibble(
-  group = c("A", "B"),
-  pop = c(25, 50)
-)
-Census
-
-mean(poll_data$yes)
-
-group_support <- poll_data %>%
-  group_by(group) %>%
-  summarise(perc_support = mean(yes))
-group_support
-
-overall_support <- group_support %>%
-  summarise(total_support = sum(perc_support * Census$pop/sum(Census$pop)))
-overall_support
-
-### Example 2 with api survey data 
-
-#Load data 
-library(survey)
-data(api)
-
-Census <- tibble(
-  stype = c("E", "H", "M"),
-  pop = c(4421, 755, 1018)
-)
-
-d <- apistrat %>% as.tibble()
-d %>% 
-  group_by(stype) %>% 
-  summarise(school_count = n())
-
-d.group.ave <- d %>% 
-  group_by(stype) %>%
-  summarise(ave_score = mean(api00))
-d.group.ave
-
-d.total.ave <- d.group.ave %>%
-  summarise(ave_score = sum(ave_score * Census$pop/sum(Census$pop)))
-d.total.ave
-
-apipop %>% as.tibble() %>%
-  summarise(mean(api00))
-
-### MRP with rstanarm 
-
-library(rstanarm)
-library(bayesplot)
-theme_set(bayesplot::theme_default())
-library(dplyr)
-library(tidyr)
-
-
-
-
-
-
-
-
-
-
-

### 2020-06-17 Code/mrp/stan_mrp.R

@@ -1,48 +1,0 @@
-# Load packages.
-library(tidyverse)
-library(rstan)
-library(bayesplot)
-library(tidybayes)
-
-# Set Stan options.
-options(mc.cores = parallel::detectCores())
-
-# Specify data and hyperparameter values.
-sim_values <- list(
-  N = 100,                            # Number of individuals.
-  K = 2,                              # Number of groups.
-  g = sample(2, 100, replace = TRUE), # Vector of group assignments.
-  mu = .76,                           # Mean of the population model.
-  tau = .1                            # Variance of the population model.
-)
-
-# Generate data.
-sim_data <- stan(
-  file = here::here("Code", "mrp", "generate_data.stan"),
-  data = sim_values,
-  iter = 1,
-  chains = 1,
-  seed = 42,
-  algorithm = "Fixed_param"
-)
-
-# Extract simulated data and group intercepts.
-sim_y <- extract(sim_data)$y
-sim_beta <- extract(sim_data)$beta
-
-# Calibrate the model.
-fit <- stan(
-  file = here::here("Code", "mrp", "regression.stan"),
-  data = data,
-  control = list(adapt_delta = 0.99),
-  seed = 42
-)
-
-tibble(sim_beta, sim_y)
-
-
-
-
-
-
-

### 2020-07-03 Cases/mrp/Case Study (McKenna) .Rmd
Wokring on Postratification

@@
 # Importing the data. 
-sample <- read_csv(here::here("code", "mrp", "data", "sample.csv"))
-proststrat <- read_csv(here::here("code", "mrp", "data", "poststrat.csv"))
-true_popn <- read_csv(here::here("code", "mrp", "data", "true_popn.csv"))
+sample <- read_csv(here::here("data", "sample.csv"))
+proststrat <- read_csv(here::here("data", "poststrat.csv"))
+true_popn <- read_csv(here::here("data", "true_popn.csv"))
 ```
@@
 )
+
+fit
+```
+
+```{r, eval = FALSE}
+posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)
+poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
+model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
+round(model_popn_pref, 3)
+
+true_popn_pref <- sum(true_popn$satisfaction * poststrat$N) / sum(poststrat$N)
+round(true_popn_pref, 3)
+
+state_df <- data.frame(
+  State = 1:50,
+  model_state_sd = rep(-1, 50),
+  model_state_pref = rep(-1, 50),
+  sample_state_pref = rep(-1, 50),
+  true_state_pref = rep(-1, 50),
+  N = rep(-1, 50)
+)
+
+for(i in 1:length(levels(as.factor(poststrat$state)))) {
+  poststrat_state <- poststrat[poststrat$state == i, ]
+    posterior_prob_state <- posterior_linpred(
+    fit,
+    transform = TRUE,
+    draws = 1000,
+    newdata = as.data.frame(poststrat_state)
+  )
+  poststrat_prob_state <- (posterior_prob_state %*% poststrat_state$N) / sum(poststrat_state$N)
+  #This is the estimate for popn in state:
+  state_df$model_state_pref[i] <- round(mean(poststrat_prob_state), 4)
+  state_df$model_state_sd[i] <- round(sd(poststrat_prob_state), 4)
+  #This is the estimate for sample
+  state_df$sample_state_pref[i] <- round(mean(sample$cat_pref[sample$state == i]), 4)
+  #And what is the actual popn?
+  state_df$true_state_pref[i] <-
+    round(sum(true_popn$cat_pref[true_popn$state == i] * poststrat_state$N) /
+            sum(poststrat_state$N), digits = 4)
+  state_df$N[i] <- length(sample$satisfaction[sample$state == i])
+}
+
+state_df[c(1,3:6)]
 ```
@@
 )
+
+  n_iter <- 1000
+  n_chain <- 1
+  n_sim <- (n_iter * n_chain)/2 
 ```
@@
 )
+```
+
+```{r, eval = FALSE}
+
+  stanfit_final_sim <- extract(fit, pars=c("b0","a_income","a_age","a_eth","a_state","a_male","sigma_age","sigma_eth","sigma_income", "sigma_male","sigma_state"))
+
+n_pscell <- length(poststrat$N)
+n_state <- max(poststrat$state)
+
+stanfit_final_ypred <- array(NA, c(n_sim, n_pscell))
+  for(l in 1:n_pscell){
+    stanfit_final_ypred[,l] <- invlogit(stanfit_final_sim$b0 + 
+                                        stanfit_final_sim$a_age * poststrat$age[l] +
+                                        stanfit_final_sim$a_income * poststrat$income[l] +
+                                        stanfit_final_sim$a_eth * poststrat$eth[l] +
+                                        stanfit_final_sim$a_state * poststrat$state[l] +
+                                        stanfit_final_sim$a_male * poststrat$male[l])
+  }
+
+  stanfit_final_ps <- c(NA, n_sim)
+  for(s in 1:n_sim){
+    stanfit_final_ps[s] <- sum(poststrat$N*stanfit_final_ypred[s,])/sum(poststrat$N)
+  }
+
+stanfit_final_q <- round(quantile(stanfit_final_ps, c(0.025,0.50,0.975)),3)
+  stanfit_final_sd <- round(sd(stanfit_final_ps),4)
+  stanfit_final_pop_est <- cbind(stanfit_final_q[2], stanfit_final_sd, stanfit_final_q[1],
+                                 stanfit_final_q[3])
+
 ```

### 2020-07-04 Code/mrp/Case Study (McKenna) .Rmd
Looking at the final model, though it isn't running yet

@@
 ```{r, eval = FALSE}
-stanfit_final <- stan(file= "stan_mrp.stan",
-                        data= "stan_data", 
-                        iter=n_iter, chains=n_chain)
+fit <- stan(
+  file = here::here("Code", "mrp", "stan_mrp.stan"),
+  data = stan_data,
+  seed = 42 
+)
 ```

### 2020-07-05 Cases/mrp/Case Study (McKenna) .Rmd
writing updates

--- 2020-06-17 Cases/mrp/Case Study (McKenna) .Rmd
@@
 title: "Case Study (McKenna)"
-author: "McKenna Weech"
+author: "McKenna Weech, Hannah Thompson"
 date: "3/10/2020"
@@
 Using population knowledge sample are classified into cells based off of chosen classification variables.
-Hierarchical Bayesian models are used to infer(?) treatment within cells and population knowlege is used to weight each cell according to their prevalence within the total population.
+Hierarchical Bayesian models are used to infer(?) treatment within cells and population knowledge is used to weight each cell according to their prevalence within the total population.
+Multilevel regression and poststratification (Gelman & Little, 1997) proceeds by fitting a hierarchical regression model to survey data, and then using the population size of each poststratification cell to construct weighted survey estimates.
+The accuracy of poststratification within MRP can be dependent on whehter the matrix that is used in poststratification is an accurate representation of the target population.
+This combination of MRP and postsrtatification has been seen as an effective method when adjusting a sample to be more representative of a population for specific variables.
 
@@
     poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
-      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
+      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]])
+
+#Adjust the N to be the number observed in each category in each group
   }
@@
 # Now let's adjust for the probability of response
+
   p_response_baseline <- 0.01
@@
 
-Post-stratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people
+Post-stratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people.
+Using poststratificationcan immprove accracy of the estimates based on the information known.
 

### 2020-07-06 Code/mrp/Poststratification.R
commit to files

@@ -1,5 +1,7 @@
 library(tidyverse)
 
+# This is just reference for simple postratification 
+
 # Generate data not in stan. 
 mu_1 <- 5
 sigma_1 <- 1

### 2020-07-06 Cases/mrp/Case Study (McKenna) .Rmd
added writing, spelling errors, minor changes
Clarified some of the text

@@
 Multi-level regression and post-stratification helps to infer treatment size for a whole population from a non-representative sample.
-Using population knowledge sample are classified into cells based off of chosen classification variables.
+Using population knowledge samples are classified into cells based off of chosen classification variables.
 Hierarchical Bayesian models are used to infer(?) treatment within cells and population knowledge is used to weight each cell according to their prevalence within the total population.
@@
 
-Data is generated using a function from...(find reference).
+Data is generated using a function used in case study (noted in references)
 
@@
   J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
-  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
+  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) 
+  # Columns of post-strat matrix, plus one for size
   colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
@@
 # Importing the data. 
-sample <- read_csv(here::here("code", "mrp", "data", "sample.csv"))
-proststrat <- read_csv(here::here("code", "mrp", "data", "poststrat.csv"))
-true_popn <- read_csv(here::here("code", "mrp", "data", "true_popn.csv"))
+sample <- read_csv(here::here("data", "sample.csv"))
+proststrat <- read_csv(here::here( "data", "poststrat.csv"))
+true_popn <- read_csv(here::here( "data", "true_popn.csv"))
 ```
@@
 
-First we will build a model to predict the our outcome for each cell. Then we will use the post-stratification table to correctly weight each cell to predict outcome for the whole population.
+First we will build a model to generate parameter estimates for each cell. Then we will use the post-stratification table to correctly weight the estimates for the whole population.
 

### 2020-07-09 Cases/mrp/Case Study (McKenna) .Rmd
Added some comments about what to include IN BOLD

@@
 
-Multi-level regression and post-stratification helps to infer treatment size for a whole population from a non-representative sample.
-Using population knowledge samples are classified into cells based off of chosen classification variables.
-Hierarchical Bayesian models are used to infer(?) treatment within cells and population knowledge is used to weight each cell according to their prevalence within the total population.
-Multilevel regression and poststratification (Gelman & Little, 1997) proceeds by fitting a hierarchical regression model to survey data, and then using the population size of each poststratification cell to construct weighted survey estimates.
-The accuracy of poststratification within MRP can be dependent on whehter the matrix that is used in poststratification is an accurate representation of the target population.
-This combination of MRP and postsrtatification has been seen as an effective method when adjusting a sample to be more representative of a population for specific variables.
+Multilevel regression and post-stratification helps to infer treatment size for a whole population from a non-representative sample.
+Using population knowledge, samples are classified into cells based off of chosen classification variables.
+Hierarchical Bayesian models are used to infer treatment within cells and population knowledge is used to weight each cell according to their prevalence within the total population.
+Multilevel regression and post-stratification (Gelman & Little, 1997) proceeds by fitting a hierarchical regression model to survey data, and then using the population size of each post-stratification cell to construct weighted survey estimates.
+The accuracy of post-stratification within MRP can be dependent on whether the matrix that is used in post-stratification is an accurate representation of the target population.
+This combination of multilevel regression and post-stratification has been seen as an effective method when adjusting a sample to be more representative of a population for specific variables.
 
@@
 
-Categorical classification variables are chosen and cell are assigned baised off of category classification.
+Categorical classification variables are chosen and cells are assigned based off of category classification.
 For example, if one variable is gender consisting of two categories (male and other) and one variable is age consisting of two categories (0-50 and 50-100) then there would be four cells: male 0-50, male 50-100, other 0-50, and other 50-100.
 
-In this case study there are five classification variables choosen: age, income, ethnicity, gender, and state.
+In this case study there are five classification variables: age, income, ethnicity, gender, and state.
 Each variable is transformed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300 (7 x 3 x 3 x 2 x 50 = 6300).
 
-Data is generated using a function used in case study (noted in references)
+Data is generated using a function used in case study (noted in references).
 
@@
 
-```{r message = FALSE, echo = FALSE}
+```{r load-data, message=FALSE}
 library(tidyverse) #Load packages
@@
 
-We will use Bayesian hierarchical modeling to take advantage of partial pooling to account for empty cells.
+We will use Bayesian hierarchical modeling to take advantage of partial pooling to account for underweighted cells.
 
 ### McKenna's logit model
+
+BEFORE FITTING logit_hier.stan INCLUDE IT HERE AND EXPLAIN THE MODEL...
+
+```{stan logit-hier, output.var="logit_hier", eval=FALSE}
+
+```
+
+...THEN YOU CAN FIT.
 
@@
 
-#### Downes logit model
+### Downes logit model
+
+BEFORE FITTING downes_copy.stan INCLUDE IT HERE AND EXPLAIN THE MODEL...
+
+```{stan downes, output.var="downes", eval=FALSE}
+
+```
+
+...THEN YOU CAN FIT.
 
@@
 
-#### Stan user guide logit model
+### Stan user guide logit model
+
+BEFORE FITTING stan_mrp.stan INCLUDE IT HERE AND EXPLAIN THE MODEL...
+
+```{stan stan-mrp, output.var="stan_mrp", eval=FALSE}
+
+```
+
+...THEN YOU CAN FIT.
 
@@
 Post-stratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people.
-Using poststratificationcan immprove accracy of the estimates based on the information known.
+Using post-stratificatio ncan improve accuracy of the estimates based on the information known.
+
+IF YOU NEED TO INCLUDE THIS, WE WILL NEED SOMETHING IN THE YAML TO GET THIS WORK FOR A GITHUB_DOCUMENT (MARC WILL FIGURE THAT OUT). AN ALTERNATIVE IS TO EXPRESS AS CODE INSTEAD OF MATH.
+
+THIS...
 
 $$\omega=\displaystyle\frac{$$\sum_{j=1}^{J}\beta_{j}*N_{j}$$}{$$\sum_{j=1}^{J}N_{j}$$}$$
+
+OR...
+
+```
+something / something
+```
+
 Post-stratification can be performed in stan using the generated quantities block.
@@
 
-Because we are using simulated data we can see how our poststratified predictions compare to the true population.
+Because we are using simulated data we can see how our post-stratified predictions compare to the true population.

### 2020-07-15 Cases/mrp/Case Study (McKenna) .Rmd
Inserted the stan models into the casestudy and began to explain them

@@
 
-BEFORE FITTING logit_hier.stan INCLUDE IT HERE AND EXPLAIN THE MODEL...
+Our first model is a hierarchical logit model.
+A logit model is appropriate for our data because of the biniary outcome variable.
+The hierarchical model is group baised on the group assignments determined by the categorical variables in the data.
 
 ```{stan logit-hier, output.var="logit_hier", eval=FALSE}
+data {
+  int<lower=1> D;
+  int<lower=0> N;
+  int<lower=1> L;
+  int<lower=0,upper=1> y[N];
+  int<lower=1,upper=L> ll[N];
+  matrix[N, D] x;
+}
 
+parameters {
+  real mu[D];
+  real<lower=0> sigma[D];
+  vector[D] beta[L];
+}
+
+model {
+  mu ~ normal(0, 100);
+  sigma ~ normal(0, 5);
+  for (l in 1:L) {
+    beta[l] ~ normal(mu, sigma);
+  }
+  for (n in 1:N) {
+    y[n] ~ bernoulli_logit((x[n,] * beta[ll[n]]));
+  }
+}
 ```
@@
 ```{stan downes, output.var="downes", eval=FALSE}
+data {
+  int<lower=0> n;                                       // Number of survey participants
 
+  int<lower=0> n_age;                                 // These are the number of categories
+  int<lower=0> n_eth;                                    // for each poststratification factor
+  int<lower=0> n_income;                                  // in the final model
+  int<lower=0> n_male;                                   
+  int<lower=0> n_state;
+
+  int<lower=0,upper=1> outcome[n];                      // observed outcome data, 1=Yes, 0=No
+
+  int<lower=0,upper=n_age> age[n];                  // These are the variables containing
+  int<lower=0,upper=n_eth> eth[n];                        // the observed data for each
+  int<lower=0,upper=n_income> income[n];                    // poststratification factor in the 
+  int<lower=0,upper=n_male> male[n];                      // final model
+  int<lower=0,upper=n_state> state[n];      
+ }
+parameters {                                            // Model parameters to be estimated:
+  real b0;                                              // "intercept"
+  real a_age[n_age];                                // age varying coeffs (depart from linear fit)
+  real a_eth[n_eth];                                      // remoteness class varying coeffs 
+  real a_income[n_income];                                    // seifa ieo varying coeffs (depart linear fit)
+  real a_male[n_male];                                // english fluency varying coeffs
+  real a_state[n_state];                                  // occupation varying coeffs
+  real<lower=0> sigma_age;                            // age var(sd) component
+  real<lower=0> sigma_eth;                               // remoteness class var(sd) component
+  real<lower=0> sigma_income;                              // seifa ieo var(sd) component
+  real<lower=0> sigma_male;                            // english fluency var(sd) component
+  real<lower=0> sigma_state;                             // occupation var(sd) component
+}
+transformed parameters {                                // Model specification is here
+  vector[n] outcome_hat;
+  for (i in 1:n) {
+    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
+  }
+}
+model {                                                 // Model distributions for varying coefficients
+  b0 ~ cauchy(0,2.5);                                   // and prior distributions for unmodelled                            // Can modify Cauchy scale parameter
+                                                        // Can also specify a uniform distribution here
+  a_age ~ normal(0, sigma_age);                     // or by setting upper and lower limits for
+  a_eth ~ normal(0, sigma_eth);                           // unmodelled parameters in the parameter step
+  a_income ~ normal(0, sigma_income);                         // above  
+  a_male ~ normal(0, sigma_male);                      
+  a_state ~ normal(0, sigma_state);
+
+  sigma_age ~ cauchy(0,2.5);
+  sigma_eth ~ cauchy(0,2.5);
+  sigma_income ~ cauchy(0,2.5);
+  sigma_male ~ cauchy(0,2.5);
+  sigma_state ~ cauchy(0,2.5);
+
+  outcome ~ bernoulli_logit(outcome_hat);               // For a continuous outcome, specify a
+                                                        // normal distribution with an additional
+                                                        // variance component, i.e.
+                                                        // outcome ~ normal(outcome_hat, sigma_outcome)
+                                                        // Note the prior distributions for 
+                                                        // unmodelled parameters will change.
+}
 ```
@@
 ```{stan stan-mrp, output.var="stan_mrp", eval=FALSE}
+data {
+  int<lower = 0> N;
+  int<lower = 1, upper = 7> age[N];
+  int<lower = 1, upper = 3> income[N];
+  int<lower = 1, upper = 3> eth[N];
+  int<lower = 1, upper = 2> male[N];
+  int<lower = 1, upper = 50> state[N];
+  int<lower = 0> y[N];
+  int<lower = 0> P[7, 3, 3, 2, 50];
+}
+parameters {
+  real alpha;
+  real epsilon;
+  real<lower = 0> sigma_beta;
+  real<lower = 0> sigma_gamma;
+  real<lower = 0> sigma_delta;
+  real<lower = 0> sigma_rho;
+  vector<multiplier = sigma_beta>[7] beta;
+  vector<multiplier = sigma_gamma>[3] gamma;
+  vector<multiplier = sigma_delta>[3] delta;
+  vector<multiplier = sigma_rho>[50] rho;
+}
+model {
+  y ~ bernoulli_logit(alpha + beta[age] + gamma[income] + delta[eth] + {epsilon, -epsilon}[male] + rho[state]);
+  alpha ~ normal(0, 2);
+  epsilon ~ normal(0, 2);
+  sigma_beta ~ normal(0, 1);
+  sigma_gamma  ~ normal(0, 1);
+  sigma_delta ~ normal(0, 1);
+  sigma_rho ~ normal(0, 1);
+  beta ~ normal(0, sigma_beta);
+  gamma ~ normal(0, sigma_gamma);
+  delta ~ normal(0, sigma_delta);
+  rho ~ norma(0, sigma_rho);
+}
+generated quantities {
+  real expect_pos = 0;
+  int total = 0;
+  for (b in 1:7)
+    for (c in 1:3)
+      for (d in 1:3)
+        for (f in 1:2)
+          for (g in 1:50){
+        total += P[b, c, d, f, g];
+        expect_pos
+          += P[b, c, d, f, g]
+             * inv_logit(alpha + beta[b] + gamma[c] + delta[d] + {epsilon, -epsilon}[f] + rho[g]);
+      }
+  real<lower = 0, upper = 1> phi = expect_pos / total;
+}
 

### 2020-08-05 Cases/mrp/Case Study (McKenna) .Rmd
Started describing the models and identifying gaps in understanding that need to be addressed.

@@
 data {
-  int<lower=1> D;
-  int<lower=0> N;
-  int<lower=1> L;
-  int<lower=0,upper=1> y[N];
-  int<lower=1,upper=L> ll[N];
-  matrix[N, D] x;
+  int<lower=1> D;                // Number of variables.
+  int<lower=0> N;                // Number of observations.
+  int<lower=1> L;                // Number of groups.
+  int<lower=0,upper=1> y[N];     // Outcome variable. 
+  int<lower=1,upper=L> ll[N];    // Group assignment. 
+  matrix[N, D] x;                // Matrix of predictors. 
 }
@@
 ```
+```{r, eval = FALSE}
+posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)
+
+?posterior_linpred
+
+poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
+
+model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
+
+round(model_popn_pref, 3)
+```
 
@@
 
-BEFORE FITTING downes_copy.stan INCLUDE IT HERE AND EXPLAIN THE MODEL...
+The data section of the Downes model not only specifies the individual predictor values but also the number of categories for each categorical variable.
+Each category is given a varying coefficient in the parameter section.
+
+[Note to McKenna]
+Questions to answer: 
+Why cauchy?
+Actual model specification?
+Why varying coefficients?
 
@@
   real a_age[n_age];                                  // age varying coeffs (depart from linear fit)
-  real a_eth[n_eth];                                      // remoteness class varying coeffs 
-  real a_income[n_income];                                    // seifa ieo varying coeffs (depart linear fit)
-  real a_male[n_male];                                // english fluency varying coeffs
-  real a_state[n_state];                                  // occupation varying coeffs
+  real a_eth[n_eth];                                  // ethnicity class varying coeffs 
+  real a_income[n_income];                            // income varying coeffs (depart linear fit)
+  real a_male[n_male];                                // gender varying coeffs
+  real a_state[n_state];                              // state varying coeffs
   real<lower=0> sigma_age;                            // age var(sd) component
-  real<lower=0> sigma_eth;                               // remoteness class var(sd) component
-  real<lower=0> sigma_income;                              // seifa ieo var(sd) component
-  real<lower=0> sigma_male;                            // english fluency var(sd) component
-  real<lower=0> sigma_state;                             // occupation var(sd) component
+  real<lower=0> sigma_eth;                            // ethnicit var(sd) component
+  real<lower=0> sigma_income;                         // income var(sd) component
+  real<lower=0> sigma_male;                           // gender fluency var(sd) component
+  real<lower=0> sigma_state;                          // state var(sd) component
 }
@@
 
-BEFORE FITTING stan_mrp.stan INCLUDE IT HERE AND EXPLAIN THE MODEL...
+The data for the Stan User Guide model is specified with lower and upper bounds on the data for the number of categories for each variable.
+In this stan model, post-stratification takes place in the generated quantities section.
+
+[Note to McKenna]
+Questions to answer: 
+What the epsilon, -epsilon is that?
 

### 2020-08-05 Cases/mrp/Case Study (McKenna) .Rmd
Added group assignments to the data.

@@
 library(here)
+```
 
+```{r, eval = FALSE}
+# I set this to eval = FALSE just for now because it wasn't knitting so I will have to come back and take a look at this.
 options(mc.cores = parallel::detectCores()) # Set Stan to use all available cores.
@@
       p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) 
-
 #Adjust the N to be the number observed in each category in each group
   }
-
 # Now let's adjust for the probability of response
-
   p_response_baseline <- 0.01
@@
   }
-
 #male or not, eth, age, income level, state, city
@@
 }
+```
 
+```{r}
 # Importing the data. 
-sample <- read_csv(here::here("data", "sample.csv"))
-proststrat <- read_csv(here::here( "data", "poststrat.csv"))
-true_popn <- read_csv(here::here( "data", "true_popn.csv"))
+sample <- read_csv(here::here("Data", "sample.csv"))
+proststrat <- read_csv(here::here( "Data", "poststrat.csv"))
+true_popn <- read_csv(here::here( "Data", "true_popn.csv"))
+
+# Add groups to data. 
+proststrat_group <- proststrat %>% 
+  mutate(group = row_number())
+
+sample_group <- left_join(sample,
+                          proststrat_group,
+                          by = c(
+                            "male" = "male", 
+                            "age" = "age", 
+                            "eth" = "eth", 
+                            "income" = "income",
+                            "state" = "state") )
 ```
@@
 ```{r}
-predictors <- sample %>% 
+predictors <- sample_group %>% 
   select(male, age, eth, income, state)
@@
   N = 1200,                                           # Number of observations.
-  L = 5,                                              # Number of groups. 
-  y = sample$service_failure,                         # Outcome variables. 
-  ll = sample(5, 1200, replace = TRUE),               # Group assignment. 
+  L = 6300,                                           # Number of groups. 
+  y = sample_group$service_failure,                   # Outcome variables. 
+  ll = sample_group$group,                            # Group assignment. 
   x = predictors                                      # Matrix of predictors. 

### 2020-09-25 Code/mrp/Case Study (McKenna) .Rmd
altertered iterations on downes model

@@
 Using population knowledge sample are classified into cells based off of chosen classification variables.
-Hierarchical Bayesian models are used to infer(?) treatment within cells and population knowlege is used to weight each cell according to their prevalence within the total population.
+Hierarchical Bayesian models are used to infer(?) treatment within cells and population knowledge is used to weight each cell according to their prevalence within the total population.
 
@@
 
-Categorical classification variables are chosen and cell are assigned baised off of category classification.
+Categorical classification variables are chosen and cell are assigned based off of category classification.
 For example, if one variable is gender consisting of two categories (male and other) and one variable is age consisting of two categories (0-50 and 50-100) then there would be four cells: male 0-50, male 50-100, other 0-50, and other 50-100.
 
-In this case study there are five classification variables choosen: age, income, ethnicity, gender, and state.
+In this case study there are five classification variables chosen: age, income, ethnicity, gender, and state.
 Each variable is transformed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).
@@
 
-  ## For respondent i, people[i] is that person's poststrat cell,
+  ## For respondent i, people[i] is that person's post-strat cell,
   ## some number between 1 and 32
@@
   poststrat_prob_state <- (posterior_prob_state %*% poststrat_state$N) / sum(poststrat_state$N)
-  #This is the estimate for popn in state:
+  #This is the estimate for pop in state:
   state_df$model_state_pref[i] <- round(mean(poststrat_prob_state), 4)
@@
   state_df$sample_state_pref[i] <- round(mean(sample$cat_pref[sample$state == i]), 4)
-  #And what is the actual popn?
+  #And what is the actual pop?
   state_df$true_state_pref[i] <-
@@
 
-  n_iter <- 1000
-  n_chain <- 1
+  n_iter <- 2000
+  n_chain <- 2
   n_sim <- (n_iter * n_chain)/2 
@@
 
-Postratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people
+Post-Stratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people
 
 $$\omega=\displaystyle\frac{$$\sum_{j=1}^{J}\beta_{j}*N_{j}$$}{$$\sum_{j=1}^{J}N_{j}$$}$$
-Postratification can be performed in stan using the generated quantities block.
+Post-Stratification can be performed in Stan using the generated quantities block.
 
@@
 ## Compare to Population 
-Because we are using simulated data we can see how our poststratified predictions compare to the true population
+Because we are using simulated data we can see how our Post-Stratified predictions compare to the true population

### 2020-09-25 Cases/mrp/Case Study (McKenna) .Rmd
Working on the postratifying code.

@@
 Why cauchy?
-Actual model specification?
+Actual model specification? - looks like the model is specified in the transformed parameters section. why?
 Why varying coefficients?
@@
 }
-transformed parameters {                              // Model specification is here
-  vector[n] outcome_hat;
-  for (i in 1:n) {
-    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
-  }
-}
+// transformed parameters {                              // Model specification is here
+//   vector[n] outcome_hat;
+//   for (i in 1:n) {
+//    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
+//   }
+// }
 model {                                              // Model distributions for varying coefficients
@@
 
-  outcome ~ bernoulli_logit(outcome_hat);            // For a continuous outcome, specify a
+  for (i in 1:n) {
+   outcome[i] = bernoulli_logit(b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]]);
+  }
+
+//  outcome ~ bernoulli_logit(outcome_hat);            // For a continuous outcome, specify a
                                                      // normal distribution with an additional

### 2020-09-29 Cases/mrp/Case Study (McKenna) .Rmd
Updating poststratification.

@@
 sample <- read_csv(here::here("Data", "sample.csv"))
-proststrat <- read_csv(here::here( "Data", "poststrat.csv"))
+poststrat <- read_csv(here::here( "Data", "poststrat.csv"))
 true_popn <- read_csv(here::here( "Data", "true_popn.csv"))
@@
 # Add groups to data. 
-proststrat_group <- proststrat %>% 
+poststrat_group <- poststrat %>% 
   mutate(group = row_number())
@@
 sample_group <- left_join(sample,
-                          proststrat_group,
+                          poststrat_group,
                           by = c(
@@
 
-We will use Bayesian hierarchical modeling to take advantage of partial pooling to account for underweighted cells.
+We will use Bayesian hierarchical modeling to take advantage of partial pooling to account for underweight cells.
 
@@
 ```{r, eval = FALSE}
+# I think we will need to use a for loop like they do in the downes model to construct our predictions into a format that we can then postratify them.
+I got this for loop from the downes code and I have just begun to adjust it for our model.
+ n_sim <- (n_iter * n_chain)/2   # They set the chains in their code but I don't think we did for our model so we'll have to take a look and see how to convert this 
+n_pscell <- length(poststrat$N) # (n_pscell is the number of poststratification cells defined by the model)
+n_state <- max(poststrat$STATE)
+stanfit_final_ypred <- array(NA, c(n_sim, n_pscell))
+
+for(l in 1:n_pscell){
+    stanfit_final_ypred[,l] <- bernoulli_logit((x[n,] * beta[ll[n]])  # This is the part I am confused the most on.
+Just trying to specify the model in the right way to be able to make the service failure assumptions to then postratify.
+                                        )
+
+stanfit_final_ps <- c(NA, n_sim)
+
+# THEN WE CAN FINALY POSTSTRATIFY....I think 
+for(s in 1:n_sim){
+    stanfit_final_ps[s] <- sum(poststrat$N*stanfit_final_ypred[s,])/sum(poststrat$N)
+  }
+
+# This is just some other code that I am working on to try and look at a different way to post. I think this mainly comes from the original case study from Lauren. 
 posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)
-
-?posterior_linpred
 

### 2020-09-29 Cases/mrp/Case Study (McKenna) .Rmd
Deleting the second fake case study that was messing with our lives

@@
 # This is just some other code that I am working on to try and look at a different way to post. I think this mainly comes from the original case study from Lauren.
+
 posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)
+poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
+model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
+round(model_popn_pref, 3)
 
-poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
+true_popn_pref <- sum(true_popn$satisfaction * poststrat$N) / sum(poststrat$N)
+round(true_popn_pref, 3)
 
-model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
+state_df <- data.frame(
+  State = 1:50,
+  model_state_sd = rep(-1, 50),
+  model_state_pref = rep(-1, 50),
+  sample_state_pref = rep(-1, 50),
+  true_state_pref = rep(-1, 50),
+  N = rep(-1, 50)
+)
 
-round(model_popn_pref, 3)
+for(i in 1:length(levels(as.factor(poststrat$state)))) {
+  poststrat_state <- poststrat[poststrat$state == i, ]
+    posterior_prob_state <- posterior_linpred(
+    fit,
+    transform = TRUE,
+    draws = 1000,
+    newdata = as.data.frame(poststrat_state)
+  )
+  poststrat_prob_state <- (posterior_prob_state %*% poststrat_state$N) / sum(poststrat_state$N)
+  #This is the estimate for pop in state:
+  state_df$model_state_pref[i] <- round(mean(poststrat_prob_state), 4)
+  state_df$model_state_sd[i] <- round(sd(poststrat_prob_state), 4)
+  #This is the estimate for sample
+  state_df$sample_state_pref[i] <- round(mean(sample$cat_pref[sample$state == i]), 4)
+  #And what is the actual pop?
+  state_df$true_state_pref[i] <-
+    round(sum(true_popn$cat_pref[true_popn$state == i] * poststrat_state$N) /
+            sum(poststrat_state$N), digits = 4)
+  state_df$N[i] <- length(sample$satisfaction[sample$state == i])
+}
+
+state_df[c(1,3:6)]
 ```

### 2020-09-30 Cases/mrp/Case Study (McKenna) .Rmd
working with altering group amts

@@
 ```{r, eval = FALSE}
-# I set this to eval = FALSE just for now because it wasn't knitting so I will have to come back and take a look at this.
 options(mc.cores = parallel::detectCores()) # Set Stan to use all available cores.
@@
 ```{r}
-# Importing the data. 
+# Importing the data, will see it exported in environment 
 sample <- read_csv(here::here("Data", "sample.csv"))
@@
 Our first model is a hierarchical logit model.
-A logit model is appropriate for our data because of the biniary outcome variable.
-The hierarchical model is group baised on the group assignments determined by the categorical variables in the data.
+A logit model is appropriate for our data because of the binary outcome variable.
+The hierarchical model is group based on the group assignments determined by the categorical variables in the data.
 
@@
 
-...THEN YOU CAN FIT.
-
 ```{r}
@@
 ```
+
 ```{r, eval = FALSE}
-# I think we will need to use a for loop like they do in the downes model to construct our predictions into a format that we can then postratify them.
+# I think we will need to use a for loop like they do in the downes model to construct our predictions into a format that we can then post-stratify them.
 I got this for loop from the downes code and I have just begun to adjust it for our model.
  n_sim <- (n_iter * n_chain)/2   # They set the chains in their code but I don't think we did for our model so we'll have to take a look and see how to convert this 
-n_pscell <- length(poststrat$N) # (n_pscell is the number of poststratification cells defined by the model)
+n_pscell <- length(poststrat$N) # (n_pscell is the number of post-stratification cells defined by the model)
 n_state <- max(poststrat$STATE)
@@
     stanfit_final_ypred[,l] <- bernoulli_logit((x[n,] * beta[ll[n]])  # This is the part I am confused the most on.
-Just trying to specify the model in the right way to be able to make the service failure assumptions to then postratify.
+Just trying to specify the model in the right way to be able to make the service failure assumptions to then post-stratify.
                                         )
@@
 model {                                              // Model distributions for varying coefficients
-  b0 ~ cauchy(0,2.5);                                // and prior distributions for unmodelled                                                                // Can modify Cauchy scale parameter
+  b0 ~ cauchy(0,2.5);                                // and prior distributions for unmodeled                                                                // Can modify Cauchy scale parameter
                                                      // Can also specify a uniform distribution here
   a_age ~ normal(0, sigma_age);                      // or by setting upper and lower limits for
-  a_eth ~ normal(0, sigma_eth);                      // unmodelled parameters in the parameter step
+  a_eth ~ normal(0, sigma_eth);                      // unmodeled parameters in the parameter step
   a_income ~ normal(0, sigma_income);                // above  
@@
                                                      // Note the prior distributions for 
-                                                     // unmodelled parameters will change.
+                                                     // unmodeled parameters will change.
 }
@@
 Post-stratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people.
-Using post-stratificatio ncan improve accuracy of the estimates based on the information known.
+Using post-stratification can improve accuracy of the estimates based on the information known.
 

### 2020-11-10 Cases/mrp/Case Study (McKenna) .Rmd
Simplifying the dataset.

--- 2020-09-29 Cases/mrp/Case Study (McKenna) .Rmd
@@
 }
+
+mrp_sim <- simulate_mrp_data(n=1200)
+
+sample <- mrp_sim[["sample"]]
+poststrat <- mrp_sim[["poststrat"]]
+true_popn <- mrp_sim[["true_popn"]]
 ```
 
+This is a simplified version of the data generating formula that creates a data frame with only three variables instead of five. For simplicity sake income and state have been excluded.
+
 ```{r}
-# Importing the data. 
-sample <- read_csv(here::here("Data", "sample.csv"))
-poststrat <- read_csv(here::here( "Data", "poststrat.csv"))
-true_popn <- read_csv(here::here( "Data", "true_popn.csv"))
+simulate_mrp_data <- function(n) {
+  J <- c(2, 2, 2) # male or not, eth, age, income level, state
+  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) 
+  # Columns of post-strat matrix, plus one for size
+  colnames(poststrat) <- c("male", "eth", "age")
+  count <- 0
+  for (i1 in 1:J[1]){
+    for (i2 in 1:J[2]){
+      for (i3 in 1:J[3]){
+            count <- count + 1
+            # Fill them in so we know what category we are referring to
+            poststrat[count, 1:3] <- c(i1-1, i2, i3)
+          }
+        }
+      }
+  # Proportion in each sample in the population
+  p_male <- c(0.52, 0.48)
+  p_eth <- c(0.5, 0.5)
+  p_age <- c(0.2,0.8)
+  p_income<-c(.45,.55)
+  poststrat$N<-0
+  for (j in 1:prod(J)){
+    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
+                              p_age[poststrat[j,3]]) 
+    #Adjust the N to be the number observed in each category in each group
+  }
+  # Now let's adjust for the probability of response
+  p_response_baseline <- 0.01
+  p_response_male <- c(2, 0.8) / 2.8
+  p_response_eth <- c(1, 1.2, 2.5) / 4.7
+  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
+  p_response <- rep(NA, prod(J))
+  for (j in 1:prod(J)) {
+    p_response[j] <-
+      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
+      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]]
+  }
+  people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
+  ## For respondent i, people[i] is that person's poststrat cell,
+  ## some number between 1 and 32
+  n_cell <- rep(NA, prod(J))
+  for (j in 1:prod(J)) {
+    n_cell[j] <- sum(people == j)
+  }
+  coef_male <- c(0,-0.3)
+  coef_eth <- c(0, 0.6, 0.9)
+  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
+  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
+                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
+  true_popn <- data.frame(poststrat[, 1:3], service_failure = rep(NA, prod(J)))
+  for (j in 1:prod(J)) {
+    true_popn$satisfaction[j] <- plogis(
+      coef_male[poststrat[j, 1] + 1] +
+        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
+        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
+    )
+  }
+  #male or not, eth, age, income level, state, city
+  y <- rbinom(n, 1, true_popn$satisfaction[people])
+  male <- poststrat[people, 1]
+  eth <- poststrat[people, 2]
+  age <- poststrat[people, 3]
+  sample <- data.frame(service_failure = y,
+                       male, age, eth,
+                       id = 1:length(people))
+  #Make all numeric:
+  for (i in 1:ncol(poststrat)) {
+    poststrat[, i] <- as.numeric(poststrat[, i])
+  }
+  for (i in 1:ncol(true_popn)) {
+    true_popn[, i] <- as.numeric(true_popn[, i])
+  }
+  for (i in 1:ncol(sample)) {
+    sample[, i] <- as.numeric(sample[, i])
+  }
+  list(
+    sample = sample,
+    poststrat = poststrat,
+    true_popn = true_popn
+  )
+}
 
+mrp_sim <- simulate_mrp_data(n=1200)
+
+sample <- mrp_sim[["sample"]]
+poststrat <- mrp_sim[["poststrat"]]
+true_popn <- mrp_sim[["true_popn"]]
+```
+
+```{r, eval=FALSE}
 # Add groups to data. 
@@
                             "age" = "age", 
-                            "eth" = "eth", 
-                            "income" = "income",
-                            "state" = "state") )
+                            "eth" = "eth" 
+                            ) )
 ```
@@
   int<lower=0,upper=1> y[N];     // Outcome variable. 
-  int<lower=1,upper=L> ll[N];    // Group assignment. 
+  int<lower=1,upper=L> ll[N];    /p / Group assignment. 
   matrix[N, D] x;                // Matrix of predictors. 
@@
 
-```{r}
+```{r, eval = FALSE}
 predictors <- sample_group %>% 

### 2020-11-13 Code/mrp/sampledata.Rmd

---
title: "sampledata"
output: html_document
---

```{r setup, include=FALSE}
# Load packages.
library(tidyverse)
library(rstan)
library(bayesplot)
library(tidybayes)

# Set Stan options.
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)

# Specify data and hyperparameter values.
sim_values <- list(
  N = 500,                            # Number of observations.
  K = 5,                              # Number of groups.
  I = 7,                              # Number of observation-level covariates.
  J = 3,                              # Number of population-level covariates.

  # Vector of group assignments.
  g = sample(5, 500, replace = TRUE),

  # Matrix of observation-level covariates.
  X = cbind(
    rep(1, 500),
    matrix(runif(500 * (7 - 1), min = 1, max = 10), nrow = 500)
  ),

  # Matrix of population-level covariates.
  Z = cbind(
    rep(1, 5),
    matrix(runif(5 * (3 - 1), min = 2, max = 5), nrow = 5)
  )
)

# Generate data.
sim_data <- stan(
  file = here::here("Code", "generate_data.stan"),
  data = sim_values,
  iter = 1,
  chains = 1,
  seed = 42,
  algorithm = "Fixed_param"
)

# Extract simulated data and parameters.
sim_y <- extract(sim_data)$y
sim_Gamma <- extract(sim_data)$Gamma
sim_Omega <- extract(sim_data)$Omega
sim_tau <- extract(sim_data)$tau
sim_Beta <- extract(sim_data)$Beta
sim_sigma <- extract(sim_data)$sigma

data <- list(
  N = sim_values$N,     # Number of observations.
  K = sim_values$K,     # Number of groups.
  I = sim_values$I,     # Number of observation-level covariates.
  J = sim_values$J,     # Number of population-level covariates.
  y = as.vector(sim_y), # Vector of observations.
  g = sim_values$g,     # Vector of group assignments.
  X = sim_values$X,     # Matrix of observation-level covariates.
  Z = sim_values$Z      # Matrix of population-level covariates.
)

fit_centered <- stan(
  file = here::here("Code", "hlm_centered.stan"),
  data = data,
  control = list(adapt_delta = 0.99),
  seed = 42
)

### 2020-11-20 Cases/mrp/Case Study (McKenna) .Rmd
complete updates

--- 2020-09-30 Cases/mrp/Case Study (McKenna) .Rmd
@@
 
-In this case study there are five classification variables: age, income, ethnicity, gender, and state.
-Each variable is transformed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300 (7 x 3 x 3 x 2 x 50 = 6300).
+In this case study there are three classification variables: age, ethnicity, and gender.
+Each variable is transformed into categorical variables with age having seven categories, ethnicity having three, and gender having two making the total number of cells 42 (7 x 3 x 2 = 42).
 
@@
 
-```{r, eval = FALSE}
-options(mc.cores = parallel::detectCores()) # Set Stan to use all available cores.
-rstan_options(auto_write = TRUE)            # Don't recompile Stan code that hasn't changed.
-
-# Data generating function for reference. 
+```{r}
 simulate_mrp_data <- function(n) {
-  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
-  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) 
+  J <- c(2, 3, 7) # male or not, eth, age
+  # poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) 
+  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)))) 
   # Columns of post-strat matrix, plus one for size
-  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
+  colnames(poststrat) <- c("male", "eth", "age")
   count <- 0
@@
       for (i3 in 1:J[3]){
-        for (i4 in 1:J[4]){
-          for (i5 in 1:J[5]){
             count <- count + 1
             # Fill them in so we know what category we are referring to
-              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
-          }
-        }
+            poststrat[count, 1:3] <- c(i1-1, i2, i3)
           }
@@
   p_male <- c(0.52, 0.48)
-  p_eth <- c(0.5, 0.2, 0.3)
-  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
-  p_income<-c(.50,.35,.15)
-  p_state_tmp<-runif(50,10,20)
-  p_state<-p_state_tmp/sum(p_state_tmp)
+  p_eth <- c(0.2, 0.3, 0.5)
+  p_age <- c(0.1, 0.1, 0.2, 0.2, 0.1, 0.1, 0.2)
   poststrat$N<-0
@@
     poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
-      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) 
+                              p_age[poststrat[j,3]]) 
     #Adjust the N to be the number observed in each category in each group
@@
   p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
-  p_response_inc <- c(1, 0.9, 0.8) / 2.7
-  p_response_state <- rbeta(50, 1, 1)
-  p_response_state <- p_response_state / sum(p_response_state)
   p_response <- rep(NA, prod(J))
@@
       p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
-      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
-      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
+      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]]
   }
@@
   coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
-  coef_income <- c(0,-0.2, 0.6)
-  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
   coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
                            c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
-  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
+  true_popn <- data.frame(poststrat[, 1:3], service_failure = rep(NA, prod(J)))
   for (j in 1:prod(J)) {
@@
         coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
-        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
         coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
@@
   }
-#male or not, eth, age, income level, state, city
+  #male or not, eth, age
   y <- rbinom(n, 1, true_popn$satisfaction[people])
@@
   age <- poststrat[people, 3]
-  income <- poststrat[people, 4]
-  state <- poststrat[people, 5]
   sample <- data.frame(service_failure = y,
-                       male, age, eth, income, state,
+                       male, age, eth,
                        id = 1:length(people))
@@
 }
+mrp_sim <- simulate_mrp_data(n=1200)
+sample <- mrp_sim[["sample"]]
+poststrat <- mrp_sim[["poststrat"]]
+true_popn <- mrp_sim[["true_popn"]]
 ```
@@
 ```{r}
-# Importing the data, will see it exported in environment 
-sample <- read_csv(here::here("Data", "sample.csv"))
-poststrat <- read_csv(here::here( "Data", "poststrat.csv"))
-true_popn <- read_csv(here::here( "Data", "true_popn.csv"))
-
 # Add groups to data. 
@@
                             "age" = "age", 
-                            "eth" = "eth", 
-                            "income" = "income",
-                            "state" = "state") )
+                            "eth" = "eth") )
 ```
@@
 
-```{r}
+```{r, eval= FALSE}
 predictors <- sample_group %>% 
-  select(male, age, eth, income, state)
+  select(male, age, eth)
 
 data_list <- list(
-  D = 5,                                              # Number of variables. 
+  D = 3,                                              # Number of variables. 
   N = 1200,                                           # Number of observations.
-  L = 6300,                                           # Number of groups. 
+  L = 42,                                             # Number of groups. 
   y = sample_group$service_failure,                   # Outcome variables. 

### 2021-02-17 Cases/mrp/Case Study (McKenna) .Rmd
edit messages

@@
 ## Model
+# Here we are loading the packages needed to run our model
 
@@
 library(here)
+options(mc.cores = parallel::detectCores())
 ```
@@
   poststrat <- as.data.frame(array(NA, c(prod(J), length(J)))) 
-  # Columns of post-strat matrix, plus one for size
+  # Columns of post-strat matrix with the various variables that we will be using
   colnames(poststrat) <- c("male", "eth", "age")
@@
       }
-  # Proportion in each sample in the population
+  # Proportion in each sample in the population, we cut down the proportions in this, you can adjust them based on how many you would like in each category
   p_male <- c(0.52, 0.48)
@@
   data = data_list,
+  iter = 2000,
+  thin = 2,
   seed = 42 
